### 2019-10-29 clean_analysis.Rmd
fixed and bayesian learner

---
output:
  html_document: default
  word_document: default
---
--
title: "opponent modelling"
author: "Ismail Guennouni"
date: "30 July 2018"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
dat <- read.csv("data20180719.csv")
```

```{r}
# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
library(tidyr)
library(dplyr)
library(MASS)
library(ggpubr)
library(PairedData)
library(multcompView)

# transform 'winner' variable in numeric score
dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat$block <- factor(as.numeric(cut(dat$round,2)),labels =c("first half", "second half"))

# create a new variable "game.f" as a factor variable of games
dat$game.f <- factor(dat$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))

# overall score to pay bonuses 
dat_score <- dat %>% 
  group_by(human_id) %>% 
      summarize(overall_score = sum(score))
(avg_bonus <- floor(mean(abs(dat_score$overall_score))))*0.02

#Group data by human_id and calculate mean score per block of each game.
dat2 <- dat %>% 
  group_by(human_id,condition,game,block,game.f) %>% 
      summarize(block_score = mean(score))

# Group data by game and ID
dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
# head(dat3,6)

# Subsetting scores data by game
rps <- subset(dat3,  game.f == "RPS",game_score)
fwg <- subset(dat3,  game.f == "FWG",game_score)
num <- subset(dat3,  game.f == "NUM",game_score)
# head(rps,6)
```

```{r}
# Look at some summary statistics of group means #############################

group_by(dat2, game.f) %>%
  summarise(
    mean = mean(block_score, na.rm = TRUE),
    sd = sd(block_score, na.rm = TRUE)
  )

group_by(dat2, game.f, block) %>%
  summarise(
    count = n(),
    mean = mean(block_score, na.rm = TRUE),
    sd = sd(block_score, na.rm = TRUE)
  )

group_by(dat2, game.f, condition,block) %>%
  summarise(
    count = n(),
    mean = mean(block_score, na.rm = TRUE),
    sd = sd(block_score, na.rm = TRUE)
  )
```

```{r}
# PLOTS  #############################

# Plot scores per game

ggboxplot(dat3, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")

ggerrorplot(dat3, x = "game.f", y = "game_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")

# Plot paired scores between games
#pd <- paired(rps,fwg)
#pd2 <- paired(fwg,num)
#head(pd)
#plot(pd, type = "profile")
#plot(pd2, type = "profile")
ggpaired(dat3, x = "game.f", y = "game_score",color = "game.f", id = "human_id", line.color = "gray", line.size = 0.4, palette = "npg")

# Plot results by game and block (for all 3 games, learning is happening) 
ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")

# Group data by game and ID
dat4 <- group_by(dat2, human_id,condition,game.f) %>% summarise(game_score = mean(block_score))

# Level 2 is harder to win against than level 1
ggboxplot(dat2, x = "condition", y = "block_score", palette = c("#00AFBB", "#E7B800"), fill="condition",ylab = "Percentage score", xlab = "Conditions")

ggerrorplot(dat2, x = "condition", y = "block_score", desc_stat = "mean_ci" , palette = c("#00AFBB", "#E7B800"), color="condition",ylab = "Percentage score", xlab = "Conditions")

# Main effect of block 
ggerrorplot(dat2, x = "block", y = "block_score", desc_stat = "mean_ci" , palette = c("#00AFBB", "#E7B800"), color="block",ylab = "Percentage score", xlab = "Block")

# Breaking it down by game (seems to be true for RPS and FWG, less so for Numbers )
ggboxplot(dat4, x = "game.f", y = "game_score", palette = c("#00AFBB","#E7B800","#FC4E07"), fill="condition",order = c("RPS", "FWG","NUM"),ylab = "Game Score", xlab = "Conditions")

```

```{r}
# Testing score against hypothesis of random play  ######################################

# Normality of scores 
shapiro.test(dat3$game_score)

# Testing Scores against random play (expected 0 average score)
t.test(as.numeric(rps$game_score), mu = 0, alternative = "two.sided")
t.test(as.numeric(fwg$game_score), mu = 0, alternative = "two.sided")
t.test(as.numeric(num$game_score), mu = 0, alternative = "two.sided")

```

```{r}
# AFEX PACKAGE FOR RUNNING RM ANOVA AND POST HOC TESTS ############################
citation(package = "afex", lib.loc = NULL, auto = NULL)
library(afex)
a1 <- aov_car( block_score ~ game.f*block*condition + Error(human_id/(game.f*block)), dat2)
summary(a1)
(a1_nice <- nice(a1, es = attr(a1$anova_table, "es"),
  observed = attr(a1$anova_table, "observed"),
  correction = attr(a1$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(a1$anova_table,
  "p_adjust_method"), sig_symbols = attr(a1$anova_table, "sig_symbols")))

write.table(a1_nice,file = "a1.txt", sep = ",", quote = FALSE, row.names = F)

## Note to Self: no need to worry abour the HF warning. You don't have pb with sphericity according to Mauchly tests, and the warning only applies to Huynh-Feldt corrections for violations of sphericity. 
```

```{r}
#Pair waise comparison and post hoc tests for the interaction: Game * Block using lsmeans

# game score differences statistically significant?
(ls0 <- lsmeans(a1, "game.f"))
(lsm0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))

# Main effect of block 
(ls01 <- lsmeans(a1, "block"))
(lsm01 <- update(pairs(ls01, reverse = TRUE), by=NULL, adjust = "holm"))
lsmip(a1, ~block)

# Main effect of condition
(ls02 <- lsmeans(a1, "condition"))
(lsm02 <- update(pairs(ls02, reverse = TRUE), by=NULL, adjust = "holm"))

# Pairwise comparison of first halves by game ( first half RPS vs first half WFG scores....)
(ls1 <- lsmeans(a1, "game.f", by="block"))
(lsm1 <- update(pairs(ls1, reverse = TRUE), by=NULL, adjust = "holm"))
plot(lsm1,by="block")
lsmip(a1, game.f ~ block)

# Pairwise comparison of each game score by block (first half RPS vs second half RPS....) + Control for family wise error:
ls2 <- lsmeans(a1, c("block","game.f"))
(lsm2 <- update(pairs(ls2, reverse = TRUE), by=NULL, adjust = "holm"))
(contr2 <- contrast(ls2, list(G1H2vG2H1 = c(0,1,-1,0,0,0))))
(contr3 <- contrast(ls2, list(G1H1vs0 = c(1,0,0,0,0,0))))
lsmip(a1, block ~ game.f)
lsmip(a1, ~ block * game.f)

# Pairwise comparison of scores facing the two types of players by game: 
lsc <- lsmeans(a1, "condition", by="game.f")
(lsmc <- update(pairs(lsc), by=NULL, adjust = "holm"))
plot(lsmc,by="game.f")
lsmip(a1, condition ~ game.f)

```

```{r}
#Pair waise comparison and post hoc tests : Game by Block and Condition

#library(multcompView)
#use cld to check for comparison pairs belonging to same group, meaning not significantly different from each other...
#cld(lsm4)

#plots
ls4 <- lsmeans(a1, "block",c("condition","game.f"))
ls4
(lsm4 <- update(pairs(ls4, reverse = TRUE), by=NULL, adjust = "holm"))

plot(lsm4,by="game.f")
lsmip(a1, game.f ~ block | condition)

# Interaction plot of game and block by condition 
lsmip(a1, game.f ~ block | condition)
lsmip(a1, condition ~ block * game.f)
```

```{r}
# Transfer harder for level2 opponent than when facing level 1 opponent? 
# learning to specifiy contrasts - 
# the below compares the score on each block and game for each type and tells me which scores belong to same group
# the idea is that if transfer is harder vs lvl2 player, then fwg first half score for lvl2 facing player should be sig lower than fwg first-half score vs lvl1 agent.not the case here as thye belong to same group.

(means.int <- lsmeans(a1, specs = c("game.f","block","condition")))

# Transfer level1: compare H1FWG with H1RPS 
con1  <- contrast(means.int, list(H1_G2vsH1_G1forlvl1 = c(-1,1,0,0,0,0,0,0,0,0,0,0), H1_G3vsH1_G1forlvl1=c(-1,0,1,0,0,0,0,0,0,0,0,0)))
summary(con1, adjust = "holm")

# Transfer level2: compare H1FWG with H1RPS 
con2  <- contrast(means.int, list(H1_G2vsH1_G1forlvl2 = c(0,0,0,0,0,0,-1,1,0,0,0,0), H1_G3vsH1_G1forlvl2=c(0,0,0,0,0,0,-1,0,1,0,0,0)))
summary(con2, adjust = "holm")

# compare first half (H1) scores between level 1 and level 2 players in FWG and NUM
con3 <- contrast(means.int, list(G1vG2forH1 = c(0,1,0,0,0,0,0,-1,0,0,0,0), G2vG3forh1=c(0,0,1,0,0,0,0,0,-1,0,0,0)))
summary(con3, adjust ="holm")

# Within game learning harder for level2 opponent than when facing level 1 opponent? compare differences between block for each game and type
con4 <- contrast(means.int, list(L2vL1forRPS = c(1,0,0,-1,0,0,-1,0,0,1,0,0), L2vL1forFWG=c(0,1,0,0,-1,0,0,-1,0,0,1,0), L2vL1forNUM=c(0,0,1,0,0,-1,0,0,-1,0,0,1)))
summary(con4, adjust ="holm")

```

```{r}

#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########

dat_26 <- subset(dat,round >1 & round <7, drop =TRUE)
dat2_6 <- dat_26 %>% 
  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
      summarise(early_score = mean(score))

# Check group means and SDs
group_by(dat2_6, game.f) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
group_by(dat2_6, game.f,condition) %>%
  summarise(
    count = n(),
    mean = mean(early_score, na.rm = TRUE),
    sd = sd(early_score, na.rm = TRUE)
    )
# plot scores per game 
ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")

# testing differences between early scores across games 
library(afex)
aov_early <- aov_car(early_score ~ game.f*condition + Error(human_id/(game.f)),data=dat2_6)
summary(aov_early)

aov_ear_nice <- nice(aov_early, es = attr(aov_early$anova_table, "es"),
  observed = attr(aov_early$anova_table, "observed"),
  correction = attr(aov_early$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(aov_early$anova_table,
  "p_adjust_method"), sig_symbols = attr(aov_early$anova_table, "sig_symbols"))

write.table(aov_ear_nice,file = "aov_ear.txt", sep = ",", quote = FALSE, row.names = F)

# including confidence

aov_conf_26 <- aov_car(early_score ~ game.f*condition*difficulty + Error(human_id/(game.f)),data=dat2_6)
summary(aov_conf_26)

(ls4 <- lsmeans(aov_early, "game.f"))
(summary(ls4, infer = c(TRUE,TRUE), null = 0,level = 0.95, adjust = "bon"))

(means.int2 <- lsmeans(aov_early, specs = c("game.f","condition")))
(trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "none",ref=c("FWG","NUM")))
(contr26 <- contrast(means.int2, list(G2L1vsG2L2 = c(0,1,0,0,-1,0))))

write.table(format(trans26, digits=2),file = "trans26.txt", sep = ",", quote = FALSE, row.names = F)

# compare early scores in FWG for lvl 1 and lvl2 / same for NUM

contrast(means.int2, list(G1vG2for26 = c(0,1,0,0,-1,0), G2vG3for26=c(0,0,1,0,0,-1)))

# Plot interactions for early rouns, condition by game

lsmip(aov_early, ~ game.f | condition )

# plots overall effect by game :
ggboxplot(dat2_6,"game.f", "early_score", fill = "game.f",palette = c("#00AFBB", "#E7B800", "#FC4E07"),order = c("RPS","FWG","NUM"))

# Note to Self: possible future work exstension is to pick the guys who scored highly on the first rounds of the second game and fit the various learning models to them only. 
# Two ways to test learning: compare first half between games for different conditions 
# compare early score between games for different conditions 
# Check whteher confidence and difficulty  -> add them as covariates in big anova and early score anova *confidence*difficulty.... --> too hard to interpret

# do a model comparison with model without confidence and difficulty -> start witn ANCOVA (try and see what happens with various interactions).  
```

```{r}
# adding confidence and difficulty feedback 
datcd <- dat %>% 
  group_by(human_id,condition,confidence,difficulty) %>% 
      summarise(avg_score = mean(score))

# testing conf, diff and score for normality 
shapiro.test(datcd$avg_score)
shapiro.test(datcd$confidence)
shapiro.test(datcd$difficulty)

# histograms 
hist(datcd$confidence, breaks = 20)
hist(datcd$difficulty, breaks=10)

# descriptive stats 
group_by(datcd, condition) %>%
  summarise(
    count = n(),
    median = median(confidence, na.rm = TRUE),
    IQR = IQR(confidence, na.rm = TRUE)
  )

group_by(datcd, condition) %>%
  summarise(
    count = n(),
    median = median(difficulty, na.rm = TRUE),
    IQR = IQR(difficulty, na.rm = TRUE)
  )
# Comparing confidence and difficulty by condition
(res1 <- wilcox.test(confidence ~ condition, data = datcd,exact = FALSE))
(res2 <- wilcox.test(difficulty ~ condition, data = datcd,exact = FALSE))

# Correlation confidence difficulty and score: 
mat <- as.matrix(datcd[,unlist(lapply(datcd, is.numeric))])
cor.test(datcd$confidence, datcd$avg_score, method="spearman")
cor.test(datcd$difficulty, datcd$avg_score, method="spearman")

# Transforming confidence into 4 lvl factor
datcd$confidence.f <- factor(as.numeric(cut(datcd$confidence,2)),labels =c("low conf","high conf"))
summary(datcd$confidence.f)
table(datcd$confidence.f,datcd$condition)

#  explore interaction block confidence
#(lsm7 <- lsmeans(acd, c("confidence.f","block")))
#(update(pairs(lsm7, reverse = TRUE, adjust = "holm"), by=NULL))
#plot(lsm7, by ="confidence.f")
#lsmip(acd, confidence.f ~ block)

#
#(lsm8 <- lsmeans(acd, c("confidence.f","block","game.f")))
#lsmip(acd, confidence.f ~ block*game.f)
# checking that low confidence NUMBERS play is not different from random play
#con3 <- contrast(lsm8, list(G1vG2forconf = c(0,0,0,0,0,0,0,0,0,0,1,0)))
#summary(con3, adjust ="holm")

# low and high confidence players have similar initial score in RPS
#con4 <- contrast(lsm8, list(HCvLCforRPS = c(-1,1,0,0,0,0,0,0,0,0,0,0)))
#summary(con4, adjust="holm")
```

```{r}
# ANCOVA with confidence as covariate 
dat_ancova <- dat %>% 
  group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 
      summarise(avg_score = mean(score))
# Centering variables for ANCOVA 
dat_ancova$conf_cen <- scale(dat_ancova$confidence, center=TRUE, scale=FALSE) 
dat_ancova$diff_cen <- scale(dat_ancova$difficulty, center=TRUE, scale=FALSE)

# run RM anova using afex library (ran anova including difficulty as well but wasn't significant)
library(afex)
acd <- aov_car( avg_score ~ game.f*block*condition + conf_cen + diff_cen + Error(human_id/(game.f*block)), factorize = FALSE,dat_ancova)
summary(acd)

nice(acd, es = attr(acd$anova_table, "es"),
  observed = attr(acd$anova_table, "observed"),
  correction = attr(acd$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(acd$anova_table,
  "p_adjust_method"), sig_symbols = attr(acd$anova_table, "sig_symbols"))

# post hoc tests
(anc1 <- lsmeans(acd, c("conf_cen")))

(lsm6 <- lsmeans(acd, c("conf_cen","condition")))
update(pairs(lsm6, reverse = TRUE, adjust = "holm"), by=NULL)
plot(lsm6, by ="condition")
plot(lsm6, by ="conf_cen")
lsmip(acd, conf_cen ~ condition)

```

```{r}

# transform data by differencing two consecutive scores, filter for first and second transfer 
library(dplyr)
dat_test1 <- dat %>% 
  group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 
      summarise(avg_score = mean(score)) %>%
         group_by(human_id) %>%
            mutate(diff_score = avg_score - lag(avg_score, default = 0)) %>%
              mutate(learn_phase =c("init RPS","within RPS","transfer 1","within WFG","transfer 2","within MOD"))

head(dat_test1)        
# define dataset with first transfer only 
dat_trans1 <- dat_test1 %>%
  filter (learn_phase == "transfer 1") %>%
    select(-c(game.f,block,avg_score,learn_phase))

head(dat_trans1)
# Data of transfer as difference between RPS_H2 and FWG_H1 is normally distributed
shapiro.test(dat_trans1$diff_score)

# Regression transfer score on condition and confidence
summary(lm(diff_score~ confidence + difficulty + factor(condition)+confidence*factor(condition), data = dat_trans1))

# tets hypothesis diff_score = 0 (transfer) against alternative it is negative -> No transfer
t.test( dat_trans1$diff_score, mu = 0 ,alternative = "less")

# To be sure.... Compare means of two condition 
t.test(dat_trans1$diff_score ~ condition, data = dat_trans1,exact = FALSE)

#DOING THE SAME FOR TRANSFER 2 :

dat_trans2 <- dat_test1 %>%
  filter (learn_phase == "transfer 2") %>%
    select(-c(game.f,block,avg_score,learn_phase))

# Regression transfer score on condition and confidence -> no effects 
summary(lm(diff_score~ confidence + difficulty + factor(condition) + confidence*factor(condition), data = dat_trans2))
```

```{r}
# Does confidence moderate transfer ?
# Looking at early rounds only as proxy for transfer 
dat_fwg <- dat2_6 %>%
  filter (game.f == "FWG")
dat_num <- dat2_6 %>%
  filter (game.f == "NUM")

# correlation confidence and transfer as proxied by score in early rounds : 
shapiro.test(dat_fwg$confidence)
cor.test(dat_fwg$confidence, dat_fwg$early_score, method="spearman")
cor.test(dat_num$confidence, dat_num$early_score, method="spearman")

# model explaining early scores in fwg by confidene and condition -> no effects 
summary(lm(early_score ~ confidence*condition, data=dat_fwg))
summary(lm(early_score ~ confidence*condition, data=dat_num))

```

```{r}
# checking whether theta changes between games

# lvl1 opponent 
bic <- read.csv("BIC_result.csv")
head(bic)

dat_lvl1 <- bic %>%
  select(c(id,condition,level2_3_theta1,level2_3_theta2,level2_3_theta3)) %>%
    gather(key = game, value = theta,-c(id,condition)) %>%
      group_by(id)
dat_lvl1$games <- factor(dat_lvl1$game, labels=c("RPS","FWG","MOD"),levels=c("level2_3_theta1","level2_3_theta2","level2_3_theta3"))

library(afex)
aov2 <- aov_car( theta ~ games + Error(id/(games)), dat_lvl1)
summary(aov2)

table2 <- nice(aov2, es = attr(aov2$anova_table, "es"),
  observed = attr(aov2$anova_table, "observed"),
  correction = attr(aov2$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(aov2$anova_table,
  "p_adjust_method"), sig_symbols = attr(aov2$anova_table, "sig_symbols"))

kable(table2)

dat_lvl1 %>% 
  group_by(games) %>%
  summarise(theta.m = mean(theta),
            SD = sd(theta, na.rm =TRUE ))

#plot 
ggerrorplot(dat_lvl1, x = "games", y = "theta", group = 1, color="games", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","MOD"), ylab = "Theta", xlab = "Games")

# lvl2 opponent 
dat_lvl2 <- bic %>%
  select(c(id,condition,level3_3_theta1,level3_3_theta2,level3_3_theta3)) %>%
    gather(key = game, value = theta,-c(id,condition)) %>%
      group_by(id)
dat_lvl2$games <- factor(dat_lvl2$game, labels=c("RPS","FWG","MOD"),levels=c("level3_3_theta1","level3_3_theta2","level3_3_theta3"))

# anova
aov3 <- aov_car( theta ~ games + Error(id/(games)), dat_lvl2)
summary(aov3)

table3 <- nice(aov3, es = attr(aov3$anova_table, "es"),
  observed = attr(aov3$anova_table, "observed"),
  correction = attr(aov3$anova_table, "correction"), MSE = NULL,
  intercept = NULL, p_adjust_method = attr(aov3$anova_table,
  "p_adjust_method"), sig_symbols = attr(aov3$anova_table, "sig_symbols"))

kable(table3)

# mean comparison
dat_lvl2 %>% 
  group_by(games) %>%
  summarise(theta.m = mean(theta),
            SD = sd(theta, na.rm =TRUE ))

require(gridExtra)
#plot lvl1 
plot1 <- ggerrorplot(dat_lvl1, x = "games", y = "theta", group = 1, color="games", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","MOD"), ylab = "Theta", xlab = "Games")
#plot lvl2
plot2 <- ggerrorplot(dat_lvl2, x = "games", y = "theta", group = 1, color="games", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","MOD"), ylab = "Theta", xlab = "Games")

grid.arrange(plot1, plot2, ncol=2)

```

### 2019-10-29 comp_model_1019.Rmd
fixed and bayesian learner

---
title: "opponent modelling"
author: "Maarten Speekenbrink"
date: "24 July 2018"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

## Reading data

```{r}
dat <- read.csv("data20180719.csv")
#dat <- read.csv("test_data.csv")
```

## Preprosessing and transforming data

```{r}
# using some functions from the 'tidyverse' (also for me to get use to them ;-)
library(tidyr)
library(dplyr)
# transform 'winner' variable in numeric score
dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
dat$block <- as.numeric(cut(dat$round,2))
# create a new data.frame in a 'wide format'
widedata <- dat %>% 
  unite(game_block,game,block) %>% # this creates a new variable which combines game and block
    group_by(human_id,condition,game_block) %>% # let the functions know you want to separate things by ID, condition, and game_block
      summarize(mean_score = mean(score)) %>% # compute average score (i.e wins - losses)
        spread(game_block,mean_score) # reformat in the 'wide' format
# save the data file as a .csv to use in e.g. SPSS
write.csv(widedata,row.names=FALSE,file="scores_wide.csv")

```

```{r estimate-models, cache=TRUE}
# read in the various files which 
rps_predict_opp <- read.csv("rps_predict_opp.csv")
fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
numbers_predict_opp <- read.csv("numbers_predict_opp.csv")

# recode actions to make them equal to the codes in these files
dat$h_action <- recode(dat$human_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
dat$a_action <- recode(dat$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")

# logit tranformation
my_logit <- function(x) {
  ret <- log(x/(1-x))
  ret[x==0] <- -Inf
  ret[x==1] <- Inf 
  return(ret)
}

# inverse logit transformation
my_logistic <- function(x) {
  ret <- 1/(1+exp(-x))
  ret[x == -Inf] <- 0.0
  ret[x == Inf] <- 1.0
  return(ret)
}

```

## Modelling fixed type participant
```{r}
# FIXED STRATEGIES (level-k) 
# create a function which computes the -2 log Likelihood over the three games for a particular strategy
# modelLL <- function(par,data,strategy, return_value=c("-2logLik","likelihood_by_trial")) {
#   # par = parameter vector (just has one element here) 
#   # dat = data subset for one participant
#   # strategy = c("level1","level2","level3","WSLS")
#   # return = -2logLik (default, for use in optimization) or "likelihood_by_trial" (for later plotting, etc)
#   return_value <- match.arg(return_value)
#   
#   # count the number of supplied parameters. If 1, it is a _1 model, 
#   # if 3, it is a _3 model. For the _3 model we will use unbounded
#   # optimization (transforming parameters from a logit scale back to 0 to 1)
#   n_theta <- length(par)
#   if(n_theta == 3) par <-my_logistic(par)
#   theta <- par[1]
#   # set up a vector to store the likelihood
#   lik <- rep(0.0,nrow(data))
#   for(t in 1:nrow(data)) {
#     t_game <- data[t,"game"]
#     pred_file <- switch(as.character(t_game),rps=rps_predict,fwg = fwg_predict, numbers = numbers_predict)
#     if(n_theta == 3) {
#       theta <- switch(as.character(t_game),rps=par[1],fwg = par[2], numbers = par[3])
#     }
#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
#     if(data[t,"round"] == 1) {
#       # first round is uniform prediction
#       pred <- NA
#       lik[t] <- 1/nopts
#     } else {
#       # get prediction from file
#       pred <- as.character(filter(pred_file,human_previous == as.character(data[t-1,"h_action"]) & computer_previous == as.character(data[t-1,"a_action"]))[strategy][1,])
#       if(as.character(data[t,"h_action"]) == pred) {
#         lik[t] <- theta + (1-theta)/nopts
#       } else {
#         lik[t] <- (1-theta)/nopts
#       }
#     }
#     # for debugging uncomment the line below
#     # cat(as.character(pred),as.character(data[t,"h_action"]),lik[t],"\n")
#   }
#   if(return_value == "-2logLik") {
#     ret <- -2*sum(log(lik))
#     if(ret == Inf) {
#       return(1e+300)
#     } else {
#       return(ret)
#     }
#   }
#   if(return_value == "likelihood_by_trial") return(lik)
# }
# 
# all_modelling <- list()
# for(id in unique(dat$human_id)) {
#   all_modelling[[id]] <- list()
#   tdat <- subset(dat,human_id == id)
#   # level 1
#   all_modelling[[id]]$level1_1 <- optimize(modelLL,interval=c(0,1),data=tdat,strategy="level1")
#   all_modelling[[id]]$level1_3 <- optim(my_logit(rep(all_modelling[[id]]$level1_1$minimum,3)),fn=modelLL,data=tdat,strategy="level1")
#   # level 2
#   all_modelling[[id]]$level2_1 <- optimize(modelLL,interval=c(0,1),data=tdat,strategy="level2")
#   all_modelling[[id]]$level2_3 <- optim(my_logit(rep(all_modelling[[id]]$level2_1$minimum,3)),fn=modelLL,data=tdat,strategy="level2")
#   # level 3
#   all_modelling[[id]]$level3_1 <- optimize(modelLL,interval=c(0,1),data=tdat,strategy="level3")
#   all_modelling[[id]]$level3_3 <- optim(my_logit(rep(all_modelling[[id]]$level3_1$minimum,3)),fn=modelLL,data=tdat,strategy="level3")
#   # WSLS
#   all_modelling[[id]]$WSLS_1 <- optimize(modelLL,interval=c(0,1),data=tdat,strategy="WSLS")
#   all_modelling[[id]]$WSLS_3 <- optim(my_logit(rep(all_modelling[[id]]$WSLS_1$minimum,3)),fn=modelLL,data=tdat,strategy="WSLS")
# }
# 
# save(all_modelling,file="all_modelling.RData")

```

```{r}
# create a table with BIC
# BIC_results <- data.frame()
# for(id in unique(dat$human_id)) {
#     BIC_results <- rbind(BIC_results,
#                          data.frame(
#                            "id" = id,
#                            "condition" = dat[dat$human_id==id,"condition"][1],
#                            "random_BIC" = -2*(100*log(1/3) + 50*log(1/5)), 
#                            "level1_1_theta" = all_modelling[[id]]$level1_1$minimum,
#                            "level1_1_BIC" = all_modelling[[id]]$level1_1$objective + 1*log(150),
#                            "level1_3_theta1" = my_logistic(all_modelling[[id]]$level1_3$par[1]),
#                            "level1_3_theta2" = my_logistic(all_modelling[[id]]$level1_3$par[2]),
#                            "level1_3_theta3" = my_logistic(all_modelling[[id]]$level1_3$par[3]),
#                            "level1_3_BIC" = all_modelling[[id]]$level1_3$value + 3*log(150),
#                            "level2_1_theta" = all_modelling[[id]]$level2_1$minimum,
#                            "level2_1_BIC" = all_modelling[[id]]$level2_1$objective + 1*log(150),
#                            "level2_3_theta1" = my_logistic(all_modelling[[id]]$level2_3$par[1]),
#                            "level2_3_theta2" = my_logistic(all_modelling[[id]]$level2_3$par[2]),
#                            "level2_3_theta3" = my_logistic(all_modelling[[id]]$level2_3$par[3]),
#                            "level2_3_BIC" = all_modelling[[id]]$level2_3$value + 3*log(150),
#                            "level3_1_theta" = all_modelling[[id]]$level3_1$minimum,
#                            "level3_1_BIC" = all_modelling[[id]]$level3_1$objective + 1*log(150),
#                            "level3_3_theta1" = my_logistic(all_modelling[[id]]$level3_3$par[1]),
#                            "level3_3_theta2" = my_logistic(all_modelling[[id]]$level3_3$par[2]),
#                            "level3_3_theta3" = my_logistic(all_modelling[[id]]$level3_3$par[3]),
#                            "level3_3_BIC" = all_modelling[[id]]$level3_3$value + 3*log(150),
#                            "WSLS_1_theta" = all_modelling[[id]]$WSLS_1$minimum,
#                            "WSLS_1_BIC" = all_modelling[[id]]$WSLS_1$objective + 1*log(150),
#                            "WSLS_3_theta1" = my_logistic(all_modelling[[id]]$WSLS_3$par[1]),
#                            "WSLS_3_theta2" = my_logistic(all_modelling[[id]]$WSLS_3$par[2]),
#                            "WSLS_3_theta3" = my_logistic(all_modelling[[id]]$WSLS_3$par[3]),
#                            "WSLS_3_BIC" = all_modelling[[id]]$WSLS_3$value + 3*log(150)
#                          ))
# }
# write.csv(BIC_results,file="BIC_result.csv",row.names = FALSE)
# kable(BIC_results)
```

```{r}

# create a table with best fitting models by condition
# table(dat$condition[dat$round==1 & dat$game == "rps"],c("random","level1_1","level2_1","level3_1","WSLS_1","level1_3","level2_3","level3_3","WSLS_3")[apply(BIC_results[,c("random_BIC","level1_1_BIC","level2_1_BIC","level3_1_BIC","WSLS_1_BIC","level1_3_BIC","level2_3_BIC","level3_3_BIC","WSLS_3_BIC")],1,which.min)])
# 
# ## treat 1 theta and 3 theta versions the same
# # create a table with best fitting models by condition
# table(dat$condition[dat$round==1 & dat$game == "rps"],c("random","level1","level2","level3","WSLS","level1","level2","level3","WSLS")[apply(BIC_results[,c("random_BIC","level1_1_BIC","level2_1_BIC","level3_1_BIC","WSLS_1_BIC","level1_3_BIC","level2_3_BIC","level3_3_BIC","WSLS_3_BIC")],1,which.min)])
#

```

## Fixed type: Likelihood of the different models by trial

This plot ks based on the three parameter versions of each strategy, and shows the average probability according to each model of participants' choices. It can be seen that, compared to the RPS game, where the fit grows slowly over trials, the fit in the later games increases much more rapidly.

```{r}
# long_likelihood_by_trial <- data.frame()
# for(id in unique(dat$human_id)) {
#   tdat <- subset(dat,human_id == id)
#   for(strategy in c("level1","level2","level3","WSLS")) {
#     long_likelihood_by_trial <- rbind(long_likelihood_by_trial,
#                                       data.frame(id = id,
#                                                  condition = dat[dat$human_id==id,"condition"][1],
#                                                  strategy = strategy,
#                                                  round = 1:50,
#                                                  game = rep(c("rps","fwg","numbers"),each=50),
#                                                  likelihood = modelLL(all_modelling[[id]][[paste(strategy,"_3",sep="")]]$par,
#                                                                       data=tdat,
#                                                                       strategy = strategy,
#                                                                       return_value = "likelihood_by_trial")
#                                       )
#                                 )
#   }
# }
# library(ggplot2)
# plot_dat <- long_likelihood_by_trial %>% group_by(condition,game,round,strategy) %>%
#       summarize(probability = mean(likelihood))
# # make sure the different games are ordered in the way they were played
# plot_dat$game <- factor(plot_dat$game,levels=c("rps","fwg","numbers"))
# ggplot(plot_dat,aes(x=round,y=probability,colour=strategy)) + geom_line() + facet_grid(game~condition)
```

## Fitting simple Bayesian learning model with flat prior
```{r}

best_response <- function(game,ai_action){
  if (game == "rps"){
    if (ai_action == "R") {return("P")}
    else if (ai_action == "P") {return("S")}
    else if (ai_action == "S") {return("R")}
  } else if (game == "fwg"){ 
    if (ai_action == "F") {return("W")}
    else if (ai_action == "W") {return("G")}
    else if (ai_action == "G") {return("F")}
  } else if (game == "numbers") {
    if (ai_action == "1") {return("2")}
    else if (ai_action == "2") {return("3")}
    else if (ai_action == "3") {return("4")}
    else if (ai_action == "4") {return("5")}
    else if (ai_action == "5") {return("1")}
  }
}
```

```{r}
naive_bayes <- function(par,data,opp_strategy_vec,return_value=c("-2loglik","likelihood_by_trial")) {
  # par = parameter, noise in computer choice
  # dat = data subset for one participant
  # opp_strategy_vec = c("level0","level1","level2")
  # return = -2logLik 
  # or "likelihood_by_trial" vector  (for later plotting, etc)

  return_value <- match.arg(return_value)
  theta <- par[1]
  eps <- par[2]

  num_strat = length(opp_strategy_vec) 
  # set up a vector to store the likelihood
  lik_opp <- matrix(0.0,num_strat, nrow(data))
  lik_hum <- matrix(0.0,nrow(data))
  br_hum <- rep(NA,num_strat)
  # Initiate prior vector as uniform
  opp_prior_vec <-rep(1/num_strat, num_strat)

  for(t in 1:nrow(data)) {
    t_game <- data[t,"game"]
    pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)
    if(t_game == "numbers") nopts <- 5 else nopts <- 3
    if(data[t,"round"] == 1) {
      # first round is uniform prediction
      pred <- NA
      lik_opp[,t] <- opp_prior_vec
      lik_hum[t] <- 1/nopts 
    } else {
      # get prediction of opponent action from CSV files
      for (strategy in opp_strategy_vec) {
        k = match(strategy,opp_strategy_vec)
        pred_opp <- as.character(filter(pred_file_opp,human_previous == as.character(data[t-1,"h_action"]) & computer_previous == as.character(data[t-1,"a_action"]))[strategy][1,])
        # Given opponent action predicted, what would be human action best response for each opp strat
        br_hum[[k]] <- best_response(t_game,as.character(pred_opp))
        #cat(as.character(br_hum[[k]]), "\n")
        # Multiply prior by likelihood of observation to get posterior 
        if(as.character(data[t,"a_action"]) == pred_opp) {
          lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
        } else {
          lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
        }
      }
      # Get which opponent strategy human current actn maps to (if index = 0 then human current action is br to level-0 comp_strat...)
      # NOTE!! -> ...assumes this is unique. check
      indices <- which(br_hum %in% as.character(data[t,"h_action"]))
      #cat(as.character(indices),  "\n")

      # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
      # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
      if(length(indices) == 0){
        lik_hum[t] <- eps/nopts
      # if same br action for multiple possible ai opponents, add probabilities 
      } else {
        lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
      }
      # Standardising the probabilities and updating prior
      lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
      opp_prior_vec <- lik_opp[,t]
    }
    # for debugging uncomment the line below
    #cat(as.character(pred_opp),as.character(data[t,"h_action"]),lik[,t],"\n")
  }
  if(return_value == "-2loglik") {
    ret <- -2*sum(log(lik_hum))
    if(is.infinite(ret)) {
      return(1e+300)
    } else {
      return(ret)
    }
  }
  if(return_value == "likelihood_by_trial") return(lik_hum)
}

```

```{r}

naive_bayes_modelling <- list()
for(id in unique(dat$human_id)) {
  naive_bayes_modelling[[id]] <- list()
  tdat <- subset(dat,human_id == id)
  naive_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),"-2loglik", lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
}

save(naive_bayes_modelling,file="naive_bayes_modelling.RData")

```
```{r}
Nbayes_par_results <- data.frame()
for(id in unique(dat$human_id)) {
Nbayes_par_results <- rbind(Nbayes_par_results,
                       data.frame(
                         "id" = id,
                         "condition" = dat[dat$human_id==id,"condition"][1],
                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
                         "theta" = naive_bayes_modelling[[id]]$par[1],
                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
                         "eps" = naive_bayes_modelling[[id]]$par[2]))
}

# Plotting the theta/eps scatter for all participants...
plot(Nbayes_par_results$theta,Nbayes_par_results$eps,xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))

write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
#kable(Nbayes_par_results)
```

## Q-learning
```{r}
# 
# Q_learn <- function(beta,lambda,data){
#   # actions 
#   # beta= inverse temperature parameter in softmax choicd=e function
#   # lambda = learning rate (one per game?)
#   # data : participant and ai choice data. 
#   # Returns Q-values per trial and predicts choice using softmax
#   Q_vals_RPS = rep(0.0,3)
#   names(Q_vals_RPS) <- c("R","P","S")
#   Q_vals_FWG = rep(0.0,3)
#   names(Q_vals_FWG) <- c("F","W","G")
#   Q_vals_NUM = rep(0.0,5)
#   names(Q_vals_NUM) <- c("1","2","3","4","5")
#   
#   for(t in 1:nrow(data)) {
#     t_game <- data[t,"game"]
#     Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
#     if(data[t,"round"] == 1) {
#       # first round is uniform prediction
#       Q_vals <- rep(0.0, nopts)
#       #lik[,t] <- prior_vec
#     } else {
#       
#     }
#     
#     
#   }
#   
# }

```

### 2019-11-01 comp_model_1019.Rmd

@@
 dat <- read.csv("data20180719.csv")
-#dat <- read.csv("test_data.csv")
+# dat <- read.csv("test_data.csv")
 ```
@@
 # create a new data.frame in a 'wide format'
-widedata <- dat %>% 
-  unite(game_block,game,block) %>% # this creates a new variable which combines game and block
-    group_by(human_id,condition,game_block) %>% # let the functions know you want to separate things by ID, condition, and game_block
-      summarize(mean_score = mean(score)) %>% # compute average score (i.e wins - losses)
-        spread(game_block,mean_score) # reformat in the 'wide' format
-# save the data file as a .csv to use in e.g. SPSS
-write.csv(widedata,row.names=FALSE,file="scores_wide.csv")
+# widedata <- dat %>%
+#   unite(game_block,game,block) %>% # this creates a new variable which combines game and block
+#     group_by(human_id,condition,game_block) %>% # let the functions know you want to separate things by ID, condition, and game_block
+#       summarize(mean_score = mean(score)) %>% # compute average score (i.e wins - losses)
+#         spread(game_block,mean_score) # reformat in the 'wide' format
+# # save the data file as a .csv to use in e.g. SPSS
+# write.csv(widedata,row.names=FALSE,file="scores_wide.csv")
 
@@
 ```{r}
-
-naive_bayes_modelling <- list()
-for(id in unique(dat$human_id)) {
-  naive_bayes_modelling[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
-  naive_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),"-2loglik", lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-}
-
-save(naive_bayes_modelling,file="naive_bayes_modelling.RData")
-
-```
-```{r}
-Nbayes_par_results <- data.frame()
-for(id in unique(dat$human_id)) {
-Nbayes_par_results <- rbind(Nbayes_par_results,
-                       data.frame(
-                         "id" = id,
-                         "condition" = dat[dat$human_id==id,"condition"][1],
-                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
-                         "theta" = naive_bayes_modelling[[id]]$par[1],
-                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
-                         "eps" = naive_bayes_modelling[[id]]$par[2]))
-}
-
-# Plotting the theta/eps scatter for all participants...
-plot(Nbayes_par_results$theta,Nbayes_par_results$eps,xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
-
-write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
+# 
+# naive_bayes_modelling <- list()
+# for(id in unique(dat$human_id)) {
+#   naive_bayes_modelling[[id]] <- list()
+#   tdat <- subset(dat,human_id == id)
+#   naive_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),"-2loglik", lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+# }
+# 
+# save(naive_bayes_modelling,file="naive_bayes_modelling.RData")
+# 
+# ```
+# ```{r}
+# Nbayes_par_results <- data.frame()
+# for(id in unique(dat$human_id)) {
+# Nbayes_par_results <- rbind(Nbayes_par_results,
+#                        data.frame(
+#                          "id" = id,
+#                          "condition" = dat[dat$human_id==id,"condition"][1],
+#                          # Theta is the parameter governing AI stochasticity. Truth is 0.9
+#                          "theta" = naive_bayes_modelling[[id]]$par[1],
+#                          # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
+#                          "eps" = naive_bayes_modelling[[id]]$par[2]))
+# }
+# 
+# # Plotting the theta/eps scatter for all participants...
+# plot(Nbayes_par_results$theta,Nbayes_par_results$eps,xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
+# 
+# write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
 #kable(Nbayes_par_results)
@@
 ```{r}
-# 
-# Q_learn <- function(beta,lambda,data){
-#   # actions 
-#   # beta= inverse temperature parameter in softmax choicd=e function
-#   # lambda = learning rate (one per game?)
-#   # data : participant and ai choice data. 
-#   # Returns Q-values per trial and predicts choice using softmax
-#   Q_vals_RPS = rep(0.0,3)
-#   names(Q_vals_RPS) <- c("R","P","S")
-#   Q_vals_FWG = rep(0.0,3)
-#   names(Q_vals_FWG) <- c("F","W","G")
-#   Q_vals_NUM = rep(0.0,5)
-#   names(Q_vals_NUM) <- c("1","2","3","4","5")
-#   
-#   for(t in 1:nrow(data)) {
-#     t_game <- data[t,"game"]
-#     Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
-#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
-#     if(data[t,"round"] == 1) {
-#       # first round is uniform prediction
-#       Q_vals <- rep(0.0, nopts)
-#       #lik[,t] <- prior_vec
-#     } else {
-#       
-#     }
-#     
-#     
-#   }
-#   
-# }
+
+Q_learn <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
+  # actions
+  # beta= inverse temperature parameter in softmax choice function
+  # lambda = learning rate (one per game?)
+  # data : participant and ai choice data.
+  # Returns Q-values per trial and predicts choice using softmax
+  beta <- par[1]
+  lambda <- par[2]
+  Q_vals_RPS = matrix(0.0,3)
+  names(Q_vals_RPS) <- c("R","P","S")
+  Q_vals_FWG = matrix(0.0,3)
+  names(Q_vals_FWG) <- c("F","W","G")
+  Q_vals_NUM = matrix(0.0,5)
+  names(Q_vals_NUM) <- c("1","2","3","4","5")
+
+  lik_hum <- matrix(0.0,nrow(data))
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    if(t_game == "numbers") nopts <- 5 else nopts <- 3
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
+      lik_hum[t] <- 1/nopts
+    } else {
+      # Get reward and past human action
+      reward <- as.numeric(data[t-1,"score"])
+      h_act_prev <- as.character(data[t-1,"h_action"])
+      Q_vals[h_act_prev] <- Q_vals[[h_act_prev]] + as.numeric(lambda)*( reward - Q_vals[[h_act_prev]])
+
+      # cat(Q_vals,"\n")
+
+      # Assume human chooses action probabilistically using softmax on Q values
+      probs <- exp(Q_vals/beta)/sum(exp(Q_vals/beta))
+
+      # Get actual human action and compute likelihood
+      h_act <- as.character(data[t,"h_action"])
+      act_index <- match(h_act, names(Q_vals))
+      lik_hum[t] <- probs[[act_index]]
+    }
+  }
+  if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+
+}
 
 ```
+
+```{r}
+QL_modelling <- list()
+for(id in unique(dat$human_id)) {
+  QL_modelling[[id]] <- list()
+  tdat <- subset(dat,human_id == id)
+  QL_modelling[[id]] <- optim(c(0.1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.01), upper = c(0.99,10), method="L-BFGS-B")
+}
+
+save(QL_modelling,file="QL_modelling.RData")
+
+```
+
+## Q-learning with state space including last actions

### 2019-11-08 comp_model_1019.Rmd
added parametric EWA

@@
 
-## Q-learning with state space including last actions
+## Parametric EWA
+
+```{r}
+
+indicator <- function(strat,action)
+  if (strat == action) { 
+    return (1)
+  else
+
+EWA_par <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
+  # actions
+  # beta= inverse temperature parameter in softmax choice function
+  # lambda = learning rate (one per game?)
+  # data : participant and ai choice data.
+  # Returns Q-values per trial and predicts choice using softmax
+  phi <- par[1]
+  delta <- par[2]
+  kappa <- par[3]
+  lambda <- par[4]
+
+  N <- 1
+
+  A_RPS = matrix(0.0,3)
+  names(A_RPS) <- c("R","P","S")
+  A_FWG = matrix(0.0,3)
+  names(A_FWG) <- c("F","W","G")
+  A_NUM = matrix(0.0,5)
+  names(A_NUM) <- c("1","2","3","4","5")
+
+  lik_hum <- matrix(0.0,nrow(data))
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    if(t_game == "numbers") nopts <- 5 else nopts <- 3
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
+      lik_hum[t] <- 1/nopts
+    } else {
+      # Get reward and past human action
+      reward <- as.numeric(data[t-1,"score"])
+      h_act_prev <- as.character(data[t-1,"h_action"])
+
+      Att[h_act_prev] <- (phi*N*Att[[h_act_prev]]  + reward
+
+      # cat(Q_vals,"\n")
+
+      # Assume human chooses action probabilistically using softmax on Q values
+      probs <- exp(Q_vals/beta)/sum(exp(Q_vals/beta))
+
+      # Get actual human action and compute likelihood
+      h_act <- as.character(data[t,"h_action"])
+      act_index <- match(h_act, names(Q_vals))
+      lik_hum[t] <- probs[[act_index]]
+    }
+  }

### 2019-11-11 comp_model_1019.Rmd
added self tuned EWA

--- 2019-11-01 comp_model_1019.Rmd
@@
 ```{r}
-QL_modelling <- list()
-for(id in unique(dat$human_id)) {
-  QL_modelling[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
-  QL_modelling[[id]] <- optim(c(0.1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.01), upper = c(0.99,10), method="L-BFGS-B")
+# QL_modelling <- list()
+# for(id in unique(dat$human_id)) {
+#   QL_modelling[[id]] <- list()
+#   tdat <- subset(dat,human_id == id)
+#   QL_modelling[[id]] <- optim(c(0.1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.01), upper = c(0.99,10), method="L-BFGS-B")
+# }
+# 
+# save(QL_modelling,file="QL_modelling.RData")
+# 
+# 
+# ```
+# 
+# 
+# ## Parametric EWA 
+# 
+# ```{r}
+# 
+# # Define reward matrices from the prospective of the row player (human in our case)
+reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
+
+reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
+
+reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
+dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+
+# 
+# 
+# EWA_par <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
+#   # par: vector of parameters to the EWA model 
+#   # Data :choice data by trial for each participant 
+#   # Returns sum of loglikelihoods or likelihood per trial 
+#   phi <- par[1]
+#   delta <- par[2]
+#   rho <- par[3]
+#   lambda <- par[4]
+#   
+#   # Initiate N(0) = 1 as in Camerer and Ho 1997 paper. 
+#   N <- 1
+#   
+#   # Define attraction vectors for each game 
+#   A_RPS = matrix(0.0,3)
+#   names(A_RPS) <- c("R","P","S")
+#   A_FWG = matrix(0.0,3)
+#   names(A_FWG) <- c("F","W","G")
+#   A_NUM = matrix(0.0,5)
+#   names(A_NUM) <- c("1","2","3","4","5")
+#   
+#   # Initiate likelihood by trial vector 
+#   lik_hum <- matrix(0.0,nrow(data))
+# 
+#   for(t in 1:nrow(data)) {
+#     t_game <- data[t,"game"]
+#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
+#     if(data[t,"round"] == 1) {
+#       # first round is uniform prediction
+#       Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
+#       reward <- switch(as.character(t_game),rps=reward_RPS,fwg = reward_FWG, numbers = reward_NUM)
+#       lik_hum[t] <- 1/nopts
+#     } else {
+#       # Get reward and past human action
+#       h_act_prev <- as.character(data[t-1,"h_action"])
+#       a_act_prev <- as.character(data[t-1,"a_action"])
+#       for (i in length(Att)) {
+#         action <- as.character(names(Att)[i])
+#         # cat("this is current strat",action,"\n")
+#         # cat("this is previous humna action",h_act_prev,"\n")
+#         
+#         # Attraction vector update rule 
+#         Att[[i]] <- (phi*N*Att[[i]]  + ( delta + (1- delta)*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (rho*N + 1)
+#       }
+#       #Update the value of N 
+#       N <- rho*N + 1 
+#       
+#       # Assume human chooses action probabilistically using softmax on Attraction values
+#       probs <- exp(lambda*Att)/sum(exp(lambda*Att))
+#       
+#       # Get actual human action and compute likelihood
+#       h_act <- as.character(data[t,"h_action"])
+#       act_index <- match(h_act, names(Att))
+#       lik_hum[t] <- probs[[act_index]]
+#     }
+#   }
+#   
+#  if(return_value == "-2loglik") {
+#     ret <- -2*sum(log(lik_hum))
+#     if(is.infinite(ret)) {
+#       return(1e+300)
+#     } else {
+#       return(ret)
+#     }
+#   }
+#   if(return_value == "likelihood_by_trial") return(lik_hum)
+# }
+```
+
+```{r}
+#######################################################################################
+
+##  Self-Tuning EWA:
+
+EWA_self <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
+
+  lambda <- par[[1]]
+  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper. 
+  N <- 1.0
+
+  # Define attraction vectors for each game 
+  A_RPS = matrix(0.0,3)
+  names(A_RPS) <- c("R","P","S")
+  A_FWG = matrix(0.0,3)
+  names(A_FWG) <- c("F","W","G")
+  A_NUM = matrix(0.0,5)
+  names(A_NUM) <- c("1","2","3","4","5")
+
+  # Initiate likelihood by trial vector 
+  lik_hum <- matrix(0.0,nrow(data))
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    if(t_game == "numbers") nopts <- 5 else nopts <- 3
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
+      reward <- switch(as.character(t_game),rps=reward_RPS,fwg = reward_FWG, numbers = reward_NUM)
+      game_data <- subset(data, game == t_game)
+      lik_hum[t] <- 1/nopts
+
+      R_t <- rep(0.0,nopts)
+      H_t <- R_t
+
+    } else {
+
+      indx <- data[t,"round"]
+      # Get reward and past human action
+      h_act_prev <- as.character(game_data[indx-1,"h_action"])
+      a_act_prev <- as.character(game_data[indx-1,"a_action"])
+
+      # Estimate phi(t)
+      R_t <- as.numeric(names(Att) == a_act_prev)
+      # cat("This is R(t)",R_t,"\n")
+
+      H_t <- (H_t*(indx-2) + R_t)/(indx-1)
+      # cat("this is H(t)",H_t,"\n")
+
+      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
+      # cat("This is Phit(t)",Phi_t,"\t")
+
+      # Estimate vector Delta(t)
+      delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
+      # cat("this is delta(t)",delta_t,"\n")
+
+      for (i in length(Att)) {
+        action <- as.character(names(Att)[i])
+        # cat("this is current strat",action,"\n")
+        # cat("this is previous humna action",h_act_prev,"\n")
+
+        # Attraction vector update rule 
+        Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
+      }
+      #Update the value of N 
+      N <- Phi_t*N + 1
+
+      # Assume human chooses action probabilistically using softmax on Attraction values
+      probs <- exp(lambda*Att)/sum(exp(lambda*Att))
+
+      # Get actual human action and compute likelihood
+      h_act <- as.character(game_data[indx,"h_action"])
+      act_index <- match(h_act, names(Att))
+      lik_hum[t] <- probs[[act_index]]
+    }
   }
 
-save(QL_modelling,file="QL_modelling.RData")
+ if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+}
 
@@
 
-## Q-learning with state space including last actions
+```{r}
+# 
+# EWA_modelling <- list()
+# for(id in unique(dat$human_id)) {
+# 
+#   EWA_modelling[[id]] <- list()
+#   tdat <- subset(dat,human_id == id)
+#   EWA_modelling[[id]] <- optim(c(0.5,0.5,0.5,0.5),fn=EWA_par,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.001,0.001,0.001), upper = c(1,0.99,0.99,1), method="L-BFGS-B")
+# }
+# 
+# save(EWA_modelling,file="EWA_modelling.RData")
+
+EWA_self_modelling <- list()
+for(id in unique(dat$human_id)) {
+  EWA_self_modelling[[id]] <- list()
+  tdat <- subset(dat,human_id == id)
+  EWA_self_modelling[[id]] <- optim(10.0,fn=EWA_self,gr = NULL, data=tdat,"-2loglik", lower = 0.001, upper = 200, method="L-BFGS-B")
+}
+
+save(EWA_self_modelling,file="EWA_self_modelling.RData")
+
+```

### 2019-11-11 comp_model_1019.Rmd
tried DEoptim

@@
 library(dplyr)
+library(DEoptim)
 # transform 'winner' variable in numeric score
@@
 #
-# ```
+
+```
+
+```{r}
 # 
@@
 
-  lambda <- par[[1]]
+  lambda <- par[1]
   # Initiate N(0) = 1 as in Camerer and Ho 1997 paper. 
@@
   tdat <- subset(dat,human_id == id)
-  EWA_self_modelling[[id]] <- optim(10.0,fn=EWA_self,gr = NULL, data=tdat,"-2loglik", lower = 0.001, upper = 200, method="L-BFGS-B")
+#   EWA_self_modelling[[id]] <- optim(10.0,fn=EWA_self,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
+# }
+  EWA_self_modelling[[id]] <- DEoptim(EWA_self, 0.0, 10.0, data=tdat,"-2loglik")
 }

### 2019-11-12 comp_model_1019.Rmd
bug fix 1 self EWA

@@
 
+## Parametric Experience Weighted Attraction model (Camerer & Ho 1997)
 ```{r}
-# 
-# 
-# ## Parametric EWA 
-# 
-# ```{r}
-# 
+
 # # Define reward matrices from the prospective of the row player (human in our case)
@@
 # 
-# EWA_par <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
-#   # par: vector of parameters to the EWA model 
-#   # Data :choice data by trial for each participant 
-#   # Returns sum of loglikelihoods or likelihood per trial 
-#   phi <- par[1]
-#   delta <- par[2]
-#   rho <- par[3]
-#   lambda <- par[4]
-#   
-#   # Initiate N(0) = 1 as in Camerer and Ho 1997 paper. 
-#   N <- 1
-#   
-#   # Define attraction vectors for each game 
-#   A_RPS = matrix(0.0,3)
-#   names(A_RPS) <- c("R","P","S")
-#   A_FWG = matrix(0.0,3)
-#   names(A_FWG) <- c("F","W","G")
-#   A_NUM = matrix(0.0,5)
-#   names(A_NUM) <- c("1","2","3","4","5")
-#   
-#   # Initiate likelihood by trial vector 
-#   lik_hum <- matrix(0.0,nrow(data))
-# 
-#   for(t in 1:nrow(data)) {
-#     t_game <- data[t,"game"]
-#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
-#     if(data[t,"round"] == 1) {
-#       # first round is uniform prediction
-#       Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
-#       reward <- switch(as.character(t_game),rps=reward_RPS,fwg = reward_FWG, numbers = reward_NUM)
-#       lik_hum[t] <- 1/nopts
-#     } else {
-#       # Get reward and past human action
-#       h_act_prev <- as.character(data[t-1,"h_action"])
-#       a_act_prev <- as.character(data[t-1,"a_action"])
-#       for (i in length(Att)) {
-#         action <- as.character(names(Att)[i])
-#         # cat("this is current strat",action,"\n")
-#         # cat("this is previous humna action",h_act_prev,"\n")
-#         
-#         # Attraction vector update rule 
-#         Att[[i]] <- (phi*N*Att[[i]]  + ( delta + (1- delta)*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (rho*N + 1)
-#       }
-#       #Update the value of N 
-#       N <- rho*N + 1 
-#       
-#       # Assume human chooses action probabilistically using softmax on Attraction values
-#       probs <- exp(lambda*Att)/sum(exp(lambda*Att))
-#       
-#       # Get actual human action and compute likelihood
-#       h_act <- as.character(data[t,"h_action"])
-#       act_index <- match(h_act, names(Att))
-#       lik_hum[t] <- probs[[act_index]]
-#     }
-#   }
-#   
-#  if(return_value == "-2loglik") {
-#     ret <- -2*sum(log(lik_hum))
-#     if(is.infinite(ret)) {
-#       return(1e+300)
-#     } else {
-#       return(ret)
-#     }
-#   }
-#   if(return_value == "likelihood_by_trial") return(lik_hum)
-# }
+EWA_par <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
+  # par: vector of parameters to the EWA model
+  # Data :choice data by trial for each participant
+  # Returns sum of loglikelihoods or likelihood per trial
+  phi <- par[1]
+  delta <- par[2]
+  rho <- par[3]
+  lambda <- par[4]
+
+  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.
+  N <- 1
+
+  # Define attraction vectors for each game
+  A_RPS = matrix(0.0,3)
+  names(A_RPS) <- c("R","P","S")
+  A_FWG = matrix(0.0,3)
+  names(A_FWG) <- c("F","W","G")
+  A_NUM = matrix(0.0,5)
+  names(A_NUM) <- c("1","2","3","4","5")
+
+  # Initiate likelihood by trial vector
+  lik_hum <- matrix(0.0,nrow(data))
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    if(t_game == "numbers") nopts <- 5 else nopts <- 3
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
+      reward <- switch(as.character(t_game),rps=reward_RPS,fwg = reward_FWG, numbers = reward_NUM)
+      lik_hum[t] <- 1/nopts
+    } else {
+      # Get reward and past human action
+      h_act_prev <- as.character(data[t-1,"h_action"])
+      a_act_prev <- as.character(data[t-1,"a_action"])
+      for (i in 1:length(Att)) {
+        action <- as.character(names(Att)[i])
+        # cat("this is current strat",action,"\n")
+        # cat("this is previous human action",h_act_prev,"\n")
+
+        # Attraction vector update rule
+        Att[[i]] <- (phi*N*Att[[i]]  + ( delta + (1- delta)*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (rho*N + 1)
+      }
+      #Update the value of N
+      N <- rho*N + 1
+
+      # Assume human chooses action probabilistically using softmax on Attraction values
+      probs <- exp(lambda*Att)/sum(exp(lambda*Att))
+
+      # Get actual human action and compute likelihood
+      h_act <- as.character(data[t,"h_action"])
+      act_index <- match(h_act, names(Att))
+      lik_hum[t] <- probs[[act_index]]
+    }
+  }
+
+ if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+}
 ```
@@
 ```{r}
+
+EWA_modelling <- list()
+for(id in unique(dat$human_id)) {
+  EWA_modelling[[id]] <- list()
+  tdat <- subset(dat,human_id == id)
+  # EWA_modelling[[id]] <- optim(c(0.5,0.5,0.5,0.5),fn=EWA_par,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.001,0.001,0.001), upper = c(1,0.99,0.99,1), method="L-BFGS-B")
+  EWA_modelling[[id]] <- DEoptim(fn=EWA_par,lower = c(0.001,0.001,0.001,0.001), upper = c(1,0.99,0.99,1), data=tdat,"-2loglik")
+}
+
+save(EWA_modelling,file="EWA_modelling.RData")
+
+```
+
+##  Self-Tuning EWA (Camerer & Ho 2007) 
+```{r}
 #######################################################################################
-
-##  Self-Tuning EWA:
 
@@
       R_t <- rep(0.0,nopts)
-      H_t <- R_t
+      H_t = R_t
 
@@
       # Estimate vector Delta(t)
+
       delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
-      # cat("this is delta(t)",delta_t,"\n")
+      #cat("this is delta(t)",delta_t,"\n")
 
-      for (i in length(Att)) {
+      for (i in 1:length(Att)) {
         action <- as.character(names(Att)[i])
@@
       N <- Phi_t*N + 1
+      #cat(Att,'\n')
 
@@
 ```{r}
-# 
-# EWA_modelling <- list()
-# for(id in unique(dat$human_id)) {
-# 
-#   EWA_modelling[[id]] <- list()
-#   tdat <- subset(dat,human_id == id)
-#   EWA_modelling[[id]] <- optim(c(0.5,0.5,0.5,0.5),fn=EWA_par,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.001,0.001,0.001), upper = c(1,0.99,0.99,1), method="L-BFGS-B")
-# }
-# 
-# save(EWA_modelling,file="EWA_modelling.RData")
 
@@
 # }
-  EWA_self_modelling[[id]] <- DEoptim(EWA_self, 0.0, 10.0, data=tdat,"-2loglik")
+  EWA_self_modelling[[id]] <- DEoptim(fn=EWA_self, lower = 0.0, upper = 10.0, data=tdat)
 }

### 2019-11-12 comp_model_1019.Rmd
all results added

@@
 dat <- read.csv("data20180719.csv")
-# dat <- read.csv("test_data.csv")
+#dat <- read.csv("test_data.csv")
 ```
@@
 ```{r}
-naive_bayes <- function(par,data,opp_strategy_vec,return_value=c("-2loglik","likelihood_by_trial")) {
+naive_bayes <- function(par,data,opp_strategy_vec,return_value) {
   # par = parameter, noise in computer choice
@@
 
-  return_value <- match.arg(return_value)
+  #return_value <- match.arg(return_value)
   theta <- par[1]
@@
 ```{r}
-# 
-# naive_bayes_modelling <- list()
-# for(id in unique(dat$human_id)) {
-#   naive_bayes_modelling[[id]] <- list()
-#   tdat <- subset(dat,human_id == id)
-#   naive_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),"-2loglik", lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-# }
-# 
-# save(naive_bayes_modelling,file="naive_bayes_modelling.RData")
-# 
+
+naive_bayes_modelling <- list()
+for(id in unique(dat$human_id)) {
+  naive_bayes_modelling[[id]] <- list()
+  tdat <- subset(dat,human_id == id)
+  naive_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+}
+
+save(naive_bayes_modelling,file="naive_bayes_modelling.RData")
+
 # ```
+
 # ```{r}
@@
 ```{r}
-
 Q_learn <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
@@
 
+##Q-learning fit
 ```{r}
-# QL_modelling <- list()
-# for(id in unique(dat$human_id)) {
-#   QL_modelling[[id]] <- list()
-#   tdat <- subset(dat,human_id == id)
-#   QL_modelling[[id]] <- optim(c(0.1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.01), upper = c(0.99,10), method="L-BFGS-B")
-# }
-# 
-# save(QL_modelling,file="QL_modelling.RData")
-# 
-#
+QL_modelling <- list()
+for(id in unique(dat$human_id)) {
+  QL_modelling[[id]] <- list()
+  tdat <- subset(dat,human_id == id)
+  QL_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.001), upper = c(10,0.99), method="L-BFGS-B")
+}
+
+save(QL_modelling,file="QL_modelling.RData")
 
@@
 ```{r}
+EWA_par <- function(par,data,return_value){
+  # par: vector of parameters to the EWA model
+  # Data :choice data by trial for each participant
+  # Returns sum of loglikelihoods or likelihood per trial
+  phi <- par[1]
+  delta <- par[2]
+  rho <- par[3]
+  lambda <- par[4]
+
+  # Define attraction vectors for each game
+  A_RPS = matrix(0.0,3)
+  names(A_RPS) <- c("R","P","S")
+  A_FWG = matrix(0.0,3)
+  names(A_FWG) <- c("F","W","G")
+  A_NUM = matrix(0.0,5)
+  names(A_NUM) <- c("1","2","3","4","5")
 
@@
   dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-
-# 
-# 
-EWA_par <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
-  # par: vector of parameters to the EWA model
-  # Data :choice data by trial for each participant
-  # Returns sum of loglikelihoods or likelihood per trial
-  phi <- par[1]
-  delta <- par[2]
-  rho <- par[3]
-  lambda <- par[4]
-
-  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.
-  N <- 1
-
-  # Define attraction vectors for each game
-  A_RPS = matrix(0.0,3)
-  names(A_RPS) <- c("R","P","S")
-  A_FWG = matrix(0.0,3)
-  names(A_FWG) <- c("F","W","G")
-  A_NUM = matrix(0.0,5)
-  names(A_NUM) <- c("1","2","3","4","5")
 
@@
       lik_hum[t] <- 1/nopts
+      # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.
+      N <- 1
+
     } else {
@@
     ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret)) {
+    if(is.infinite(ret) || is.nan(ret) ) {
       return(1e+300)
@@
 
+## Fitting Parametric EWA to data 
 ```{r}
@@
   # EWA_modelling[[id]] <- optim(c(0.5,0.5,0.5,0.5),fn=EWA_par,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.001,0.001,0.001), upper = c(1,0.99,0.99,1), method="L-BFGS-B")
-  EWA_modelling[[id]] <- DEoptim(fn=EWA_par,lower = c(0.001,0.001,0.001,0.001), upper = c(1,0.99,0.99,1), data=tdat,"-2loglik")
+  EWA_modelling[[id]] <- DEoptim(fn=EWA_par,lower = c(0.01,0.01,0.01,0.01), upper = c(10,1,1,10), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))
 }
@@
 ```{r}
-#######################################################################################
 
-EWA_self <- function(par,data,return_value=c("-2loglik","likelihood_by_trial")){
+EWA_self <- function(par,data,return_value){
 
@@
   # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.
-  N <- 1.0
 
@@
   names(A_NUM) <- c("1","2","3","4","5")
+
+  # # Define reward matrices from the prospective of the row player (human in our case)
+  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
+
+  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
+
+  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
+  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
 
@@
       lik_hum[t] <- 1/nopts
+      N <- 1.0
 
@@
 ```{r}
+##Plotting self_tuning EWA likelihood function for lambda from 0 to 100
+
+lambdas <- seq(0,100,1)
+data_test <- subset(data,human_id =="oXdDF_U-Dft2ja2lAAAs")
+
+plot(lambdas,EWA_self(lambdas,data_test,"-2loglik"))
+```
+
+## Fitting Self-Tuning EWA to data 
+```{r}
 
@@
 # }
-  EWA_self_modelling[[id]] <- DEoptim(fn=EWA_self, lower = 0.0, upper = 10.0, data=tdat)
+  EWA_self_modelling[[id]] <- DEoptim(fn=EWA_self, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
 }
@@
 ```
+```{r}
+cat(EWA_self_modelling[["38VxtUSv_h6RR5-tAAA2"]]$optim$bestmem)
+```
+
+## Putting results together 
+```{r}
+All_results <- data.frame()
+for(id in unique(dat$human_id)) {
+All_results <- rbind(All_results,
+                       data.frame(
+                         "id" = id,
+                         "condition" = dat[dat$human_id==id,"condition"][1],
+                         "random_BIC" = -2*(100*log(1/3) + 50*log(1/5)),
+
+                         # Naive Bayes, Theta is the parameter governing AI stochasticity. Truth is 0.9
+                         "NB_theta" = naive_bayes_modelling[[id]]$par[1],
+                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
+                         "NB_eps" = naive_bayes_modelling[[id]]$par[2],
+                         "NB_BIC" = naive_bayes_modelling[[id]]$value + 2*log(150),
+
+                         # Q-Learning 
+                         # beta ->  inverse temperature parameter in softmax choice function
+                         "QL_Beta" = QL_modelling[[id]]$par[1],
+                         # lambda -> learning rate in QL update
+                         "QL_beta" = QL_modelling[[id]]$par[2],
+                         "QL_BIC" = QL_modelling[[id]]$value + 2*log(150),
+
+                         # Parametric EWA
+                         # Phi is depreciation of past attractions
+                         "EWA_Phi" = EWA_modelling[[id]]$optim$bestmem[1],
+                         # Delta is weight of foregone payoffs vs actual payoffs
+                         "EWA_Delta" = EWA_modelling[[id]]$optim$bestmem[2],
+                         # Rho is depreciation of the experience measure N(t)
+                         "EWA_Rho" = EWA_modelling[[id]]$optim$bestmem[3],
+                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
+                         "EWA_Lambda" = EWA_modelling[[id]]$optim$bestmem[4],
+                         # Parametric EWA BIC
+                         "EWA_BIC" = EWA_modelling[[id]]$optim$bestval + 4*log(150),
+                         "EWA_2LL" = EWA_modelling[[id]]$optim$bestval,
+
+                         # Self-Tuning EWA (only 1 parameter)
+                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
+                         "EWA_self_Lambda" = EWA_self_modelling[[id]]$optim$bestmem[1],
+                         # Parametric EWA BIC
+                         "EWA_self_BIC" = EWA_self_modelling[[id]]$optim$bestval + 1*log(150)
+                         ))
+}
+
+write.csv(All_results,file="All_results.csv",row.names = FALSE)
+
+```

### 2019-11-14 comp_model_1019.Rmd
added param & model recovery

@@
     ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret)) {
+    if(is.infinite(ret) || is.nan(ret)) {
       return(1e+300)
@@
   beta <- par[1]
-  lambda <- par[2]
+  alpha <- par[2]
   Q_vals_RPS = matrix(0.0,3)
@@
       h_act_prev <- as.character(data[t-1,"h_action"])
-      Q_vals[h_act_prev] <- Q_vals[[h_act_prev]] + as.numeric(lambda)*( reward - Q_vals[[h_act_prev]])
+      Q_vals[h_act_prev] <- Q_vals[[h_act_prev]] + as.numeric(alpha)*( reward - Q_vals[[h_act_prev]])
 
@@
   tdat <- subset(dat,human_id == id)
-  QL_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0.001,0.001), upper = c(10,0.99), method="L-BFGS-B")
+  QL_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
 }
@@
       R_t <- rep(0.0,nopts)
-      H_t = R_t
+      H_t <- R_t
 
@@
 
-lambdas <- seq(0,100,1)
-data_test <- subset(data,human_id =="oXdDF_U-Dft2ja2lAAAs")
+lambdas <- seq(1,10,0.01)
+count = 0.0
 
-plot(lambdas,EWA_self(lambdas,data_test,"-2loglik"))
+for(id in unique(dat$human_id)) {
+  if (count <= 15) {
+      tdat <- subset(dat,human_id == id)
+      likelihoods <- sapply(lambdas, EWA_self, tdat, "-2loglik")
+      plot(lambdas,likelihoods)
+      count <- count + 1
+  }
+}
+
 ```
@@
                          # lambda -> learning rate in QL update
-                         "QL_beta" = QL_modelling[[id]]$par[2],
+                         "QL_alpha" = QL_modelling[[id]]$par[2],
                          "QL_BIC" = QL_modelling[[id]]$value + 2*log(150),
@@
                          # Parametric EWA BIC
+                         "EWA_self_2LL" = EWA_self_modelling[[id]]$optim$bestval,
                          "EWA_self_BIC" = EWA_self_modelling[[id]]$optim$bestval + 1*log(150)

### 2019-11-14 param_model_recovery.Rmd
added param & model recovery

---
title: "Simulation_EWA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r}
# Build function that will simulate a self tuning EWA player given parameter Lambda, and generate actions for 50 rounds
# of each game. 
# NOTE : haven't introduced noise in either human or computer actions.

gen_data <- function(par,num_rounds){

  lambda <- par[1]
  games <- c("rps","fwg","numbers")
  condition <- sample(c("level1","level2"),1)
  data <- data.frame()

  # Define attraction vectors for each game 
  A_RPS = matrix(0.0,3)
  names(A_RPS) <- c("R","P","S")
  A_FWG = matrix(0.0,3)
  names(A_FWG) <- c("F","W","G")
  A_NUM = matrix(0.0,5)
  names(A_NUM) <- c("1","2","3","4","5")

  # # Define reward matrices from the prospective of the row player (human in our case)
  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))

  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))

  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))

  for (t_game in games){
      # Initiate dataframe
      game_data <- setNames(data.frame(matrix(ncol = 6, nrow = num_rounds)), c("condition","game", "round", "h_action","a_action","score"))
      # Initialize attraction vector, rewards + randomly select first actions
      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
      game_actions <- names(Att)
      reward <- switch(as.character(t_game), rps=reward_RPS, fwg=reward_FWG, numbers=reward_NUM)
      pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)

    for(t in 1:num_rounds) {
      if(t_game == "numbers") nopts <- 5 else nopts <- 3
      game_data[t,"game"]<- t_game
      game_data[t,"round"] <- t
      game_data[t,"condition"] <- condition

      if(t == 1) {

        game_data[t,"h_action"] <- as.character(sample(game_actions, 1 ))
        game_data[t,"a_action"] <- as.character(sample(game_actions, 1 ))
        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]
        lik_hum <- c(1/nopts)
        N <- 1.0
        R_t <- rep(0.0,nopts)
        H_t <- R_t

      } else {

        # Get reward and past human action
        h_act_prev <- as.character(game_data[t-1,"h_action"])
        a_act_prev <- as.character(game_data[t-1,"a_action"])

        # Estimate phi(t)
        R_t <- as.numeric(game_actions == a_act_prev)
        # cat("This is R(t)",R_t,"\n")

        H_t <- (H_t*(t-2) + R_t)/(t-1)
        # cat("this is H(t)",H_t,"\n")

        Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
        # cat("This is Phit(t)",Phi_t,"\t")

        # Estimate vector Delta(t)
        delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[t-1,"score"]))
        #cat("this is delta(t)",delta_t,"\n")

        for (i in 1:length(Att)) {
          action <- as.character(game_actions[i])
          # Attraction vector update rule 
          Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
        }
        #Update the value of N 
        N <- Phi_t*N + 1
        #cat(Att,'\n')

        # Assume human chooses action probabilistically using softmax on Attraction values
        probs <- exp(lambda*Att)/sum(exp(lambda*Att))

        # Get actual human action and compute likelihood
        game_data[t,"h_action"] <- sample(game_actions, size=1,prob=probs)
        act_index <- match(game_data[t,"h_action"], game_actions)
        lik_hum[t] <- probs[[act_index]]

        # Simulate opponent action and get score 
        game_data[t,"a_action"] <- as.character(filter(pred_file_opp,human_previous == as.character(game_data[t-1,"h_action"]) & computer_previous == as.character(game_data[t-1,"a_action"]))[condition][1,])
        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]

      }

    }# End for loop over rounds
    data <- rbind(data,game_data)

  }# end of game for loop
  return(data)

}

```

```{r}
## Generate N lambdas in chosen interval, get the corresponding datasets of actions and scores, use Self_EWA to infer Lambda from these datasets. 
EWA_self_simulation <- data.frame()
lambdas = runif(100, 0, 10)
num_rounds <- 50 
count <- 1

for(lambda in lambdas){

  EWA_self_simulation[count,"real_lambda"] <- lambda
  tdat <- gen_data(par = lambda, num_rounds)

  # Fit various models to generated data (from S_EWA type player)
  optim_S_EWA  <- DEoptim(fn=EWA_self, lower = 0.0, upper = 10.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))

  optim_EWA    <- DEoptim(fn=EWA_par,lower = c(0,0,0,0), upper = c(20,1,1,20), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))

  optim_QL     <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")

  optim_NB     <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")

  # Get condition
  EWA_self_simulation[count, "condition"]  <- as.character(tdat$condition[1])

  # Get best fit parameters and -2 Log Likelihoods for all models

  # Self-tuning EWA 
  EWA_self_simulation[count, "S_EWA_infrd_lambda"] <- optim_S_EWA$optim$bestmem[1]
  EWA_self_simulation[count, "S_EWA_2LL"]          <- optim_S_EWA$optim$bestval

  #Parametric EWA
  EWA_self_simulation[count, "EWA_infrd_phi"]    <- optim_EWA$optim$bestmem[1]
  EWA_self_simulation[count, "EWA_infrd_delta"]  <- optim_EWA$optim$bestmem[2]
  EWA_self_simulation[count, "EWA_infrd_rho"]    <- optim_EWA$optim$bestmem[3]
  EWA_self_simulation[count, "EWA_infrd_lambda"] <- optim_EWA$optim$bestmem[4]
  EWA_self_simulation[count, "EWA_2LL"]          <- optim_EWA$optim$bestval

  # Q-Learning
  EWA_self_simulation[count, "QL_infrd_beta"]   <- optim_QL$par[1]
  EWA_self_simulation[count, "QL_infrd_alpha"]  <- optim_QL$par[2]
  EWA_self_simulation[count, "QL_2LL"]          <- optim_QL$value

  # Naive Bayes (nopts-arm bandit with prior vec transfered across games)
  EWA_self_simulation[count, "NB_infrd_theta"] <- optim_NB$par[1]
  EWA_self_simulation[count, "NB_infrd_eps"]   <- optim_NB$par[2]
  EWA_self_simulation[count, "NB_2LL"]         <- optim_NB$value

  # Random
  EWA_self_simulation[count, "Random_2LL"]     <- -2*(2*num_rounds*log(1/3) + num_rounds*log(1/5))

  count <- count + 1
}

save(EWA_self_simulation,file="EWA_self_simulation.RData")

```

```{r}
plot(EWA_self_simulation$real_lambda,EWA_self_simulation$S_EWA_infrd_lambda)
# cor.test(EWA_self_simulation$real_lambda, EWA_self_simulation$S_EWA_infrd_lambda, method=c("pearson", "kendall", "spearman"))

# create a table with best fitting models by condition
table(EWA_self_simulation[, "condition"],c("random","Naive_Bayes","QL","EWA","S_EWA")[apply(EWA_self_simulation[,c("Random_2LL","NB_2LL","QL_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])
```
```{r}

```

### 2019-11-15 comp_model_1019.Rmd
added tabular Q learning

@@
 ```{r}
-naive_bayes <- function(par,data,opp_strategy_vec,return_value) {
-  # par = parameter, noise in computer choice
+naive_bayes <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {
+  # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
+  # Epsilone: parameter controlling noise in human choice. Probability human will deviate from its best response. In [0,1].
   # dat = data subset for one participant
-  # opp_strategy_vec = c("level0","level1","level2")
+  # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
   # return = -2logLik 
   # or "likelihood_by_trial" vector  (for later plotting, etc)
+  # opp_mod_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise.
 
@@
   num_strat = length(opp_strategy_vec)
-  # set up a vector to store the likelihood
+
+  #lik_opp is a vector that holds and update probability distribution of opp strategy given actions.
   lik_opp <- matrix(0.0,num_strat, nrow(data))
-  lik_hum <- matrix(0.0,nrow(data))
-  br_hum <- rep(NA,num_strat)
   # Initiate prior vector as uniform
   opp_prior_vec <-rep(1/num_strat, num_strat)
+
+  lik_hum <- matrix(0.0,nrow(data))
+  # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
+  br_hum <- rep(NA,num_strat)
 
@@
       pred <- NA
+      lik_hum[t] <- 1/nopts
+      if (opp_mod_transfer) {
+        opp_prior_vec <- rep(1/num_strat, num_strat)
         lik_opp[,t] <- opp_prior_vec
-      lik_hum[t] <- 1/nopts 
+        }
+
+    # Rounds after first
     } else {
@@
         #cat(as.character(br_hum[[k]]), "\n")
-        # Multiply prior by likelihood of observation to get posterior 
+
+        # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
         if(as.character(data[t,"a_action"]) == pred_opp) {
@@
       # Get which opponent strategy human current actn maps to (if index = 0 then human current action is br to level-0 comp_strat...)
-      # NOTE!! -> ...assumes this is unique. check
       indices <- which(br_hum %in% as.character(data[t,"h_action"]))
@@
 ```{r}
+# 
+# naive_bayes_modelling <- list()
+# for(id in unique(dat$human_id)) {
+#   naive_bayes_modelling[[id]] <- list()
+#   tdat <- subset(dat,human_id == id)
 
-naive_bayes_modelling <- list()
+#   naive_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = 0.0, upper = 1.0, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE,parallelType=1))
+
+#   naive_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+# }
+# save(naive_bayes_modelling,file="naive_bayes_modelling.RData")
+
+# Fitting a bayesiam model with No Transfer of opp strat distribution between games 
+NT_bayes_modelling <- list()
 for(id in unique(dat$human_id)) {
-  naive_bayes_modelling[[id]] <- list()
+  NT_bayes_modelling[[id]] <- list()
   tdat <- subset(dat,human_id == id)
-  naive_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+
+  # NT_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = 0.0, upper = 1.0, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE,parallelType=1))
+
+  NT_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE ,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
 }
 
-save(naive_bayes_modelling,file="naive_bayes_modelling.RData")
+save(NT_bayes_modelling,file="NT_bayes_modelling.RData")
 
@@
 
+## Fitting a QL with state space consisting of last round actions 
+```{r}
+
+Q_learn_states <- function(par,data,return_value){
+  # beta= inverse temperature parameter in softmax choice function
+  # lambda = learning rate (one per game?)
+  # data : participant and ai choice data.
+  # return_value=c("-2loglik","likelihood_by_trial")
+  # Returns Q-values per trial and predicts choice using softmax
+  beta <- par[1]
+  alpha <- par[2]
+  gamma <- 0.9
+
+  #Define matrix of state spaces for each game 
+  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+  states_RPS <- paste0(G1$Var1,G1$Var2)
+
+  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+  states_FWG <- paste0(G2$Var1,G2$Var2)
+
+  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+  states_NUM <- paste0(G3$Var1,G3$Var2)
+
+  Q_vals_RPS = matrix(0.0,9,3)
+  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
+
+  Q_vals_FWG = matrix(0.0,9,3)
+  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
+
+  Q_vals_NUM = matrix(0.0,25,5)
+  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
+
+  lik_hum <- matrix(0.0,nrow(data))
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    if(t_game == "numbers") nopts <- 5 else nopts <- 3
+
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
+      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
+      lik_hum[t] <- 1/nopts
+      # Randomly select prev_state and actions for first round
+      state_prev  <- sample(state_vec, size = 1)
+      h_act_prev <- sample(colnames(Q_vals), size =1)
+      a_act_prev <- sample(colnames(Q_vals), size =1)
+      reward <- 0
+
+    } else {
+      # Get reward and past human action
+      reward <- as.numeric(data[t-1,"score"])
+      h_act_prev <- as.character(data[t-1,"h_action"])
+      a_act_prev <- as.character(data[t-1,"a_action"])
+    }
+    # cat(state_prev, " This is the previous state", "\n")
+    new_state <- paste0(h_act_prev,a_act_prev)
+    # cat(new_state,"This is new state","\n")
+
+    # Q_learning: update rule 
+    Q_vals[state_prev, a_act_prev] <- Q_vals[state_prev, a_act_prev] + alpha*( reward + gamma*max(Q_vals[new_state,])- Q_vals[state_prev, a_act_prev])
+
+    # Assume human chooses action probabilistically using softmax on Q values
+    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
+    #cat(probs,"\n")
+
+    # Get actual human action and compute likelihood
+    h_act <- as.character(data[t,"h_action"])
+    act_index <- match(h_act, colnames(Q_vals))
+    lik_hum[t] <- probs[[act_index]]
+
+    # Update state
+    state_prev <- new_state 
+    #}
+  }
+  if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret) || is.nan(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+
+}
+
+```
+
+```{r}
+# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
+# Q_learn_states(c(0.1,0.1), data, "-2loglik")
+
+QL_states_modelling <- list()
+for(id in unique(dat$human_id)) {
+  QL_states_modelling[[id]] <- list()
+  tdat <- subset(dat,human_id == id)
+  QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
+}
+
+save(QL_states_modelling,file="QL_states_modelling.RData")
+
+```
+
 ## Putting results together 

### 2019-11-15 param_model_recovery.Rmd
added tabular Q learning

@@
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+## Build function that will simulate a self tuning EWA player given parameter Lambda, and generate actions for 50 rounds
+# of each game. 
+```{r}
 
-```{r}
-# Build function that will simulate a self tuning EWA player given parameter Lambda, and generate actions for 50 rounds
-# of each game. 
 # NOTE : haven't introduced noise in either human or computer actions.
@@
 
+## Generate 100 datasets, one for each lambda and fit the 4 models to it : NB, QL, EWA and S_EWA 
 ```{r}
@@
 EWA_self_simulation <- data.frame()
-lambdas = runif(100, 0, 10)
+lambdas = runif(100, 0, 1)
 num_rounds <- 50 
@@
 
-save(EWA_self_simulation,file="EWA_self_simulation.RData")
+save(EWA_self_simulation,file="EWA_low_lambda_simulation.RData")
 
@@
 
+## Plotting parameter recovery scatter plots and model recovery results
 ```{r}
+
 plot(EWA_self_simulation$real_lambda,EWA_self_simulation$S_EWA_infrd_lambda)
-# cor.test(EWA_self_simulation$real_lambda, EWA_self_simulation$S_EWA_infrd_lambda, method=c("pearson", "kendall", "spearman"))
+# We can evaluate the correlation between real and infered lambdas and test it for significance
+cor.test(EWA_self_simulation$real_lambda, EWA_self_simulation$S_EWA_infrd_lambda, method=c("pearson", "kendall", "spearman"))
 
-# create a table with best fitting models by condition
-table(EWA_self_simulation[, "condition"],c("random","Naive_Bayes","QL","EWA","S_EWA")[apply(EWA_self_simulation[,c("Random_2LL","NB_2LL","QL_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])
+# Model recovery: create a table with best fitting models by condition
+model_recov_results <- table(EWA_self_simulation[, "condition"],c("random","N_Bayes","QL","EWA","S_EWA")[apply(EWA_self_simulation[,c("Random_2LL","NB_2LL","QL_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])
+
+ write.csv(model_recov_results,file="model_recov_results.csv",row.names = TRUE)
+ kable(model_recov_results)
 ```

### 2019-11-18 comp_model_1019.Rmd
best models analysis

@@
 title: "opponent modelling"
-author: "Maarten Speekenbrink"
-date: "24 July 2018"
-output: html_document
+author: "Ismail Guennouni & Maarten Speekenbrink"
+date: "1 November 2019"
+output:
+  pdf_document: default
+  html_document: default
 ---
@@
 library(DEoptim)
+# library(ggpubr)
 # transform 'winner' variable in numeric score
@@
 ```{r}
-# 
-# naive_bayes_modelling <- list()
-# for(id in unique(dat$human_id)) {
-#   naive_bayes_modelling[[id]] <- list()
-#   tdat <- subset(dat,human_id == id)
 
-#   naive_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = 0.0, upper = 1.0, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE,parallelType=1))
+# Fitting a bayesiam model WITH TRANSFER of opp strat distribution between games 
+TR_bayes_modelling <- list()
+for(id in unique(dat$human_id)) {
+  TR_bayes_modelling[[id]] <- list()
+  tdat <- subset(dat,human_id == id)
+# TR_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = 0.0, upper = 1.0, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE,parallelType=1))
 
-#   naive_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-# }
-# save(naive_bayes_modelling,file="naive_bayes_modelling.RData")
+TR_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+}
 
-# Fitting a bayesiam model with No Transfer of opp strat distribution between games 
+save(TR_bayes_modelling,file="TR_bayes_modelling.RData")
+
+# Fitting a bayesiam model with NO TRANSFER of opp strat distribution between games 
 NT_bayes_modelling <- list()
@@
 
-# ```
+```
 
-# ```{r}
-# Nbayes_par_results <- data.frame()
-# for(id in unique(dat$human_id)) {
-# Nbayes_par_results <- rbind(Nbayes_par_results,
-#                        data.frame(
-#                          "id" = id,
-#                          "condition" = dat[dat$human_id==id,"condition"][1],
-#                          # Theta is the parameter governing AI stochasticity. Truth is 0.9
-#                          "theta" = naive_bayes_modelling[[id]]$par[1],
-#                          # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
-#                          "eps" = naive_bayes_modelling[[id]]$par[2]))
-# }
-# 
-# # Plotting the theta/eps scatter for all participants...
+```{r}
+Nbayes_par_results <- data.frame()
+for(id in unique(dat$human_id)) {
+Nbayes_par_results <- rbind(Nbayes_par_results,
+                       data.frame(
+                         "id" = id,
+                         "condition" = dat[dat$human_id==id,"condition"][1],
+                         # BICs 
+                         "BIC_transfer" = TR_bayes_modelling[[id]]$value + 2*log(150),
+                         "BIC_no_transfer" = NT_bayes_modelling[[id]]$value+ 2*log(150),
+                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
+                         "theta_transfer" = TR_bayes_modelling[[id]]$par[1],
+                         "theta_no_transfer" = NT_bayes_modelling[[id]]$par[1],
+                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
+                         "eps_transfer" = TR_bayes_modelling[[id]]$par[2],
+                         "eps_no_transfer" = NT_bayes_modelling[[id]]$par[2]))
+}
+
+# Plotting the theta/eps scatter for all participants...
 # plot(Nbayes_par_results$theta,Nbayes_par_results$eps,xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
@@
 # write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
-#kable(Nbayes_par_results)
+# kable(Nbayes_par_results)
 ```
@@
 ```
+
+##Q-Learning with state space consisting of last round play
+```{r}
+
+Q_learn_states <- function(par,data,return_value){
+  # beta= inverse temperature parameter in softmax choice function
+  # lambda = learning rate (one per game?)
+  # data : participant and ai choice data.
+  # return_value=c("-2loglik","likelihood_by_trial")
+  # Returns Q-values per trial and predicts choice using softmax
+  beta <- par[1]
+  alpha <- par[2]
+  #fix discount factor at 0.9 
+  gamma <- 0.9
+
+  #Define matrix of state spaces for each game 
+  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+  states_RPS <- paste0(G1$Var1,G1$Var2)
+
+  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+  states_FWG <- paste0(G2$Var1,G2$Var2)
+
+  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+  states_NUM <- paste0(G3$Var1,G3$Var2)
+
+  Q_vals_RPS = matrix(0.0,9,3)
+  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
+
+  Q_vals_FWG = matrix(0.0,9,3)
+  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
+
+  Q_vals_NUM = matrix(0.0,25,5)
+  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
+
+  lik_hum <- matrix(0.0,nrow(data))
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    if(t_game == "numbers") nopts <- 5 else nopts <- 3
+
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
+      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
+      lik_hum[t] <- 1/nopts
+      # Randomly select prev_state and actions for first round
+      state_prev  <- sample(state_vec, size = 1)
+      h_act_prev <- sample(colnames(Q_vals), size =1)
+      a_act_prev <- sample(colnames(Q_vals), size =1)
+      reward <- 0
+
+    } else {
+      # Get reward and past human action
+      reward <- as.numeric(data[t-1,"score"])
+      h_act_prev <- as.character(data[t-1,"h_action"])
+      a_act_prev <- as.character(data[t-1,"a_action"])
+    }
+    # cat(state_prev, " This is the previous state", "\n")
+    new_state <- paste0(h_act_prev,a_act_prev)
+    # cat(new_state,"This is new state","\n")
+
+    # Q_learning: update rule 
+    Q_vals[state_prev, a_act_prev] <- Q_vals[state_prev, a_act_prev] + alpha*( reward + gamma*max(Q_vals[new_state,])- Q_vals[state_prev, a_act_prev])
+
+    # Assume human chooses action probabilistically using softmax on Q values
+    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
+    #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }
+
+    # Get actual human action and compute likelihood
+    h_act <- as.character(data[t,"h_action"])
+    act_index <- match(h_act, colnames(Q_vals))
+    lik_hum[t] <- probs[[act_index]]
+
+    # Update state
+    state_prev <- new_state 
+    #}
+  }
+  if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret) || is.nan(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+
+}
+
+```
+
+## Fitting Q_learning with states
+```{r}
+# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
+# Q_learn_states(c(0.1,0.1), data, "-2loglik")
+
+QL_states_modelling <- list()
+for(id in unique(dat$human_id)) {
+  QL_states_modelling[[id]] <- list()
+  tdat <- subset(dat,human_id == id)
+  QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
+}
+
+save(QL_states_modelling,file="QL_states_modelling.RData")
+
+```
+#Notes: Q-Learning as done above is far from optimal.
+The reason is that most states are never visited during play ( anecdotal evidence, about 40-60% in RPS/FWG and 10-20% in NUM).
+This method needs a lot more rounds to start modelling players behavior correctly.
 
@@
 ##Plotting self_tuning EWA likelihood function for lambda from 0 to 100 
-
-lambdas <- seq(1,10,0.01)
-count = 0.0
-
-for(id in unique(dat$human_id)) {
-  if (count <= 15) {
-      tdat <- subset(dat,human_id == id)
-      likelihoods <- sapply(lambdas, EWA_self, tdat, "-2loglik")
-      plot(lambdas,likelihoods)
-      count <- count + 1
-  }
-}
+# 
+# lambdas <- seq(1,10,0.01)
+# count = 0.0
+# 
+# 
+# 
+# for(id in unique(dat$human_id)) {
+#   if (count <= 15) {
+#       tdat <- subset(dat,human_id == id)
+#       likelihoods <- sapply(lambdas, EWA_self, tdat, "-2loglik")
+#       plot(lambdas,likelihoods)
+#       count <- count + 1
+#   }
+# }
 
@@
 ```{r}
-cat(EWA_self_modelling[["38VxtUSv_h6RR5-tAAA2"]]$optim$bestmem)
-```
-
-## Fitting a QL with state space consisting of last round actions 
-```{r}
-
-Q_learn_states <- function(par,data,return_value){
-  # beta= inverse temperature parameter in softmax choice function
-  # lambda = learning rate (one per game?)
-  # data : participant and ai choice data.
-  # return_value=c("-2loglik","likelihood_by_trial")
-  # Returns Q-values per trial and predicts choice using softmax
-  beta <- par[1]
-  alpha <- par[2]
-  gamma <- 0.9
-
-  #Define matrix of state spaces for each game 
-  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
-  states_RPS <- paste0(G1$Var1,G1$Var2)
-
-  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
-  states_FWG <- paste0(G2$Var1,G2$Var2)
-
-  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-  states_NUM <- paste0(G3$Var1,G3$Var2)
-
-  Q_vals_RPS = matrix(0.0,9,3)
-  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
-
-  Q_vals_FWG = matrix(0.0,9,3)
-  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
-
-  Q_vals_NUM = matrix(0.0,25,5)
-  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
-
-  lik_hum <- matrix(0.0,nrow(data))
-
-  for(t in 1:nrow(data)) {
-    t_game <- data[t,"game"]
-    if(t_game == "numbers") nopts <- 5 else nopts <- 3
-
-    if(data[t,"round"] == 1) {
-      # first round is uniform prediction
-      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
-      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
-      lik_hum[t] <- 1/nopts
-      # Randomly select prev_state and actions for first round
-      state_prev  <- sample(state_vec, size = 1)
-      h_act_prev <- sample(colnames(Q_vals), size =1)
-      a_act_prev <- sample(colnames(Q_vals), size =1)
-      reward <- 0
-
-    } else {
-      # Get reward and past human action
-      reward <- as.numeric(data[t-1,"score"])
-      h_act_prev <- as.character(data[t-1,"h_action"])
-      a_act_prev <- as.character(data[t-1,"a_action"])
-    }
-    # cat(state_prev, " This is the previous state", "\n")
-    new_state <- paste0(h_act_prev,a_act_prev)
-    # cat(new_state,"This is new state","\n")
-
-    # Q_learning: update rule 
-    Q_vals[state_prev, a_act_prev] <- Q_vals[state_prev, a_act_prev] + alpha*( reward + gamma*max(Q_vals[new_state,])- Q_vals[state_prev, a_act_prev])
-
-    # Assume human chooses action probabilistically using softmax on Q values
-    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
-    #cat(probs,"\n")
-
-    # Get actual human action and compute likelihood
-    h_act <- as.character(data[t,"h_action"])
-    act_index <- match(h_act, colnames(Q_vals))
-    lik_hum[t] <- probs[[act_index]]
-
-    # Update state
-    state_prev <- new_state 
-    #}
-  }
-  if(return_value == "-2loglik") {
-    ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret) || is.nan(ret)) {
-      return(1e+300)
-    } else {
-      return(ret)
-    }
-  }
-  if(return_value == "likelihood_by_trial") return(lik_hum)
-
-}
-
-```
-
-```{r}
-# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
-# Q_learn_states(c(0.1,0.1), data, "-2loglik")
-
-QL_states_modelling <- list()
-for(id in unique(dat$human_id)) {
-  QL_states_modelling[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
-  QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
-}
-
-save(QL_states_modelling,file="QL_states_modelling.RData")
-
+# cat(EWA_self_modelling[["38VxtUSv_h6RR5-tAAA2"]]$optim$bestmem)
 ```
@@
                        data.frame(
-                         "id" = id,
+                         "ID" = id,
                          "condition" = dat[dat$human_id==id,"condition"][1],
-                         "random_BIC" = -2*(100*log(1/3) + 50*log(1/5)),
+                         "Random_BIC" = -2*(100*log(1/3) + 50*log(1/5)),
 
-                         # Naive Bayes, Theta is the parameter governing AI stochasticity. Truth is 0.9
-                         "NB_theta" = naive_bayes_modelling[[id]]$par[1],
+                         # Bayesian updating with/without transfer
+                         "Bayes_Tr_BIC" = TR_bayes_modelling[[id]]$value + 2*log(150),
+                         "Bayes_No_Tr_BIC" = NT_bayes_modelling[[id]]$value+ 2*log(150),
+                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
+                         "theta_transfer" = TR_bayes_modelling[[id]]$par[1],
+                         "theta_no_transfer" = NT_bayes_modelling[[id]]$par[1],
                          # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
-                         "NB_eps" = naive_bayes_modelling[[id]]$par[2],
-                         "NB_BIC" = naive_bayes_modelling[[id]]$value + 2*log(150),
+                         "eps_transfer" = TR_bayes_modelling[[id]]$par[2],
+                         "eps_no_transfer" = NT_bayes_modelling[[id]]$par[2],
 
                          # Q-Learning
+                         "QL_BIC" = QL_modelling[[id]]$value + 2*log(150),
                          # beta ->  inverse temperature parameter in softmax choice function
                          "QL_Beta" = QL_modelling[[id]]$par[1],
-                         # lambda -> learning rate in QL update
+                         # alpha -> learning rate in QL update
                          "QL_alpha" = QL_modelling[[id]]$par[2],
-                         "QL_BIC" = QL_modelling[[id]]$value + 2*log(150),
+
+                         # Q-learning with last round states
+                         "QL_states_BIC" = QL_states_modelling[[id]]$value + 2*log(150),
+                         # beta ->  inverse temperature parameter in softmax choice function
+                         "QL_states_Beta" = QL_states_modelling[[id]]$par[1],
+                         # alpha -> learning rate in QL update
+                         "QL_states_alpha" = QL_states_modelling[[id]]$par[2],
 
                          # Parametric EWA
+                         # Parametric EWA BIC
+                         "EWA_BIC" = EWA_modelling[[id]]$optim$bestval + 4*log(150),
+                         "EWA_2LL" = EWA_modelling[[id]]$optim$bestval,
                          # Phi is depreciation of past attractions
@@
                          "EWA_Lambda" = EWA_modelling[[id]]$optim$bestmem[4],
-                         # Parametric EWA BIC
-                         "EWA_BIC" = EWA_modelling[[id]]$optim$bestval + 4*log(150),
-                         "EWA_2LL" = EWA_modelling[[id]]$optim$bestval,
 
                          # Self-Tuning EWA (only 1 parameter)
-                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
-                         "EWA_self_Lambda" = EWA_self_modelling[[id]]$optim$bestmem[1],
                           # Parametric EWA BIC
                          "EWA_self_2LL" = EWA_self_modelling[[id]]$optim$bestval,
-                         "EWA_self_BIC" = EWA_self_modelling[[id]]$optim$bestval + 1*log(150)
+                         "EWA_self_BIC" = EWA_self_modelling[[id]]$optim$bestval + 1*log(150),
+                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
+                         "EWA_self_Lambda" = EWA_self_modelling[[id]]$optim$bestmem[1]
+
                          ))
@@
 ```
+
+## Building table of best model per participant
+```{r}
+Table_results <- table(All_results[, "condition"],c("random","Bayes Tr","Bayes No Tr","QL", "QL_states","EWA","S_EWA")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)])
+
+ write.csv(Table_results,file="Table_results.csv",row.names = TRUE)
+ kable(Table_results)
+
+```
+# Looks like most participants behavior can be explained by Bayes with or without transfer. Most others are consistent with random behavior, and only 1 qith QL and 1 with S_EWA.
+
+## Question: Can we see evidence for transfer by looking at difference in BICS btwn Bayes with and without transfer.
+Let's test correlation between difference in BICs  with early rounds score (evidence for transfer)
+```{r}
+
+Corr_Tr_model <- data.frame()
+for(id in unique(dat$human_id)) {
+  tdat <- subset(dat,human_id == id)
+  tot_score <- sum(tdat$score)
+  early_dat <- subset(tdat,between(tdat$round,2,5) & (game =="fwg" | game =="numbers") )
+  tr_score <- sum(early_dat$score)
+  id_results <- subset(All_results, ID == id)
+  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)
+
+  best_model <- c("random","Bayes Tr","Bayes No Tr","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
+  # 
+  Corr_Tr_model <- rbind(Corr_Tr_model ,
+                       data.frame(
+                         "id" = id,
+                         "condition" = dat[dat$human_id==id,"condition"][1],
+                         "BIC_diff_Bayes" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
+                         "BIC_diff_rand" =  id_results[,"Random_BIC"] - min_BIC,
+                         "Early_game_score" = tr_score,
+                         "Total_score" = tot_score,
+                         "Best_model" = best_model
+                       ))
+}
+
+# Correlate difference between BICs of Bayes transfer and no transfer with early rounds score (evidence for transfer) 
+cor.test(Corr_Tr_model$BIC_diff_Bayes,Corr_Tr_model$Early_game_score, method=c("pearson", "kendall", "spearman"))
+
+# Correlation between early game score and difference between best model and random BIC
+cor.test(Corr_Tr_model$BIC_diff_rand, Corr_Tr_model$Early_game_score, method=c("pearson", "kendall", "spearman"))
+
+```
+# Notes : There is positive and stat significant correlation between the difference between the best model BIC and random BIC on one hand, and the early scores from the target games ( FWG and NUM).
+
+## Let's compare total scores of each participant by the model of best fit, see if Bayes+transfer total scores are higher than Bayes + no transfer
+
+```{r}
+
+# ggboxplot(Corr_Tr_model, x = "model", y = "Total_score", 
+#           color = "model", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+#           order = c("Random", "No Transfer", "Transfer"),
+#           ylab = "Total Score", xlab = "Model with best fit")
+
+Corr_Tr_model$model <- recode(Corr_Tr_model$Best_model,"Bayes Tr" = "Tranfer","Bayes No Tr" = "No Transfer", .default = "Random")
+
+model <- factor(Corr_Tr_model$model)
+tapply(Corr_Tr_model$Total_score, model, mean) 
+# Compute the analysis of variance
+res.aov <- aov(Total_score ~ model, data = Corr_Tr_model)
+# Summary of the analysis
+summary(res.aov)
+
+pairwise.t.test(Corr_Tr_model$Total_score, model, p.adj = "holm")
+
+``` 
+#Scores are indeed higher but difference is not statistically significant.
+
+## What next?: Fitting models that explicitly take into account opponent strategy. LOLA? Won't work, it suffers from same issues as normal QL in that most states are not visited during game play.
+
+```{r}
+
+```

### 2019-11-19 comp_model_1019.Rmd
transfer vs best model correlation test

@@
 summary(res.aov)
+TukeyHSD(res.aov)
 
-pairwise.t.test(Corr_Tr_model$Total_score, model, p.adj = "holm")
+## What if we remove from data people who play randomly and then compare Transfer v No Transfer? 
+Bayes_only <- subset(Corr_Tr_model, model != "Random" )
+
+Bayes.aov <- aov(Early_game_score ~ model, data = Bayes_only)
+# Summary of the analysis
+summary(Bayes.aov)
+TukeyHSD(Bayes.aov)
+
+wilcox.test(Early_game_score ~ model,data = Bayes_only)
 
@@
 
-## What next?: Fitting models that explicitly take into account opponent strategy. LOLA? Won't work, it suffers from same issues as normal QL in that most states are not visited during game play.
+## What next?: Fitting models that explicitly take into account opponent strategy.
+LOLA?
+Won't work, it suffers from same issues as normal QL in that most states are not visited during game play.
+Influence model?
+Like belief lerning.
+it still has no sequential memory, still computes distribution on beliefs.
+We need to incorporate models that can mimic human memory by looking at history of play and leverage sequence prediction capabilities.
 

### 2019-11-26 comp_model_1019.Rmd
added QL_states mod recovery

@@
 ```{r}
-naive_bayes <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {
+naive_bayes <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer=TRUE) {
   # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
@@
 }
-
 save(QL_modelling,file="QL_modelling.RData")
@@
 
-Q_learn_states <- function(par,data,return_value){
-  # beta= inverse temperature parameter in softmax choice function
-  # lambda = learning rate (one per game?)
+Q_learn_states <- function(par,data,return_value,gamma){
+  # Par[1] -> beta= inverse temperature parameter in softmax choice function
+  # Par[2] -> lambda = learning rate (one per game?)
   # data : participant and ai choice data.
   # return_value=c("-2loglik","likelihood_by_trial")
+  # Gamma is discount factor for future rewards 
   # Returns Q-values per trial and predicts choice using softmax
@@
   alpha <- par[2]
-  #fix discount factor at 0.9 
-  gamma <- 0.9
+
+  #gamma <- 0.9
 
@@
 
-  Q_vals_RPS = matrix(0.0,9,3)
+  Q_vals_RPS = matrix(-0.5,9,3)
   dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
 
-  Q_vals_FWG = matrix(0.0,9,3)
+  Q_vals_FWG = matrix(-0.5,9,3)
   dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
 
-  Q_vals_NUM = matrix(0.0,25,5)
+  Q_vals_NUM = matrix(-0.5,25,5)
   dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
@@
       # Randomly select prev_state and actions for first round
-      state_prev  <- sample(state_vec, size = 1)
-      h_act_prev <- sample(colnames(Q_vals), size =1)
-      a_act_prev <- sample(colnames(Q_vals), size =1)
+      curr_state <- sample(state_vec, size = 1)
+      h_act <- sample(colnames(Q_vals), size =1)
+      ai_act <- sample(colnames(Q_vals), size =1)
       reward <- 0
@@
     } else {
-      # Get reward and past human action
+      # Get past human action and associated reward 
+      h_act <- as.character(data[t-1,"h_action"])
+      ai_act <- as.character(data[t-1,"a_action"])
       reward <- as.numeric(data[t-1,"score"])
-      h_act_prev <- as.character(data[t-1,"h_action"])
-      a_act_prev <- as.character(data[t-1,"a_action"])
     }
-    # cat(state_prev, " This is the previous state", "\n")
-    new_state <- paste0(h_act_prev,a_act_prev)
+    # cat(curr_state, " This is the previous state", "\n")
+    new_state <- paste0(h_act,ai_act)
     # cat(new_state,"This is new state","\n")
 
-    # Q_learning: update rule 
-    Q_vals[state_prev, a_act_prev] <- Q_vals[state_prev, a_act_prev] + alpha*( reward + gamma*max(Q_vals[new_state,])- Q_vals[state_prev, a_act_prev])
+    # Q_learning: update rule (time  = t-1)
+    Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
 
@@
     # Update state
-    state_prev <- new_state 
+    curr_state<- new_state 
     #}
@@
   tdat <- subset(dat,human_id == id)
-  QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
+  # QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
+
+   QL_states_modelling[[id]] <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))
 }
 
-save(QL_states_modelling,file="QL_states_modelling.RData")
+save(QL_states_modelling, file="QL_states_modelling.RData")
+
+# QL_states_gamma <- list()
+# for(id in unique(dat$human_id)) {
+#   QL_states_gamma[[id]] <- list()
+#   tdat <- subset(dat,human_id == id)
+#   QL_states_gamma[[id]] <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0.9, control=list(trace = FALSE,parallelType=1))
+# }
+# save(QL_states_gamma,file="QL_states_gamma.RData")
+
+```
+
+```{r}
+# OK, let's compare BICs and parameters for Gamma = 0 and Gamma = 0.9 (both for initial Q-values of -0.5)
+
+compare_QL_states <- data.frame()
+for(id in unique(dat$human_id)) {
+compare_QL_states  <- rbind(compare_QL_states ,
+                       data.frame(
+                         "id" = id,
+                         "condition" = dat[dat$human_id==id,"condition"][1],
+                         "Zero_Gamma_BIC" = QL_states_modelling[[id]]$optim$bestval + 2*log(150),
+                         "High_gamma_BIC" = QL_states_gamma[[id]]$optim$bestval + 2*log(150),
+                         "diff" = QL_states_modelling[[id]]$optim$bestval - QL_states_gamma[[id]]$optim$bestval
+                       ))
+}
 
@@
   tot_score <- sum(tdat$score)
-  early_dat <- subset(tdat,between(tdat$round,2,5) & (game =="fwg" | game =="numbers") )
+  tot_time <- sum(tdat$human_rt)
+  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
   tr_score <- sum(early_dat$score)
@@
                          "condition" = dat[dat$human_id==id,"condition"][1],
+                         "Total_time" = sum(tdat$human_rt),
                          "BIC_diff_Bayes" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
@@
 model <- factor(Corr_Tr_model$model)
+# Total score by best predictive model 
 tapply(Corr_Tr_model$Total_score, model, mean)
+
 # Compute the analysis of variance
@@
 
+# Total time by best predictive model
+tapply(Corr_Tr_model$Total_time, model, mean)
+time.aov <- aov(Total_time ~ model, data = Corr_Tr_model)
+# Summary of the analysis
+summary(time.aov)
+TukeyHSD(time.aov)
+
 ``` 

### 2019-11-26 param_model_recovery.Rmd
best models analysis
added QL_states mod recovery

@@
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+
 ## Build function that will simulate a self tuning EWA player given parameter Lambda, and generate actions for 50 rounds
@@
 
-gen_data <- function(par,num_rounds){
+gen_data_SEWA <- function(par,num_rounds){
 
@@
 
-## Generate 100 datasets, one for each lambda and fit the 4 models to it : NB, QL, EWA and S_EWA 
+```{r}
+gen_data_QL_states <- function(beta, alpha, num_rounds, gamma) {
+
+  games <- c("rps","fwg","numbers")
+  condition <- sample(c("level1","level2"),1)
+  data <- data.frame()
+
+  #Define matrix of state spaces for each game 
+  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+  states_RPS <- paste0(G1$Var1,G1$Var2)
+
+  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+  states_FWG <- paste0(G2$Var1,G2$Var2)
+
+  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+  states_NUM <- paste0(G3$Var1,G3$Var2)
+
+  # Initialize Matrix of Q-values 
+  Q_vals_RPS = matrix(-0.5,9,3)
+  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
+
+  Q_vals_FWG = matrix(-0.5,9,3)
+  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
+
+  Q_vals_NUM = matrix(-0.5,25,5)
+  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
+
+  # Build tables that give reward for human player(Row) vs ai player(column) actions. 
+  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
+
+  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
+
+  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
+  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+
+   for (t_game in games){
+      # Initiate dataframe
+      game_data <- setNames(data.frame(matrix(ncol = 6, nrow = num_rounds)), c("condition","game", "round", "h_action","a_action","score"))
+
+      # Initialize attraction vector, rewards + randomly select first actions
+      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
+      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
+      game_actions <- switch(as.character(t_game),rps=c("R", "P", "S"),fwg = c("F", "W", "G"), numbers = c("1", "2", "3", "4", "5"))
+      reward <- switch(as.character(t_game), rps=reward_RPS, fwg=reward_FWG, numbers=reward_NUM)
+      pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)
+
+      for(t in 1:num_rounds) {
+        if(t_game == "numbers") nopts <- 5 else nopts <- 3
+        game_data[t,"game"]<- t_game
+        game_data[t,"round"] <- t
+        game_data[t,"condition"] <- condition
+
+        if(t == 1) {
+          # Initialize previous state randomly. 
+          prev_state  <- sample(state_vec, size = 1)
+          # Sample huamn and ai actions in first round randomly 
+          h_act <- as.character(sample(game_actions, 1 ))
+          ai_act  <- as.character(sample(game_actions, 1 ))
+          # Get reward from first round. 
+          R <- reward[h_act, ai_act]
+
+          #Fill in table 
+          game_data[t,"h_action"] <- h_act
+          game_data[t,"a_action"] <- ai_act 
+          game_data[t,"score"] <- R
+
+        } else {
+          h_act<- as.character(game_data[t-1,"h_action"])
+          ai_act <- as.character(game_data[t-1,"a_action"])
+          R <- as.numeric(game_data[t-1,"score"])
+
+        }
+
+        # cat("round", t, "\n")
+        # cat(prev_state, " This is the previous state", "\n")
+        # cat("observed human action",h_act, "\n")
+        # cat("observed ai action",ai_act, "\n")
+
+        ###### New state is the state we get to after human plays h_actand ai plays  ai_act 
+        new_state <- paste0(h_act,ai_act)
+        ######
+        # cat(new_state,"This is new state","\n")
+        # cat("this is alpha",alpha,"\n")
+
+        # Q_learning: update rule
+        # cat("this is the Q vals",Q_vals[prev_state, h_act],"\n")
+        # cat("max Q_vals",max(Q_vals[new_state,]),"\n")
+        # cat("This is the reward", R ,"\n")
+
+        Q_vals[prev_state, h_act] <- Q_vals[prev_state, h_act] + alpha*( R + gamma*max(Q_vals[new_state,]) - Q_vals[prev_state, h_act])
+        probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
+
+        # Select human action with softmax
+        game_data[t,"h_action"] <- sample(game_actions, size=1,prob=probs)
+
+        # Update state
+        prev_state <- new_state
+
+         # Simulate opponent action and get score 
+        game_data[t,"a_action"] <- as.character(filter(pred_file_opp,human_previous == h_act & computer_previous == ai_act)[condition][1,])
+        # Calculate score 
+        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]
+
+      }# End for loop over rounds
+      data <- rbind(data,game_data)
+  }
+  # end of game for loop
+  return(data)
+
+}
+
+QL_dta <- gen_data_QL_states(5,0.5, num_rounds = 5, gamma = 0.9)
+
+```
+
+```{r}
+
+# Function to fit various models to simulated data and get table of results.
+ # Fit various models to generated data (from S_EWA type player)
+
+fit_models <- function(tdat,num_rounds =50) {
+
+  optim_S_EWA  <- DEoptim(fn=EWA_self, lower = 0.0, upper = 10.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
+
+  optim_EWA    <- DEoptim(fn=EWA_par,lower = c(0,0,0,0), upper = c(20,1,1,20), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))
+
+  #optim_QL     <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
+
+  optim_QL_states <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))
+
+  optim_NB     <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+
+  dataframe <-  data.frame(
+
+  # Get condition
+   "condition"  = as.character(tdat$condition[1]),
+
+  # Get best fit parameters and -2 Log Likelihoods for all models
+
+  # Self-tuning EWA 
+   "S_EWA_infrd_lambda" = optim_S_EWA$optim$bestmem[1],
+   "S_EWA_2LL"          = optim_S_EWA$optim$bestval,
+
+  #Parametric EWA
+    "EWA_infrd_phi"    = optim_EWA$optim$bestmem[1],
+    "EWA_infrd_delta"  = optim_EWA$optim$bestmem[2],
+    "EWA_infrd_rho"    = optim_EWA$optim$bestmem[3],
+    "EWA_infrd_lambda" = optim_EWA$optim$bestmem[4],
+    "EWA_2LL"          = optim_EWA$optim$bestval,
+
+  # Q-Learning with state as prev round
+    "QL_states_infrd_beta"   = optim_QL_states$optim$bestmem[1],
+    "QL_states_infrd_alpha"  = optim_QL_states$optim$bestmem[2],
+    "QL_states_2LL"          = optim_QL_states$optim$bestval,
+
+  # Naive Bayes (nopts-arm bandit with prior vec transfered across games)
+    "NB_infrd_theta" = optim_NB$par[1],
+    "NB_infrd_eps"   = optim_NB$par[2],
+    "NB_2LL"         = optim_NB$value,
+
+  # Random
+   "Random_2LL"     = -2*(2*num_rounds*log(1/3) + num_rounds*log(1/5))
+
+  )
+
+  return(dataframe)
+
+}
+
+sim_results <- function(beta,alpha,num_rounds,gamma) {
+  #Generate simulated data using Q_learning with previous round as state
+  tdat = gen_data_QL_states(beta,alpha, num_rounds, gamma)
+  # Fit various models to generated data 
+  df <- fit_models(tdat)
+  df$alpha <- alpha
+  df$beta <- beta
+  return(df)
+}
+
+```
+
+## Run simulation to generate datasets and return results of model fits 
+```{r}
+
+betas = runif(100,0,10)
+alphas = runif(100,0,1)
+
+pars <- as.array(mapply(c,betas, alphas, SIMPLIFY = FALSE ))
+
+list_of_dataframes <- mapply(FUN = sim_results, betas, alphas,num_rounds = 50.0, gamma = 0.0, SIMPLIFY = FALSE)
+
+QL_states_mod_recovery <- bind_rows(list_of_dataframes, .id = "column_label")
+
+save(QL_states_mod_recovery,file="QL_states_mod_recovery.RData")
+
+# a <- c(1,2,3)
+# b <- c(4,5,6)
+# df <- data.frame(
+#   "first_var" = a,
+#   "second_var" = b
+# )
+# df
+
+```
+
+## Generate 100 datasets using S_EWA agent, one for each lambda and fit the 4 models to it : NB, QL, EWA and S_EWA 
 ```{r}
@@
   EWA_self_simulation[count,"real_lambda"] <- lambda
-  tdat <- gen_data(par = lambda, num_rounds)
+  tdat <- gen_data_SEWA(par = lambda, num_rounds)
 
@@
 ```
+
 ```{r}
-
+a = c(1,2,3)
+b = c(4,5,6)
+mapply(c, a, b, SIMPLIFY=FALSE)
 ```

### 2019-11-26 comp_model_1019.Rmd
bug fixes bayes model

@@
 
-## Modelling fixed type participant
+## Modelling fixed level-k type participant
 ```{r}
@@
 
-## Fixed type: Likelihood of the different models by trial
+## Fixed level-k type: Likelihood of the different models by trial
 
@@
 
+#### New work
+
 ## Fitting simple Bayesian learning model with flat prior
@@
 
+```
+
+#Fit a bayesian model to observed human play. Prior is vector of possible level-k opponent strategies.
+```{r}
+# Function to produce best reponse to ai_action 
 best_response <- function(game,ai_action){
@@
 }
-```
-
-```{r}
-naive_bayes <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer=TRUE) {
+
+naive_bayes <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {
   # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
@@
 
+  # Load tables predicting oppponent move
+  rps_predict_opp <- read.csv("rps_predict_opp.csv")
+  fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
+  numbers_predict_opp <- read.csv("numbers_predict_opp.csv")
+
   #lik_opp is a vector that holds and update probability distribution of opp strategy given actions.
@@
     pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)
+
     if(t_game == "numbers") nopts <- 5 else nopts <- 3
@@
       # first round is uniform prediction
-      pred <- NA
+      pred_opp <- NA
       lik_hum[t] <- 1/nopts
-      if (opp_mod_transfer) {
+      if (!(opp_mod_transfer)) {
         opp_prior_vec <- rep(1/num_strat, num_strat)
@@
         k = match(strategy,opp_strategy_vec)
-        pred_opp <- as.character(filter(pred_file_opp,human_previous == as.character(data[t-1,"h_action"]) & computer_previous == as.character(data[t-1,"a_action"]))[strategy][1,])
+        pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[k]])
+
         # Given opponent action predicted, what would be human action best response for each opp strat
         br_hum[[k]] <- best_response(t_game,as.character(pred_opp))
-        #cat(as.character(br_hum[[k]]), "\n")
 
@@
       indices <- which(br_hum %in% as.character(data[t,"h_action"]))
-      #cat(as.character(indices),  "\n")
 
@@
   }
-  if(return_value == "likelihood_by_trial") return(lik_hum)
+  #if(return_value == "likelihood_by_trial") return(lik_hum)
 }
@@
   tdat <- subset(dat,human_id == id)
-# TR_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = 0.0, upper = 1.0, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE,parallelType=1))
-
-TR_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-}
-
+
+  TR_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
+
+# TR_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+}
 save(TR_bayes_modelling,file="TR_bayes_modelling.RData")
 
-# Fitting a bayesiam model with NO TRANSFER of opp strat distribution between games 
+```
+
+# Fitting a bayesian model with NO TRANSFER of opp strat distribution between games 
+```{r}
 NT_bayes_modelling <- list()
@@
 
-  # NT_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = 0.0, upper = 1.0, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE,parallelType=1))
-
-  NT_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE ,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+  NT_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
+
+#   NT_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE ,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
 }
@@
 
+# Summarise results in dataframe for both transfer and no transfer models 
 ```{r}
@@
 
-## Q-learning
+## Q-learning (Basic)
 ```{r}
@@
 
-##Q-learning fit
+## Q-learning fit
 ```{r}
@@
 
-##Q-Learning with state space consisting of last round play
+## Q-Learning with state space consisting of last round play
 ```{r}
@@
     }
+
     # cat(curr_state, " This is the previous state", "\n")
@@
                          # Q-learning with last round states
-                         "QL_states_BIC" = QL_states_modelling[[id]]$value + 2*log(150),
+                         "QL_states_BIC" = QL_states_modelling[[id]]$optim$bestval + 2*log(150),
                          # beta ->  inverse temperature parameter in softmax choice function
-                         "QL_states_Beta" = QL_states_modelling[[id]]$par[1],
+                         "QL_states_Beta" = QL_states_modelling[[id]]$optim$bestmem[1],
                          # alpha -> learning rate in QL update
-                         "QL_states_alpha" = QL_states_modelling[[id]]$par[2],
+                         "QL_states_alpha" = QL_states_modelling[[id]]$optim$bestmem[2],
 
@@
   tot_time <- sum(tdat$human_rt)
-  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
+  early_dat <- subset(tdat,between(tdat$round,2,11) & (game =="fwg" | game =="numbers") )
   tr_score <- sum(early_dat$score)
@@
                          "condition" = dat[dat$human_id==id,"condition"][1],
-                         "Total_time" = sum(tdat$human_rt),
-                         "BIC_diff_Bayes" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
-                         "BIC_diff_rand" =  id_results[,"Random_BIC"] - min_BIC,
                          "Early_game_score" = tr_score,
                          "Total_score" = tot_score,
-                         "Best_model" = best_model
+                         "Best_model" = best_model,
+                         "Total_time" = sum(tdat$human_rt),
+                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
+                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
+
                        ))
 }
+```
 
 # Correlate difference between BICs of Bayes transfer and no transfer with early rounds score (evidence for transfer) 
-cor.test(Corr_Tr_model$BIC_diff_Bayes,Corr_Tr_model$Early_game_score, method=c("pearson", "kendall", "spearman"))
-
-# Correlation between early game score and difference between best model and random BIC
-cor.test(Corr_Tr_model$BIC_diff_rand, Corr_Tr_model$Early_game_score, method=c("pearson", "kendall", "spearman"))
+```{r}
+
+cor.test(Corr_Tr_model$TR_minus_NT_BIC,Corr_Tr_model$Early_game_score, method="spearman")
+
+```
+
+#Correlation between early game score and difference between best model and random BIC
+```{r}
+cor.test(Corr_Tr_model$Rand_minus_best_BIC, Corr_Tr_model$Early_game_score, method="spearman")
 
@@
 # Notes : There is positive and stat significant correlation between the difference between the best model BIC and random BIC on one hand, and the early scores from the target games ( FWG and NUM).
+What does this mean?
+It can be interpreted as a validation of early game score as good measure of how non-random play is....
 
@@
 Corr_Tr_model$model <- recode(Corr_Tr_model$Best_model,"Bayes Tr" = "Tranfer","Bayes No Tr" = "No Transfer", .default = "Random")
-
 model <- factor(Corr_Tr_model$model)
+condition <- factor(Corr_Tr_model$condition)
+
 # Total score by best predictive model 
@@
 # Compute the analysis of variance
-res.aov <- aov(Total_score ~ model, data = Corr_Tr_model)
+res.aov <- aov(Total_score ~ model + condition, data = Corr_Tr_model)
 # Summary of the analysis
@@
 TukeyHSD(res.aov)
+```
 
 ## What if we remove from data people who play randomly and then compare Transfer v No Transfer? 
+```{r}
+
 Bayes_only <- subset(Corr_Tr_model, model != "Random" )
 
-Bayes.aov <- aov(Early_game_score ~ model, data = Bayes_only)
-# Summary of the analysis
-summary(Bayes.aov)
-TukeyHSD(Bayes.aov)
-
-wilcox.test(Early_game_score ~ model,data = Bayes_only)
+group_by(Bayes_only, model) %>%
+  summarise(
+    count = n(),
+    mean = mean(Early_game_score, na.rm = TRUE),
+    sd = sd(Early_game_score, na.rm = TRUE)
+  )
+
+wilcox.test(Early_game_score ~ model, data = Bayes_only) 
+```
 
 # Total time by best predictive model
+```{r}
 tapply(Corr_Tr_model$Total_time, model, mean)
+
+wilcox.test(Early_game_score ~ model, data = Bayes_only)
+
 time.aov <- aov(Total_time ~ model, data = Corr_Tr_model)
@@
 ``` 
-#Scores are indeed higher but difference is not statistically significant.
+#Early game scores for people best modelled with a Bayesian model with transfer are indeed higher than those best modelled without transfer but difference is not statistically significant.
 

### 2019-11-26 opponent_comp_models.Rmd
bug fixes bayes model

--- 2019-11-14 param_model_recovery.Rmd
@@
 ---
-title: "Simulation_EWA"
+title: "Opponent_comp_models"
 output: html_document
@@
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
-
-```{r}
-# Build function that will simulate a self tuning EWA player given parameter Lambda, and generate actions for 50 rounds
-# of each game. 
-# NOTE : haven't introduced noise in either human or computer actions.
-
-gen_data <- function(par,num_rounds){
-
-  lambda <- par[1]
-  games <- c("rps","fwg","numbers")
-  condition <- sample(c("level1","level2"),1)
-  data <- data.frame()
-
-  # Define attraction vectors for each game 
-  A_RPS = matrix(0.0,3)
-  names(A_RPS) <- c("R","P","S")
-  A_FWG = matrix(0.0,3)
-  names(A_FWG) <- c("F","W","G")
-  A_NUM = matrix(0.0,5)
-  names(A_NUM) <- c("1","2","3","4","5")
-
-  # # Define reward matrices from the prospective of the row player (human in our case)
-  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
-
-  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
-
-  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
-  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-
-  for (t_game in games){
-      # Initiate dataframe
-      game_data <- setNames(data.frame(matrix(ncol = 6, nrow = num_rounds)), c("condition","game", "round", "h_action","a_action","score"))
-      # Initialize attraction vector, rewards + randomly select first actions
-      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
-      game_actions <- names(Att)
-      reward <- switch(as.character(t_game), rps=reward_RPS, fwg=reward_FWG, numbers=reward_NUM)
-      pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)
-
-    for(t in 1:num_rounds) {
-      if(t_game == "numbers") nopts <- 5 else nopts <- 3
-      game_data[t,"game"]<- t_game
-      game_data[t,"round"] <- t
-      game_data[t,"condition"] <- condition
-
-      if(t == 1) {
-
-        game_data[t,"h_action"] <- as.character(sample(game_actions, 1 ))
-        game_data[t,"a_action"] <- as.character(sample(game_actions, 1 ))
-        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]
-        lik_hum <- c(1/nopts)
-        N <- 1.0
-        R_t <- rep(0.0,nopts)
-        H_t <- R_t
-
-      } else {
-
-        # Get reward and past human action
-        h_act_prev <- as.character(game_data[t-1,"h_action"])
-        a_act_prev <- as.character(game_data[t-1,"a_action"])
-
-        # Estimate phi(t)
-        R_t <- as.numeric(game_actions == a_act_prev)
-        # cat("This is R(t)",R_t,"\n")
-
-        H_t <- (H_t*(t-2) + R_t)/(t-1)
-        # cat("this is H(t)",H_t,"\n")
-
-        Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
-        # cat("This is Phit(t)",Phi_t,"\t")
-
-        # Estimate vector Delta(t)
-        delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[t-1,"score"]))
-        #cat("this is delta(t)",delta_t,"\n")
-
-        for (i in 1:length(Att)) {
-          action <- as.character(game_actions[i])
-          # Attraction vector update rule 
-          Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
-        }
-        #Update the value of N 
-        N <- Phi_t*N + 1
-        #cat(Att,'\n')
-
-        # Assume human chooses action probabilistically using softmax on Attraction values
-        probs <- exp(lambda*Att)/sum(exp(lambda*Att))
-
-        # Get actual human action and compute likelihood
-        game_data[t,"h_action"] <- sample(game_actions, size=1,prob=probs)
-        act_index <- match(game_data[t,"h_action"], game_actions)
-        lik_hum[t] <- probs[[act_index]]
-
-        # Simulate opponent action and get score 
-        game_data[t,"a_action"] <- as.character(filter(pred_file_opp,human_previous == as.character(game_data[t-1,"h_action"]) & computer_previous == as.character(game_data[t-1,"a_action"]))[condition][1,])
-        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]
-
-      }
-
-    }# End for loop over rounds
-    data <- rbind(data,game_data)
-
-  }# end of game for loop
-  return(data)
-
-}
-
-```
-
-```{r}
-## Generate N lambdas in chosen interval, get the corresponding datasets of actions and scores, use Self_EWA to infer Lambda from these datasets. 
-EWA_self_simulation <- data.frame()
-lambdas = runif(100, 0, 10)
-num_rounds <- 50 
-count <- 1
-
-for(lambda in lambdas){
-
-  EWA_self_simulation[count,"real_lambda"] <- lambda
-  tdat <- gen_data(par = lambda, num_rounds)
-
-  # Fit various models to generated data (from S_EWA type player)
-  optim_S_EWA  <- DEoptim(fn=EWA_self, lower = 0.0, upper = 10.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
-
-  optim_EWA    <- DEoptim(fn=EWA_par,lower = c(0,0,0,0), upper = c(20,1,1,20), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))
-
-  optim_QL     <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
-
-  optim_NB     <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-
-  # Get condition
-  EWA_self_simulation[count, "condition"]  <- as.character(tdat$condition[1])
-
-  # Get best fit parameters and -2 Log Likelihoods for all models
-
-  # Self-tuning EWA 
-  EWA_self_simulation[count, "S_EWA_infrd_lambda"] <- optim_S_EWA$optim$bestmem[1]
-  EWA_self_simulation[count, "S_EWA_2LL"]          <- optim_S_EWA$optim$bestval
-
-  #Parametric EWA
-  EWA_self_simulation[count, "EWA_infrd_phi"]    <- optim_EWA$optim$bestmem[1]
-  EWA_self_simulation[count, "EWA_infrd_delta"]  <- optim_EWA$optim$bestmem[2]
-  EWA_self_simulation[count, "EWA_infrd_rho"]    <- optim_EWA$optim$bestmem[3]
-  EWA_self_simulation[count, "EWA_infrd_lambda"] <- optim_EWA$optim$bestmem[4]
-  EWA_self_simulation[count, "EWA_2LL"]          <- optim_EWA$optim$bestval
-
-  # Q-Learning
-  EWA_self_simulation[count, "QL_infrd_beta"]   <- optim_QL$par[1]
-  EWA_self_simulation[count, "QL_infrd_alpha"]  <- optim_QL$par[2]
-  EWA_self_simulation[count, "QL_2LL"]          <- optim_QL$value
-
-  # Naive Bayes (nopts-arm bandit with prior vec transfered across games)
-  EWA_self_simulation[count, "NB_infrd_theta"] <- optim_NB$par[1]
-  EWA_self_simulation[count, "NB_infrd_eps"]   <- optim_NB$par[2]
-  EWA_self_simulation[count, "NB_2LL"]         <- optim_NB$value
-
-  # Random
-  EWA_self_simulation[count, "Random_2LL"]     <- -2*(2*num_rounds*log(1/3) + num_rounds*log(1/5))
-
-  count <- count + 1
-}
-
-save(EWA_self_simulation,file="EWA_self_simulation.RData")
-
-```
-
-```{r}
-plot(EWA_self_simulation$real_lambda,EWA_self_simulation$S_EWA_infrd_lambda)
-# cor.test(EWA_self_simulation$real_lambda, EWA_self_simulation$S_EWA_infrd_lambda, method=c("pearson", "kendall", "spearman"))
-
-# create a table with best fitting models by condition
-table(EWA_self_simulation[, "condition"],c("random","Naive_Bayes","QL","EWA","S_EWA")[apply(EWA_self_simulation[,c("Random_2LL","NB_2LL","QL_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])
-```
+## Sequence prdiction algorithm (N-gram?)
 ```{r}

### 2019-11-26 param_model_recovery.Rmd
bug fixes bayes model

@@
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+
+### Parameter and model recovery Q-Learning with past round as state
+
+## Build function that will simulate a QL_states player given parameters alpha and beta, and generate actions for 50 rounds
+## of each game. 
+```{r}
+gen_data_QL_states <- function(beta, alpha, num_rounds, gamma) {
+
+  games <- c("rps","fwg","numbers")
+  condition <- sample(c("level1","level2"),1)
+  data <- data.frame()
+
+  #Define matrix of state spaces for each game 
+  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+  states_RPS <- paste0(G1$Var1,G1$Var2)
+
+  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+  states_FWG <- paste0(G2$Var1,G2$Var2)
+
+  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+  states_NUM <- paste0(G3$Var1,G3$Var2)
+
+  # Initialize Matrix of Q-values 
+  Q_vals_RPS = matrix(-0.5,9,3)
+  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
+
+  Q_vals_FWG = matrix(-0.5,9,3)
+  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
+
+  Q_vals_NUM = matrix(-0.5,25,5)
+  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
+
+  # Build tables that give reward for human player(Row) vs ai player(column) actions. 
+  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
+
+  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
+
+  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
+  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+
+   for (t_game in games){
+      # Initiate dataframe
+      game_data <- setNames(data.frame(matrix(ncol = 6, nrow = num_rounds)), c("condition","game", "round", "h_action","a_action","score"))
+
+      # Initialize attraction vector, rewards + randomly select first actions
+      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
+      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
+      game_actions <- switch(as.character(t_game),rps=c("R", "P", "S"),fwg = c("F", "W", "G"), numbers = c("1", "2", "3", "4", "5"))
+      reward <- switch(as.character(t_game), rps=reward_RPS, fwg=reward_FWG, numbers=reward_NUM)
+      pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)
+
+      for(t in 1:num_rounds) {
+        if(t_game == "numbers") nopts <- 5 else nopts <- 3
+        game_data[t,"game"]<- t_game
+        game_data[t,"round"] <- t
+        game_data[t,"condition"] <- condition
+
+        if(t == 1) {
+          # Initialize previous state randomly. 
+          prev_state  <- sample(state_vec, size = 1)
+          # Sample huamn and ai actions in first round randomly 
+          h_act <- as.character(sample(game_actions, 1 ))
+          ai_act  <- as.character(sample(game_actions, 1 ))
+          # Get reward from first round. 
+          R <- reward[h_act, ai_act]
+
+          #Fill in table 
+          game_data[t,"h_action"] <- h_act
+          game_data[t,"a_action"] <- ai_act 
+          game_data[t,"score"] <- R
+
+        } else {
+          h_act<- as.character(game_data[t-1,"h_action"])
+          ai_act <- as.character(game_data[t-1,"a_action"])
+          R <- as.numeric(game_data[t-1,"score"])
+
+        }
+
+        # cat("round", t, "\n")
+        # cat(prev_state, " This is the previous state", "\n")
+        # cat("observed human action",h_act, "\n")
+        # cat("observed ai action",ai_act, "\n")
+
+        ###### New state is the state we get to after human plays h_act and ai plays  ai_act 
+        new_state <- paste0(h_act,ai_act)
+        ######
+        # cat(new_state,"This is new state","\n")
+        # cat("this is alpha",alpha,"\n")
+
+        # Q_learning: update rule
+        # cat("this is the Q vals",Q_vals[prev_state, h_act],"\n")
+        # cat("max Q_vals",max(Q_vals[new_state,]),"\n")
+        # cat("This is the reward", R ,"\n")
+
+        Q_vals[prev_state, h_act] <- Q_vals[prev_state, h_act] + alpha*( R + gamma*max(Q_vals[new_state,]) - Q_vals[prev_state, h_act])
+        probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
+
+        # Select human action with softmax
+        game_data[t,"h_action"] <- sample(game_actions, size=1,prob=probs)
+
+        # Update state
+        prev_state <- new_state
+
+         # Simulate opponent action and get score 
+        game_data[t,"a_action"] <- as.character(filter(pred_file_opp,human_previous == h_act & computer_previous == ai_act)[condition][1,])
+        # Calculate score 
+        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]
+
+      }# End for loop over rounds
+      data <- rbind(data,game_data)
+  }
+  # end of game for loop
+  return(data)
+
+}
+
+# QL_dta <- gen_data_QL_states(5,0.5, num_rounds = 5, gamma = 0.9)
+
+```
+
+# Function to fit various models to simulated QL learner data and get table of results.
+```{r}
+
+fit_models <- function(tdat,num_rounds =50) {
+
+  optim_S_EWA  <- DEoptim(fn=EWA_self, lower = 0.0, upper = 10.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
+
+  optim_EWA    <- DEoptim(fn=EWA_par,lower = c(0,0,0,0), upper = c(20,1,1,20), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))
+
+  #optim_QL     <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
+
+  optim_QL_states <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))
+
+  optim_NB     <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+
+  dataframe <-  data.frame(
+
+  # Get condition
+   "condition"  = as.character(tdat$condition[1]),
+
+  # Get best fit parameters and -2 Log Likelihoods for all models
+
+  # Self-tuning EWA 
+   "S_EWA_infrd_lambda" = optim_S_EWA$optim$bestmem[1],
+   "S_EWA_2LL"          = optim_S_EWA$optim$bestval,
+
+  #Parametric EWA
+    "EWA_infrd_phi"    = optim_EWA$optim$bestmem[1],
+    "EWA_infrd_delta"  = optim_EWA$optim$bestmem[2],
+    "EWA_infrd_rho"    = optim_EWA$optim$bestmem[3],
+    "EWA_infrd_lambda" = optim_EWA$optim$bestmem[4],
+    "EWA_2LL"          = optim_EWA$optim$bestval,
+
+  # Q-Learning with state as prev round
+    "QL_states_infrd_beta"   = optim_QL_states$optim$bestmem[1],
+    "QL_states_infrd_alpha"  = optim_QL_states$optim$bestmem[2],
+    "QL_states_2LL"          = optim_QL_states$optim$bestval,
+
+  # Naive Bayes (nopts-arm bandit with prior vec transfered across games)
+    "NB_infrd_theta" = optim_NB$par[1],
+    "NB_infrd_eps"   = optim_NB$par[2],
+    "NB_2LL"         = optim_NB$value,
+
+  # Random
+   "Random_2LL"     = -2*(2*num_rounds*log(1/3) + num_rounds*log(1/5))
+
+  )
+
+  return(dataframe)
+
+}
+
+sim_results <- function(beta,alpha,num_rounds,gamma) {
+  #Generate simulated data using Q_learning with previous round as state
+  tdat = gen_data_QL_states(beta,alpha, num_rounds, gamma)
+  # Fit various models to generated data 
+  df <- fit_models(tdat)
+  df$alpha <- alpha
+  df$beta <- beta
+  return(df)
+}
+
+```
+
+## Run simulation to generate datasets and return results of model fits 
+```{r}
+
+betas = runif(100,0,10)
+alphas = runif(100,0,1)
+
+pars <- as.array(mapply(c,betas, alphas, SIMPLIFY = FALSE ))
+
+list_of_dataframes <- mapply(FUN = sim_results, betas, alphas,num_rounds = 50.0, gamma = 0.0, SIMPLIFY = FALSE)
+
+QL_states_mod_recovery <- bind_rows(list_of_dataframes, .id = "column_label")
+
+save(QL_states_mod_recovery,file="QL_states_mod_recovery.RData")
+
+```
+
+## Plot infered vs real params, summarise model fitting results and return table of best fitting models
+```{r}
+# PLot real vs infered QL_states parameters
+plot(QL_states_mod_recovery$alpha,QL_states_mod_recovery$QL_states_infrd_alpha, xlab = "True alpha", ylab = " Infered alpha")
+plot(QL_states_mod_recovery$beta,QL_states_mod_recovery$QL_states_infrd_beta, xlab = "True beta", ylab = " Infered beta")
+
+# Evaluate the correlation between real and infered alphas/lambdas and test it for significance
+cor.test(QL_states_mod_recovery$alpha,QL_states_mod_recovery$QL_states_infrd_alpha, method= "spearman")
+cor.test(QL_states_mod_recovery$beta,QL_states_mod_recovery$QL_states_infrd_beta, method= "spearman")
+
+# Model recovery: create a table with best fitting models by condition
+QL_states_model_recov <- table(QL_states_mod_recovery[, "condition"],c("random","N_Bayes","QL_states","EWA","S_EWA")[apply(QL_states_mod_recovery[,c("Random_2LL","NB_2LL","QL_states_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])
+
+ write.csv(QL_states_model_recov,file="QL_states_model_recov.csv",row.names = TRUE)
+ kable(QL_states_model_recov)
+
+```
+
+## What if we increase num rounds to 200, does that improve model recovery? 
+```{r}
+betas = runif(100,0,10)
+alphas = runif(100,0,1)
+
+pars <- as.array(mapply(c,betas, alphas, SIMPLIFY = FALSE ))
+
+list_of_dataframes200 <- mapply(FUN = sim_results, betas, alphas,num_rounds = 200.0, gamma = 0.0, SIMPLIFY = FALSE)
+
+QL_states_recov_200 <- bind_rows(list_of_dataframes200, .id = "column_label")
+
+save(QL_states_recov_200,file="QL_states_recov_200.RData")
+
+# PLot real vs infered QL_states parameters
+plot(QL_states_recov_200$alpha,QL_states_recov_200$QL_states_infrd_alpha, xlab = "True alpha", ylab = " Infered alpha")
+plot(QL_states_recov_200$beta,QL_states_recov_200$QL_states_infrd_beta, xlab = "True beta", ylab = " Infered beta")
+
+# Evaluate the correlation between real and infered alphas/lambdas and test it for significance
+cor.test(QL_states_recov_200$alpha,QL_states_recov_200$QL_states_infrd_alpha, method= "spearman")
+cor.test(QL_states_recov_200$beta,QL_states_recov_200$QL_states_infrd_beta, method= "spearman")
+
+# Model recovery: create a table with best fitting models by condition
+QL_recov200_tab <- table(QL_states_recov_200[, "condition"],c("random","N_Bayes","QL_states","EWA","S_EWA")[apply(QL_states_recov_200[,c("Random_2LL","NB_2LL","QL_states_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])
+
+ write.csv(QL_recov200_tab,file="QL_recov200_tab",row.names = TRUE)
+ kable(QL_recov200_tab)
+```
+
+### Model and parameter recovery for Self Tuning EWA model
 
@@
 
-```{r}
-gen_data_QL_states <- function(beta, alpha, num_rounds, gamma) {
-
-  games <- c("rps","fwg","numbers")
-  condition <- sample(c("level1","level2"),1)
-  data <- data.frame()
-
-  #Define matrix of state spaces for each game 
-  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
-  states_RPS <- paste0(G1$Var1,G1$Var2)
-
-  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
-  states_FWG <- paste0(G2$Var1,G2$Var2)
-
-  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-  states_NUM <- paste0(G3$Var1,G3$Var2)
-
-  # Initialize Matrix of Q-values 
-  Q_vals_RPS = matrix(-0.5,9,3)
-  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
-
-  Q_vals_FWG = matrix(-0.5,9,3)
-  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
-
-  Q_vals_NUM = matrix(-0.5,25,5)
-  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
-
-  # Build tables that give reward for human player(Row) vs ai player(column) actions. 
-  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
-
-  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
-  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
-
-  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
-  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-
-   for (t_game in games){
-      # Initiate dataframe
-      game_data <- setNames(data.frame(matrix(ncol = 6, nrow = num_rounds)), c("condition","game", "round", "h_action","a_action","score"))
-
-      # Initialize attraction vector, rewards + randomly select first actions
-      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
-      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
-      game_actions <- switch(as.character(t_game),rps=c("R", "P", "S"),fwg = c("F", "W", "G"), numbers = c("1", "2", "3", "4", "5"))
-      reward <- switch(as.character(t_game), rps=reward_RPS, fwg=reward_FWG, numbers=reward_NUM)
-      pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, numbers = numbers_predict_opp)
-
-      for(t in 1:num_rounds) {
-        if(t_game == "numbers") nopts <- 5 else nopts <- 3
-        game_data[t,"game"]<- t_game
-        game_data[t,"round"] <- t
-        game_data[t,"condition"] <- condition
-
-        if(t == 1) {
-          # Initialize previous state randomly. 
-          prev_state  <- sample(state_vec, size = 1)
-          # Sample huamn and ai actions in first round randomly 
-          h_act <- as.character(sample(game_actions, 1 ))
-          ai_act  <- as.character(sample(game_actions, 1 ))
-          # Get reward from first round. 
-          R <- reward[h_act, ai_act]
-
-          #Fill in table 
-          game_data[t,"h_action"] <- h_act
-          game_data[t,"a_action"] <- ai_act 
-          game_data[t,"score"] <- R
-
-        } else {
-          h_act<- as.character(game_data[t-1,"h_action"])
-          ai_act <- as.character(game_data[t-1,"a_action"])
-          R <- as.numeric(game_data[t-1,"score"])
-
-        }
-
-        # cat("round", t, "\n")
-        # cat(prev_state, " This is the previous state", "\n")
-        # cat("observed human action",h_act, "\n")
-        # cat("observed ai action",ai_act, "\n")
-
-        ###### New state is the state we get to after human plays h_actand ai plays  ai_act 
-        new_state <- paste0(h_act,ai_act)
-        ######
-        # cat(new_state,"This is new state","\n")
-        # cat("this is alpha",alpha,"\n")
-
-        # Q_learning: update rule
-        # cat("this is the Q vals",Q_vals[prev_state, h_act],"\n")
-        # cat("max Q_vals",max(Q_vals[new_state,]),"\n")
-        # cat("This is the reward", R ,"\n")
-
-        Q_vals[prev_state, h_act] <- Q_vals[prev_state, h_act] + alpha*( R + gamma*max(Q_vals[new_state,]) - Q_vals[prev_state, h_act])
-        probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
-
-        # Select human action with softmax
-        game_data[t,"h_action"] <- sample(game_actions, size=1,prob=probs)
-
-        # Update state
-        prev_state <- new_state
-
-         # Simulate opponent action and get score 
-        game_data[t,"a_action"] <- as.character(filter(pred_file_opp,human_previous == h_act & computer_previous == ai_act)[condition][1,])
-        # Calculate score 
-        game_data[t,"score"] <- reward[game_data[t,"h_action"], game_data[t,"a_action"]]
-
-      }# End for loop over rounds
-      data <- rbind(data,game_data)
-  }
-  # end of game for loop
-  return(data)
-
-}
-
-QL_dta <- gen_data_QL_states(5,0.5, num_rounds = 5, gamma = 0.9)
-
-```
-
-```{r}
-
-# Function to fit various models to simulated data and get table of results.
- # Fit various models to generated data (from S_EWA type player)
-
-fit_models <- function(tdat,num_rounds =50) {
-
-  optim_S_EWA  <- DEoptim(fn=EWA_self, lower = 0.0, upper = 10.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
-
-  optim_EWA    <- DEoptim(fn=EWA_par,lower = c(0,0,0,0), upper = c(20,1,1,20), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))
-
-  #optim_QL     <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
-
-  optim_QL_states <- DEoptim(fn=Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))
-
-  optim_NB     <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-
-  dataframe <-  data.frame(
-
-  # Get condition
-   "condition"  = as.character(tdat$condition[1]),
-
-  # Get best fit parameters and -2 Log Likelihoods for all models
-
-  # Self-tuning EWA 
-   "S_EWA_infrd_lambda" = optim_S_EWA$optim$bestmem[1],
-   "S_EWA_2LL"          = optim_S_EWA$optim$bestval,
-
-  #Parametric EWA
-    "EWA_infrd_phi"    = optim_EWA$optim$bestmem[1],
-    "EWA_infrd_delta"  = optim_EWA$optim$bestmem[2],
-    "EWA_infrd_rho"    = optim_EWA$optim$bestmem[3],
-    "EWA_infrd_lambda" = optim_EWA$optim$bestmem[4],
-    "EWA_2LL"          = optim_EWA$optim$bestval,
-
-  # Q-Learning with state as prev round
-    "QL_states_infrd_beta"   = optim_QL_states$optim$bestmem[1],
-    "QL_states_infrd_alpha"  = optim_QL_states$optim$bestmem[2],
-    "QL_states_2LL"          = optim_QL_states$optim$bestval,
-
-  # Naive Bayes (nopts-arm bandit with prior vec transfered across games)
-    "NB_infrd_theta" = optim_NB$par[1],
-    "NB_infrd_eps"   = optim_NB$par[2],
-    "NB_2LL"         = optim_NB$value,
-
-  # Random
-   "Random_2LL"     = -2*(2*num_rounds*log(1/3) + num_rounds*log(1/5))
-
-  )
-
-  return(dataframe)
-
-}
-
-sim_results <- function(beta,alpha,num_rounds,gamma) {
-  #Generate simulated data using Q_learning with previous round as state
-  tdat = gen_data_QL_states(beta,alpha, num_rounds, gamma)
-  # Fit various models to generated data 
-  df <- fit_models(tdat)
-  df$alpha <- alpha
-  df$beta <- beta
-  return(df)
-}
-
-```
-
-## Run simulation to generate datasets and return results of model fits 
-```{r}
-
-betas = runif(100,0,10)
-alphas = runif(100,0,1)
-
-pars <- as.array(mapply(c,betas, alphas, SIMPLIFY = FALSE ))
-
-list_of_dataframes <- mapply(FUN = sim_results, betas, alphas,num_rounds = 50.0, gamma = 0.0, SIMPLIFY = FALSE)
-
-QL_states_mod_recovery <- bind_rows(list_of_dataframes, .id = "column_label")
-
-save(QL_states_mod_recovery,file="QL_states_mod_recovery.RData")
-
-# a <- c(1,2,3)
-# b <- c(4,5,6)
-# df <- data.frame(
-#   "first_var" = a,
-#   "second_var" = b
-# )
-# df
-
-```
-
 ## Generate 100 datasets using S_EWA agent, one for each lambda and fit the 4 models to it : NB, QL, EWA and S_EWA 
@@
 EWA_self_simulation <- data.frame()
-lambdas = runif(100, 0, 1)
+lambdas = runif(100, 0, 10)
 num_rounds <- 50 
@@
 
-for(lambda in lambdas){
+for(lambda in lambdas) {
 
@@
   # Fit various models to generated data (from S_EWA type player)
-  optim_S_EWA  <- DEoptim(fn=EWA_self, lower = 0.0, upper = 10.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
+  optim_S_EWA  <- DEoptim(fn = EWA_self, lower = 0.0, upper = 10.0, data= tdat, "-2loglik", control = list(trace = FALSE,parallelType =1))
 
-  optim_EWA    <- DEoptim(fn=EWA_par,lower = c(0,0,0,0), upper = c(20,1,1,20), data=tdat,"-2loglik",control=list(trace = FALSE,parallelType=1))
+  optim_EWA    <- DEoptim(fn = EWA_par,lower = c(0,0,0,0), upper = c(20,1,1,20), data=tdat,"-2loglik",control= list(trace = FALSE,parallelType=1))
 
-  optim_QL     <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
+  # optim_QL     <- optim(c(1,0.1),fn=Q_learn,gr = NULL, data=tdat,"-2loglik", lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
 
-  optim_NB     <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+  optim_QL_states <- DEoptim(fn = Q_learn_states,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE,parallelType=1))
+
+  optim_NB     <- optim(c(0.1,0.1),fn = naive_bayes, gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", lower = c(0.01,0.01), upper = c(0.99,0.99), method ="L-BFGS-B")
 
@@
 
-  # Q-Learning
-  EWA_self_simulation[count, "QL_infrd_beta"]   <- optim_QL$par[1]
-  EWA_self_simulation[count, "QL_infrd_alpha"]  <- optim_QL$par[2]
-  EWA_self_simulation[count, "QL_2LL"]          <- optim_QL$value
+  # Q-Learning with previous round as state
+  EWA_self_simulation[count, "QL_infrd_beta"]   <- optim_QL_states$optim$bestmem[1]
+  EWA_self_simulation[count, "QL_infrd_alpha"]  <- optim_QL_states$optim$bestmem[2]
+  EWA_self_simulation[count, "QL_2LL"]          <- optim_QL_states$optim$bestval
 
@@
 
-save(EWA_self_simulation,file="EWA_low_lambda_simulation.RData")
+save(EWA_self_simulation,file="SEWA_simulation.RData")
 
@@
 # We can evaluate the correlation between real and infered lambdas and test it for significance
-cor.test(EWA_self_simulation$real_lambda, EWA_self_simulation$S_EWA_infrd_lambda, method=c("pearson", "kendall", "spearman"))
+cor.test(EWA_self_simulation$real_lambda, EWA_self_simulation$S_EWA_infrd_lambda, method=c("spearman"))
 
 # Model recovery: create a table with best fitting models by condition
-model_recov_results <- table(EWA_self_simulation[, "condition"],c("random","N_Bayes","QL","EWA","S_EWA")[apply(EWA_self_simulation[,c("Random_2LL","NB_2LL","QL_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])
+SEWA_recov_results <- table(EWA_self_simulation[, "condition"],c("random","N_Bayes","QL","EWA","S_EWA")[apply(EWA_self_simulation[,c("Random_2LL","NB_2LL","QL_2LL","EWA_2LL","S_EWA_2LL")],1,which.min)])
 
- write.csv(model_recov_results,file="model_recov_results.csv",row.names = TRUE)
- kable(model_recov_results)
+ write.csv(SEWA_recov_results,file="SEWA_recov_results.csv",row.names = TRUE)
+ kable(SEWA_recov_results)
 ```
@@
 ```{r}
-a = c(1,2,3)
-b = c(4,5,6)
-mapply(c, a, b, SIMPLIFY=FALSE)
+
 ```

### 2019-11-27 comp_model_1019.Rmd
Bayes bug fixes

@@
 library(DEoptim)
+library(optimParallel)
 # library(ggpubr)
@@
 
+data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
+naive_bayes(c(0.01,0.99),data,c("level0","level1","level2"),"-2loglik",FALSE)
 ```
@@
 
-  TR_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
-
-# TR_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+  # TR_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))
+
+  TR_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
 }
@@
 
-  NT_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
-
-#   NT_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE ,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+  # NT_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
+
+  NT_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE ,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
 }

### 2019-11-28 comp_model_1019.Rmd
updated results after fixes

@@
 library(DEoptim)
-library(optimParallel)
+#library(optimParallel)
 # library(ggpubr)
@@
 ## Fixed level-k type: Likelihood of the different models by trial
-
 This plot ks based on the three parameter versions of each strategy, and shows the average probability according to each model of participants' choices.
@@
 ## Fitting simple Bayesian learning model with flat prior
-```{r}
-
-```
 
@@
 naive_bayes <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {
-  # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
-  # Epsilone: parameter controlling noise in human choice. Probability human will deviate from its best response. In [0,1].
+
   # dat = data subset for one participant
@@
 
-  #return_value <- match.arg(return_value)
+  # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
+  # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
   theta <- par[1]
@@
       lik_hum[t] <- 1/nopts
+      ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transferreset prior to uniform)
       if (!(opp_mod_transfer)) {
@@
         k = match(strategy,opp_strategy_vec)
-        pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[k]])
+        pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])
 
@@
     # for debugging uncomment the line below
-    #cat(as.character(pred_opp),as.character(data[t,"h_action"]),lik[,t],"\n")
+    #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"\n")
   }
@@
   }
-  #if(return_value == "likelihood_by_trial") return(lik_hum)
-}
-
-data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
-naive_bayes(c(0.01,0.99),data,c("level0","level1","level2"),"-2loglik",FALSE)
-```
-
-```{r}
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+}
+
+# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
+# naive_bayes(c(0.9,0.99),data,c("level0","level1","level2"),"-2loglik",FALSE)
+```
+
+```{r}
+rps_predict_opp <- read.csv("rps_predict_opp.csv")
+red_opp <- filter(rps_predict_opp, rps_predict_opp$human_previous == "R" & rps_predict_opp$computer_previous == "S")
+
+as.character(red_opp[["level0"]])
+```
 
 # Fitting a bayesiam model WITH TRANSFER of opp strat distribution between games 
+```{r}
+
 TR_bayes_modelling <- list()
@@
 
-# Plotting the theta/eps scatter for all participants...
-# plot(Nbayes_par_results$theta,Nbayes_par_results$eps,xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
+#Plotting the theta/eps scatter for all participants...
+plot(Nbayes_par_results$theta,Nbayes_par_results$eps,xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
 # 
@@
   tot_time <- sum(tdat$human_rt)
-  early_dat <- subset(tdat,between(tdat$round,2,11) & (game =="fwg" | game =="numbers") )
+  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
   tr_score <- sum(early_dat$score)
@@
 ```
+# Histogram of best fitting models 
+```{r}
+barplot(table(Corr_Tr_model$Best_model))
+```
 # Notes : There is positive and stat significant correlation between the difference between the best model BIC and random BIC on one hand, and the early scores from the target games ( FWG and NUM).

### 2019-11-28 param_model_recovery.Rmd
updated results after fixes

@@
 
-  optim_NB     <- optim(c(0.1,0.1),fn = naive_bayes, gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", lower = c(0.01,0.01), upper = c(0.99,0.99), method ="L-BFGS-B")
+  optim_NB     <- optim(c(0.1,0.1),fn=naive_bayes, gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
 

### 2019-11-28 comp_model_1019.Rmd
plots

@@
 library(DEoptim)
-#library(optimParallel)
-# library(ggpubr)
+library(optimParallel)
+library(ggpubr)
 # transform 'winner' variable in numeric score
@@
 #Plotting the theta/eps scatter for all participants...
-plot(Nbayes_par_results$theta,Nbayes_par_results$eps,xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
+plot(Nbayes_par_results$theta_transfer,Nbayes_par_results$eps_transfer, xlab="Theta", ylab= "Epsilone",col = ifelse(as.character(Nbayes_par_results$condition) == "Level2",'red','green'))
 # 
-# write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
-# kable(Nbayes_par_results)
+write.csv(Nbayes_par_results,file="Nbayes_par_results.csv",row.names = FALSE)
 ```
@@
   tot_time <- sum(tdat$human_rt)
-  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
+  early_dat <- subset(tdat,between(tdat$round,2,11) & (game =="fwg"))
+  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
   tr_score <- sum(early_dat$score)
@@
 
-  best_model <- c("random","Bayes Tr","Bayes No Tr","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
+  best_model <- c("random","Bayes Tr","Bayes NT","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
   # 
@@
                        data.frame(
-                         "id" = id,
+                         "human_id" = id,
                          "condition" = dat[dat$human_id==id,"condition"][1],
@@
 
-Corr_Tr_model$model <- recode(Corr_Tr_model$Best_model,"Bayes Tr" = "Tranfer","Bayes No Tr" = "No Transfer", .default = "Random")
+Corr_Tr_model$model <- recode(Corr_Tr_model$Best_model,"Bayes Tr" = "Tranfer","Bayes No Tr" = "No Transfer", "QL_states" = "Q_Learning",  .default = "Random")
 model <- factor(Corr_Tr_model$model)
@@
 
-Bayes_only <- subset(Corr_Tr_model, model != "Random" )
-
-group_by(Bayes_only, model) %>%
+Non_Random_Only <- subset(Corr_Tr_model, model != "Random" )
+
+group_by(Non_Random_Only, model) %>%
   summarise(
@@
 
-wilcox.test(Early_game_score ~ model, data = Bayes_only) 
+res2 <- aov(Early_game_score ~ model, data = Non_Random_Only) 
+summary(res2)
+TukeyHSD(res2)
 ```
@@
 tapply(Corr_Tr_model$Total_time, model, mean)
-
-wilcox.test(Early_game_score ~ model, data = Bayes_only)
 

### 2019-11-28 score_plots.Rmd
plots

---
title: "Score_plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
library(dyplr)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
datalist = list()
i = 0
new_dat <- setNames(data.frame(matrix(ncol = 20, nrow = 0)), colnames(dat))
for(id in unique(dat$human_id)) {
  i <- i+1
  tdat <- subset(dat,human_id == id)
  tdat$part_num <- i
  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
  datalist[[i]] <- tdat
}

# Merge all datasets into one 
new_dat <- dplyr::bind_rows(datalist)
# or new_dat <- data.table::rbindlist(datalist)

# Add column for time t
new_dat <- new_dat %>% group_by(human_id) %>% mutate(t = row_number())

# Participant number as a factor 
# tdat$part_num <- as.factor(tdat$part_num)

# Add best fitting model per participant
new_dat <- merge(new_dat, Corr_Tr_model[, c("human_id", "Best_model")], by="human_id")
```

```{r}
ggplot(data = new_dat, aes(x = t, y=acc_sum, group = part_num)) + 
  geom_line(aes(color= Best_model))
```

```{r}
temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
dat_by_model <- temp %>% group_by(Best_model,t) %>% 
  summarize(model_acc_sum = mean(acc_sum))

ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
   geom_line(aes(color= Best_model))
```

### 2019-12-03 Experiment_2/clean_analysis.Rmd
add exp2 files

--- 2019-10-29 clean_analysis.Rmd
@@
 author: "Ismail Guennouni"
-date: "30 July 2018"
+date: "18 August 2019"
 output: html_document
@@
 ```{r}
-dat <- read.csv("data20180719.csv")
+dat <- read.csv("MyData.csv")
 ```
@@
 # transform 'winner' variable in numeric score
-dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
-# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
-dat$block <- factor(as.numeric(cut(dat$round,2)),labels =c("first half", "second half"))
+dat$score <- recode(dat$winner, human = 1, tie = 0, AI = -1)
+
+# Create a new variable stage.f as a factor for the stages 1,2 ,3 4 in game
+dat$stage.f <- factor(dat$stage, labels = c("Stage 1","Stage 2","Stage 3", "Stage 4"),levels=c(1,2,3,4))
 
 # create a new variable "game.f" as a factor variable of games
-dat$game.f <- factor(dat$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))
+dat$game.f <- factor(dat$game, labels = c("RPS","FWG","SHOOT"),levels=c("rps","fwg","shootout"))
 
@@
 dat_score <- dat %>% 
-  group_by(human_id) %>% 
+  group_by(prolific_id, condition) %>% 
       summarize(overall_score = sum(score))
-(avg_bonus <- floor(mean(abs(dat_score$overall_score))))*0.02
+dat_score$avg_bonus <- floor(dat_score$overall_score)*0.02
 
-#Group data by human_id and calculate mean score per block of each game.
-dat2 <- dat %>% 
-  group_by(human_id,condition,game,block,game.f) %>% 
-      summarize(block_score = mean(score))
+write.csv(dat_score,row.names=FALSE,file="bonus_payment.csv")
+
+#Average bonus per participant 
+bonus_to_be_paid <- mean(dat_score$avg_bonus)
+
+# check num level 1 and level 2 facing players
+group_by(dat_score, condition) %>%
+  summarise(count_conditions = n()) 
+```
+
+```{r}
+
+#Group data by human_id and calculate mean score per stage of each game.
+dat$interaction_lvl <- recode(dat$stage, "1" = 1, "2" = 1, "3" = 2, "4" = 2) %>% factor(levels = c(1,2), labels = c("first interaction", "second interaction"))
+
+# Create factor variable that determines type of opponent 
+dat$opp_type <- factor(dat$round_condition, labels=c("Level_1", "Level_2"), levels = c("Level1", "Level2"))
+
+# Create factor variable coding condition (which opponent was faced first)
+dat$condition.f <- factor(dat$condition, labels = c("lvl_1 first", "lvl_2 first"), levels = c("Level1","Level2"))
+
+#Adjust shootout score tor eflect easier game
+dat$adj_score <- recode(dat$score, ifelse(dat$game.f =="SHOOT", dat$score -0.33,dat$score))
+
+# Create summarised dataset by interaction (all of first/second  opponent interactions by game)
+dat_int <- dat %>% 
+  group_by(human_id,game.f,opp_type,interaction_lvl,condition.f) %>% 
+  summarize(int_score = mean(adj_score))
+
+# correlation between score vs levels 1 and 2
+
+dat_opps <- dat_int %>%
+  group_by(human_id, opp_type) %>%
+  summarize(opp_score = mean(int_score))
+
+data_opps_wide <- spread(dat_opps,opp_type, opp_score)
+
+ggscatter(data_opps_wide, x = "Level_1", y = "Level_2", add = "reg.line", conf.int = TRUE, cor.coef = TRUE, cor.method = "pearson",
+          xlab = "scores against Level1", ylab = "scores against Level2")
+
+# Create summarised dataset by stage
+dat_stages <- dat %>% 
+  group_by(human_id,game.f,stage.f,opp_type) %>% 
+  summarize(stage_score = mean(adj_score))
 
 # Group data by game and ID
-dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
+dat_games <- group_by(dat, human_id,game.f) %>% summarise(game_score = mean(adj_score))
 # head(dat3,6)
@@
 # Subsetting scores data by game
-rps <- subset(dat3,  game.f == "RPS",game_score)
-fwg <- subset(dat3,  game.f == "FWG",game_score)
-num <- subset(dat3,  game.f == "NUM",game_score)
+rps <- subset(dat_games,  game.f == "RPS",game_score)
+fwg <- subset(dat_games,  game.f == "FWG",game_score)
+shoot <- subset(dat_games,  game.f == "SHOOT",game_score)
 # head(rps,6)
@@
 
-group_by(dat2, game.f) %>%
+group_by(dat_int, game.f) %>%
   summarise(
-    mean = mean(block_score, na.rm = TRUE),
-    sd = sd(block_score, na.rm = TRUE)
+    mean = mean(int_score, na.rm = TRUE),
+    sd = sd(int_score, na.rm = TRUE)
   )
 
-group_by(dat2, game.f, block) %>%
+group_by(dat_int, game.f, opp_type,interaction_lvl) %>%
   summarise(
     count = n(),
-    mean = mean(block_score, na.rm = TRUE),
-    sd = sd(block_score, na.rm = TRUE)
-  )
-
-group_by(dat2, game.f, condition,block) %>%
-  summarise(
-    count = n(),
-    mean = mean(block_score, na.rm = TRUE),
-    sd = sd(block_score, na.rm = TRUE)
+    mean = mean(int_score, na.rm = TRUE),
+    sd = sd(int_score, na.rm = TRUE)
   )
@@
 
-ggboxplot(dat3, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
+#ggboxplot(dat_games, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average score per round", xlab = "Games")
 
-ggerrorplot(dat3, x = "game.f", y = "game_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
+#ggerrorplot(dat_games, x = "game.f", y = "game_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average score per round", xlab = "Games")
 
+```
+
+```{r}
 # Plot paired scores between games
-#pd <- paired(rps,fwg)
-#pd2 <- paired(fwg,num)
-#head(pd)
-#plot(pd, type = "profile")
-#plot(pd2, type = "profile")
-ggpaired(dat3, x = "game.f", y = "game_score",color = "game.f", id = "human_id", line.color = "gray", line.size = 0.4, palette = "npg")
+#ggpaired(dat3, x = "game.f", y = "game_score",color = "game.f", id = "human_id", line.color = "gray", line.size = 0.4, palette = "npg")
 
-# Plot results by game and block (for all 3 games, learning is happening) 
-ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")
+# Plot results by game and stage (for all 3 games, learning is happening) 
+#ggboxplot(dat_stages, x = "game.f", y = "stage_score", palette = c("#00AFBB", "#E7B800","#FC4E07"), order = c("RPS", "FWG","SHOOT"), fill="game.f", ylab = "Percentage score", xlab = "Games")
+```
 
-# Group data by game and ID
-dat4 <- group_by(dat2, human_id,condition,game.f) %>% summarise(game_score = mean(block_score))
+```{r}
 
-# Level 2 is harder to win against than level 1
-ggboxplot(dat2, x = "condition", y = "block_score", palette = c("#00AFBB", "#E7B800"), fill="condition",ylab = "Percentage score", xlab = "Conditions")
+# Group data by game, condition and ID
+#dat4 <- group_by(dat_block, human_id,condition,game.f) %>% summarise(game_score = mean(block_opp_score))
+#ggerrorplot(dat4, x = "game.f", y = "game_score", desc_stat = "mean_ci" , palette =c("#00AFBB","#E7B800","#FC4E07"),color = "game.f", ylab = "Game score", xlab = "Games")
 
-ggerrorplot(dat2, x = "condition", y = "block_score", desc_stat = "mean_ci" , palette = c("#00AFBB", "#E7B800"), color="condition",ylab = "Percentage score", xlab = "Conditions")
+# Facing Level 2 first is harder than facing level 1 first?
+#ggboxplot(dat2, x = "condition", y = "stage_score", palette = c("#00AFBB", "#E7B800"), fill="condition",ylab = "Percentage score", xlab = "Conditions")
 
-# Main effect of block 
-ggerrorplot(dat2, x = "block", y = "block_score", desc_stat = "mean_ci" , palette = c("#00AFBB", "#E7B800"), color="block",ylab = "Percentage score", xlab = "Block")
+#ggerrorplot(dat2, x = "condition", y = "stage_score", desc_stat = "mean_ci" , palette = c("#00AFBB", "#E7B800"), color="condition",ylab = "Percentage score", xlab = "Conditions")
+
+# Main effect of Stage
+#ggerrorplot(dat2, x = "stage", y = "stage_score", desc_stat = "mean_ci" , palette = c("blue", "red", "purple", "orange"), color="stage",ylab = "Percentage score", xlab = "stage")
 
 # Breaking it down by game (seems to be true for RPS and FWG, less so for Numbers )
-ggboxplot(dat4, x = "game.f", y = "game_score", palette = c("#00AFBB","#E7B800","#FC4E07"), fill="condition",order = c("RPS", "FWG","NUM"),ylab = "Game Score", xlab = "Conditions")
+#ggboxplot(dat4, x = "game.f", y = "game_score", palette = c("#00AFBB","#E7B800","#FC4E07"),order = c("RPS", "FWG","SHOOT"), ylab = "Game Score", xlab = "Conditions")
 
@@
 # Normality of scores 
-shapiro.test(dat3$game_score)
+shapiro.test(dat_games$game_score)
 
@@
 t.test(as.numeric(fwg$game_score), mu = 0, alternative = "two.sided")
-t.test(as.numeric(num$game_score), mu = 0, alternative = "two.sided")
+t.test(as.numeric(shoot$game_score), mu = 0, alternative = "two.sided")
 
@@
 library(afex)
-a1 <- aov_car( block_score ~ game.f*block*condition + Error(human_id/(game.f*block)), dat2)
+a1 <- aov_car(int_score ~ game.f*interaction_lvl*condition.f*opp_type + Error(human_id/(game.f*interaction_lvl*opp_type)), dat_int)
 summary(a1)
@@
 ```{r}
-#Pair waise comparison and post hoc tests for the interaction: Game * Block using lsmeans
+#Pair waise comparison and post hoc tests for the interactions
+library(lsmeans)
 
-# game score differences statistically significant?
-(ls0 <- lsmeans(a1, "game.f"))
-(lsm0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
+# game score differences statistically significant? by opponent type?
+(ls0 <- lsmeans(a1, "game.f", by = "opp_type"))
+(ls0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
 
-# Main effect of block 
-(ls01 <- lsmeans(a1, "block"))
+# Interaction effect by game for within game learning 
+(ls01 <- lsmeans(a1, "game.f", by = "interaction_lvl"))
 (lsm01 <- update(pairs(ls01, reverse = TRUE), by=NULL, adjust = "holm"))
-lsmip(a1, ~block)
+lsmip(a1, game.f ~ interaction_lvl |opp_type)
 
-# Main effect of condition
-(ls02 <- lsmeans(a1, "condition"))
-(lsm02 <- update(pairs(ls02, reverse = TRUE), by=NULL, adjust = "holm"))
+# Pairwise comparison of first halves by game ( first interaction RPS vs first interaction WFG scores....)
+(ls1 <- lsmeans(a1, "opp_type", by="game.f"))
+(lsm1 <- update(pairs(ls1, reverse = TRUE), by=NULL, adjust = "holm"))
+#plot(lsm1,by="opp_type")
 
-# Pairwise comparison of first halves by game ( first half RPS vs first half WFG scores....)
-(ls1 <- lsmeans(a1, "game.f", by="block"))
-(lsm1 <- update(pairs(ls1, reverse = TRUE), by=NULL, adjust = "holm"))
-plot(lsm1,by="block")
-lsmip(a1, game.f ~ block)
+#Pairwise comparison of each game score by block (first opponent RPS vs second opponent RPS....) + Control for family wise error:
+(ls2 <- lsmeans(a1, c("interaction_lvl","game.f"), by="opp_type"))
 
-# Pairwise comparison of each game score by block (first half RPS vs second half RPS....) + Control for family wise error:
-ls2 <- lsmeans(a1, c("block","game.f"))
-(lsm2 <- update(pairs(ls2, reverse = TRUE), by=NULL, adjust = "holm"))
-(contr2 <- contrast(ls2, list(G1H2vG2H1 = c(0,1,-1,0,0,0))))
-(contr3 <- contrast(ls2, list(G1H1vs0 = c(1,0,0,0,0,0))))
-lsmip(a1, block ~ game.f)
-lsmip(a1, ~ block * game.f)
+# Test differences  between first and second ineractions by game and opponent type
+(contr_g1_12 <- contrast(ls2, list(G1_I1vsG1_I2 = c(-1,1,0,0,0,0))))
+(contr_g2_12 <- contrast(ls2, list(G2_I1vsG2_I2 = c(0,0,-1,1,0,0))))
+(contr_g3_12 <- contrast(ls2, list(G3_I1vsG3_I2 = c(-1,1,0,0,0,0))))
+
+# Learning transfer: compare first interaction by game and type of opponent 
+(contr4 <- contrast(ls2, list(G1_I1vsG2_I1 = c(-1,0,1,0,0,0))))
+(contr5 <- contrast(ls2, list(G3_I1vsG2_I1 = c(0,0,-1,0,1,0))))
+(contr6 <- contrast(ls2, list(G3_I1vsG1_I1 = c(-1,0,0,0,1,0))))
+
+#plots
+lsmip(a1, interaction_lvl ~ game.f)
+lsmip(a1, interaction_lvl ~ game.f| opp_type)
 
 # Pairwise comparison of scores facing the two types of players by game: 
-lsc <- lsmeans(a1, "condition", by="game.f")
-(lsmc <- update(pairs(lsc), by=NULL, adjust = "holm"))
-plot(lsmc,by="game.f")
-lsmip(a1, condition ~ game.f)
+#lsc <- lsmeans(a1, "condition", by="game.f")
+#(lsmc <- update(pairs(lsc), by=NULL, adjust = "holm"))
+#plot(lsmc,by="game.f")
+#lsmip(a1, condition ~ game.f)
 
@@
 #Pair waise comparison and post hoc tests : Game by Block and Condition
+dat_s12 = subset(dat, (stage < 3 ), drop =TRUE)
+dat_S12 <- dat_s12 %>% 
+  group_by(human_id,stage,condition,game.f) %>% 
+      summarise(avg_score_12 = mean(score))
+a2 <- aov_car( avg_score_12 ~ game.f*stage*condition + Error(human_id/(game.f*stage)), dat_S12)
 
@@
 #plots
-ls4 <- lsmeans(a1, "block",c("condition","game.f"))
-ls4
-(lsm4 <- update(pairs(ls4, reverse = TRUE), by=NULL, adjust = "holm"))
+ls4 <- lsmeans(a2, "stage",c("condition","game.f"))
 
-plot(lsm4,by="game.f")
-lsmip(a1, game.f ~ block | condition)
+#(lsm4 <- update(pairs(ls4, reverse = TRUE), by=NULL, adjust = "holm"))
+#plot(lsm4,by="game.f")
+
+lsmip(a2, stage ~ game.f )
 
 # Interaction plot of game and block by condition 
-lsmip(a1, game.f ~ block | condition)
-lsmip(a1, condition ~ block * game.f)
+lsmip(a2, stage ~ game.f | condition)
+lsmip(a2, condition ~ stage * game.f)
 ```
@@
 
-(means.int <- lsmeans(a1, specs = c("game.f","block","condition")))
+(means.int <- lsmeans(a1, specs = c("game.f","stage"), by="condition"))
 
-# Transfer level1: compare H1FWG with H1RPS 
-con1  <- contrast(means.int, list(H1_G2vsH1_G1forlvl1 = c(-1,1,0,0,0,0,0,0,0,0,0,0), H1_G3vsH1_G1forlvl1=c(-1,0,1,0,0,0,0,0,0,0,0,0)))
+# Transfer level1: compare FWG_S1 and SHOOT_S1 with RPS_S1 
+con1  <- contrast(means.int, list(G1_S1vsG2_S1 = c(-1,1,0,0,0,0,0,0,0,0,0,0), G3_S1vsG1_S1=c(-1,0,1,0,0,0,0,0,0,0,0,0)))
 summary(con1, adjust = "holm")
 
+# Transfer level1: compare FWG_S2 and SHOOT_S1 with RPS_S2 
+#con2  <- contrast(means.int, list(G1_S2vsG2_S2 = c(0,0,0,-1,1,0,0,0,0,0,0,0), G3_S1vsG1_S1=c(0,0,0,-1,0,1,0,0,0,0,0,0)))
+#summary(con2, adjust = "holm")
+
 # Transfer level2: compare H1FWG with H1RPS 
-con2  <- contrast(means.int, list(H1_G2vsH1_G1forlvl2 = c(0,0,0,0,0,0,-1,1,0,0,0,0), H1_G3vsH1_G1forlvl2=c(0,0,0,0,0,0,-1,0,1,0,0,0)))
-summary(con2, adjust = "holm")
+#con2  <- contrast(means.int, list(H1_G2vsH1_G1forlvl2 = c(0,0,0,0,0,0,-1,1,0,0,0,0), #H1_G3vsH1_G1forlvl2=c(0,0,0,0,0,0,-1,0,1,0,0,0)))
+#summary(con2, adjust = "holm")
 
 # compare first half (H1) scores between level 1 and level 2 players in FWG and NUM
-con3 <- contrast(means.int, list(G1vG2forH1 = c(0,1,0,0,0,0,0,-1,0,0,0,0), G2vG3forh1=c(0,0,1,0,0,0,0,0,-1,0,0,0)))
-summary(con3, adjust ="holm")
+#con3 <- contrast(means.int, list(G1vG2forH1 = c(0,1,0,0,0,0,0,-1,0,0,0,0), G2vG3forh1=c(0,0,1,0,0,0,0,0,-1,0,0,0)))
+#summary(con3, adjust ="holm")
 
 # Within game learning harder for level2 opponent than when facing level 1 opponent? compare differences between block for each game and type
-con4 <- contrast(means.int, list(L2vL1forRPS = c(1,0,0,-1,0,0,-1,0,0,1,0,0), L2vL1forFWG=c(0,1,0,0,-1,0,0,-1,0,0,1,0), L2vL1forNUM=c(0,0,1,0,0,-1,0,0,-1,0,0,1)))
-summary(con4, adjust ="holm")
+#con4 <- contrast(means.int, list(L2vL1forRPS = c(1,0,0,-1,0,0,-1,0,0,1,0,0), L2vL1forFWG=c(0,1,0,0,-1,0,0,-1,0,0,1,0), L2vL1forNUM=c(0,0,1,0,0,-1,0,0,-1,0,0,1)))
+#summary(con4, adjust ="holm")
+
+```
+
+```{r}
+# Only looking at withing game learning (3vs 1 and 4vs 2 in each game)
+
+dat_within13 <- subset(dat_stages,(stage.f == 1 | stage.f == 3 ), drop =TRUE) %>%      
+  group_by(human_id,stage.f,condition,game.f) %>% 
+      summarise(first_int_score = mean(stage_score))
+
+a1vs3 <- aov_car( first_int_score ~ game.f*stage*condition + Error(human_id/(game.f*stage)), dat_within13)
+
+ls1_3 <- lsmeans(a1vs3, c("stage","game.f"), by = NULL)
+(lsm1_3 <- update(pairs(ls1_3, reverse = TRUE), by=NULL, adjust = "holm"))
+lsmip(a1vs3, game.f ~ stage)
+
+# Now  stage 2 vs 4
+dat_within24 <- subset(dat,(stage == 2 | stage == 4 ), drop =TRUE) %>%      
+  group_by(human_id,stage,condition,game.f,stage) %>% 
+      summarise(first_int_score = mean(score))
+
+a2vs4 <- aov_car( first_int_score ~ game.f*stage*condition + Error(human_id/(game.f*stage)), dat_within24)
+
+ls2_4 <- lsmeans(a2vs4, c("stage","game.f"), by="condition")
+lsmip(a2vs4, game.f ~ stage)
 
@@
 
-dat_26 <- subset(dat,round >1 & round <7, drop =TRUE)
+dat_26 <- subset(dat,(round >1 & round < 7) & (interaction_lvl == "first interaction" ), drop =TRUE)
+
 dat2_6 <- dat_26 %>% 
-  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
-      summarise(early_score = mean(score))
+  group_by(human_id,condition.f,game.f,opp_type,confidence,difficulty) %>% 
+      summarise(early_score = mean(adj_score))
 
@@
     )
-group_by(dat2_6, game.f,condition) %>%
+group_by(dat2_6, game.f,opp_type) %>%
   summarise(
@@
 # plot scores per game 
-ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
+ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Score", xlab = "Games")
+```
+
+```{r}
 
@@
 library(afex)
-aov_early <- aov_car(early_score ~ game.f*condition + Error(human_id/(game.f)),data=dat2_6)
+
+aov_early <- aov_car(early_score ~ game.f*opp_type*condition.f + Error(human_id/(game.f*opp_type)),data=dat2_6)
 summary(aov_early)
@@
 # including confidence 
+#ov_conf_26 <- aov_car(early_score ~ game.f*condition*difficulty + Error(human_id/(game.f)),data=dat2_6)
+#summary(aov_conf_26)
 
-aov_conf_26 <- aov_car(early_score ~ game.f*condition*difficulty + Error(human_id/(game.f)),data=dat2_6)
-summary(aov_conf_26)
-
-(ls4 <- lsmeans(aov_early, "game.f"))
+# Here we can change the null to 0.33 to check for whether early shoot higher scores are due to random play.
+(ls4 <- lsmeans(aov_early, "game.f", by="opp_type"))
 (summary(ls4, infer = c(TRUE,TRUE), null = 0,level = 0.95, adjust = "bon"))
 
-(means.int2 <- lsmeans(aov_early, specs = c("game.f","condition")))
-(trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "none",ref=c("FWG","NUM")))
+lsmip(aov_early,  opp_type ~ game.f )
+lsmip(aov_early,  opp_type ~ game.f | condition.f)
+
+```
+
+```{r}
+(means.int2 <- lsmeans(aov_early, specs = c("game.f","opp_type")))
+(trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "none",ref=c("FWG","SHOOT")))
 (contr26 <- contrast(means.int2, list(G2L1vsG2L2 = c(0,1,0,0,-1,0))))
@@
 # compare early scores in FWG for lvl 1 and lvl2 / same for NUM
-
-contrast(means.int2, list(G1vG2for26 = c(0,1,0,0,-1,0), G2vG3for26=c(0,0,1,0,0,-1)))
+contrast(means.int2, list(L1vL2fwg = c(0,1,0,0,-1,0), L1vL2shoot=c(0,0,1,0,0,-1)))
 
 # Plot interactions for early rouns, condition by game
-
-lsmip(aov_early, ~ game.f | condition )
+lsmip(aov_early, stage ~ game.f | condition )
 
 # plots overall effect by game :
-ggboxplot(dat2_6,"game.f", "early_score", fill = "game.f",palette = c("#00AFBB", "#E7B800", "#FC4E07"),order = c("RPS","FWG","NUM"))
+ggboxplot(dat2_6,"game.f", "early_score", fill = "game.f",palette = c("#00AFBB", "#E7B800", "#FC4E07"),order = c("RPS","FWG","SHOOT"))
 
@@
 lsmip(acd, conf_cen ~ condition)
+
+```
+
+```{r}
+library(dplyr)
 

### 2019-12-03 Experiment_2/Experiment_2_modelling.Rmd
create exp 2 folder
Bayesian learner exp2

--- 2019-11-26 opponent_comp_models.Rmd
@@
 ---
-title: "Opponent_comp_models"
+title: "Experiment_2_modelling"
 output: html_document
@@
 knitr::opts_chunk$set(echo = TRUE)
+
 ```
 
-## R Markdown
+```{r}
+library(tidyr)
+library(dplyr)
+library(DEoptim)
+library(optimParallel)
+library(ggpubr)
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+# dat_exp2 <- read.csv("MyData.csv")
+# 
+# # transform 'winner' variable in numeric score
+# dat_exp2$score <- recode(dat_exp2$winner, human = 1, tie = 0, AI = -1)
+# 
+# # Create a new variable stage.f as a factor for the stages 1,2 ,3 4 in game
+# dat_exp2$stage.f <- factor(dat_exp2$stage, labels = c("Stage 1","Stage 2","Stage 3", "Stage 4"),levels=c(1,2,3,4))
+# 
+# # create a new variable "game.f" as a factor variable of games
+# dat_exp2$game.f <- factor(dat_exp2$game, labels = c("RPS","FWG","SHOOT"),levels=c("rps","fwg","shootout"))
+# 
+# # recode actions to make them equal to the codes in these files
+# dat_exp2$h_action <- recode(dat_exp2$human_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G")
+# dat_exp2$a_action <- recode(dat_exp2$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G")
+# 
+# write.csv(dat_exp2, row.names=FALSE,file="data_exp2.csv")
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
 ```
 
-## Including Plots
+```{r}
+# Read in cleaned data file
+dat_exp2 <- read.csv("data_exp2.csv")
 
-You can also embed plots, for example:
+# Function to produce best reponse to ai_action in exp2
+exp2_best_response <- function(game,ai_action){
+  if (game == "rps"){
+    if (ai_action == "R") {return("P")}
+    else if (ai_action == "P") {return("S")}
+    else if (ai_action == "S") {return("R")}
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+  } else if (game == "fwg"){ 
+    if (ai_action == "F") {return("W")}
+    else if (ai_action == "W") {return("G")}
+    else if (ai_action == "G") {return("F")}
+
+  } else if (game == "shootout") {
+    if (ai_action == "left") {return("center/right")}
+    else if (ai_action == "center") {return("left/right")}
+    else if (ai_action == "right") {return("left/center")}
+    else if (ai_action == "left/right") {return("center")}
+    else if (ai_action == "left/center") {return("right")}
+    else if (ai_action == "center/right") {return("left")}
+  }
+}
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
-## Sequence prdiction algorithm (N-gram?)
 ```{r}
 
+exp2_naive_bayes <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {
+
+  # dat = data subset for one participant
+  # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
+  # return = -2logLik 
+  # or "likelihood_by_trial" vector  (for later plotting, etc)
+  # opp_mod_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise.
+
+  # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
+  # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
+  theta <- par[1]
+  eps <- par[2]
+
+  num_strat = length(opp_strategy_vec)
+
+  # Load tables predicting oppponent movel
+
+  rps_predict_opp <- read.csv("rps_predict_opp.csv")
+  fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
+  shootout_predict_opp <- read.csv("shootout_predict_opp.csv")
+
+  #lik_opp is a vector that holds and update probability distribution of opp strategy given actions.
+  lik_opp <- matrix(0.0,num_strat, nrow(data))
+  # Initiate prior vector as uniform
+  opp_prior_vec <-rep(1/num_strat, num_strat)
+
+  lik_hum <- matrix(0.0,nrow(data))
+  # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
+  br_hum <- rep(NA,num_strat)
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, shootout = shootout_predict_opp)
+    nopts <- 3
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      pred_opp <- NA
+      lik_hum[t] <- 1/nopts
+
+      ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer reset prior to uniform)#####
+      if (!(opp_mod_transfer) || data[t,"stage"] == 1) {
+        opp_prior_vec <- rep(1/num_strat, num_strat)
+
+      # we are round 1 of stage 2, keep opp vector from round 20 of stage 1  for stage 3
+      } else if (data[t,"stage"] == 2) { 
+        opp1_prior <- opp_prior_vec
+        opp_prior_vec <- rep(1/num_strat, num_strat)
+
+      # we are round 1 of stage 3, keep opp vector from round 20 of stage 2  for stage 4
+      } else if (data[t,"stage"] == 3) { 
+        opp2_prior <- opp_prior_vec
+        opp_prior_vec <- opp1_prior
+
+      # We are in round 1 of stage 4, use vector of priors from stage 2
+      }  else if (data[t,"stage"] == 4){ 
+        opp_prior_vec <- opp2_prior
+      }
+
+    # Rounds 2 to End of stage
+    } else {
+      # get prediction of opponent action from CSV files
+      for (strategy in opp_strategy_vec) {
+        k = match(strategy,opp_strategy_vec)
+        pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])
+
+        # Given opponent action predicted, what would be human action best response for each opp strat
+        br_hum[[k]] <- exp2_best_response(t_game,as.character(pred_opp))
+
+        # First we deal with easy case of unique predicted action ( multiple possible preds in shoot are separated by "/" sign)
+        if (!grepl("/",pred_opp,fixed = TRUE)) {
+           # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
+          if(as.character(data[t,"a_action"]) == pred_opp) {
+            lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
+          } else {
+            lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
+          }
+        # Here we are in shootout and opponent predicted action is a vector of two possible moves (e.g "left/center")  
+        } else {
+          if(grepl(as.character(data[t,"a_action"]), pred_opp,fixed = TRUE)) {
+            # Assume each action has likelihood of 50%
+             lik_opp[k,t] <- 0.5*(theta + (1-theta)/nopts)*opp_prior_vec[k]
+          } else {
+            #the 2 is to standardise the theta dependent probs: P(ai plays pred | opp is level k)
+            lik_opp[k,t] <- 2*((1-theta)/nopts)*opp_prior_vec[k]
+          }
+        }
+
+      # Get which opponent strategy human current actn maps to (if index = 0 then human current action is br to level-0 comp_strat...)
+      indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))
+
+      # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
+      # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
+      if(length(indices) == 0){
+        lik_hum[t] <- eps/nopts
+      # if same br action for multiple possible ai opponents, add probabilities 
+      } else {
+        lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
+      }
+    }  
+      # Standardising the probabilities and updating prior
+      lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
+      opp_prior_vec <- lik_opp[,t]
+    }
+  # for debugging uncomment the line below
+  #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"\n")
+  }
+
+  if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret) || is.nan(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+
+}
+
 ```
+
+```{r}
+
+test_data = subset(dat_exp2,human_id == "bZg1T3MNoItL6b7qAAAj")
+exp2_naive_bayes(c(0.5,0.1),test_data,c("level0","level1","level2"),"-2loglik",TRUE)
+```
+
+```{r}
+exp2_TR_bayes <- list()
+for(id in unique(dat_exp2$human_id)) {
+  exp2_TR_bayes[[id]] <- list()
+  tdat <- subset(dat_exp2,human_id == id)
+
+  # TR_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))
+
+  exp2_TR_bayes[[id]] <- optim(c(0.1,0.1),fn=exp2_naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+}
+save(exp2_TR_bayes, file="exp2_TR_bayes.RData")
+
+```
+
+```{r}
+
+exp2_NT_bayes <- list()
+for(id in unique(dat_exp2$human_id)) {
+  exp2_NT_bayes[[id]] <- list()
+  tdat <- subset(dat_exp2,human_id == id)
+
+  # exp2_NT_bayes[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
+
+  exp2_NT_bayes[[id]] <- optim(c(0.1,0.1),fn=exp2_naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+}
+
+save(exp2_NT_bayes,file="exp2_NT_bayes.RData")
+```
+
+```{r}
+cat("job done")
+```

### 2019-12-04 Experiment_2/Experiment_2_modelling.Rmd
model comparison exp2

@@
 ```
-
+## Fitting Bayesian model with transfer  
 ```{r}
@@
 
+## Fitting Bayesian model with NO trnsfer 
 ```{r}
@@
 
+## Fitting Q_learning with state space of possible last round plays 
 ```{r}
-cat("job done")
+exp2_QL_states <- function(par,data,return_value,gamma){
+  # Par[1] -> beta= inverse temperature parameter in softmax choice function
+  # Par[2] -> lambda = learning rate (one per game?)
+  # data : participant and ai choice data.
+  # return_value=c("-2loglik","likelihood_by_trial")
+  # Gamma is discount factor for future rewards 
+  # Returns Q-values per trial and predicts choice using softmax
+  beta <- par[1]
+  alpha <- par[2]
+
+  #gamma <- 0.9
+
+  #Define matrix of state spaces for each game 
+  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+  states_RPS <- paste0(G1$Var1,G1$Var2)
+
+  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+  states_FWG <- paste0(G2$Var1,G2$Var2)
+
+  G3 <- expand.grid(c("left","center","right"), c("left","center","right"))
+  states_SHOOT <- paste0(G3$Var1,G3$Var2)
+
+  Q_vals_RPS = matrix(-0.5,9,3)
+  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
+
+  Q_vals_FWG = matrix(-0.5,9,3)
+  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
+
+  Q_vals_SHOOT = matrix(-0.5,9,3)
+  dimnames(Q_vals_SHOOT) = list(states_SHOOT, c("left","center","right"))
+
+  lik_hum <- matrix(0.0,nrow(data))
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    nopts <- 3
+
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
+      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, shootout = states_SHOOT)
+      lik_hum[t] <- 1/nopts
+      # Randomly select state and previous actions for first round
+      curr_state <- sample(state_vec, size = 1)
+      h_act <- sample(colnames(Q_vals), size =1)
+      ai_act <- sample(colnames(Q_vals), size =1)
+      reward <- 0
+
+    } else {
+      # Get past human action and associated reward 
+      h_act <- as.character(data[t-1,"h_action"])
+      ai_act <- as.character(data[t-1,"a_action"])
+      reward <- as.numeric(data[t-1,"score"])
+    }
+
+    # cat(curr_state, " This is the previous state", "\n")
+    new_state <- paste0(h_act,ai_act)
+    # cat(new_state,"This is new state","\n")
+
+    # Q_learning: update rule (time  = t-1)
+    Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
+
+    # Assume human chooses action probabilistically using softmax on Q values
+    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
+    if (data[t,"round"] == 20) { cat(probs,"\n") }
+
+    # Get actual human action and compute likelihood
+    h_act <- as.character(data[t,"h_action"])
+    act_index <- match(h_act, colnames(Q_vals))
+    lik_hum[t] <- probs[[act_index]]
+
+    # Update state
+    curr_state <- new_state 
+    #}
+  }
+  if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret) || is.nan(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+
+}
+
 ```
+
+```{r}
+exp2_QL_states(c(5,0.4),test_data, "-2loglik", 0.0)
+```
+
+```{r}
+exp2_QLS_modelling <- list()
+for(id in unique(dat_exp2$human_id)) {
+  exp2_QLS_modelling[[id]] <- list()
+  tdat <- subset(dat_exp2,human_id == id)
+  # QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
+
+   exp2_QLS_modelling[[id]] <- DEoptim(fn=exp2_QL_states,lower = c(0,0), upper = c(20,1), data=tdat,"-2loglik", gamma = 0, control=list(trace = FALSE, parallelType=1))
+}
+
+save(exp2_QLS_modelling, file="exp2_QLS_modelling.RData")
+```
+
+```{r}
+exp2_EWA_self <- function(par,data,return_value){
+
+  lambda <- par[1]
+  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.
+
+  # Define attraction vectors for each game 
+  A_RPS = matrix(0.0,3)
+  names(A_RPS) <- c("R","P","S")
+  A_FWG = matrix(0.0,3)
+  names(A_FWG) <- c("F","W","G")
+  A_SHOOT = matrix(0.0,3)
+  names(A_SHOOT) <- c("left","center","right")
+
+  # # Define reward matrices from the prospective of the row player (human in our case)
+  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
+
+  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
+
+  reward_SHOOT <- t(matrix(c(-1,1,1,1,-1,1,1,1,-1),nrow=3, ncol=3))
+  dimnames(reward_SHOOT) = list(c("left","center","right"), c("left","center","right"))
+
+  # Initiate likelihood by trial vector 
+  lik_hum <- matrix(0.0,nrow(data))
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    nopts <- 3
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      Att <- switch(as.character(t_game), rps=A_RPS, fwg = A_FWG, shootout = A_SHOOT)
+      reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, shootout = reward_SHOOT)
+      game_data <- subset(data, game == t_game)
+      lik_hum[t] <- 1/nopts
+      N <- 1.0
+
+      R_t <- rep(0.0,nopts)
+      H_t <- R_t
+
+    } else {
+
+      indx <- data[t,"round"]
+      # Get reward and past human action
+      h_act_prev <- as.character(game_data[indx-1,"h_action"])
+      a_act_prev <- as.character(game_data[indx-1,"a_action"])
+
+      # Estimate phi(t)
+      R_t <- as.numeric(names(Att) == a_act_prev)
+      # cat("This is R(t)",R_t,"\n")
+
+      H_t <- (H_t*(indx-2) + R_t)/(indx-1)
+      # cat("this is H(t)",H_t,"\n")
+
+      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
+      # cat("This is Phit(t)",Phi_t,"\t")
+
+      # Estimate vector Delta(t)
+
+      delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
+      #cat("this is delta(t)",delta_t,"\n")
+
+      for (i in 1:length(Att)) {
+        action <- as.character(names(Att)[i])
+        # cat("this is current strat",action,"\n")
+        # cat("this is previous humna action",h_act_prev,"\n")
+
+        # Attraction vector update rule 
+        Att[[i]] <- (Phi_t*N*Att[[i]]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
+      }
+      #Update the value of N 
+      N <- Phi_t*N + 1
+      #cat(Att,'\n')
+
+      # Assume human chooses action probabilistically using softmax on Attraction values
+      probs <- exp(lambda*Att)/sum(exp(lambda*Att))
+
+      # Get actual human action and compute likelihood
+      h_act <- as.character(game_data[indx,"h_action"])
+      act_index <- match(h_act, names(Att))
+      lik_hum[t] <- probs[[act_index]]
+    }
+  }
+
+ if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret) || is.nan(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+}
+
+# exp2_EWA_self(1,test_data,"-2loglik")
+
+```
+
+## Fitting SEWA 
+```{r}
+
+exp2_SEWA_modelling <- list()
+for(id in unique(dat_exp2$human_id)) {
+  exp2_SEWA_modelling[[id]] <- list()
+  tdat <- subset(dat_exp2,human_id == id)
+#   exp2_SEWA_modelling[[id]] <- optim(10.0,fn=exp2_EWA_self,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
+# }
+  exp2_SEWA_modelling[[id]] <- DEoptim(fn=exp2_EWA_self, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
+}
+
+save(exp2_SEWA_modelling,file="exp2_SEWA_modelling.RData")
+```
+
+## Putting all results together 
+```{r}
+
+# Load various modelling tabeles
+
+load("exp2_TR_bayes.RData")
+load("exp2_NT_bayes.RData")
+load("exp2_QLS_modelling.RData")
+load("exp2_SEWA_modelling.RData")
+
+exp2_results <- data.frame()
+for(id in unique(dat_exp2$human_id)) {
+exp2_results <- rbind(exp2_results,
+                       data.frame(
+                         "ID" = id,
+                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
+                         "Random_BIC" = -2*(180*log(1/3)),
+
+                         # Bayesian updating with/without transfer
+                         "Bayes_Tr_BIC" = exp2_TR_bayes[[id]]$value + 2*log(180),
+                         "Bayes_No_Tr_BIC" = exp2_NT_bayes[[id]]$value+ 2*log(180),
+                         # Theta is the parameter governing AI stochasticity. Truth is 0.9
+                         "theta_transfer" = exp2_TR_bayes[[id]]$par[1],
+                         "theta_no_transfer" = exp2_NT_bayes[[id]]$par[1],
+                         # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
+                         "eps_transfer" = exp2_TR_bayes[[id]]$par[2],
+                         "eps_no_transfer" = exp2_NT_bayes[[id]]$par[2],
+
+                         # Q-learning with last round states
+                         "QL_states_BIC" = exp2_QLS_modelling[[id]]$optim$bestval + 2*log(180),
+                         # beta ->  inverse temperature parameter in softmax choice function
+                         "QL_states_Beta" = exp2_QLS_modelling[[id]]$optim$bestmem[1],
+                         # alpha -> learning rate in QL update
+                         "QL_states_alpha" = exp2_QLS_modelling[[id]]$optim$bestmem[2],
+
+                         # Self-Tuning EWA (only 1 parameter)
+                          # Parametric EWA BIC
+                         "EWA_self_2LL" = exp2_SEWA_modelling[[id]]$optim$bestval,
+                         "EWA_self_BIC" = exp2_SEWA_modelling[[id]]$optim$bestval + 1*log(180),
+                         #Lambda is a parameter of the softmax choice function (inverse Temperature)
+                         "EWA_self_Lambda" = exp2_SEWA_modelling[[id]]$optim$bestmem[1]
+
+                         ))
+}
+
+write.csv(exp2_results,file="exp2_results.csv",row.names = FALSE)
+
+```
+
+```{r}
+exp2_table_results <- table(exp2_results[, "condition"],c("random","Bayes Tr","Bayes No Tr", "QL_states","S_EWA")[apply(exp2_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC")],1,which.min)])
+
+ write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
+ kable(exp2_table_results)
+```
+```{r}
+exp2_model_comp <- data.frame()
+for(id in unique(dat_exp2$human_id)) {
+  tdat <- subset(dat_exp2,human_id == id)
+  tot_score <- sum(tdat$score)
+  tot_time <- sum(tdat$human_rt)
+  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
+  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
+  tr_score <- sum(early_dat$score)
+  id_results <- subset(exp2_results, ID == id)
+  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC")],1,min)
+
+  best_model <- c("random","Bayes Tr","Bayes NT", "QL_states","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC")],1,which.min)]
+  # 
+ exp2_model_comp <- rbind(exp2_model_comp ,
+                       data.frame(
+                         "human_id" = id,
+                         "condition" = dat_exp2[dat_exp2$human_id==id,"condition"][1],
+                         "Early_game_score" = tr_score,
+                         "Total_score" = tot_score,
+                         "Best_model" = best_model,
+                         "Total_time" = sum(tdat$human_rt),
+                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
+                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
+
+                       ))
+}
+
+write.csv(exp2_model_comp,file="exp2_model_comp.csv",row.names = FALSE)
+```
+
+# Correlate difference between BICs of Bayes transfer and no transfer with early rounds score (evidence for transfer) 
+```{r}
+
+cor.test(exp2_model_comp$TR_minus_NT_BIC, exp2_model_comp$Early_game_score, method="spearman")
+
+```
+
+#Correlation between early game score and difference between best model and random BIC
+```{r}
+cor.test(exp2_model_comp$Rand_minus_best_BIC, exp2_model_comp$Early_game_score, method="spearman")
+
+```
+
+# Histogram of best fitting models 
+```{r}
+barplot(table(exp2_model_comp$Best_model))
+```
+
+## Let's compare total scores of each participant by the model of best fit, see if Bayes+transfer total scores are higher than Bayes + no transfer
+
+```{r}
+
+# ggboxplot(exp2_model_comp, x = "model", y = "Total_score",
+#           color = "model", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
+#           order = c("Random", "No Transfer", "Transfer"),
+#           ylab = "Total Score", xlab = "Model with best fit")
+
+exp2_model_comp$model <- recode(exp2_model_comp$Best_model,"Bayes Tr" = "Tranfer","Bayes NT" = "No Transfer", "QL_states" = "Q_Learning",  .default = "Random")
+model <- factor(exp2_model_comp$model)
+condition <- factor(exp2_model_comp$condition)
+
+# Total score by best predictive model 
+tapply(exp2_model_comp$Total_score, model, mean)
+
+# Compute the analysis of variance
+res.aov <- aov(Total_score ~ model + condition, data = exp2_model_comp)
+# Summary of the analysis
+summary(res.aov)
+TukeyHSD(res.aov)
+```
+# Total time by best predictive model
+```{r}
+tapply(exp2_model_comp$Total_time, model, mean)
+
+time.aov <- aov(Total_time ~ model, data = exp2_model_comp)
+# Summary of the analysis
+summary(time.aov)
+TukeyHSD(time.aov)
+
+```

### 2019-12-04 Experiment_2/exp2_score_plots.Rmd
model comparison exp2

---
title: "Cumulative Score Plots Experiment 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
```

```{r}

dat_exp2 = read.csv("data_exp2.csv")

#Adjust shootout score tor eflect easier game
dat_exp2$adj_score <- ifelse(as.character(dat_exp2$game) == "shootout", dat_exp2$score - 0.333, dat_exp2$score)

# Load data comparing models BIC for each participant 
model_comp = read.csv("exp2_model_comp.csv")
```

```{r}
datalist2 = list()
i = 0

#Build empty datafrsme with same names as original data
exp2_cum_score <- setNames(data.frame(matrix(ncol = ncol(dat_exp2), nrow = 0)), colnames(dat_exp2))
for(id in unique(dat_exp2$human_id)) {
  i <- i+1
  tdat <- subset(dat_exp2,human_id == id)
  tdat$part_num <- i
  # NB : USE ADJUSTED SCORE IN SHOOTOUT
  tdat <- within(tdat, acc_sum <- cumsum(tdat$adj_score))
  datalist2[[i]] <- tdat
}

# Merge all datasets into one 
exp2_cum_score <- dplyr::bind_rows(datalist2)
# or exp2_cum_score <- data.table::rbindlist(datalist)

# Add column for time t
exp2_cum_score <- exp2_cum_score %>% group_by(human_id) %>% mutate(t = row_number())

# Participant number as a factor 
# tdat$part_num <- as.factor(tdat$part_num)

# Add best fitting model per participant
exp2_cum_score <- merge(exp2_cum_score, model_comp[, c("human_id", "Best_model")], by="human_id")
```

```{r}
ggplot(data = exp2_cum_score, aes(x = t, y=acc_sum, group = part_num)) + 
  geom_line(aes(color= Best_model))
```

```{r}
temp <- exp2_cum_score[,c("t","acc_sum","Best_model","condition","part_num")]
dat_by_model <- temp %>% group_by(Best_model,t) %>% 
  summarize(model_acc_sum = mean(acc_sum))

ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
   geom_line(aes(color= Best_model)) +
  scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))
```

### 2019-12-04 comp_model_1019.Rmd
model comparison exp2

@@
 library(ggpubr)
-# transform 'winner' variable in numeric score
-dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
-# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
-dat$block <- as.numeric(cut(dat$round,2))
+
 # create a new data.frame in a 'wide format'
@@
 
+# transform 'winner' variable in numeric score
+dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
+# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
+dat$block <- as.numeric(cut(dat$round,2))
+
 # recode actions to make them equal to the codes in these files
@@
 dat$a_action <- recode(dat$ai_action,"rock" = "R", "paper" = "P", "scissors" = "S", "fire" = "F", "water" = "W", "grass" = "G", "one" = "1", "two" = "2", "three" = "3", "four" = "4", "five" = "5")
+
+write.csv(dat,file = "exp1_data.csv", row.names = FALSE)
 
@@
 ```{r}
+load("TR_bayes_modelling.RData")
+load("NT_bayes_modelling.RData")
+load("QL_modelling.RData")
+load("QL_states_modelling.RData")
+load("EWA_modelling.RData")
+load("EWA_self_modelling.RData")
+
 All_results <- data.frame()
@@
 ```{r}
-
-Corr_Tr_model <- data.frame()
+# id_results_tst <- subset(All_results, ID == "38VxtUSv_h6RR5-tAAA2")
+```
+
+```{r}
+
+exp1_model_comp <- data.frame()
 for(id in unique(dat$human_id)) {
@@
   # 
-  Corr_Tr_model <- rbind(Corr_Tr_model ,
+  exp1_model_comp <- rbind(exp1_model_comp,
                        data.frame(
@@
 }
+
+write.csv(exp1_model_comp,file = "exp1_model_comp.csv", row.names = FALSE)
+
 ```
@@
 
-cor.test(Corr_Tr_model$TR_minus_NT_BIC,Corr_Tr_model$Early_game_score, method="spearman")
+cor.test(exp1_model_comp$TR_minus_NT_BIC,exp1_model_comp$Early_game_score, method="spearman")
 
@@
 ```{r}
-cor.test(Corr_Tr_model$Rand_minus_best_BIC, Corr_Tr_model$Early_game_score, method="spearman")
+cor.test(exp1_model_comp$Rand_minus_best_BIC, exp1_model_comp$Early_game_score, method="spearman")
 
@@
 ```{r}
-barplot(table(Corr_Tr_model$Best_model))
+barplot(table(exp1_model_comp$Best_model))
 ```
@@
 
-# ggboxplot(Corr_Tr_model, x = "model", y = "Total_score",
+# ggboxplot(exp1_model_comp, x = "model", y = "Total_score",
 #           color = "model", palette = c("#00AFBB", "#E7B800", "#FC4E07"),
@@
 
-Corr_Tr_model$model <- recode(Corr_Tr_model$Best_model,"Bayes Tr" = "Tranfer","Bayes No Tr" = "No Transfer", "QL_states" = "Q_Learning",  .default = "Random")
-model <- factor(Corr_Tr_model$model)
-condition <- factor(Corr_Tr_model$condition)
+exp1_model_comp$model <- recode(exp1_model_comp$Best_model,"Bayes Tr" = "Tranfer","Bayes No Tr" = "No Transfer", "QL_states" = "Q_Learning",  .default = "Random")
+model <- factor(exp1_model_comp$model)
+condition <- factor(exp1_model_comp$condition)
 
 # Total score by best predictive model 
-tapply(Corr_Tr_model$Total_score, model, mean)
+tapply(exp1_model_comp$Total_score, model, mean)
 
 # Compute the analysis of variance
-res.aov <- aov(Total_score ~ model + condition, data = Corr_Tr_model)
+res.aov <- aov(Total_score ~ model + condition, data = exp1_model_comp)
 # Summary of the analysis
@@
 
-Non_Random_Only <- subset(Corr_Tr_model, model != "Random" )
+Non_Random_Only <- subset(exp1_model_comp, model != "Random" )
 
@@
 ```{r}
-tapply(Corr_Tr_model$Total_time, model, mean)
-
-time.aov <- aov(Total_time ~ model, data = Corr_Tr_model)
+tapply(exp1_model_comp$Total_time, model, mean)
+
+time.aov <- aov(Total_time ~ model, data = exp1_model_comp)
 # Summary of the analysis

### 2019-12-04 score_plots.Rmd
create exp 2 folder
model comparison exp2

@@
 
-## R Markdown
+```{r}
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+exp1_dat = read.csv("exp1_data.csv")
+exp1_model_comp = read.csv("exp1_model_comp.csv")
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-library(dyplr)
-```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
-```{r}
 datalist = list()
 i = 0
-new_dat <- setNames(data.frame(matrix(ncol = 20, nrow = 0)), colnames(dat))
-for(id in unique(dat$human_id)) {
+new_dat <- setNames(data.frame(matrix(ncol = ncol(exp1_dat), nrow = 0)), colnames(exp1_dat))
+for(id in unique(exp1_dat$human_id)) {
   i <- i+1
-  tdat <- subset(dat,human_id == id)
+  tdat <- subset(exp1_dat,human_id == id)
   tdat$part_num <- i
@@
 # Add column for time t
-new_dat <- new_dat %>% group_by(human_id) %>% mutate(t = row_number())
+new_dat <- new_dat %>% group_by(exp1_dat$human_id) %>% mutate(t = row_number())
 
@@
 # Add best fitting model per participant
-new_dat <- merge(new_dat, Corr_Tr_model[, c("human_id", "Best_model")], by="human_id")
+new_dat <- merge(new_dat, exp1_model_comp[, c("human_id", "Best_model")], by="human_id")
 ```

### 2019-12-04 Experiment_2/exp2_score_plots.Rmd
plot bug fix

@@
 ggplot(data = exp2_cum_score, aes(x = t, y=acc_sum, group = part_num)) + 
-  geom_line(aes(color= Best_model))
+  geom_line(aes(color= Best_model)) +
+  scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))
 ```

### 2019-12-04 Experiment_2/exp2_score_plots.Rmd
plots library fix

@@
 library(dplyr)
+library(ggpubr)
 ```
@@
 ```{r}
+
 temp <- exp2_cum_score[,c("t","acc_sum","Best_model","condition","part_num")]

### 2019-12-05 Report/draft_report.Rnw
report init

\documentclass{article}

\begin{document}
\SweaveOpts{concordance=TRUE}

\section*{Introduction}

\section*{Methods}

\section*{Results}

\section*{Discussion}

\section*{Conclusion}

\end{document}

### 2019-12-09 Report/EasySweaveTemplate.Rnw
first draft intro

\documentclass[12pt]{article}         % the type of document and font size (default 10pt)
\usepackage[margin=1.0in]{geometry}   % sets all margins to 1in, can be changed
\usepackage{moreverb}                 % for verbatimtabinput -- LaTeX environment
\usepackage{url}                      % for \url{} command
\usepackage{amssymb}                  % for many mathematical symbols
\usepackage[pdftex]{lscape}           % for landscaped tables
\usepackage{longtable}                % for tables that break over multiple pages
\title{Easiest Sweave Template Ever}  % to specify title
\author{Your name goes here}          % to specify author(s)
\begin{document}                      % document begins here

% If .nw file contains graphs: To specify that EPS/PDF graph files are to be 
% saved to 'graphics' sub-folder
%     NOTE: 'graphics' sub-folder must exist prior to Sweave step
%\SweaveOpts{prefix.string=graphics/plot}

% If .nw file contains graphs: to modify (shrink/enlarge} size of graphics 
% file inserted
%         NOTE: can be specified/modified before any graph chunk
\setkeys{Gin}{width=1.0\textwidth}

\maketitle              % makes the title
%\tableofcontents        % inserts TOC (section, sub-section, etc numbers and titles)
%\listoftables           % inserts LOT (numbers and captions)
%\listoffigures          % inserts LOF (numbers and captions)
%                        %     NOTE: graph chunk must be wrapped with \begin{figure}, 
%                        %  \end{figure}, and \caption{}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Where everything else goes

\section{How to typeset \textsf{R} code}

If you want to see both the input and output, do this:

<<>>=
runif(10)
@

If you want to see output, but no input, do this:

<<echo = FALSE>>=
runif(10)
@

If you want to see input, but no output, do this:

<<results = hide>>=
runif(13)
@

If you want to run some \textsf{R} code but hide the input/output from the reader then you can do both at the same time:

<<echo = FALSE, results = hide>>=
x <- 2:11
y <- runif(10)
@

\bigskip   % leave some empty space (optional)

and you can double-check that it worked later (if you like)

<<keep.source = TRUE>>=
x  # use keep.source=TRUE if you want comments printed
y
@

If you want to write some \textsf{R} code but not have it evaluated at all then do this:

<<eval = FALSE>>=
# whatever you write here must be syntactically correct R code
runif(1000000000000000000000000)
@

If you would like to include a figure that's generated completely by \textsf{R} code, then you can do something like the following.

\begin{figure}
<<echo = FALSE, fig = TRUE>>=
plot(y ~ x)
@
\caption{Here is the plot we made}
\end{figure}

Sometimes we would like the output to look like \LaTeX\ output instead of \textsf{R} output.  In that case, do the following.

<<results = tex>>=
library(xtable)
xtable(summary(lm(y ~ x)), caption = "Here is the table we made")
@

\end{document}

### 2019-12-09 Report/draft_report.Rnw
first draft intro

@@
-\documentclass{article}
+\documentclass[12pt]{article}         % the type of document and font size (default 10pt)
+\usepackage[margin=1.0in]{geometry}   % sets all margins to 1in, can be changed
+\usepackage{moreverb}                 % for verbatimtabinput -- LaTeX environment
+\usepackage{url}                      % for \url{} command
+\usepackage{amssymb}                  % for many mathematical symbols
+\usepackage[pdftex]{lscape}           % for landscaped tables
+\usepackage{longtable}                % for tables that break over multiple pages
+\title{Transfer of Learned Opponent Models of ToM Agents in Zero Sum Games}  % to specify title
+\author{Ismail Guennouni, Maarten Speekenbrink}             % to specify author(s)
+\begin{document}                      % document begins here
 
-\begin{document}
+% If .nw file contains graphs: To specify that EPS/PDF graph files are to be 
+% saved to 'graphics' sub-folder
+%     NOTE: 'graphics' sub-folder must exist prior to Sweave step
+%\SweaveOpts{prefix.string=graphics/plot}
+
+% If .nw file contains graphs: to modify (shrink/enlarge} size of graphics 
+% file inserted
+%         NOTE: can be specified/modified before any graph chunk
+\setkeys{Gin}{width=1.0\textwidth}
+
+\maketitle              % makes the title
+%\tableofcontents        % inserts TOC (section, sub-section, etc numbers and titles)
+%\listoftables           % inserts LOT (numbers and captions)
+%\listoffigures          % inserts LOF (numbers and captions)
+%                        %     NOTE: graph chunk must be wrapped with \begin{figure}, 
+%                        %  \end{figure}, and \caption{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Where everything else goes
+
 \SweaveOpts{concordance=TRUE}
@@
 \section*{Introduction}
+
+Being able to successfully transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008) and is likely to be a key component towards building a general artificial intelligence.
+Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
+More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
+
+We are interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Premack & Woodruff, 1978) play a role in determining human behaviour.
+\\
+
+In order to explore learning transferin strategic settings,  it is generally useful to reduce the complexity of real life interactions by using an experimental paradigm that reduces non relevant confounding effects.
+In the context of inter-dependent decision making, the study of simple games as a means of a model of more complex interactions plays this essential role.
+More specifically, when studying learning, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
+Repeated games, in which players interact repeatedly and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are therefore used whenever we are interested in the evolution of learning.
+
+The use of games to study behavior gave rise to the field of behavioural game theory, in which computational models where developed to describe the way in which humans actually play simple economic games, as opposed to game theory which stipulates how a rational agent should normatively play.
+A major contribution that facilitated the development of behavioural game theory was the idea that humans possess a 'bounded rationality'.
+Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as solving for Nash equilibria.
+Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
+
+This concept finds its natural application in 'level-k' theory, first adopted by Stahl & wilson (1995) which posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
+At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment (Arad & Rubinstein, 2012).
+Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
+Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below and so on.
+\\
+
+The literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal actions in later games, having had experience with a similar game environment initially.
+For instance, Ho et al.
+(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games having had experience with simialr games.
+They find there is no evidence of immediate transfer ( Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
+In a series of experiments using economic signalling games, Cooper & Kagel (2003, 2004, 2008) find that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+They show that this transfer is driven by the emergence of strategically sophisticated players who are able to
+represent the strategic implications of their actions andhow changes in the opponent payoffs results in new optimal plays.
+
+In a seminal work on learning transfer between dissimilar games, Haruvy & Stahl (2012) confirmed that subjects do learn over dissimilar games and that this learning is significant.
+They also showed that players learn abstract aspects of the game that are then transfered to new settings, such as .
+This rule learning model (Stahl, 1996) was able to capture participants dynamic behavior and show that the propensity to select particular rules is perfectly transfered across games.
 

### 2019-12-09 Report/draft_report.tex
first draft intro

--- 2019-12-05 Report/draft_report.Rnw
@@
-\documentclass{article}
+\documentclass[12pt]{article}         % the type of document and font size (default 10pt)
+\usepackage[margin=1.0in]{geometry}   % sets all margins to 1in, can be changed
+\usepackage{moreverb}                 % for verbatimtabinput -- LaTeX environment
+\usepackage{url}                      % for \url{} command
+\usepackage{amssymb}                  % for many mathematical symbols
+\usepackage[pdftex]{lscape}           % for landscaped tables
+\usepackage{longtable}                % for tables that break over multiple pages
+\title{Transfer of learning about ToM opponents in zero sum games}  % to specify title
+\author{Ismail Guennouni}             % to specify author(s)
+\usepackage{Sweave}
+\begin{document}                      % document begins here
 
-\begin{document}
-\SweaveOpts{concordance=TRUE}
+% If .nw file contains graphs: To specify that EPS/PDF graph files are to be 
+% saved to 'graphics' sub-folder
+%     NOTE: 'graphics' sub-folder must exist prior to Sweave step
+%\SweaveOpts{prefix.string=graphics/plot}
+
+% If .nw file contains graphs: to modify (shrink/enlarge} size of graphics 
+% file inserted
+%         NOTE: can be specified/modified before any graph chunk
+\setkeys{Gin}{width=1.0\textwidth}
+
+\maketitle              % makes the title
+%\tableofcontents        % inserts TOC (section, sub-section, etc numbers and titles)
+%\listoftables           % inserts LOT (numbers and captions)
+%\listoffigures          % inserts LOF (numbers and captions)
+%                        %     NOTE: graph chunk must be wrapped with \begin{figure}, 
+%                        %  \end{figure}, and \caption{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Where everything else goes
+
+\input{draft_report-concordance}
 
 \section*{Introduction}
+
+We are interested in the way in which people build and use models of their opponent, when engaged in situations involving an interaction with strategic considerations.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Premack & Woodruff, 1978) play a role in determining human behaviour.
+It is generally useful to reduce the complexity of real life phenomena we want to study using a simple model of reality that allows us to probe the interesting research questions in an experimental paradigm that reduces non relevant confounding effects and the complexity of real interactions.
+In the context of inter-dependent decision making, the study of simple games as a means of a model of more complex interactions played this essential role.
+\\
+
+In order to explore learning in strategic interactions, it is essential to study repeated games in which players interact repeatedly and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990).
+These consist of a repetition of a simple one-shot game such as the prisoner's dilemma (known as the base game) either with a finite horizon (known number of repetitions at inception) or 'infinitely' (meaning the number of repetitions is very high or unknown to the players).
+This framework introduces a time dimension that is essential to learning.
+It allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
+\\
+
+The field of behavioural game theory was developed and contributed to a better understanding of the ways in which human players actually behave in experimental settings.
+A major contribution that preceded the development of behavioural game theory was the idea that humans possess a “bounded rationality”.
+Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as solving for Nash equilibria.
+Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
+This concept finds its natural application in 'level-k' theory, which posits that deviations from Nash equilibrium solutions are explained by the fact that humans have a heterogenous degree of strategic sophistication.
+At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment (Arad & Rubinstein, 2012).
+Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
+Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below and so on \\
 

### 2019-12-11 Report/article.Rmd
updated report

---
title             : "Learning to learn in a changing environment"
shorttitle        : "Learning to learn"

author: 
  - name          : "Maarten Speekenbrink"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
    email         : "m.speekenbrink@ucl.ac.uk"
  - name          : "Akhat Rakishev"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Department of Experimental Psychology, University College London"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load-packages, include = FALSE}
library("papaja")
require(knitr)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
```

```{r texreport}
texreport <- function(object,effect.name,...) UseMethod("texreport")
texreport.default <- function(object,effect.name,...) return(NULL)

texreport.summary.merMod <- function(object,effect.name,print.estimate=TRUE) {
  if(effect.name %in% rownames(object$coefficients)) {
    tab <- object$coefficients
    estimate <- tab[effect.name,"Estimate"]
    se <- tab[effect.name,"Std. Error"]
    Tval <- tab[effect.name,"t value"]
    df <- tab[effect.name,"df"]
    pval <- tab[effect.name,"Pr(>|t|)"]
    if(pval < .001) ptext <- "$p < .001$" else {
      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
      }
    }
    txt <- paste("$b = ",round(estimate,2),"$, $SE = ",round(se,2),"$, $t(",round(df,2),") = ",round(Tval,2),"$, ",sep="")
    txt <- paste(txt,ptext,sep="")
  } else {
    txt <- "error"
  }
  txt
}

texreport.summary.Anova.mlm <- function(object,effect.name,effect.size=TRUE,sphericity.correction=TRUE) {
  if(effect.name %in% rownames(object$sphericity.tests) && sphericity.correction && object$sphericity.test[effect.name,"p-value"] < .05) {
    epsilon <- object$pval.adjustments[effect.name,"HF eps"]
    pval <- object$pval.adjustments[effect.name,"Pr(>F[HF])"]
  } else {
    epsilon <- 1
    pval <- object$univariate.tests[effect.name,"Pr(>F)"]
  }
  df1 <- object$univariate.tests[effect.name,"num Df"]*epsilon
  df2 <- object$univariate.tests[effect.name,"den Df"]*epsilon
  Fval <- object$univariate.tests[effect.name,"F"]
  etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
  # generate latex output
  if(pval < .001) ptext <- "$p < .001$" else {
    if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
      ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
    }
  }
  txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
  if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
  txt <- paste(txt,ptext,sep="")
  txt
}

texreport.linearHypothesis.mlm <- function(object,effect.size=TRUE) {
  if(ncol(object$SSPH) == 1 & nrow(object$SSPH) == 1 & ncol(object$SSPE) == 1 & nrow(object$SSPE) == 1) {
    df1 <- object$df
    df2 <- object$df.residual
    Fval <- (object$SSPH/df1)/(object$SSPE/df2)
    pval <- 1-pf(Fval,object$df,object$df.residual)
    etasq <- object$SSPH/(object$SSPH + object$SSPE)
    # generate latex output
    if(pval < .001) ptext <- "$p < .001$" else {
      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
      }
    }
    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
    if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
    txt <- paste(txt,ptext,sep="")
  } else {
    txt <- "error"
  }
  txt
}

texreport.anova.lme <- function(object,effect.name,effect.size=FALSE) {
  if(effect.name %in% rownames(object)) {
    pval <- object[effect.name,"p-value"]
    if(is.null(pval)) pval <- object[effect.name,"Pr(>F)"]
    df1 <- object[effect.name,"numDF"]
    df2 <- object[effect.name,"denDF"]
    Fval <- object[effect.name,"F-value"]
    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
    # generate latex output
    if(pval < .001) ptext <- "$p < .001$" else {
      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
      }
    }
    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
    txt <- paste(txt,ptext,sep="")
    txt
  }
}

texreport.anova <- function(object,effect.name,effect.size=FALSE) {
  if(effect.name %in% rownames(object)) {
    pval <- object[effect.name,"Pr(>F)"]
    df1 <- object[effect.name,"NumDF"]
    df2 <- object[effect.name,"DenDF"]
    Fval <- object[effect.name,"F.value"]
    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
    # generate latex output
    if(pval < .001) ptext <- "$p < .001$" else {
      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
      }
    }
    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
    txt <- paste(txt,ptext,sep="")
    txt
  }
}

```

```{r read-data,warning=FALSE}
source("R/readData.R")
demo_exit <- read.csv("data/demographics_and_exit_clean.csv")
trial_data <- read.csv("data/trial_data_clean.csv")
trial_data$trial <- 1:100
```

# Introduction

## Optimal learning

If the volatility $\sigma_{\xi}(t)$ and noise $\sigma_\epsilon$ are know, optimal Bayesian learning is implemented by the Kalman filter
$$\hat{\mu}_{t+1} = \hat{\mu}_t + k_t (y_t - \hat{\mu}_{t})$$
where the "Kalman gain" is $$k_t = \frac{s_t + \sigma^2_{\xi}(t)}{s_t + \sigma^2_\xi(t) + \sigma^2_\epsilon}$$ and $s_t$ is the prior uncertainty about the mean $\mu_t$, computed recursively as $$s_t = (1-k_t)(s_{t-1} + \sigma^2_\xi(t))$$. Note that the updating of estimates $\hat{\mu}_t$ takes the same form as the well-known delta-rule, where each update is proportional to the prediction error ($y_t - \hat{\mu}_t$), with the proportionality constant $k_t$ is the learning rate, which is usually constant in the delta-rule, but time-varying in the Kalman filter and dependent on the prior uncertainty ($s_t$), and the level of volatility ($\sigma_\xi$) and environmental noise ($\sigma_\epsilon$). If both latter parameters are constant, then as $t \rightarrow \infty$, the Kalman gain converges to a constant and thus becomes equal to the constant-learning rate delta-rule. This is the steady-state Kalman filter, and provides a means to determine the optimal (constant) learning rate. The steady state is 
\begin{equation}k(t)^* = \frac{1}{2} \left(\sqrt{\frac{\sigma^4_\xi}{\sigma^4_\epsilon} + 4 \frac{\sigma^2_\xi}{\sigma^2_\epsilon}} - \frac{\sigma^2_\xi}{\sigma^2_\epsilon} \right)\end{equation}

## A particle filter

When the parameters are unknown, the optimal learning rule becomes intractible. Bayesian scheme's for estimating the parameters on-line need to rely on approximations, such as Monte Carlo Markov Chain estimation, which are impractible for on-line estimation, as for each time point, estimation would have to be started fresh. When the parameters are time-varying,

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants and design

One hundred participants (`r  sum(dat$gender[dat$trial == 1] == "Female",na.rm=TRUE)` females, `r  sum(dat$gender[dat$trial == 1] == "Male",na.rm=TRUE)` males, `r sum(is.na(dat$gender[dat$trial == 1]))` other or preferred not to say), aged between `r min(dat$age)` and `r max(dat$age)` ($M = `r round(mean(dat$age[dat$trial==1]),2)`$, $SD = `r round(sd(dat$age[dat$trial==1]),2)`$), voluntarily participated in the study. The participants were recruited from the UCL Psychology and Language Sciences subject pool or by personal invitation from the researchers. Eligible university students ($n=`r sum(dat$version[dat$trial==1] == "sona")`$) received course credit for their participation. In addition, all participants were invited to enter a draw to win one of two gift vouchers (worth £50 and £20). Participants were informed that the chance of winning the prizes was dependent on their performance during the experiment. The study was approved by the UCL ethics committe and all participants provided informed consent before participating in the experiment.

Participants were randomly allocated to either the Gradual change and Abrupt change condition. In the gradual condition, the level of volatility changed according to a sinusoid function, smoothly increasing and decreasing over time. In the abrupt condition, the level of volatility changed in a stepwise manner, being low in some blocks of trials and abruptly increasing in others.

## The Fisher Game

All participants played "The Fisher Game", an online browser-based game programmed in HTML and javascript. In the game, particpants controlled the position of a fisherman's boat in order to catch as many fish as possible. They could maximise the number of fish caught by placing the horizontal position of the boat such that the fishing rod was located at the centre of a school of fish. The further away the rod was from the centre of the school of fish, the less fish they could catch. The horizontal position of the school of fish moved from trial to trial, with the level of movement dependent on the level of volatility. On each of 100 trials participants were asked to choose a position for their boat, effectively predicting were the school of fish would be on that trial. After making their prediction, participants received information about the actual location of the school of fish and how many fish they caught. The game then proceeded to the next trial.

More formally, on each trial $t$ the location of fish $y_t$ was equal to mean fish location $\mu_t$ plus random noise $\epsilon_t$. The mean fish location $\mu_t$ was in turn equal to of the mean fish location on a previous trial, $\mu_{t-1}$,  plus random change $\zeta_t$ representing the effect of volatility:

$$\begin{aligned}
y_t &= \mu_t + \epsilon_t && & \epsilon_t &\sim \mathcal{N}(0,\sigma_\epsilon) \\
\mu_t &= \mu_{t-1} + \xi_t && & \zeta_t &\sim \mathcal{N}(0,\sigma_\xi(t))
\end{aligned}$$

The standard deviation of the noise was set to $\sigma_\epsilon = 4$ in all conditions and did not vary over time. The level of volatility, $\sigma_\xi(t)$ (the standard deviation of the changes in mean fish location) varied over time in a way that was specific to each condition. In the Gradual change condition, the volatility varied according to a sinus function:

$$ \sigma_\xi(t) = 16.5 + 13.5 \times \sin \left( -2.5 + \frac{5 \times (t - 1)}{99} \right)$$

In the Abrupt change condition, volatility varied in stepwise way:

$$\sigma_\xi(t) = \begin{cases} 3 & \text{if } t \in [1;25] \text{ or } [51;75] \\ 30 & \text{if } t \in [26;50] \text{ or } [76,;100] \end{cases} $$
In both conditions lowest volatility was equal to $\sigma_\xi(t) = 3$ and the highest volatility was equal to $\sigma_\xi(t) = 30$. Overall, in both conditions there were two low and two high volatility periods.

```{r task-structure, out.width = "85%", fig.cap = "Data generating process used in the experiment. a) schematic representation of data generation process; b) example of generated data: graphs in the top row show variation of volatility by trial, graphs in the middle row show mean fish location, graphs in the bottom row show observed fish locations."}
include_graphics("img/task_structure.eps")
```

We generated ten different random sequences of fish location per condition in advance according to the data generating process described above. This allowed to let each player observe a randomly generated set of locations, making it unlikely that the results would be dependent on the particulars of a single random sequence or that players would be able to help each other by discussing known fish locations.

The number of fish caught each trial  was then determined by dividing 0.1 by absolute prediction error (difference between response  and actual location , see the formula below). As generated data and participants’ responses were transformed to fit a 0-1 scale, the reward formula allowed players to catch very high amounts of fish in case of very accurate predictions (capped at 300). At the same time, they were still able to catch few fish even in case of very inaccurate predictions. We used this scoring method to keep players motivated, as due to the randomness in the data generating process it was impossible to exactly predict the next fish location. The scores were not used in actual analysis.

## Procedure

Participants completed the game at their own pace in a single session. After providing informed consent, participants provided demographic information (age, gender, and nationality). They then read instructions, in which they were informed about the game interface, the goal of the game, and the conditions of the prize draw.

Following the instructions the game started. On each trial, participants could see the location of the school of fish on the previous trial on the game viewport. They were also able to see all past locations of the school of fish in the "location graph" on the right of the game viewport. They then chose the horizontal position of the fishing boat through a mouseclick at any position on the game viewport. After making their choice, the boat smoothly moved to the chosen location, and the school of fish moved to the new location. Participants were then informed about the number of fish they caught on that trial.

```{r game-screen, out.width = "85%", fig.cap = "Illustration of online game interface. Yellow and blue text labels point on to respective interface elements."}
include_graphics("img/game_screen.eps")
```

Upon completion of the game participants were redirected to a post-game questionnaire were they were asked to answer the following three questions about the study: "How do you think fish locations were determined from day to day?", "What was your strategy to determine where to fish next?", and "What do you think was the aim of this study?". The answers were given in a free format and were not mandatory.

# Results

## Exclusions

Four of the 100 participants were excluded from further analysis because both the mean squared error of their choices and the mean reaction time further than two standard deviations removed from the sample mean. Of the remaining `r with(subset(trial_data,trial == 1),length(condition))` participants `r with(subset(trial_data,trial == 1),{tab <- table(condition); tab[names(tab) == "abrupt"]})` were in the abrupt and `r with(subset(trial_data,trial == 1),{tab <- table(condition); tab[names(tab) == "gradual"]})` in the gradual condition.

## Performance

Participants' average mean squared error was equal to 0.012 (SD = 0.006) and average mean reaction time to 2207.43 (SD = 949.815) milliseconds. Mean reaction times did not differ between conditions (t(72.37) = 1.17, p = .248). Mean squared error was significantly higher (t(78.09) = -4.23, p < .001) in the gradual condition (M = .015) than in the abrupt condition (M = .010).

## Empirical learning rates

According to the "delta-rule", fish locations are learned as

$$\hat{y}_{t+1} = \hat{y}_{t} + \eta(t) \left( y_{t} - \hat{y}_{t} \right)$$
where we allow the learning-rate $\eta(t) > 0$ to vary from trial to trial. Assuming that participants location choices $r_t$ are a noisy reflection of their location predictions:
$$\begin{aligned} r_t = \hat{y}_t + e_t && e_t \sim \mathcal{N}(0,\sigma_e)\end{aligned}$$
we substitute $r_t = \hat{y}_t$ and re-arrange this equation to

$$\begin{aligned} r_{t+1} - r_{t} &= \eta(t) \left( y_{t} - r_{t} \right) \\ u_t &= \eta(t) d_t \end{aligned}$$
with $u_{i,t} = (r_{i,t+1} - r_{i,t})$ representing the update in location choice from trial $t$ to trial $t+1$ and $d_{i,t}= (y_{i,t} - r_{i,t})$ the deviation between location choice and true location on trial $t$. To assess the relation between $\eta(t)$ and the optimal learning rate $\omega_t = \frac{\sigma_\xi^2(t)}{\sigma_\xi^2(t) + \sigma^2_\epsilon}$, we estimated a linear mixed-effects model

<!-- with $u_{i,t} = (r_{i,t+1} - r_{i,t})$ (the update in location choice from trial $t$ to trial $t+1$ for participant $i$) as dependent variable and $d_{i,t}= (y_{i,t} - r_{i,t})$ (the deviation between location choice and true location on trial $t$ for participant $i$) as predictor: -->

$$u_{i,t} = \left(\beta_d + b_{di} + \beta_{dC} C_i + \beta_{d\omega} \omega_{it} + b_{d\omega i} \omega_{it} \right) d_{it} + e_{t,i}$$
where $C$ is a contrast-coded predictor for condition ($C = 1$ for the abrupt, and $C = -1$ for the gradual condition), each $\beta$ term is a fixed effect, and each $b$ term a participant-wise random effect. Random intercepts and slopes were allowed to correlate. The model was estimated with the lme4 package for R [@R-lme4], and $p$-values were computed with the lmerTest package [@R-lmerTest]. 
```{r mixed-effects,cache=TRUE,echo=FALSE}
require(lmerTest)
dat <- subset(trial_data,trial < 100)
dat$omega <- .5*(sqrt(dat$volatility^4/4^4 + 4*dat$volatility^2/4^2) - dat$volatility^2/4^2) # (2*dat$volatility^2)/(2*dat$volatility^2 + 4^2)

mod0 <- lmer(update ~ condition_as_number*omega*error + (scale(omega)*error|id),data=dat)
mod1 <- lmer(update ~ error + condition_as_number:error + omega:error + condition_as_number:omega:error - 1 + (0 + error + scale(omega):error|id),data=dat)
mod1_summ <- summary(mod1)
mod0_summ <- summary(mod0)
aov_full_reduced <- anova(mod0,mod1)
```
There was a significant main effect of deviation, `r texreport(mod1_summ,"error")`. This effect of error was moderated by the steady-state learning rate, `r texreport(mod1_summ,"error:omega")` and condition, `r texreport(mod1_summ,"error:condition_as_number")`. There was also a three-way interaction between deviation, optimal learning rate, and condition, `r texreport(mod1_summ,"error:condition_as_number:omega")`.

We also estimated a linear-mixed effects model which, in addition to these effects, included fixed effects of condition ($C$), optimal learning rate ($\omega$), as well as all two-way and three-way interactions between these variables and deviation ($d$). This model also included an additional random effect for optimal learning rate ($\omega$). Comparing these two models indicated that the latter, more complex model fitted the data significantly better than the first, simpler model, $\chi^2(`r aov_full_reduced$'Chi Df'[2]`) = `r printnum(aov_full_reduced$'Chisq'[2])`$, $p = `r round(aov_full_reduced$'Pr(>Chisq)'[2],3)`$. Hence, we report the results from the full model. There was a significant main effect of deviation, `r texreport(mod0_summ,"error")`. This effect of error was moderated by the optimal learning rate, `r texreport(mod0_summ,"omega:error")` and condition, `r texreport(mod0_summ,"condition_as_number:error")`. There was also a three-way interaction between deviation, optimal learning rate, and condition, `r texreport(mod0_summ,"condition_as_number:omega:error")`. Finally, there was a significant main effect of condition, `r texreport(mod0_summ,"condition_as_number")`, which is difficult to interpret, but indicates a small bias where ...

These effects are more easily interpreted when inspecting the model-predicted learning rate (Figure \@ref(fig:learning-rate-plot)). As can be seen there, while on average, people adapt their learning rate to the changes in volatility, the adaptation is more marked in the gradual compared to the abrupt change condition. Also, the predicted learning rates are mostly higher than the optimal steady-state learning rates.  
```{r learning-rate-plot,echo=FALSE,out.width = "85%", fig.width=6, fig.height=3, fig.cap="Predicted learning rates from the linear mixed-effects model as a function of the optimal learning rate."}
require(ggplot2)
require(lmerTest)
coef <- fixef(mod0)

# newdata <- expand.grid(condition=c("abrupt","gradual"),omega = seq(min(dat$omega),max(dat$omega),length=100))
# newdata$condition_as_number <- 1
# newdata$condition_as_number[newdata$condition == "abrupt"] <- -1
# coeff <-  fixef(mod0)
# 
# newdata$pred_eta <- coeff["error"] + coeff["condition_as_number:error"]*newdata$condition_as_number + coeff["omega:error"]*newdata$omega + coeff["condition_as_number:omega:error"]*newdata$condition_as_number*newdata$omega
# ggplot(newdata,aes(x=omega,y=pred_eta,colour=condition)) + geom_line() + ylab("predicted learning rate") + xlab("optimal learning rate") + ylim(c(min(newdata$omega),max(newdata$pred_eta))) + xlim(c(min(newdata$omega),max(newdata$pred_eta))) + geom_abline(slope=1,intercept=0,lty=2,colour=grey(.5))

newdata <- data.frame(condition=rep(c("abrupt","gradual"),each=100),volatility = c(subset(trial_data,condition=="abrupt")$volatility[1:100],subset(trial_data,condition=="gradual")$volatility[1:100]),trial=1:100)
newdata$omega <- .5*(sqrt(newdata$volatility^4/4^4 + 4*newdata$volatility^2/4^2) - newdata$volatility^2/4^2) # (2*newdata$volatility^2)/(2*newdata$volatility^2 + 4^2)
newdata$condition_as_number <- 1
newdata$condition_as_number[newdata$condition == "abrupt"] <- -1
newdata$type = "optimal"

newdata <- rbind(newdata,cbind(newdata[,1:5],type="estimated"))

coeff <-  fixef(mod1)
newdata$omega[newdata$type=="estimated"] <- coeff["error"] + coeff["error:condition_as_number"]*newdata$condition_as_number[newdata$type=="estimated"] + coeff["error:omega"]*newdata$omega[newdata$type=="estimated"] + coeff["error:condition_as_number:omega"]*newdata$condition_as_number[newdata$type=="estimated"]*newdata$omega[newdata$type=="estimated"]

# coeff <-  fixef(mod0)
# newdata$omega[newdata$type=="estimated"] <- coeff["error"] + coeff["condition_as_number:error"]*newdata$condition_as_number[newdata$type=="estimated"] + coeff["omega:error"]*newdata$omega[newdata$type=="estimated"] + coeff["condition_as_number:omega:error"]*newdata$condition_as_number[newdata$type=="estimated"]*newdata$omega[newdata$type=="estimated"]

ggplot(newdata,aes(x=trial,y=omega,colour=type)) + geom_line() + ylab("(predicted) learning rate") + xlab("trial") + facet_wrap(~condition) + theme(legend.position="bottom") #+ ylim(c(min(newdata$omega),max(newdata$pred_eta))) + xlim(c(min(newdata$omega),max(newdata$pred_eta))) + geom_abline(slope=1,intercept=0,lty=2,colour=grey(.5))

```

<!--
. However, as the comparison just fails significance, we also report the results of the more complex model in the appendix.

provides us with a trial-by-trial estimate of the learning rate
$$\hat{\eta}(t) = \frac{r_{t + 1} - r_{t}}{y_t - r_t}$$
Under the assumption that $r_t$ is Normal distributed, this empricial learning rate follows a general Cauchy distribution.
-->

# Discussion

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2019-12-11 Report/draft_report.Rnw
updated report

--- 2019-12-05 Report/draft_report.Rnw
@@
-\documentclass{article}
+\documentclass[12pt]{article}         % the type of document and font size (default 10pt)
+\usepackage[margin=1.0in]{geometry}   % sets all margins to 1in, can be changed
+\usepackage{moreverb}                 % for verbatimtabinput -- LaTeX environment
+\usepackage{url}                      % for \url{} command
+\usepackage{amssymb}                  % for many mathematical symbols
+\usepackage[pdftex]{lscape}           % for landscaped tables
+\usepackage{longtable}                % for tables that break over multiple pages
+\title{Transfer of Learned Opponent Models in Zero Sum Games}  % to specify title
+\author{Ismail Guennouni, Maarten Speekenbrink}             % to specify author(s)
+\begin{document}                      % document begins here
 
-\begin{document}
+% If .nw file contains graphs: To specify that EPS/PDF graph files are to be 
+% saved to 'graphics' sub-folder
+%     NOTE: 'graphics' sub-folder must exist prior to Sweave step
+%\SweaveOpts{prefix.string=graphics/plot}
+
+% If .nw file contains graphs: to modify (shrink/enlarge} size of graphics 
+% file inserted
+%         NOTE: can be specified/modified before any graph chunk
+\setkeys{Gin}{width=1.0\textwidth}
+
+\maketitle              % makes the title
+%\tableofcontents        % inserts TOC (section, sub-section, etc numbers and titles)
+%\listoftables           % inserts LOT (numbers and captions)
+%\listoffigures          % inserts LOF (numbers and captions)
+%                        %     NOTE: graph chunk must be wrapped with \begin{figure}, 
+%                        %  \end{figure}, and \caption{}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Where everything else goes
+
 \SweaveOpts{concordance=TRUE}
@@
 
+Being able to rapidly learn a model of the environment and successfully transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008).
+Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge (Lake et al., 2017).
+More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
+This is a major theme in current research on artificial intelligence, and neural networks in particular.
+While these approaches have made important strides in various challenges from machine vision to game play, we have not been able to build AI systems that learn as fast and as efficiently as humans do, and more importantly that have the ability to generalize and transfer knowledge to new domains.
+Therefore, being able to capture mechanisms that underpin how humans learn and transfer models of the environment is likely to be a key component towards building a general artificial intelligence.
+
+In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Premack & Woodruff, 1978) play a role in determining human behaviour.
+
+In order to explore learning transfer in strategic settings,  it is generally useful to reduce the complexity of real life interactions by using an experimental paradigm that reduces non relevant confounding effects.
+In the context of inter-dependent decision making, the study of simple games as a model of more complex interactions plays this essential role.
+More specifically, when studying learning, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
+Repeated games, in which players interact repeatedly and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are therefore used whenever we are interested in the evolution of learning.
+
+Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions  (Risk Dominance) in later games, having had experience with a similar game environment initially.
+For instance, Ho et al.
+(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games having had experience with similar games.
+They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
+Camerer & Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to conordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
+They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity.
+If the games were only strategically similar, then the transfer was much weaker.
+
+Juvina et al.(2014)  made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
+However, they show that surface similarity is not necessary for deep transfer, and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
+In a series of experiments using economic signalling games, Cooper & Kagel (2003, 2004, 2008) find that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
+
+Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
+A notable exception is the effort by Haruvy and Stahl (2012) to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
+Participants played ten games, presented as 4x4 normal form (matrix payoffs).
+Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
+They also showed that players learn abstract aspects of the game that are then transfered to new settings.
+Their rule learning model, based on Stahl (1996) was able to capture participants dynamic behavior and show that the propensity to select particular rules is perfectly transfered across games.
+
+In most of the experimental paradigms we saw, participants were playing other human players either one on one or as a group.
+In this case, players are learning about the game but so are their opponents.
+While the approach of matching groups of human players repeatedly to play economic games has ecological validity in recreating environments where social decision making can be studied, it complicates the detection and modelling of strategies used by participants.
+It is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
+It is also difficult to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
+One potential solution is to replace the human opponent with a computerised agent, allowing researchers to manipulate the opponent's behaviour and observe how the human participants adapt their behaviour.
+For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use, and found that human participants do adapt to the opponent they are facing.
+Shachat & Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
+They found that the players changed their strategies towards exploiting the deviations from the MSNE, and that this exploitation was very likely if the deviation from the MSNE play was high.
+
+One of the major limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
+They either used deterministic strategies that did not consider the human participant's play, as in the case of pre-determined mixed strategy algorithms, or strategies that only depended on the player's frequency or patterns of past plays, not considering the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
+Thes computerised opponents used did not play the way humans participants would.
+After all, we are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.It is important to also have agents that "play like humans", and one way of achieving that is to embed theses agents with limited recursive reasoning abilities: Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
+Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
+This concept finds its natural application in 'level-k' theory, first adopted by Stahl & wilson (1995).
+It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
+At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment (Arad & Rubinstein, 2012).
+Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
+Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below and so on.
+
+Another potential issue in the experimental paradigms used in the learning transfer literature is the use of social dilemmas and cooperative/competitive settings that may invoke confounding factors in learning and transfer.
+Social dilemma games and coordination games crystallise the conflict humans deal with between competing with others out of self-interest or cooperating to reach a socially optimal contingent on others cooperation.
+Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
+Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
+As such, these confounding factors may impede teasing out the process of opponent modelling and that of whether/how these models are transfered.
+By contrast, purely competitive settings and zero sum games in particular would be more appropritate.
+They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building.
+Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent whihc is more amenable to modelling learing.
+Games with unique mixed strategy nash equilibrium leading to nil average rewards facilites infering whether participants have learned to exploit the non random play of the opponent, and these are the games we will focus on for the purpose of exploring opponent modelling and learing transfer.
+
+###################################### This Study #######################################################
+
+To address some of these limitations in the exisintg literature on learning transfer, we propose to explore opponent modelling and its transfer with the use of computer agents posssessing human-like theory of mind abilities with limited degrees of iterated reasoning.
+The agents will have a fixed strategy played stochastically with a high likelihood, and will either be level-1 or level-2 players, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
+We also use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
+We measure transfer of learning about the opponent strategy between games that are similar and dissimilar.
+The first two games we use are identical except for the choice label.
+In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimialr to the frst two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with 0 expected reward against a Nash player.
+
+Finally, unlike the vast majority of experimental paradigms, we make participants play the games in an engaging, interactive and ultimately more ecological way rather than simply provide the matrix form of the game.
+We use visual aids representing the player and their computer opponent as well as the various actions that people can select built on a highly interactive interface providing image, audio and sometimes video feedback at each step, from choosing actions, to presenting outcomes of the rounds and players scores.
+
 \section*{Methods}
+
+We ran two experiments where human participants played against computer opponents a total of 3 different games.
+In the first experiment, participants played 3 games sequentially against the same computer opponent.
+The computer opponent either used a level-1 or level-2 strategy.
+The three games were rock-paper-scissors, fire-water-grass, and the numbers game.
+A typical Rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
+If one player choses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
+Otherwise it is a draw and both players receive a reward of 0.
+It has a unique MSNE consisting of randomly playing one of the three options each time.
+
+The second game is identical to Rock-Paper-Scissors in all but action labels.
+We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
+We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
+Finally, the numbers game is a generalization of rock-paper-scissors.
+In the variant we use, 2 participants concurrently pick a number between 1 and 5.
+To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent.
+For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
+To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
+This game has a structure similar to RPS in which every action is dominated by exactly one choice.
+All other possible combination of choices that are not consecutive are considered ties.
+A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score.
+Similar to RPS, the MSNE is to play each action with equal probability in a random way.
+
+Participants were informed they would play three different games against the *same* computer opponent.
+Each participant plays all three games consecutively and in the same order described above.
+Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant’s choice.
+A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
+The score was calculated as the number of wins minus the number of losses.
+Ties did not affect the score.
+In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
+The overall score of the players was translated into the bonus by making each point worth £0.02.
+This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they’d won all rounds against the computer opponent.
+
+In the second experiment, participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
+The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
+The first two games were identical to the ones used in the first experiment.
+In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper.
+Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
+If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
+Otherwise, the goalkeeper catches the ball and the player loses the round.
+There is no possibility of ties in this game.
+What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose “right” in the next round, we can win by both choosing “left” and “centre”.
+A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
+As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
+
+Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
+Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
+Participants start by facing one of the opoonents in stage one, then face the other in stage two.
+This is repeated in the same order in stages 3 and 4.
+Which opponent they faced first was counterbalanced.
+All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
+
+In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
+During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
+A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent.
+After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
+Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction.
+The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
+An example of the interface for the rock-paper-scissors game is provided in figure XXXXXXX
+
+To summarise, all the games used in both experiments have a unique MSNE consisting of randomising across actions.
+If participants follow this strategy, or simply dont engage in learning how the opponent plays, they woud score 0 on average against both level-1 and level-2 players.
+Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
 
@@
 
+\section{References}
+Goodie, A. S., Doshi, P., & Young, D. L. (2012). Levels of theory-of-mind reasoning in competitive games. Journal of Behavioral Decision Making, 25(1), 95–108.
+Return to ref 34 in article
+
 \end{document}

### 2019-12-11 Report/draft_report.tex
updated report

--- 2019-12-09 Report/draft_report.Rnw
@@
 \usepackage{longtable}                % for tables that break over multiple pages
-\title{Transfer of Learned Opponent Models of ToM Agents in Zero Sum Games}  % to specify title
+\title{Transfer of Learned Opponent Models in Zero Sum Games}  % to specify title
 \author{Ismail Guennouni, Maarten Speekenbrink}             % to specify author(s)
+\usepackage{Sweave}
 \begin{document}                      % document begins here
@@
 
-\SweaveOpts{concordance=TRUE}
+\input{draft_report-concordance}
 
@@
 
-Being able to successfully transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008) and is likely to be a key component towards building a general artificial intelligence.
-Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
+Being able to rapidly learn a model of the environment and successfully transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008).
+Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge (Lake et al., 2017).
 More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
+This is a major theme in current research on artificial intelligence, and neural networks in particular.
+While these architectures have made important strides in various challenges from machine vision to game play, we have not been able to build AI systems that learn as fast and as efficiently as humans do, and more importantly that have the ability to generalize and transfer knowledge to new domains.
+Therefore, being able to capture mechanisms that underpin how humans learn and transfer models of the environment is likely to be a key component towards building a general artificial intelligence.
 
-We are interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
+  In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
 These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Premack & Woodruff, 1978) play a role in determining human behaviour.
-\\
 
-In order to explore learning transferin strategic settings,  it is generally useful to reduce the complexity of real life interactions by using an experimental paradigm that reduces non relevant confounding effects.
-In the context of inter-dependent decision making, the study of simple games as a means of a model of more complex interactions plays this essential role.
+In order to explore learning transfer in strategic settings,  it is generally useful to reduce the complexity of real life interactions by using an experimental paradigm that reduces non relevant confounding effects.
+In the context of inter-dependent decision making, the study of simple games as a model of more complex interactions plays this essential role.
 More specifically, when studying learning, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
@@
 
-The use of games to study behavior gave rise to the field of behavioural game theory, in which computational models where developed to describe the way in which humans actually play simple economic games, as opposed to game theory which stipulates how a rational agent should normatively play.
-A major contribution that facilitated the development of behavioural game theory was the idea that humans possess a 'bounded rationality'.
-Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as solving for Nash equilibria.
+Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal or salient actions in later games, having had experience with a similar game environment initially.
+For instance, Ho et al.
+(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games having had experience with similar games.
+They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
+Camerer & Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to conordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
+They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity.
+If the games were only strategically similar, then the transfer was much weaker.
+
+Juvina et al.(2014)  made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learnig transfer.
+However, they show that surface similarity is not necessary for deep transfer, and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
+In a series of experiments using economic signalling games, Cooper & Kagel (2003, 2004, 2008) find that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
+
+Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
+A notable exception is the effort by Haruvy and Stahl (2012) to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
+Participants played ten games, presented as 4x4 normal form (matrix payoffs).
+Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
+They also showed that players learn abstract aspects of the game that are then transfered to new settings.
+Their rule learning model, based on Stahl (1996) was able to capture participants dynamic behavior and show that the propensity to select particular rules is perfectly transfered across games.
+
+In most of these studies, participants were playing other human players either one on one or as a group.
+In this case, players are learning about the game but so are their opponents.
+While the approach of matching groups of human players repeatedly to play economic games has ecological validity in recreating environments where social decision making can be studied, it complicates the detection and modelling of strategies used by participants.
+It is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
+It is also difficult to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
+
+Therefore, studies seeking to model human strategy learning have replaced the human opponent with a computerised agent, allowing researchers to manipulate the opponent's behaviour and observe how the human participants adapt their behaviour.
+For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use, and found that human participants do adapt to the opponent they are facing.
+Shachat & Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
+They found that the players changed their strategies towards exploiting the deviations from the MSNE, and that this exploitation was very likely if the deviation from the MSNE play was high.
+While useful in showing how adaptable humans are to variance in opponent strategies, the computerised opponents used did not play the way humans participants would.
+After all, we are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+Also, none of these studies looked at the learning transfer aspect.
+
+In this study, we aim to contribute to this under-explored literature through testing opponent modelling and its transfer with the use of both similar and dissimilar games played against computer opponents implementing fixed behavioral rules with differing degrees of sophistication.
+Unlike previous studies, our contribution is to focus on purely competitive situations through the use of zero sume games.
+Indeed, previous studies have used games that can give rise to confounding factors.
+For instance, social dilemma games and coordination games crystallise the conflict humans deal with between self-interest and cooperation.
+Playing these games repeatedly implicates important social constructs such as reputation building, trust and other psychological attributes such as cooperativeness.
+Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
+As such, these games are not as helpful as purely competitive settings in isolating how humans model their opponents and  the mechanism through which these models are updated, learned and eventualyl transfered.
+Zero sume games for instance do not incentivize any cooperation since one player's gain is necessarily the opponent's loss.
+As such, they encourage learning about the opponent play and exploiting that in order to maximise cumulative.
+
+Moreover, studies that looked at how players adapt to their opponent strategies when facing computer agents have mostly looked at the ability of players to detect and exploit action-based learning rules.
+They either used deterministic strategies that did not consider the human participant's play, as in the case of pre-determined mixed strategy algorithms, or strategies that only depended on the player's frequency or patterns of past plays, not considering the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
+We aim to use computer agents who mimick human theory of mind abilities and as such, play in a more "human" way.
+
+In order to build agents with human like characteristics, we use the idea that humans possess a 'bounded rationality'.
+Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
 Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-
 This concept finds its natural application in 'level-k' theory, first adopted by Stahl & wilson (1995) which posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
@@
 Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below and so on.
-\\
+In this study, our computer agents will play either as a level-1 or level-2 human player would, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
 
-The literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal actions in later games, having had experience with a similar game environment initially.
-For instance, Ho et al.
-(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games having had experience with simialr games.
-They find there is no evidence of immediate transfer ( Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-In a series of experiments using economic signalling games, Cooper & Kagel (2003, 2004, 2008) find that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
-They show that this transfer is driven by the emergence of strategically sophisticated players who are able to
-represent the strategic implications of their actions andhow changes in the opponent payoffs results in new optimal plays.
-
-In a seminal work on learning transfer between dissimilar games, Haruvy & Stahl (2012) confirmed that subjects do learn over dissimilar games and that this learning is significant.
-They also showed that players learn abstract aspects of the game that are then transfered to new settings, such as .
-This rule learning model (Stahl, 1996) was able to capture participants dynamic behavior and show that the propensity to select particular rules is perfectly transfered across games.
+Finally, unlike the vast majority of experimental paradigms, we make participants play the games in an engaging, interactive and ultimately more ecological way rather than simply provide the matrix form of the game.
+We use visual aids representing the player and their computer opponent as well as the various actions that people can select built on a highly interactive interface providing image, audio and sometimes video feedback at each step, from choosing actions, to presenting outcomes of the rounds and players scores.
 
 \section*{Methods}
+
+We ran two experiments where human participants played against computer opponents a total of 3 different games.
+In the first experiment, participants played 3 games sequentially against the same computer opponent.
+The computer opponent either used a level-1 or level-2 strategy.
+The three games were rock-paper-scissors, fire-water-grass, and the numbers game.
+A typical Rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
+If one player choses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
+Otherwise it is a draw and both players receive a reward of 0.
+It has a unique MSNE consisting of randomly playing one of the three options each time.
+
+The second game is identical to Rock-Paper-Scissors in all but action labels.
+We call is Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
+We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
+Finally, the numbers game is a generalization of rock-paper-scissors.
+In the variant we use, 2 participants concurrently pick a number between 1 and 5.
+To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent.
+For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
+To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
+This game has a structure similar to RPS in which every action is dominated by exactly one choice.
+All other possible combination of choices that are not consecutive are considered ties.
+A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score.
+Similar to RPS, the MSNE is to play each action with equal probability in a random way.
+
+Participants were informed they would play three different games against the *same* computer opponent, namely: Rock-Paper-Scissors, Fire-Water-Grass and the numbers game.
+Each participant plays all three games consecutively and in the same order described above.
+Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant’s choice.
+A total of 50 rounds of each game was played with the player’s score displayed at the end of each game.
+The score was calculated as the number of wins minus the number of losses.
+Ties did not affect the score.
+In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
+At the end of the experiment, the overall score of the players was translated into the bonus by making each point worth £0.02.
+This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they’d won all rounds against the computer opponent.
+
+In the second experiment, participants  each played 3 games sequentially against [both] computer opponents, rather than just one like in the first experiment.
+The computer opponents either used a level-1 or level-2 strategy throughout the three games.
+The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
+The first two games were identical to the ones used in the first experiment.
+In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper.
+Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
+If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
+Otherwise, the goalkeeper catches the ball and the player loses the round.
+There is no possibility of ties in this game.
+We can easily check that there is no pure strategy Nash equilibrium in this game.
+However, like the first 2 games, there is a unique mixed strategy Nash equilibrium consisting of randomising over the three actions for both players (Probability of shooting/diving in any direction is 1/3).
+What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose “right” in the next round, we can win by both choosing “left” and “centre”.
+A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
+As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
+
+Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
+Specifically, each game is divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
+Participants start by facing one of the opoonents in stage one, then face the other in stage two.
+This is repeated in the same order in stages 3 and 4.
+Whih opponent they faced first was counterbalanced.
+All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
+
+To summarise, all the games used in both experiments have a unique MSNE consisting of randomising across actions.
+If participants follow this strategy, or simply dont engage in learning how the opponent plays, they woud score 0 on average against both level-1 and level-2 players.
+Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
 

### 2019-12-12 Experiment_2/Experiment_2_modelling.Rmd
report update

@@
     # Q_learning: update rule (time  = t-1)
-    Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
+    Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act] )
 
@@
     probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
-    if (data[t,"round"] == 20) { cat(probs,"\n") }
+    #if (data[t,"round"] == 20) { cat(probs,"\n") }
 

### 2019-12-12 Report/draft_report.Rnw
report update

@@
 
-Being able to rapidly learn a model of the environment and successfully transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008).
-Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge (Lake et al., 2017).
+Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008).
+Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
 More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
-This is a major theme in current research on artificial intelligence, and neural networks in particular.
-While these approaches have made important strides in various challenges from machine vision to game play, we have not been able to build AI systems that learn as fast and as efficiently as humans do, and more importantly that have the ability to generalize and transfer knowledge to new domains.
-Therefore, being able to capture mechanisms that underpin how humans learn and transfer models of the environment is likely to be a key component towards building a general artificial intelligence.
+This typically human skill has so far eluded modern ai agents.
+Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
+Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
+Lake et al.(2017) argue that human learning transfer abilites take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 
-In order to explore learning transfer in strategic settings,  it is generally useful to reduce the complexity of real life interactions by using an experimental paradigm that reduces non relevant confounding effects.
-In the context of inter-dependent decision making, the study of simple games as a model of more complex interactions plays this essential role.
+In order to explore learning transfer in strategic settings, it is generally useful to study simple games as a model of more complex interactions.
 More specifically, when studying learning, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are therefore used whenever we are interested in the evolution of learning.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to modelling learning about the opponent.
 
-Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions  (Risk Dominance) in later games, having had experience with a similar game environment initially.
+Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
 For instance, Ho et al.
-(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games having had experience with similar games.
+(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after traingn on similar games.
 They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
@@
 One of the major limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-They either used deterministic strategies that did not consider the human participant's play, as in the case of pre-determined mixed strategy algorithms, or strategies that only depended on the player's frequency or patterns of past plays, not considering the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
-Thes computerised opponents used did not play the way humans participants would.
-After all, we are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.It is important to also have agents that "play like humans", and one way of achieving that is to embed theses agents with limited recursive reasoning abilities: Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
+They either used deterministic strategies that did not consider the human participant's play, as in the case of pre-determined mixed strategy algorithms, or strategies that only depended on the player's patterns of past plays.
+These strategies did not necessarily take into account the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
+Their play was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
+Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
 Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
@@
 Another potential issue in the experimental paradigms used in the learning transfer literature is the use of social dilemmas and cooperative/competitive settings that may invoke confounding factors in learning and transfer.
-Social dilemma games and coordination games crystallise the conflict humans deal with between competing with others out of self-interest or cooperating to reach a socially optimal contingent on others cooperation.
+Social dilemma and coordination games crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
 Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
 Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
-As such, these confounding factors may impede teasing out the process of opponent modelling and that of whether/how these models are transfered.
+As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transfered.
 By contrast, purely competitive settings and zero sum games in particular would be more appropritate.
 They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building.
-Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent whihc is more amenable to modelling learing.
-Games with unique mixed strategy nash equilibrium leading to nil average rewards facilites infering whether participants have learned to exploit the non random play of the opponent, and these are the games we will focus on for the purpose of exploring opponent modelling and learing transfer.
+Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learing.
+Games with unique mixed strategy nash equilibrium leading to nil average rewards facilites infering whether participants have learned to exploit the non random play of the opponent.
 
-###################################### This Study #######################################################
-
-To address some of these limitations in the exisintg literature on learning transfer, we propose to explore opponent modelling and its transfer with the use of computer agents posssessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically with a high likelihood, and will either be level-1 or level-2 players, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
+To address some of these limitations in the exisintg literature on learning transfer outlined above, we propose to explore opponent modelling and its transfer with the use of computer agents posssessing human-like theory of mind abilities with limited degrees of iterated reasoning.
+The agents will have a fixed strategy played stochastically, and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
 We also use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
 We measure transfer of learning about the opponent strategy between games that are similar and dissimilar.
-The first two games we use are identical except for the choice label.
-In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimialr to the frst two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with 0 expected reward against a Nash player.
+The first two games we use are identical except for action labels.
+In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with 0 expected reward against a Nash player.
 
@@
 The computer opponent either used a level-1 or level-2 strategy.
-The three games were rock-paper-scissors, fire-water-grass, and the numbers game.
-A typical Rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
+The three games were rock-paper-scissors, fire-water-grass and the numbers game.
+A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
 If one player choses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
@@
 
-Participants were informed they would play three different games against the *same* computer opponent.
+Participants were informed they would play three different games against the same computer opponent.
 Each participant plays all three games consecutively and in the same order described above.
-Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant’s choice.
+Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
 A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
@@
 In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-The overall score of the players was translated into the bonus by making each point worth £0.02.
-This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they’d won all rounds against the computer opponent.
+The overall score of the players was translated into the bonus by making each point worth $£$0.02.
+This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they'd won all rounds against the computer opponent.
 
@@
 There is no possibility of ties in this game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose “right” in the next round, we can win by both choosing “left” and “centre”.
+What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
 A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.

### 2019-12-12 Report/draft_report.tex
report update

@@
 
-Being able to rapidly learn a model of the environment and successfully transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008).
-Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge (Lake et al., 2017).
+Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008).
+Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
 More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
-This is a major theme in current research on artificial intelligence, and neural networks in particular.
-While these architectures have made important strides in various challenges from machine vision to game play, we have not been able to build AI systems that learn as fast and as efficiently as humans do, and more importantly that have the ability to generalize and transfer knowledge to new domains.
-Therefore, being able to capture mechanisms that underpin how humans learn and transfer models of the environment is likely to be a key component towards building a general artificial intelligence.
+This typically human skill has so far eluded modern ai agents.
+Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
+Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
+Lake et al.(2017) argue that human learning transfer abilites take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 
-In order to explore learning transfer in strategic settings,  it is generally useful to reduce the complexity of real life interactions by using an experimental paradigm that reduces non relevant confounding effects.
-In the context of inter-dependent decision making, the study of simple games as a model of more complex interactions plays this essential role.
+In order to explore learning transfer in strategic settings, it is generally useful to study simple games as a model of more complex interactions.
 More specifically, when studying learning, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are therefore used whenever we are interested in the evolution of learning.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to modelling learning about the opponent.
 
-Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal or salient actions in later games, having had experience with a similar game environment initially.
+Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
 For instance, Ho et al.
-(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games having had experience with similar games.
+(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after traingn on similar games.
 They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
@@
 
-Juvina et al.(2014)  made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learnig transfer.
+Juvina et al.(2014)  made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
 However, they show that surface similarity is not necessary for deep transfer, and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
@@
 
-In most of these studies, participants were playing other human players either one on one or as a group.
+In most of the experimental paradigms we saw, participants were playing other human players either one on one or as a group.
 In this case, players are learning about the game but so are their opponents.
@@
 It is also difficult to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-
-Therefore, studies seeking to model human strategy learning have replaced the human opponent with a computerised agent, allowing researchers to manipulate the opponent's behaviour and observe how the human participants adapt their behaviour.
+One potential solution is to replace the human opponent with a computerised agent, allowing researchers to manipulate the opponent's behaviour and observe how the human participants adapt their behaviour.
 For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use, and found that human participants do adapt to the opponent they are facing.
@@
 They found that the players changed their strategies towards exploiting the deviations from the MSNE, and that this exploitation was very likely if the deviation from the MSNE play was high.
-While useful in showing how adaptable humans are to variance in opponent strategies, the computerised opponents used did not play the way humans participants would.
-After all, we are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
-Also, none of these studies looked at the learning transfer aspect.
 
-In this study, we aim to contribute to this under-explored literature through testing opponent modelling and its transfer with the use of both similar and dissimilar games played against computer opponents implementing fixed behavioral rules with differing degrees of sophistication.
-Unlike previous studies, our contribution is to focus on purely competitive situations through the use of zero sume games.
-Indeed, previous studies have used games that can give rise to confounding factors.
-For instance, social dilemma games and coordination games crystallise the conflict humans deal with between self-interest and cooperation.
-Playing these games repeatedly implicates important social constructs such as reputation building, trust and other psychological attributes such as cooperativeness.
-Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
-As such, these games are not as helpful as purely competitive settings in isolating how humans model their opponents and  the mechanism through which these models are updated, learned and eventualyl transfered.
-Zero sume games for instance do not incentivize any cooperation since one player's gain is necessarily the opponent's loss.
-As such, they encourage learning about the opponent play and exploiting that in order to maximise cumulative.
-
-Moreover, studies that looked at how players adapt to their opponent strategies when facing computer agents have mostly looked at the ability of players to detect and exploit action-based learning rules.
-They either used deterministic strategies that did not consider the human participant's play, as in the case of pre-determined mixed strategy algorithms, or strategies that only depended on the player's frequency or patterns of past plays, not considering the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
-We aim to use computer agents who mimick human theory of mind abilities and as such, play in a more "human" way.
-
-In order to build agents with human like characteristics, we use the idea that humans possess a 'bounded rationality'.
+One of the major limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
+They either used deterministic strategies that did not consider the human participant's play, as in the case of pre-determined mixed strategy algorithms, or strategies that only depended on the player's patterns of past plays.
+These strategies did not necessarily take into account the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
+Their play was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
 Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
 Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in 'level-k' theory, first adopted by Stahl & wilson (1995) which posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
+This concept finds its natural application in 'level-k' theory, first adopted by Stahl & wilson (1995).
+It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
 At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment (Arad & Rubinstein, 2012).
@@
 Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below and so on.
-In this study, our computer agents will play either as a level-1 or level-2 human player would, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
+
+Another potential issue in the experimental paradigms used in the learning transfer literature is the use of social dilemmas and cooperative/competitive settings that may invoke confounding factors in learning and transfer.
+Social dilemma and coordination games crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
+Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
+Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
+As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transfered.
+By contrast, purely competitive settings and zero sum games in particular would be more appropritate.
+They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building.
+Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learing.
+Games with unique mixed strategy nash equilibrium leading to nil average rewards facilites infering whether participants have learned to exploit the non random play of the opponent.
+
+To address some of these limitations in the exisintg literature on learning transfer outlined above, we propose to explore opponent modelling and its transfer with the use of computer agents posssessing human-like theory of mind abilities with limited degrees of iterated reasoning.
+The agents will have a fixed strategy played stochastically, and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
+We also use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
+We measure transfer of learning about the opponent strategy between games that are similar and dissimilar.
+The first two games we use are identical except for action labels.
+In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with 0 expected reward against a Nash player.
 
@@
 The second game is identical to Rock-Paper-Scissors in all but action labels.
-We call is Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
+We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
 We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
@@
 
-Participants were informed they would play three different games against the *same* computer opponent, namely: Rock-Paper-Scissors, Fire-Water-Grass and the numbers game.
+Participants were informed they would play three different games against the same computer opponent.
 Each participant plays all three games consecutively and in the same order described above.
-Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant’s choice.
-A total of 50 rounds of each game was played with the player’s score displayed at the end of each game.
+Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
+A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
 The score was calculated as the number of wins minus the number of losses.
@@
 In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-At the end of the experiment, the overall score of the players was translated into the bonus by making each point worth £0.02.
-This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they’d won all rounds against the computer opponent.
+The overall score of the players was translated into the bonus by making each point worth $£$0.02.
+This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they'd won all rounds against the computer opponent.
 
-In the second experiment, participants  each played 3 games sequentially against [both] computer opponents, rather than just one like in the first experiment.
-The computer opponents either used a level-1 or level-2 strategy throughout the three games.
+In the second experiment, participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
 The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
@@
 There is no possibility of ties in this game.
-We can easily check that there is no pure strategy Nash equilibrium in this game.
-However, like the first 2 games, there is a unique mixed strategy Nash equilibrium consisting of randomising over the three actions for both players (Probability of shooting/diving in any direction is 1/3).
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose “right” in the next round, we can win by both choosing “left” and “centre”.
+What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
 A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
@@
 Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
-Specifically, each game is divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
+Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
 Participants start by facing one of the opoonents in stage one, then face the other in stage two.
 This is repeated in the same order in stages 3 and 4.
-Whih opponent they faced first was counterbalanced.
+Which opponent they faced first was counterbalanced.
 All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
+
+In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
+During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
+A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent.
+After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
+Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction.
+The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
+An example of the interface for the rock-paper-scissors game is provided in figure XXXXXXX
 

### 2019-12-12 comp_model_1019.Rmd
report update

@@
 ```
-# Looks like most participants behavior can be explained by Bayes with or without transfer. Most others are consistent with random behavior, and only 1 qith QL and 1 with S_EWA.
-
-## Question: Can we see evidence for transfer by looking at difference in BICS btwn Bayes with and without transfer.
+##### Looks like most participants behavior can be explained by Bayes with or without transfer. Most others are consistent with random behavior, and only 1 with QL and 1 with S_EWA.
+
+###### Question: Can we see evidence for transfer by looking at difference in BICS btwn Bayes with and without transfer.
 Let's test correlation between difference in BICs  with early rounds score (evidence for transfer)
@@
 
-# Correlate difference between BICs of Bayes transfer and no transfer with early rounds score (evidence for transfer) 
+### Correlate difference between BICs of Bayes transfer and no transfer with early rounds score (evidence for transfer) 
 ```{r}
@@
 
-#Correlation between early game score and difference between best model and random BIC
+### Correlation between early game score and difference between best model and random BIC
 ```{r}
@@
 ```
-# Histogram of best fitting models 
+### Histogram of best fitting models 
 ```{r}
@@
 
-```{r}
-
-```
+### Model based model: compute transition probabilities to new states.
+Weigh the value of an action by the conditional probabilty of ending up in a future state....
+once you take an action in current round, you can only end up in 3 states, with probabilities p, q and 1-p-q.
+You are learning these probabilities by updating priors (initial prior is dirichlet).
+```{r}
+MBM <- function(par,data,return_value,gamma){
+  # Par[1] -> beta= inverse temperature parameter in softmax choice function
+  # Par[2] -> lambda = learning rate (one per game?)
+  # data : participant and ai choice data.
+  # return_value=c("-2loglik","likelihood_by_trial")
+  # Gamma is discount factor for future rewards 
+  # Returns Q-values per trial and predicts choice using softmax
+  beta <- par[1]
+  alpha <- par[2]
+
+  #gamma <- 0.9
+
+  #Define matrix of state spaces for each game 
+  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+  states_RPS <- paste0(G1$Var1,G1$Var2)
+
+  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+  states_FWG <- paste0(G2$Var1,G2$Var2)
+
+  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+  states_NUM <- paste0(G3$Var1,G3$Var2)
+
+  # Matrices to store Q_values in each state 
+  Q_vals_RPS = matrix(-0.5,9,3)
+  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
+  Q_vals_FWG = matrix(-0.5,9,3)
+  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
+  Q_vals_NUM = matrix(-0.5,25,5)
+  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
+
+  # Initiate probability vectors
+
+  lik_hum <- matrix(0.0,nrow(data))
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    if(t_game == "numbers") nopts <- 5 else nopts <- 3
+
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
+      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
+      lik_hum[t] <- 1/nopts
+      # Randomly select prev_state and actions for first round
+      curr_state <- sample(state_vec, size = 1)
+      h_act <- sample(colnames(Q_vals), size =1)
+      ai_act <- sample(colnames(Q_vals), size =1)
+      reward <- 0
+
+    } else {
+      # Get past human action and associated reward 
+      h_act <- as.character(data[t-1,"h_action"])
+      ai_act <- as.character(data[t-1,"a_action"])
+      reward <- as.numeric(data[t-1,"score"])
+    }
+
+    # cat(curr_state, " This is the previous state", "\n")
+    new_state <- paste0(h_act,ai_act)
+    # cat(new_state,"This is new state","\n")
+
+    # Q_learning: update rule (time  = t-1)
+    Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
+
+    # Assume human chooses action probabilistically using softmax on Q values
+    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
+    #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }
+
+    # Get actual human action and compute likelihood
+    h_act <- as.character(data[t,"h_action"])
+    act_index <- match(h_act, colnames(Q_vals))
+    lik_hum[t] <- probs[[act_index]]
+
+    # Update state
+    curr_state<- new_state 
+    #}
+  }
+  if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret) || is.nan(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+
+}
+
+```

### 2019-12-17 Report/draft_report_v1.Rmd
added results section to report

--- 2019-12-12 Report/draft_report.tex
@@
-\documentclass[12pt]{article}         % the type of document and font size (default 10pt)
-\usepackage[margin=1.0in]{geometry}   % sets all margins to 1in, can be changed
-\usepackage{moreverb}                 % for verbatimtabinput -- LaTeX environment
-\usepackage{url}                      % for \url{} command
-\usepackage{amssymb}                  % for many mathematical symbols
-\usepackage[pdftex]{lscape}           % for landscaped tables
-\usepackage{longtable}                % for tables that break over multiple pages
-\title{Transfer of Learned Opponent Models in Zero Sum Games}  % to specify title
-\author{Ismail Guennouni, Maarten Speekenbrink}             % to specify author(s)
-\usepackage{Sweave}
-\begin{document}                      % document begins here
+---
+title             : "Transfer of Learned Opponent Models in Zero Sum Games"
+shorttitle        : "draft"
 
-% If .nw file contains graphs: To specify that EPS/PDF graph files are to be 
-% saved to 'graphics' sub-folder
-%     NOTE: 'graphics' sub-folder must exist prior to Sweave step
-%\SweaveOpts{prefix.string=graphics/plot}
+author: 
+  - name          : "Ismail Guennouni"
+    affiliation   : "1"
+    corresponding : yes    # Define only one corresponding author
+    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
+    email         : "i.guennouni.17@ucl.ac.uk"
+  - name          : "Maarten Speekenbrink"
+    affiliation   : "1"
 
-% If .nw file contains graphs: to modify (shrink/enlarge} size of graphics 
-% file inserted
-%         NOTE: can be specified/modified before any graph chunk
-\setkeys{Gin}{width=1.0\textwidth}
+affiliation:
+  - id            : "1"
+    institution   : "Department of Experimental Psychology, University College London"
 
-\maketitle              % makes the title
-%\tableofcontents        % inserts TOC (section, sub-section, etc numbers and titles)
-%\listoftables           % inserts LOT (numbers and captions)
-%\listoffigures          % inserts LOF (numbers and captions)
-%                        %     NOTE: graph chunk must be wrapped with \begin{figure}, 
-%                        %  \end{figure}, and \caption{}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Where everything else goes
+author_note: |
+  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
 
-\input{draft_report-concordance}
+  Enter author note here.
 
-\section*{Introduction}
+abstract: |
+  Enter abstract here. Each new line herein must be indented, like this line.
 
+keywords          : "keywords"
+wordcount         : "X"
+
+# bibliography      : ["r-references.bib"]
+
+floatsintext      : yes
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+linkcolor         : "blue"
+mask              : no
+draft             : no
+
+class             : "man"
+output            : papaja::apa6_pdf
+header-includes   :
+  - \usepackage[document]{ragged2e}
+---
+
+```{r load-packages, include = FALSE}
+library("papaja")
+require(knitr)
+require(citr)
+```
+
+```{r analysis-preferences}
+# Seed for random number generation
+set.seed(42)
+```
+
+```{r texreport}
+texreport <- function(object,effect.name,...) UseMethod("texreport")
+texreport.default <- function(object,effect.name,...) return(NULL)
+
+texreport.summary.merMod <- function(object,effect.name,print.estimate=TRUE) {
+  if(effect.name %in% rownames(object$coefficients)) {
+    tab <- object$coefficients
+    estimate <- tab[effect.name,"Estimate"]
+    se <- tab[effect.name,"Std. Error"]
+    Tval <- tab[effect.name,"t value"]
+    df <- tab[effect.name,"df"]
+    pval <- tab[effect.name,"Pr(>|t|)"]
+    if(pval < .001) ptext <- "$p < .001$" else {
+      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+      }
+    }
+    txt <- paste("$b = ",round(estimate,2),"$, $SE = ",round(se,2),"$, $t(",round(df,2),") = ",round(Tval,2),"$, ",sep="")
+    txt <- paste(txt,ptext,sep="")
+  } else {
+    txt <- "error"
+  }
+  txt
+}
+
+texreport.summary.Anova.mlm <- function(object,effect.name,effect.size=TRUE,sphericity.correction=TRUE) {
+  if(effect.name %in% rownames(object$sphericity.tests) && sphericity.correction && object$sphericity.test[effect.name,"p-value"] < .05) {
+    epsilon <- object$pval.adjustments[effect.name,"HF eps"]
+    pval <- object$pval.adjustments[effect.name,"Pr(>F[HF])"]
+  } else {
+    epsilon <- 1
+    pval <- object$univariate.tests[effect.name,"Pr(>F)"]
+  }
+  df1 <- object$univariate.tests[effect.name,"num Df"]*epsilon
+  df2 <- object$univariate.tests[effect.name,"den Df"]*epsilon
+  Fval <- object$univariate.tests[effect.name,"F"]
+  etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
+  # generate latex output
+  if(pval < .001) ptext <- "$p < .001$" else {
+    if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+      ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+    }
+  }
+  txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+  if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+  txt <- paste(txt,ptext,sep="")
+  txt
+}
+
+texreport.linearHypothesis.mlm <- function(object,effect.size=TRUE) {
+  if(ncol(object$SSPH) == 1 & nrow(object$SSPH) == 1 & ncol(object$SSPE) == 1 & nrow(object$SSPE) == 1) {
+    df1 <- object$df
+    df2 <- object$df.residual
+    Fval <- (object$SSPH/df1)/(object$SSPE/df2)
+    pval <- 1-pf(Fval,object$df,object$df.residual)
+    etasq <- object$SSPH/(object$SSPH + object$SSPE)
+    # generate latex output
+    if(pval < .001) ptext <- "$p < .001$" else {
+      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+      }
+    }
+    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+    if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+    txt <- paste(txt,ptext,sep="")
+  } else {
+    txt <- "error"
+  }
+  txt
+}
+
+texreport.anova.lme <- function(object,effect.name,effect.size=FALSE) {
+  if(effect.name %in% rownames(object)) {
+    pval <- object[effect.name,"p-value"]
+    if(is.null(pval)) pval <- object[effect.name,"Pr(>F)"]
+    df1 <- object[effect.name,"numDF"]
+    df2 <- object[effect.name,"denDF"]
+    Fval <- object[effect.name,"F-value"]
+    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
+    # generate latex output
+    if(pval < .001) ptext <- "$p < .001$" else {
+      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+      }
+    }
+    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+    txt <- paste(txt,ptext,sep="")
+    txt
+  }
+}
+
+texreport.anova <- function(object,effect.name,effect.size=FALSE) {
+  if(effect.name %in% rownames(object)) {
+    pval <- object[effect.name,"Pr(>F)"]
+    df1 <- object[effect.name,"NumDF"]
+    df2 <- object[effect.name,"DenDF"]
+    Fval <- object[effect.name,"F.value"]
+    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
+    # generate latex output
+    if(pval < .001) ptext <- "$p < .001$" else {
+      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+      }
+    }
+    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+    txt <- paste(txt,ptext,sep="")
+    txt
+  }
+}
+
+```
+
+```{r read-data,warning=FALSE}
+# source("R/readData.R")
+# demo_exit <-  read.csv("data/demographics_and_exit_clean.csv")
+# trial_data <- read.csv("data/trial_data_clean.csv")
+# trial_data$trial <- 1:100
+```
+
+```{r, include=FALSE} 
+options(tinytex.verbose = TRUE)
+```
+
+# Introduction
 Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008).
@@
 Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-Lake et al.(2017) argue that human learning transfer abilites take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.
+Lake et al.(2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 Juvina et al.(2014)  made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
-However, they show that surface similarity is not necessary for deep transfer, and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
+However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
 In a series of experiments using economic signalling games, Cooper & Kagel (2003, 2004, 2008) find that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
@@
 Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
-They also showed that players learn abstract aspects of the game that are then transfered to new settings.
-Their rule learning model, based on Stahl (1996) was able to capture participants dynamic behavior and show that the propensity to select particular rules is perfectly transfered across games.
+They also showed that players learn abstract aspects of the game that are then transferred to new settings.
+Their rule-learning model, based on Stahl (1996), was able to capture participants dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
 
@@
 One potential solution is to replace the human opponent with a computerised agent, allowing researchers to manipulate the opponent's behaviour and observe how the human participants adapt their behaviour.
-For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use, and found that human participants do adapt to the opponent they are facing.
+For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
 Shachat & Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
@@
 Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in 'level-k' theory, first adopted by Stahl & wilson (1995).
+This concept finds its natural application in 'level-k' theory, first adopted by Stahl & Wilson (1995).
 It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
@@
 Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
-As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transfered.
-By contrast, purely competitive settings and zero sum games in particular would be more appropritate.
+As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transferred.
+By contrast, purely competitive settings and zero sum games in particular would be more appropriate.
 They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building.
-Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learing.
-Games with unique mixed strategy nash equilibrium leading to nil average rewards facilites infering whether participants have learned to exploit the non random play of the opponent.
+Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learning.
+Games with unique mixed strategy Nash equilibrium leading to nil average rewards facilitate inferring whether participants have learned to exploit the non-random play of the opponent.
 
-To address some of these limitations in the exisintg literature on learning transfer outlined above, we propose to explore opponent modelling and its transfer with the use of computer agents posssessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically, and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
+To address some of these limitations in the existing literature on learning transfer outlined above, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
+The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
 We also use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
@@
 
-\section*{Methods}
+# Methods
 
 We ran two experiments where human participants played against computer opponents a total of 3 different games.
+
+## first experiment:
+
 In the first experiment, participants played 3 games sequentially against the same computer opponent.
@@
 The overall score of the players was translated into the bonus by making each point worth $£$0.02.
-This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they'd won all rounds against the computer opponent.
+This bonus is significant as players could increase the total payoff from the experiment by up to 60% assuming they'd won all rounds against the computer opponent.
+
+## Second Experiment
 
@@
 There is no possibility of ties in this game.
+Figure XXXXXXXXX shows a snapshot of play in the shootout game.
 What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
@@
 Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
-Participants start by facing one of the opoonents in stage one, then face the other in stage two.
+Participants start by facing one of the opponents in stage one, then face the other in stage two.
 This is repeated in the same order in stages 3 and 4.
@@
 All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
+
+```{r feedback_rps, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align = "center"}
+
+# knitr::include_graphics("../Report/images/feedback_rps.png", dpi = 108)
+
+```
 
@@
 The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-An example of the interface for the rock-paper-scissors game is provided in figure XXXXXXX
+An example of the interface for the rock-paper-scissors game is provided in Figure XX.
+
+<!-- Figure\ \@ref(fig:feedback_rps) -->
 
@@
 
-\section*{Results}
+# Results
 
-\section*{Discussion}
+## First Experiment
 
-\section*{Conclusion}
+In the first experiment, a total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
+The mean age of participants was 31.2 years.
+Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
+The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
 
-\section{References}
-Goodie, A. S., Doshi, P., & Young, D. L. (2012). Levels of theory-of-mind reasoning in competitive games. Journal of Behavioral Decision Making, 25(1), 95–108.
-Return to ref 34 in article
+Looking at the aggregate scores, the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
+Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value = 2.1e-08 ;  FWG:  t(51) = 10.04 , p-value = 1.10e-13 ; NUMBERS: t(51) = 7.17, p-value = 2.87e-09).
 
-\end{document}
+To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
+As the number of participants facing level-2 agents was slightly higher than those facing level-1 agents (28 vs 24), the ANOVA is unbalanced.
+We therefore used the “afex” (Singmann & al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
+
+There was a main effect of Game ( F(2,100) = 8.54, ges  = 0.05,  p = .0005), showing that average scores varied significantly over the games.
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
+The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
+The main effect of Block ( F(1,50) = 22.51 , p < .001, ges = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning : as players get more interaction with the agent, they learn how to win more often.
+The main effect of Condition (F(1,50) = 5.44, p = .024, ges = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
+This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
+Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, ges = 0.02), indicating that within-game learning differed between the games, as well as a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, ges = 0.01).
+
+### Learning transfer
+
+As a measure for learning transfer, we focus on participants’ scores in the earliest rounds, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
+A group of players with no experience of the game are expected to have scores not significantly different from 0.
+Any significantly positive group average scores would therefore reflect prior learning from past experiences.
+In figure XXX, the average score across participants by game for rounds 2-6 are plotted.
+Scores are also averaged across levels of condition.
+We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
+As expected for the initial RPS game, the average score is not significantly different from 0 ( t(148.85) = 1.04 , p = 0.89).
+In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
+Unexpectedly, this is also the case for NUMBERS ( t(148.85) = 3.00, p = 0.0092).
+
+### Moderation of learning transfer by type of opponent and game similarity
+
+Figure 10 shows the marginal mean scores for each game for both level-1 and level-2 facing players.
+Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
+To test these hypotheses, we run statistical tests on scores by game and opponent against the null hypothesis of 0 (no transfer).
+Table XXXXXXX shows the scores on rounds 2-6 for both type of opponents in each game.
+We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
+Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
+For level-1 facing players, there is evidence of learning transfer to both FWG and NUMBERS.
+For level-2 facing players, there is evidence for transfer to the similar game FWG (albeit scores are lower than for level-1 player) but not to the dissimilar game of NUMBERS.
+
+TABLE OF SCORES BY OPPONENT AND GAME (PG 40)
+
+Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
+We can see from TABLE XXXXX that this transfer is exclusively driven by level-1 facing players, as scores of level-2 facing players are close to nil.
+Therefore, both groups of condition can generalise to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
+
+## Second Experiment
+
+A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
+The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
+Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
+The participants faced two types of opponents, a level-1 and level-2 players, and played a total of 3 games (Rock-Paper-Scissors, Fire-Water-Grass, and the Penalty Shootout game), with repeated measures on the latter factor.
+Each game was split into 4 stages.
+The players faced either the level-1 or level-2 player on the first stage, and the other opponent in stage 2, for 20 rounds in each stage.
+Stages 3 and 4 were repetitions of the first two stages but with only 10 rounds in each stage.
+
+The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had the highest average score (M = 0.622, SD = 0.326).
+The higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
+Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
+To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will correct all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
+Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value < 0.0001 ;  FWG:  t(49) = 7.25 , p-value < 0.0001 ; SHOOT: t(49) = 13.61, p-value < 0.0001 ).
+
+Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
+We perform a two (condition: level-1 first, level-2 first) by two ( opp_type: level_1 or level_2) by three (game: RPS, FWG, SHOOT) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
+As the number of participants facing level-1 agents was slightly higher than those facing level-2 agents (27 vs 23), the ANOVA will not be balanced between the two levels of condition.
+We therefore used the “afex” (Singmann & al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
+The full results of this analysis are provided in Table XXXXXXXXX.
+
+There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, ges = 0.04,  p < .0001), meaning that we reject the null hypothesis of scores in games being equal.
+To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
+We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the SHOOT game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
+There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or  the condition factor (whether level-1 or level-2 opponent was faced first).
+This means that if we ignore potential secondary effects from interactions, neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
+
+### Learning transfer
+
+As a measure for learning transfer we will compare scores only on rounds 2-6 of each game (excluding the very first round where play is necessarily random).
+Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
+In the figure below, we show the average score across participants in rounds 2-6.
+These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
+For both the FWG and SHOOT games, score in the early rounds of the first stage are significantly higher than 0 for both opponent types.
+(Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; SHOOT:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; SHOOT:  t(270) = 3.21, p =0.004 ).
+Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shoot) when facing a level 1 opponent.
+Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
+These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
+
+# Discussion

### 2019-12-17 Report/draft_report_v1.tex
added results section to report

--- 2019-12-17 Report/draft_report_v1.Rmd
@@
----
-title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-shorttitle        : "draft"
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
+%
+\documentclass[,man,floatsintext]{apa6}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provides euro and other symbols
+\else % if luatex or xelatex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage[]{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\usepackage{xcolor}
+\usepackage{hyperref}
+\hypersetup{
+            pdftitle={Transfer of Learned Opponent Models in Zero Sum Games},
+            pdfauthor={Ismail Guennouni~\& Maarten Speekenbrink},
+            pdfkeywords={keywords},
+            colorlinks=true,
+            linkcolor=blue,
+            filecolor=Maroon,
+            citecolor=Blue,
+            urlcolor=Blue,
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-author: 
-  - name          : "Ismail Guennouni"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom"
-    email         : "i.guennouni.17@ucl.ac.uk"
-  - name          : "Maarten Speekenbrink"
-    affiliation   : "1"
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 
-affiliation:
-  - id            : "1"
-    institution   : "Department of Experimental Psychology, University College London"
+\shorttitle{draft}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Department of Experimental Psychology, University College London}
+\keywords{keywords\newline\indent Word count: X}
+\usepackage{csquotes}
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
 
-author_note: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+\usepackage{lineno}
+
+\linenumbers
+\usepackage[document]{ragged2e}
+
+\title{Transfer of Learned Opponent Models in Zero Sum Games}
+\author{Ismail Guennouni\textsuperscript{1}~\& Maarten Speekenbrink\textsuperscript{1}}
+\date{}
+
+\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
 
@@
 
-abstract: |
+Correspondence concerning this article should be addressed to Ismail Guennouni, Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom.
+E-mail: \href{mailto:i.guennouni.17@ucl.ac.uk}{\nolinkurl{i.guennouni.17@ucl.ac.uk}}}
+
+\abstract{
 Enter abstract here. Each new line herein must be indented, like this line.
 
-keywords          : "keywords"
-wordcount         : "X"
-
-# bibliography      : ["r-references.bib"]
-
-floatsintext      : yes
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-linkcolor         : "blue"
-mask              : no
-draft             : no
-
-class             : "man"
-output            : papaja::apa6_pdf
-header-includes   :
-  - \usepackage[document]{ragged2e}
----
-
-```{r load-packages, include = FALSE}
-library("papaja")
-require(knitr)
-require(citr)
-```
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-```
-
-```{r texreport}
-texreport <- function(object,effect.name,...) UseMethod("texreport")
-texreport.default <- function(object,effect.name,...) return(NULL)
-
-texreport.summary.merMod <- function(object,effect.name,print.estimate=TRUE) {
-  if(effect.name %in% rownames(object$coefficients)) {
-    tab <- object$coefficients
-    estimate <- tab[effect.name,"Estimate"]
-    se <- tab[effect.name,"Std. Error"]
-    Tval <- tab[effect.name,"t value"]
-    df <- tab[effect.name,"df"]
-    pval <- tab[effect.name,"Pr(>|t|)"]
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$b = ",round(estimate,2),"$, $SE = ",round(se,2),"$, $t(",round(df,2),") = ",round(Tval,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-  } else {
-    txt <- "error"
-  }
-  txt
 }
 
-texreport.summary.Anova.mlm <- function(object,effect.name,effect.size=TRUE,sphericity.correction=TRUE) {
-  if(effect.name %in% rownames(object$sphericity.tests) && sphericity.correction && object$sphericity.test[effect.name,"p-value"] < .05) {
-    epsilon <- object$pval.adjustments[effect.name,"HF eps"]
-    pval <- object$pval.adjustments[effect.name,"Pr(>F[HF])"]
-  } else {
-    epsilon <- 1
-    pval <- object$univariate.tests[effect.name,"Pr(>F)"]
-  }
-  df1 <- object$univariate.tests[effect.name,"num Df"]*epsilon
-  df2 <- object$univariate.tests[effect.name,"den Df"]*epsilon
-  Fval <- object$univariate.tests[effect.name,"F"]
-  etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-  # generate latex output
-  if(pval < .001) ptext <- "$p < .001$" else {
-    if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-      ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-    }
-  }
-  txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-  if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-  txt <- paste(txt,ptext,sep="")
-  txt
-}
+\begin{document}
+\maketitle
 
-texreport.linearHypothesis.mlm <- function(object,effect.size=TRUE) {
-  if(ncol(object$SSPH) == 1 & nrow(object$SSPH) == 1 & ncol(object$SSPE) == 1 & nrow(object$SSPE) == 1) {
-    df1 <- object$df
-    df2 <- object$df.residual
-    Fval <- (object$SSPH/df1)/(object$SSPE/df2)
-    pval <- 1-pf(Fval,object$df,object$df.residual)
-    etasq <- object$SSPH/(object$SSPH + object$SSPE)
-    # generate latex output
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-    if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-  } else {
-    txt <- "error"
-  }
-  txt
-}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-texreport.anova.lme <- function(object,effect.name,effect.size=FALSE) {
-  if(effect.name %in% rownames(object)) {
-    pval <- object[effect.name,"p-value"]
-    if(is.null(pval)) pval <- object[effect.name,"Pr(>F)"]
-    df1 <- object[effect.name,"numDF"]
-    df2 <- object[effect.name,"denDF"]
-    Fval <- object[effect.name,"F-value"]
-    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-    # generate latex output
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-    txt
-  }
-}
-
-texreport.anova <- function(object,effect.name,effect.size=FALSE) {
-  if(effect.name %in% rownames(object)) {
-    pval <- object[effect.name,"Pr(>F)"]
-    df1 <- object[effect.name,"NumDF"]
-    df2 <- object[effect.name,"DenDF"]
-    Fval <- object[effect.name,"F.value"]
-    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-    # generate latex output
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-    txt
-  }
-}
-
-```
-
-```{r read-data,warning=FALSE}
-# source("R/readData.R")
-# demo_exit <-  read.csv("data/demographics_and_exit_clean.csv")
-# trial_data <- read.csv("data/trial_data_clean.csv")
-# trial_data$trial <- 1:100
-```
-
-```{r, include=FALSE} 
-options(tinytex.verbose = TRUE)
-```
-
-# Introduction
 Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008).
@@
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Premack & Woodruff, 1978) play a role in determining human behaviour.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Premack \& Woodruff, 1978) play a role in determining human behaviour.
 
@@
 They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-Camerer & Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to conordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+Camerer \& Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to conordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
 They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
@@
 However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games, Cooper & Kagel (2003, 2004, 2008) find that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+In a series of experiments using economic signalling games, Cooper \& Kagel (2003, 2004, 2008) find that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
 They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
@@
 For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
-Shachat & Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
+Shachat \& Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
 They found that the players changed their strategies towards exploiting the deviations from the MSNE, and that this exploitation was very likely if the deviation from the MSNE play was high.
@@
 These strategies did not necessarily take into account the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
-Their play was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
+Their play was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+It is therefore important to have agents that \enquote{play like humans}, and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
 Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
-Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in 'level-k' theory, first adopted by Stahl & Wilson (1995).
+Instead, they will try to \enquote{satisfice} by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
+This concept finds its natural application in \enquote{level-k} theory, first adopted by Stahl \& Wilson (1995).
 It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment (Arad & Rubinstein, 2012).
+At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment (Arad \& Rubinstein, 2012).
 Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
@@
 
-# Methods
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
@@
 
-## first experiment:
+\hypertarget{first-experiment}{%
+\subsection{first experiment:}\label{first-experiment}}
 
@@
 In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-The overall score of the players was translated into the bonus by making each point worth $£$0.02.
-This bonus is significant as players could increase the total payoff from the experiment by up to 60% assuming they'd won all rounds against the computer opponent.
+The overall score of the players was translated into the bonus by making each point worth \$£\$0.02.
+This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they'd won all rounds against the computer opponent.
 
-## Second Experiment
+\hypertarget{second-experiment}{%
+\subsection{Second Experiment}\label{second-experiment}}
 
@@
 Figure XXXXXXXXX shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose ''right'' in the next round, we can win by both choosing ''left'' and ''center''.
+What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose \enquote{'right}' in the next round, we can win by both choosing \enquote{'left}' and \enquote{'center}'.
 A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
@@
 
-```{r feedback_rps, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align = "center"}
-
-# knitr::include_graphics("../Report/images/feedback_rps.png", dpi = 108)
-
-```
-
 In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
@@
 
-<!-- Figure\ \@ref(fig:feedback_rps) -->
-
 To summarise, all the games used in both experiments have a unique MSNE consisting of randomising across actions.
@@
 
-# Results
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-## First Experiment
+\hypertarget{first-experiment-1}{%
+\subsection{First Experiment}\label{first-experiment-1}}
 
@@
 As the number of participants facing level-2 agents was slightly higher than those facing level-1 agents (28 vs 24), the ANOVA is unbalanced.
-We therefore used the “afex” (Singmann & al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
+We therefore used the \enquote{afex} (Singmann \& al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
 
@@
 The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
-The main effect of Block ( F(1,50) = 22.51 , p < .001, ges = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning : as players get more interaction with the agent, they learn how to win more often.
+The main effect of Block ( F(1,50) = 22.51 , p \textless{} .001, ges = 0.03) shows that the average score in the first half of games (M = 0.29) was significantly lower than in the second half of the games played (M = 0.40), which translates to within-game learning : as players get more interaction with the agent, they learn how to win more often.
 The main effect of Condition (F(1,50) = 5.44, p = .024, ges = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
@@
 
-### Learning transfer
+\hypertarget{learning-transfer}{%
+\subsubsection{Learning transfer}\label{learning-transfer}}
 
-As a measure for learning transfer, we focus on participants’ scores in the earliest rounds, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
+As a measure for learning transfer, we focus on participants' scores in the earliest rounds, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
 A group of players with no experience of the game are expected to have scores not significantly different from 0.
@@
 As expected for the initial RPS game, the average score is not significantly different from 0 ( t(148.85) = 1.04 , p = 0.89).
-In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
+In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p \textless{} 0.0001).
 Unexpectedly, this is also the case for NUMBERS ( t(148.85) = 3.00, p = 0.0092).
 
-### Moderation of learning transfer by type of opponent and game similarity
+\hypertarget{moderation-of-learning-transfer-by-type-of-opponent-and-game-similarity}{%
+\subsubsection{Moderation of learning transfer by type of opponent and game similarity}\label{moderation-of-learning-transfer-by-type-of-opponent-and-game-similarity}}
 
@@
 
-## Second Experiment
+\hypertarget{second-experiment-1}{%
+\subsection{Second Experiment}\label{second-experiment-1}}
 
@@
 The higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
-Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will correct all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value < 0.0001 ;  FWG:  t(49) = 7.25 , p-value < 0.0001 ; SHOOT: t(49) = 13.61, p-value < 0.0001 ).
+Indeed, a player not aiming to uncover the opponent's strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
+To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will correct all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
+Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value \textless{} 0.0001 ; FWG: t(49) = 7.25 , p-value \textless{} 0.0001 ; SHOOT: t(49) = 13.61, p-value \textless{} 0.0001 ).
 
 Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
-We perform a two (condition: level-1 first, level-2 first) by two ( opp_type: level_1 or level_2) by three (game: RPS, FWG, SHOOT) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
+We perform a two (condition: level-1 first, level-2 first) by two ( opp\_type: level\_1 or level\_2) by three (game: RPS, FWG, SHOOT) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
 As the number of participants facing level-1 agents was slightly higher than those facing level-2 agents (27 vs 23), the ANOVA will not be balanced between the two levels of condition.
-We therefore used the “afex” (Singmann & al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
+We therefore used the \enquote{afex} (Singmann \& al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
 The full results of this analysis are provided in Table XXXXXXXXX.
 
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, ges = 0.04,  p < .0001), meaning that we reject the null hypothesis of scores in games being equal.
+There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, ges = 0.04, p \textless{} .0001), meaning that we reject the null hypothesis of scores in games being equal.
 To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
@@
 
-### Learning transfer
+\hypertarget{learning-transfer-1}{%
+\subsubsection{Learning transfer}\label{learning-transfer-1}}
 
@@
 For both the FWG and SHOOT games, score in the early rounds of the first stage are significantly higher than 0 for both opponent types.
-(Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; SHOOT:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; SHOOT:  t(270) = 3.21, p =0.004 ).
+(Level-1 opponent: FWG: t(270) = 4.99, p \textless{} 0.0001; SHOOT: t(270) = 6.66, p \textless{} 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p \textless{} 0.0001; SHOOT: t(270) = 3.21, p =0.004 ).
 Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shoot) when facing a level 1 opponent.
@@
 
-# Discussion
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+\end{document}

### 2020-01-13 Report/draft_report_v1.Rmd
added MBM and stayes_EWA

@@
 
-As a measure for learning transfer, we focus on participants’ scores in the earliest rounds, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
+As a measure for learning transfer, we focus on participants’ scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
 A group of players with no experience of the game are expected to have scores not significantly different from 0.

### 2020-01-13 comp_model_1019.Rmd
added MBM and stayes_EWA

@@
 
-# Fitting a bayesiam model WITH TRANSFER of opp strat distribution between games 
+# Fitting a bayesian model WITH TRANSFER of opp strat distribution between games 
 ```{r}
@@
     # Update state
-    curr_state<- new_state 
+    curr_state <- new_state 
     #}
@@
 
+##  Self-Tuning EWA with prior round play as state (Camerer & Ho 2007) 
+```{r}
+
+EWA_states <- function(par,data,return_value){
+
+  lambda <- par[1]
+  # Initiate N(0) = 1 as in Camerer and Ho 1997 paper.
+
+  #Define matrix of state spaces for each game 
+  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+  states_RPS <- paste0(G1$Var1,G1$Var2)
+
+  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+  states_FWG <- paste0(G2$Var1,G2$Var2)
+
+  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+  states_NUM <- paste0(G3$Var1,G3$Var2)
+
+  A_RPS = matrix(-0.5,9,3)
+  dimnames(A_RPS) = list(states_RPS, c("R", "P", "S"))
+
+  A_FWG = matrix(-0.5,9,3)
+  dimnames(A_FWG) = list(states_FWG, c("F", "W", "G"))
+
+  A_NUM = matrix(-0.5,25,5)
+  dimnames(A_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
+
+  # # Define reward matrices from the perspective of the row player (human in our case)
+  reward_RPS <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_RPS) = list(c("R", "P", "S"), c("R", "P", "S"))
+
+  reward_FWG <- t(matrix(c(0,-1,1,1,0,-1,-1,1,0),nrow=3,ncol=3))
+  dimnames(reward_FWG) = list(c("F", "W", "G"), c("F", "W", "G"))
+
+  reward_NUM <- t(matrix(c(0,-1,0,0,1,1,0,-1,0,0,0,1,0,-1,0,0,0,1,0,-1,-1,0,0,1,0),nrow=5, ncol=5))
+  dimnames(reward_NUM) = list(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+
+  # Initiate likelihood by trial vector 
+  lik_hum <- matrix(0.0,nrow(data))
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    if(t_game == "numbers") nopts <- 5 else nopts <- 3
+    if(data[t,"round"] == 1) {
+      Att <- switch(as.character(t_game),rps=A_RPS,fwg = A_FWG, numbers = A_NUM)
+      state_vec <- switch(as.character(t_game), rps=states_RPS, fwg = states_FWG, numbers = states_NUM)
+      reward <- switch(as.character(t_game), rps=reward_RPS, fwg = reward_FWG, numbers = reward_NUM)
+      game_data <- subset(data, game == t_game)
+      # first round is uniform prediction
+      lik_hum[t] <- 1/nopts
+      N <- 1.0
+
+      R_t <- rep(0.0,nopts)
+      H_t <- R_t
+
+      # Randomly select prev_state and actions for first round
+      curr_state <- sample(state_vec, size = 1)
+      h_act_prev <- sample(colnames(Att), size =1)
+      a_act_prev <- sample(colnames(Att), size =1)
+      #reward <- 0
+
+    } else {
+
+      indx <- data[t,"round"]
+      state_indx <- match(curr_state,state_vec)
+      #cat("this is the current state index", state_indx, "\n")
+
+      # Get reward and past human action
+      h_act_prev <- as.character(game_data[indx-1,"h_action"])
+      a_act_prev <- as.character(game_data[indx-1,"a_action"])
+      new_state <- paste0(h_act_prev,a_act_prev)
+
+      # Estimate phi(t)
+      R_t <- as.numeric(colnames(Att) == a_act_prev)
+      #cat("This is R(t)",R_t,"\n")
+
+      H_t <- (H_t*(indx-2) + R_t)/(indx-1)
+      #cat("this is H(t)",H_t,"\n")
+
+      Phi_t <- 1 - 0.5*sum((H_t-R_t)^2)
+      #cat("This is Phit(t)",Phi_t,"\t")
+
+      # Estimate vector Delta(t)
+
+      delta_t <- as.numeric(reward[,a_act_prev] >= as.numeric(game_data[indx-1,"score"]))
+      #cat("this is delta(t)",delta_t,"\n")
+
+      for (i in 1:nopts) {
+        action <- as.character(colnames(Att)[i])
+
+        #cat("this is current indexed action",action,"\n")
+        #cat("this is previous human action",h_act_prev,"\n")
+
+        # Attraction vector update rule
+        Att[state_indx,i] <- (Phi_t*N*Att[state_indx,i]  + ( delta_t[[i]] + (1- delta_t[[i]])*(action == h_act_prev))*as.numeric(reward[action,a_act_prev])) / (Phi_t*N + 1)
+      }
+
+      #Update the value of N 
+      N <- Phi_t*N + 1
+
+      # Assume human chooses action probabilistically using softmax on Attraction values
+      probs <- exp(lambda*Att[new_state,])/sum(exp(lambda*Att[new_state,]))
+
+      # Get actual human action and compute likelihood
+      h_act <- as.character(game_data[indx,"h_action"])
+      act_index <- match(h_act, colnames(Att))
+      lik_hum[t] <- probs[[act_index]]
+
+      curr_state <- new_state
+
+      # if (indx == 50) {
+      #   cat("this is the attraction matrix at last round of", "\n")
+      #   print(Att)
+      # }
+    }
+  }
+
+ if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret) || is.nan(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+}
+
+```
+
+```{r}
+# data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
+# EWA_states(0.1, data, "-2loglik")
+# optim(10.0,fn=EWA_states,gr = NULL, data=data,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
+
+EWA_states_modelling <- list()
+for(id in unique(dat$human_id)) {
+  EWA_states_modelling[[id]] <- list()
+  tdat <- subset(dat,human_id == id)
+#   EWA_states_modelling[[id]] <- optim(10.0,fn=EWA_states,gr = NULL, data=tdat,"-2loglik", lower = 0.0, upper = 200, method="L-BFGS-B")
+# }
+  EWA_states_modelling[[id]] <- DEoptim(fn=EWA_states, lower = 0.0, upper = 100.0, data=tdat, "-2loglik", control=list(trace = FALSE,parallelType=1))
+}
+
+save(EWA_states_modelling,file="EWA_states_modelling.RData")
+
+```
+
+## What next?: Fitting models that explicitly take into account opponent strategy.
+LOLA?
+Won't work, it suffers from same issues as normal QL in that most states are not visited during game play.
+Influence model?
+Like belief lerning.
+it still has no sequential memory, still computes distribution on beliefs.
+We need to incorporate models that can mimic human memory by looking at history of play and leverage sequence prediction capabilities.
+
+### Model based model: learn transition probabilities to new states.
+Weigh the value of an action by the conditional probability of ending up in a future state times the value of the new state....
+once you take an action in current round, you can only end up in 3 states, with probabilities p, q and 1-p-q.
+You are learning these probabilities by updating priors (initial prior is dirichlet).
+```{r}
+MBM <- function(par,data,return_value,gamma){
+  # Par[1] -> beta= inverse temperature parameter in softmax choice function
+  # Par[2] -> lambda = learning rate (one per game?)
+  # data : participant and ai choice data.
+  # return_value=c("-2loglik","likelihood_by_trial")
+  # Gamma is discount factor for future rewards 
+  # Returns Q-values per trial and predicts choice using softmax
+  beta <- par[1]
+  alpha <- par[2]
+
+  #gamma <- 0.9
+
+  #Define matrix of state spaces for each game 
+  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+  states_RPS <- paste0(G1$Var1,G1$Var2)
+
+  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+  states_FWG <- paste0(G2$Var1,G2$Var2)
+
+  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
+  states_NUM <- paste0(G3$Var1,G3$Var2)
+
+  # Matrices to store Q_values in each state 
+  Q_vals_RPS = matrix(-0.5,9,3)
+  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
+  Q_vals_FWG = matrix(-0.5,9,3)
+  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
+  Q_vals_NUM = matrix(-0.5,25,5)
+  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
+
+  # Transition Matrices 
+  Transit_RPS = matrix(0,9,9)
+  dimnames(Transit_RPS) = list(states_RPS, states_RPS)
+  Transit_FWG = matrix(0,9,9)
+  dimnames(Transit_FWG) = list(states_FWG, states_FWG)
+  Transit_NUM = matrix(0,25,25)
+  dimnames(Transit_NUM) = list(states_NUM, states_NUM)
+
+  lik_hum <- matrix(0.0,nrow(data))
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    if(t_game == "numbers") nopts <- 5 else nopts <- 3
+
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
+      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
+      Transit <- switch(as.character(t_game),rps=Transit_RPS,fwg = Transit_FWG, numbers = Transit_NUM)
+      lik_hum[t] <- 1/nopts
+      # Randomly select prev_state and actions for first round
+      curr_state <- sample(state_vec, size = 1)
+      h_act <- sample(colnames(Q_vals), size =1)
+      ai_act <- sample(colnames(Q_vals), size =1)
+      reward <- 0
+
+    } else {
+      # Get past human action and associated reward 
+      h_act <- as.character(data[t-1,"h_action"])
+      ai_act <- as.character(data[t-1,"a_action"])
+      reward <- as.numeric(data[t-1,"score"])
+    }
+
+    # cat(curr_state, " This is the previous state", "\n")
+    new_state <- paste0(h_act,ai_act)
+    # cat(new_state,"This is new state","\n")
+
+    # Update Transit matrix ....first create hot vector = 1 if new state, 0 otherwise 
+    hot_vector <- state_vec == new_state
+
+    # Transit probs update: TD learning on transition matrix, learning rate fixed at 0.1
+    Transit[curr_state,] <- Transit[curr_state,] + 0.1* (hot_vector - Transit[curr_state,])
+    #cat(Transit[curr_state,], "\n")
+
+    # Update Q-values as current reward + a weighted (by trasnsit probs) average of future Q-values.
+    Q_Row_max <- apply(Q_vals, 1, max, na.rm = TRUE)
+    #cat(Transit[curr_state,] * Q_Row_max, "\n")
+    Q_vals[curr_state, h_act] <- reward +  gamma*( Transit[curr_state,] %*% Q_Row_max  )
+
+    # Assume human chooses action probabilistically using softmax on Q values
+    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
+    #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }
+
+    # Get actual human action and compute likelihood
+    h_act <- as.character(data[t,"h_action"])
+    act_index <- match(h_act, colnames(Q_vals))
+    lik_hum[t] <- probs[[act_index]]
+
+    # Update state
+    curr_state<- new_state 
+    #}
+  }
+  if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret) || is.nan(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+
+}
+
+```
+
+```{r}
+MBM_modelling <- list()
+for(id in unique(dat$human_id)) {
+  MBM_modelling[[id]] <- list()
+  tdat <- subset(dat,human_id == id)
+  # MBM_modelling[[id]] <- optim(c(1,0.1),fn=QMBM,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
+
+   MBM_modelling[[id]] <- DEoptim(fn=MBM,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0.9, control=list(trace = FALSE,parallelType=1))
+}
+
+save(MBM_modelling, file="MBM_modelling.RData")
+
+```
+
 ## Putting results together 
@@
 load("EWA_self_modelling.RData")
+load("MBM_modelling.RData")
+load("EWA_states_modelling.RData")
 
@@
                          #Lambda is a parameter of the softmax choice function (inverse Temperature)
-                         "EWA_self_Lambda" = EWA_self_modelling[[id]]$optim$bestmem[1]
+                         "EWA_self_Lambda" = EWA_self_modelling[[id]]$optim$bestmem[1],
+
+                         # EWA with states
+
+                         "EWA_states_BIC" = EWA_states_modelling[[id]]$optim$bestval + 1*log(150),
+                         "EWA_states_Lambda" = EWA_states_modelling[[id]]$optim$bestmem[1],
+
+                         # MBM 
+                          # MBM BIC
+                         "MBM_BIC" = MBM_modelling[[id]]$optim$bestval + 2*log(150),
+                          # BEta parameter inverse temp in softmax 
+                         "MBM_beta" = MBM_modelling[[id]]$optim$bestmem[1],
+                         "MBM_alpha" = MBM_modelling[[id]]$optim$bestmem[2]
 
@@
 ```{r}
-Table_results <- table(All_results[, "condition"],c("random","Bayes Tr","Bayes No Tr","QL", "QL_states","EWA","S_EWA")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)])
+Table_results <- table(All_results[, "condition"],c("random","Bayes Tr","Bayes No Tr","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC","MBM_BIC")],1,which.min)])
 
@@
 ```
-##### Looks like most participants behavior can be explained by Bayes with or without transfer. Most others are consistent with random behavior, and only 1 with QL and 1 with S_EWA.
+##### Looks like most participants behavior can be explained by QL_states.
+Bayesian models best explain a few more behaviors, while the others are consistent with random behavior, and only 1 with QL and 1 with S_EWA.
 
@@
 #Early game scores for people best modelled with a Bayesian model with transfer are indeed higher than those best modelled without transfer but difference is not statistically significant.
-
-## What next?: Fitting models that explicitly take into account opponent strategy.
-LOLA?
-Won't work, it suffers from same issues as normal QL in that most states are not visited during game play.
-Influence model?
-Like belief lerning.
-it still has no sequential memory, still computes distribution on beliefs.
-We need to incorporate models that can mimic human memory by looking at history of play and leverage sequence prediction capabilities.
-
-### Model based model: compute transition probabilities to new states.
-Weigh the value of an action by the conditional probabilty of ending up in a future state....
-once you take an action in current round, you can only end up in 3 states, with probabilities p, q and 1-p-q.
-You are learning these probabilities by updating priors (initial prior is dirichlet).
-```{r}
-MBM <- function(par,data,return_value,gamma){
-  # Par[1] -> beta= inverse temperature parameter in softmax choice function
-  # Par[2] -> lambda = learning rate (one per game?)
-  # data : participant and ai choice data.
-  # return_value=c("-2loglik","likelihood_by_trial")
-  # Gamma is discount factor for future rewards 
-  # Returns Q-values per trial and predicts choice using softmax
-  beta <- par[1]
-  alpha <- par[2]
-
-  #gamma <- 0.9
-
-  #Define matrix of state spaces for each game 
-  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
-  states_RPS <- paste0(G1$Var1,G1$Var2)
-
-  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
-  states_FWG <- paste0(G2$Var1,G2$Var2)
-
-  G3 <- expand.grid(c("1", "2", "3", "4", "5"), c("1", "2", "3", "4", "5"))
-  states_NUM <- paste0(G3$Var1,G3$Var2)
-
-  # Matrices to store Q_values in each state 
-  Q_vals_RPS = matrix(-0.5,9,3)
-  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
-  Q_vals_FWG = matrix(-0.5,9,3)
-  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
-  Q_vals_NUM = matrix(-0.5,25,5)
-  dimnames(Q_vals_NUM) = list(states_NUM, c("1", "2", "3", "4", "5"))
-
-  # Initiate probability vectors
-
-  lik_hum <- matrix(0.0,nrow(data))
-
-  for(t in 1:nrow(data)) {
-    t_game <- data[t,"game"]
-    if(t_game == "numbers") nopts <- 5 else nopts <- 3
-
-    if(data[t,"round"] == 1) {
-      # first round is uniform prediction
-      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, numbers = Q_vals_NUM)
-      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, numbers = states_NUM)
-      lik_hum[t] <- 1/nopts
-      # Randomly select prev_state and actions for first round
-      curr_state <- sample(state_vec, size = 1)
-      h_act <- sample(colnames(Q_vals), size =1)
-      ai_act <- sample(colnames(Q_vals), size =1)
-      reward <- 0
-
-    } else {
-      # Get past human action and associated reward 
-      h_act <- as.character(data[t-1,"h_action"])
-      ai_act <- as.character(data[t-1,"a_action"])
-      reward <- as.numeric(data[t-1,"score"])
-    }
-
-    # cat(curr_state, " This is the previous state", "\n")
-    new_state <- paste0(h_act,ai_act)
-    # cat(new_state,"This is new state","\n")
-
-    # Q_learning: update rule (time  = t-1)
-    Q_vals[curr_state, h_act] <- Q_vals[curr_state, h_act] + alpha*( reward + gamma*max(Q_vals[new_state,]) - Q_vals[curr_state, h_act])
-
-    # Assume human chooses action probabilistically using softmax on Q values
-    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
-    #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }
-
-    # Get actual human action and compute likelihood
-    h_act <- as.character(data[t,"h_action"])
-    act_index <- match(h_act, colnames(Q_vals))
-    lik_hum[t] <- probs[[act_index]]
-
-    # Update state
-    curr_state<- new_state 
-    #}
-  }
-  if(return_value == "-2loglik") {
-    ret <- -2*sum(log(lik_hum))
-    if(is.infinite(ret) || is.nan(ret)) {
-      return(1e+300)
-    } else {
-      return(ret)
-    }
-  }
-  if(return_value == "likelihood_by_trial") return(lik_hum)
-
-}
-
-```

### 2020-01-14 Experiment_2/Experiment_2_modelling.Rmd
model based model added to experiment 2

@@
 
+## MBM in experiment 2  
+```{r}
+MBM_2 <- function(par,data,return_value,gamma){
+  # Par[1] -> beta= inverse temperature parameter in softmax choice function
+  # Par[2] -> lambda = learning rate (one per game?)
+  # data : participant and ai choice data.
+  # return_value=c("-2loglik","likelihood_by_trial")
+  # Gamma is discount factor for future rewards 
+  # Returns Q-values per trial and predicts choice using softmax
+  beta <- par[1]
+  alpha <- par[2]
+
+  #gamma <- 0.9
+
+  #Define matrix of state spaces for each game 
+  G1 <- expand.grid(c("R", "P", "S"),c("R", "P", "S"))
+  states_RPS <- paste0(G1$Var1,G1$Var2)
+
+  G2 <- expand.grid(c("F", "W", "G"), c("F", "W", "G"))
+  states_FWG <- paste0(G2$Var1,G2$Var2)
+
+  G3 <- expand.grid(c("left","right","center"), c("left","right","center"))
+  states_SHOOT <- paste0(G3$Var1,G3$Var2)
+
+  # Matrices to store Q_values in each state 
+  Q_vals_RPS = matrix(-0.5,9,3)
+  dimnames(Q_vals_RPS) = list(states_RPS, c("R", "P", "S"))
+  Q_vals_FWG = matrix(-0.5,9,3)
+  dimnames(Q_vals_FWG) = list(states_FWG, c("F", "W", "G"))
+  Q_vals_SHOOT = matrix(-0.5,9,3)
+  dimnames(Q_vals_SHOOT) = list(states_SHOOT, c("left","right","center"))
+
+  # Transition Matrices 
+  Transit_RPS = matrix(0,9,9)
+  dimnames(Transit_RPS) = list(states_RPS, states_RPS)
+  Transit_FWG = matrix(0,9,9)
+  dimnames(Transit_FWG) = list(states_FWG, states_FWG)
+  Transit_SHOOT = matrix(0,9,9)
+  dimnames(Transit_SHOOT) = list(states_SHOOT, states_SHOOT)
+
+  lik_hum <- matrix(0.0,nrow(data))
+  nopts <- 3
+
+  for(t in 1:nrow(data)) {
+    t_game <- data[t,"game"]
+    if(data[t,"round"] == 1) {
+      # first round is uniform prediction
+      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
+      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, shootout = states_SHOOT)
+      Transit <- switch(as.character(t_game),rps=Transit_RPS,fwg = Transit_FWG, shootout = Transit_SHOOT)
+      lik_hum[t] <- 1/nopts
+
+      # Randomly select prev_state and actions for first round
+      curr_state <- sample(state_vec, size = 1)
+      h_act <- sample(colnames(Q_vals), size =1)
+      ai_act <- sample(colnames(Q_vals), size =1)
+      reward <- 0
+
+    } else {
+      # Get past human action and associated reward 
+      h_act <- as.character(data[t-1,"h_action"])
+      ai_act <- as.character(data[t-1,"a_action"])
+      reward <- as.numeric(data[t-1,"score"])
+    }
+
+    # cat(curr_state, " This is the previous state", "\n")
+    new_state <- paste0(h_act,ai_act)
+    # cat(new_state,"This is new state","\n")
+
+    # Update Transit matrix ....first create hot vector = 1 if new state, 0 otherwise 
+    hot_vector <- state_vec == new_state
+
+    # Transit probs update: TD learning on transition matrix, learning rate fixed at 0.1
+    Transit[curr_state,] <- Transit[curr_state,] + 0.1* (hot_vector - Transit[curr_state,])
+    #cat(Transit[curr_state,], "\n")
+
+    # Update Q-values as current reward + a weighted (by trasnsit probs) average of future Q-values.
+    Q_Row_max <- apply(Q_vals, 1, max, na.rm = TRUE)
+    #cat(Transit[curr_state,] * Q_Row_max, "\n")
+    Q_vals[curr_state, h_act] <- reward +  gamma*( Transit[curr_state,] %*% Q_Row_max  )
+
+    # Assume human chooses action probabilistically using softmax on Q values
+    probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
+    #if (data[t,"round"] == 50) { cat(Q_vals,"\n") }
+
+    # Get actual human action and compute likelihood
+    h_act <- as.character(data[t,"h_action"])
+    act_index <- match(h_act, colnames(Q_vals))
+    lik_hum[t] <- probs[[act_index]]
+
+    # Update state
+    curr_state<- new_state 
+    #}
+  }
+  if(return_value == "-2loglik") {
+    ret <- -2*sum(log(lik_hum))
+    if(is.infinite(ret) || is.nan(ret)) {
+      return(1e+300)
+    } else {
+      return(ret)
+    }
+  }
+  if(return_value == "likelihood_by_trial") return(lik_hum)
+
+}
+
+```
+
+```{r}
+
+#MBM_2(c(2, 0.1), test_data,"-2loglik", gamma = 0.9 )
+
+MBM2_modelling <- list()
+for(id in unique(dat$human_id)) {
+  MBM_modelling[[id]] <- list()
+  tdat <- subset(dat,human_id == id)
+  # MBM_modelling[[id]] <- optim(c(1,0.1),fn=QMBM,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
+
+   MBM2_modelling[[id]] <- DEoptim(fn=MBM_2,lower = c(0,0), upper = c(10,1), data=tdat,"-2loglik", gamma = 0.9, control=list(trace = FALSE,parallelType=1))
+}
+
+save(MBM2_modelling, file="MBM2_modelling.RData")
+
+```
+
 ## Putting all results together 
@@
 
-# Load various modelling tabeles
+# Load various modelling tables
 
@@
 load("exp2_SEWA_modelling.RData")
+load("MBM2_modelling.RData")
 
@@
                          # Self-Tuning EWA (only 1 parameter)
-                          # Parametric EWA BIC
+                          # BIC
                          "EWA_self_2LL" = exp2_SEWA_modelling[[id]]$optim$bestval,
@@
                          #Lambda is a parameter of the softmax choice function (inverse Temperature)
-                         "EWA_self_Lambda" = exp2_SEWA_modelling[[id]]$optim$bestmem[1]
+                         "EWA_self_Lambda" = exp2_SEWA_modelling[[id]]$optim$bestmem[1],
+
+                         # Model Based Model
+                          # BIC
+                         "MBM_2LL" = MBM2_modelling[[id]]$optim$bestval,
+                         "MBM2_BIC" = MBM2_modelling[[id]]$optim$bestval + 2*log(180),
+                          # Alpha is learning rate, beta is temperature in softmax
+                         "MBM2_alpha" = MBM2_modelling[[id]]$optim$bestmem[1],
+                         "MBM2_beta" = MBM2_modelling[[id]]$optim$bestmem[2]
 
@@
 ```
+
 ```{r}
@@
 ```
+
 # Total time by best predictive model

### 2020-01-14 Experiment_2/Experiment_2_modelling.Rmd
draft update discussion

@@
 ```{r setup, include=FALSE}
+library(knitr)
 knitr::opts_chunk$set(echo = TRUE)
@@
 dat_exp2 <- read.csv("data_exp2.csv")
+test_data = subset(dat_exp2,human_id == "bZg1T3MNoItL6b7qAAAj")
+```
 
+```{r}
 # Function to produce best reponse to ai_action in exp2
@@
 
-test_data = subset(dat_exp2,human_id == "bZg1T3MNoItL6b7qAAAj")
 exp2_naive_bayes(c(0.5,0.1),test_data,c("level0","level1","level2"),"-2loglik",TRUE)
@@
 MBM2_modelling <- list()
-for(id in unique(dat$human_id)) {
-  MBM_modelling[[id]] <- list()
-  tdat <- subset(dat,human_id == id)
+for(id in unique(dat_exp2$human_id)) {
+  MBM2_modelling[[id]] <- list()
+  tdat <- subset(dat_exp2,human_id == id)
   # MBM_modelling[[id]] <- optim(c(1,0.1),fn=QMBM,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
@@
 ```{r}
-exp2_table_results <- table(exp2_results[, "condition"],c("random","Bayes Tr","Bayes No Tr", "QL_states","S_EWA")[apply(exp2_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC")],1,which.min)])
+exp2_table_results <- table(exp2_results[, "condition"],c("random","Bayes Tr","Bayes No Tr", "QL_states","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
 
@@
   id_results <- subset(exp2_results, ID == id)
-  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC")],1,min)
+  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
 
-  best_model <- c("random","Bayes Tr","Bayes NT", "QL_states","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC")],1,which.min)]
+  best_model <- c("random","Bayes Tr","Bayes NT", "QL_states","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
   # 

### 2020-01-14 Report/draft_report_v1.Rmd
draft update discussion

@@
 ```{r load-packages, include = FALSE}
-library("papaja")
+#library("papaja")
 require(knitr)
 require(citr)
+# using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
+library(tidyr)
+library(dplyr)
+library(MASS)
+library(ggpubr)
+library(PairedData)
+library(multcompView)
+library(lsmeans)
 ```
@@
 options(tinytex.verbose = TRUE)
+```
+
+```{r, include = FALSE}
+#Experiment 1 raw data
+dat <- read.csv("../data20180719.csv")
+
+# transform 'winner' variable in numeric score
+dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
+# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
+dat$block <- factor(as.numeric(cut(dat$round,2)),labels =c("first half", "second half"))
+
+# create a new variable "game.f" as a factor variable of games
+dat$game.f <- factor(dat$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))
+
+#Group data by human_id and calculate mean score per block of each game.
+dat2 <- dat %>% 
+  group_by(human_id,condition,game,block,game.f) %>% 
+      summarize(block_score = mean(score))
+
+# Group data by game and ID
+dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
+
+```
+
+```{r, include = TRUE}
+# AFEX PACKAGE FOR RUNNING RM ANOVA AND POST HOC TESTS ############################
+citation(package = "afex", lib.loc = NULL, auto = NULL)
+library(afex)
+a1 <- aov_car( block_score ~ game.f*block*condition + Error(human_id/(game.f*block)), dat2)
+summary(a1)
+(a1_nice <- nice(a1, es = attr(a1$anova_table, "es"),
+  observed = attr(a1$anova_table, "observed"),
+  correction = attr(a1$anova_table, "correction"), MSE = NULL,
+  intercept = NULL, p_adjust_method = attr(a1$anova_table,
+  "p_adjust_method"), sig_symbols = attr(a1$anova_table, "sig_symbols")))
+
+write.table(a1_nice,file = "a1.txt", sep = ",", quote = FALSE, row.names = F)
+```
+
+```{r}
+#Pair waise comparison and post hoc tests for the interaction: Game * Block using lsmeans
+
+# game score differences statistically significant?
+(ls0 <- lsmeans(a1, "game.f"))
+(lsm0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
+
+# Main effect of block 
+(ls01 <- lsmeans(a1, "block"))
+(lsm01 <- update(pairs(ls01, reverse = TRUE), by=NULL, adjust = "holm"))
+lsmip(a1, ~block)
+
+# Main effect of condition
+(ls02 <- lsmeans(a1, "condition"))
+(lsm02 <- update(pairs(ls02, reverse = TRUE), by=NULL, adjust = "holm"))
+
+```
+
+```{r}
+# Learning transfer using first half scores: Pairwise comparison of first halves by game ( first half RPS vs first half WFG scores....)
+(ls1 <- lsmeans(a1, "game.f", by="block"))
+(lsm1 <- update(pairs(ls1, reverse = TRUE), by=NULL, adjust = "holm"))
+lsmip(a1, game.f ~ block)
+```
+
+```{r}
+(means.int <- lsmeans(a1, specs = c("game.f","block","condition")))
+
+# Transfer level1: compare H1FWG with H1RPS 
+con1  <- contrast(means.int, list(H1_G2vsH1_G1forlvl1 = c(-1,1,0,0,0,0,0,0,0,0,0,0), H1_G3vsH1_G1forlvl1=c(-1,0,1,0,0,0,0,0,0,0,0,0)))
+summary(con1, adjust = "holm")
+
+# Transfer level2: compare H1FWG with H1RPS 
+con2  <- contrast(means.int, list(H1_G2vsH1_G1forlvl2 = c(0,0,0,0,0,0,-1,1,0,0,0,0), H1_G3vsH1_G1forlvl2=c(0,0,0,0,0,0,-1,0,1,0,0,0)))
+summary(con2, adjust = "holm")
+```
+
+```{r}
+
+#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########
+
+dat_26 <- subset(dat,round >1 & round <7, drop =TRUE)
+dat2_6 <- dat_26 %>% 
+  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
+      summarise(early_score = mean(score))
+
+# Check group means and SDs
+group_by(dat2_6, game.f) %>%
+  summarise(
+    count = n(),
+    mean = mean(early_score, na.rm = TRUE),
+    sd = sd(early_score, na.rm = TRUE)
+    )
+group_by(dat2_6, game.f,condition) %>%
+  summarise(
+    count = n(),
+    mean = mean(early_score, na.rm = TRUE),
+    sd = sd(early_score, na.rm = TRUE)
+    )
+# plot scores per game 
+ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
 ```
@@
 
-Figure 10 shows the marginal mean scores for each game for both level-1 and level-2 facing players.
+Figure XXXXX shows the marginal mean scores for each game for both level-1 and level-2 facing players.
 Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
@@
 
-As a measure for learning transfer we will compare scores only on rounds 2-6 of each game (excluding the very first round where play is necessarily random).
+As a measure for learning transfer we will compare scores only on the first 5 rounds (rounds 2-6 of each game, excluding the very first round where play is necessarily random).
 Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
@@
 
+# Computational modelling
+
+To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent.
+As a base model, we assume play is random, and each potential action is chosen with equal probability.
+Note that this corresponds to the Nash equilibrium strategy.
+Next, we include for comparison purposes a few other basic models of behavior, such as Q-learning on action choices, as well as a more sophisticatd Q-learning model incorporating a state space consisting of last round play.
+The Bayesian approach is represented by models whereby agents would update an initial belief over the opponent's strategy consisting of various level-k strategies (resp.
+0,1 and 2).
+We fitted two models in which agents best respond to the opponent model.
+In the first, the beliefs about the opponent's adopted strategy are transfered across games, and another in which no transfer of opponent models is allowed.
+
+Next, we fitted a self-tuning EWA model (Ho et al., 2004) both on action choices without states and with states consisting of lat round play.
+The self-tuning EWA model generalizes both reinforcement learning as well as fictitious play models and has been proven to do well than equilibrium models in various game situations.
+Finally, we also included a model-based reinforcement learning approach.
+whereby the agent learns the transition probabilities between states ans uses that to choose the best action, given the current state and it's belief about what the new state will be.
+
+All models were fit to each participant in both experiments, with optimal parameters being estimated using maximum likelihood.
+Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was explained by each model.
+Table XXX  shows the results for experiment 1, while Table XXXX shows those for experiment 2.
+we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
+In experiment 2 hwever, that model wasn't as successful as the bayesian approached in fitting player's action choices.
+In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) were by far the most successful.
+
+Next we compared the performance of players whose actions are consistent with each of our hypothesized models.
+Figure XXXX shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior.
+participants whose actions are most consistent with learning an opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play.
+EWA, QL and random players had, understandably the lowest performance.
+
 # Discussion
+
+In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies.
+We were interested in uncovering evidence for transfer and exploring whether it is modulated by the degree of similarity between games and the sophistication of the agent.
+
+The results of our first online experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
+We found that using results on very early rounds is a better proxy for measuring transfer as it is not tainted by any within game learning.
+Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
+
+In the second online experiment, the paradigm was better suited to explore our main research question, related to learning transfer rather than within-game learning.
+Indeed, when facing two opponents sequentially, there are many more opportunities to test transfer than before.
+Indeed, there are 2 opportunities to transfer knowledge within each game, and a total of three games, which means 6 opportunities to test transfer.
+When we made players face only one type of opponent each, we only had two possible learning transfers to test.
+In that regard, the results on learning transfer confirmed prior findings from the first experiment.
+While there was no evidence of learning transfer across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
+We also found that learning transfer is modulated by the type of opponent faced.
+When the players faced the level-1 opponent, they were able to transfer learning.
+However, when they faced the level-2 opponent, there was weaker evidence for transfer.
+The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with.
+A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
+
+Coming back to evidence for learning transfer, it is undeniable that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
+The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and SHOOT?
+what did the players learn exactly about the opponent strategy and what form did this learning take?
+
+We will proceed by eliminating multiple hypotheses.
+First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
+An example is a spatial heuristic that consists of choosing "weapons" in a particular order (for instance left to right).
+Thsi was one of the weaknesses in the design of experiment one, and we took this into accounr in experiment two by randomly shuffling the spatial order of action choices in each round.
+Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.
+
+A second possible hypothesis for learning the opponent’s strategy is the use of simple heuristis based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
+Our Q-learning with states as prior round play model is a good proxy for this type of strategies.
+While this approach certainly seemed to be the best fit for player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
+Indeed, learning the best action in a particular state cannot easily transer to a new game since the state space is different and there is no simgle mapping between the state spaces of the initial and latter games.
+These rules would thereofre need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
+
+Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, require a long time to learn.
+Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
+After all, if players were using some type of associative learning or spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
+The fact that the degree of sophisitication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
+
+The more likely explanation of the learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
+A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
+For instance, the player may think “My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be”.
+
+This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
+This type of learning would be deemed “explicit” in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
+It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
+Since it is less context dependent, this type of learning is generalizable to new situations.
+
+"""
+
+To explain the presence of learning transfer, we believe that the most probable account is that some participants are learning a “strategic rule” by which they can anticipate the opponent’s next action and best respond to it.
+Certainly, given the heterogeneity in game scores, not all participants were able to do that.
+As we can see from figure 13, some players are able to score consistently high in early stages and keep a good performance throughout the game while other never quite manage to consistently beat the opponent.
+
+Given the evidence for transfer in early rounds, we believe a significant number of participants did indeed uncover patterns in the opponent’s play that they could leverage to anticipate future actions.
+In fact, the correlation coefficient between scores against level-1 and level-2 opponents is 57%, significantly higher than 0.
+
+"""

### 2020-01-15 Experiment_2/exp2_clean_analysis.Rmd
finalise v1 of report

--- 2019-12-03 Experiment_2/clean_analysis.Rmd
@@
 #Average bonus per participant 
-bonus_to_be_paid <- mean(dat_score$avg_bonus)
+#bonus_to_be_paid <- mean(dat_score$avg_bonus)
 
@@
   summarize(int_score = mean(adj_score))
+
+write.csv(dat, file = "dat_exp2.csv")
+write.csv(dat_int, file = "dat_int_exp2.csv")
+```
+
+```{r}
 
@@
 # AFEX PACKAGE FOR RUNNING RM ANOVA AND POST HOC TESTS ############################
-citation(package = "afex", lib.loc = NULL, auto = NULL)
+#citation(package = "afex", lib.loc = NULL, auto = NULL)
 library(afex)
@@
 summary(a1)
+
 (a1_nice <- nice(a1, es = attr(a1$anova_table, "es"),

### 2020-01-15 Report/draft_report_v1.Rmd
finalise v1 of report

@@
 title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-shorttitle        : "draft"
+
+shorttitle        : "Draft-1"
 
@@
 author_note: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+  <!-- Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line. -->
 
@@
 draft             : no
+fig_caption       : yes
 
-class             : "man"
+documentclass     : "apa6"
+classoption       : "man"
 output            : papaja::apa6_pdf
@@
 ```{r load-packages, include = FALSE}
-#library("papaja")
+library(papaja)
 require(knitr)
 require(citr)
+require(bookdown)
 # using some functions dplyr, ggpubr, PairedData and sjPlot. Need to be loaded. 
@@
 library(ggpubr)
+library(afex)
 library(PairedData)
@@
 ```{r texreport}
-texreport <- function(object,effect.name,...) UseMethod("texreport")
-texreport.default <- function(object,effect.name,...) return(NULL)
+# texreport <- function(object,effect.name,...) UseMethod("texreport")
+# texreport.default <- function(object,effect.name,...) return(NULL)
+# 
+# texreport.summary.merMod <- function(object,effect.name,print.estimate=TRUE) {
+#   if(effect.name %in% rownames(object$coefficients)) {
+#     tab <- object$coefficients
+#     estimate <- tab[effect.name,"Estimate"]
+#     se <- tab[effect.name,"Std. Error"]
+#     Tval <- tab[effect.name,"t value"]
+#     df <- tab[effect.name,"df"]
+#     pval <- tab[effect.name,"Pr(>|t|)"]
+#     if(pval < .001) ptext <- "$p < .001$" else {
+#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+#       }
+#     }
+#     txt <- paste("$b = ",round(estimate,2),"$, $SE = ",round(se,2),"$, $t(",round(df,2),") = ",round(Tval,2),"$, ",sep="")
+#     txt <- paste(txt,ptext,sep="")
+#   } else {
+#     txt <- "error"
+#   }
+#   txt
+# }
 
-texreport.summary.merMod <- function(object,effect.name,print.estimate=TRUE) {
-  if(effect.name %in% rownames(object$coefficients)) {
-    tab <- object$coefficients
-    estimate <- tab[effect.name,"Estimate"]
-    se <- tab[effect.name,"Std. Error"]
-    Tval <- tab[effect.name,"t value"]
-    df <- tab[effect.name,"df"]
-    pval <- tab[effect.name,"Pr(>|t|)"]
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$b = ",round(estimate,2),"$, $SE = ",round(se,2),"$, $t(",round(df,2),") = ",round(Tval,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-  } else {
-    txt <- "error"
-  }
-  txt
-}
-
-texreport.summary.Anova.mlm <- function(object,effect.name,effect.size=TRUE,sphericity.correction=TRUE) {
-  if(effect.name %in% rownames(object$sphericity.tests) && sphericity.correction && object$sphericity.test[effect.name,"p-value"] < .05) {
-    epsilon <- object$pval.adjustments[effect.name,"HF eps"]
-    pval <- object$pval.adjustments[effect.name,"Pr(>F[HF])"]
-  } else {
-    epsilon <- 1
-    pval <- object$univariate.tests[effect.name,"Pr(>F)"]
-  }
-  df1 <- object$univariate.tests[effect.name,"num Df"]*epsilon
-  df2 <- object$univariate.tests[effect.name,"den Df"]*epsilon
-  Fval <- object$univariate.tests[effect.name,"F"]
-  etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-  # generate latex output
-  if(pval < .001) ptext <- "$p < .001$" else {
-    if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-      ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-    }
-  }
-  txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-  if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-  txt <- paste(txt,ptext,sep="")
-  txt
-}
-
-texreport.linearHypothesis.mlm <- function(object,effect.size=TRUE) {
-  if(ncol(object$SSPH) == 1 & nrow(object$SSPH) == 1 & ncol(object$SSPE) == 1 & nrow(object$SSPE) == 1) {
-    df1 <- object$df
-    df2 <- object$df.residual
-    Fval <- (object$SSPH/df1)/(object$SSPE/df2)
-    pval <- 1-pf(Fval,object$df,object$df.residual)
-    etasq <- object$SSPH/(object$SSPH + object$SSPE)
-    # generate latex output
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-    if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-  } else {
-    txt <- "error"
-  }
-  txt
-}
-
-texreport.anova.lme <- function(object,effect.name,effect.size=FALSE) {
-  if(effect.name %in% rownames(object)) {
-    pval <- object[effect.name,"p-value"]
-    if(is.null(pval)) pval <- object[effect.name,"Pr(>F)"]
-    df1 <- object[effect.name,"numDF"]
-    df2 <- object[effect.name,"denDF"]
-    Fval <- object[effect.name,"F-value"]
-    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-    # generate latex output
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-    txt
-  }
-}
-
-texreport.anova <- function(object,effect.name,effect.size=FALSE) {
-  if(effect.name %in% rownames(object)) {
-    pval <- object[effect.name,"Pr(>F)"]
-    df1 <- object[effect.name,"NumDF"]
-    df2 <- object[effect.name,"DenDF"]
-    Fval <- object[effect.name,"F.value"]
-    #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-    # generate latex output
-    if(pval < .001) ptext <- "$p < .001$" else {
-      if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-        ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-      }
-    }
-    txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-    #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-    txt <- paste(txt,ptext,sep="")
-    txt
-  }
-}
+# texreport.summary.Anova.mlm <- function(object,effect.name,effect.size=TRUE,sphericity.correction=TRUE) {
+#   if(effect.name %in% rownames(object$sphericity.tests) && sphericity.correction && object$sphericity.test[effect.name,"p-value"] < .05) {
+#     epsilon <- object$pval.adjustments[effect.name,"HF eps"]
+#     pval <- object$pval.adjustments[effect.name,"Pr(>F[HF])"]
+#   } else {
+#     epsilon <- 1
+#     pval <- object$univariate.tests[effect.name,"Pr(>F)"]
+#   }
+#   df1 <- object$univariate.tests[effect.name,"num Df"]*epsilon
+#   df2 <- object$univariate.tests[effect.name,"den Df"]*epsilon
+#   Fval <- object$univariate.tests[effect.name,"F"]
+#   etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
+#   # generate latex output
+#   if(pval < .001) ptext <- "$p < .001$" else {
+#     if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+#       ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+#     }
+#   }
+#   txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+#   if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+#   txt <- paste(txt,ptext,sep="")
+#   txt
+# }
+# 
+# texreport.linearHypothesis.mlm <- function(object,effect.size=TRUE) {
+#   if(ncol(object$SSPH) == 1 & nrow(object$SSPH) == 1 & ncol(object$SSPE) == 1 & nrow(object$SSPE) == 1) {
+#     df1 <- object$df
+#     df2 <- object$df.residual
+#     Fval <- (object$SSPH/df1)/(object$SSPE/df2)
+#     pval <- 1-pf(Fval,object$df,object$df.residual)
+#     etasq <- object$SSPH/(object$SSPH + object$SSPE)
+#     # generate latex output
+#     if(pval < .001) ptext <- "$p < .001$" else {
+#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+#       }
+#     }
+#     txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+#     if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+#     txt <- paste(txt,ptext,sep="")
+#   } else {
+#     txt <- "error"
+#   }
+#   txt
+# }
+# 
+# texreport.anova.lme <- function(object,effect.name,effect.size=FALSE) {
+#   if(effect.name %in% rownames(object)) {
+#     pval <- object[effect.name,"p-value"]
+#     if(is.null(pval)) pval <- object[effect.name,"Pr(>F)"]
+#     df1 <- object[effect.name,"numDF"]
+#     df2 <- object[effect.name,"denDF"]
+#     Fval <- object[effect.name,"F-value"]
+#     #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
+#     # generate latex output
+#     if(pval < .001) ptext <- "$p < .001$" else {
+#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+#       }
+#     }
+#     txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+#     #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+#     txt <- paste(txt,ptext,sep="")
+#     txt
+#   }
+# }
+# 
+# texreport.anova <- function(object,effect.name,effect.size=FALSE) {
+#   if(effect.name %in% rownames(object)) {
+#     pval <- object[effect.name,"Pr(>F)"]
+#     df1 <- object[effect.name,"NumDF"]
+#     df2 <- object[effect.name,"DenDF"]
+#     Fval <- object[effect.name,"F.value"]
+#     #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
+#     # generate latex output
+#     if(pval < .001) ptext <- "$p < .001$" else {
+#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
+#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
+#       }
+#     }
+#     txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
+#     #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
+#     txt <- paste(txt,ptext,sep="")
+#     txt
+#   }
+# }
 
@@
 options(tinytex.verbose = TRUE)
-```
-
-```{r, include = FALSE}
-#Experiment 1 raw data
-dat <- read.csv("../data20180719.csv")
-
-# transform 'winner' variable in numeric score
-dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
-# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
-dat$block <- factor(as.numeric(cut(dat$round,2)),labels =c("first half", "second half"))
-
-# create a new variable "game.f" as a factor variable of games
-dat$game.f <- factor(dat$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))
-
-#Group data by human_id and calculate mean score per block of each game.
-dat2 <- dat %>% 
-  group_by(human_id,condition,game,block,game.f) %>% 
-      summarize(block_score = mean(score))
-
-# Group data by game and ID
-dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
-
-```
-
-```{r, include = TRUE}
-# AFEX PACKAGE FOR RUNNING RM ANOVA AND POST HOC TESTS ############################
-citation(package = "afex", lib.loc = NULL, auto = NULL)
-library(afex)
-a1 <- aov_car( block_score ~ game.f*block*condition + Error(human_id/(game.f*block)), dat2)
-summary(a1)
-(a1_nice <- nice(a1, es = attr(a1$anova_table, "es"),
-  observed = attr(a1$anova_table, "observed"),
-  correction = attr(a1$anova_table, "correction"), MSE = NULL,
-  intercept = NULL, p_adjust_method = attr(a1$anova_table,
-  "p_adjust_method"), sig_symbols = attr(a1$anova_table, "sig_symbols")))
-
-write.table(a1_nice,file = "a1.txt", sep = ",", quote = FALSE, row.names = F)
-```
-
-```{r}
-#Pair waise comparison and post hoc tests for the interaction: Game * Block using lsmeans
-
-# game score differences statistically significant?
-(ls0 <- lsmeans(a1, "game.f"))
-(lsm0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
-
-# Main effect of block 
-(ls01 <- lsmeans(a1, "block"))
-(lsm01 <- update(pairs(ls01, reverse = TRUE), by=NULL, adjust = "holm"))
-lsmip(a1, ~block)
-
-# Main effect of condition
-(ls02 <- lsmeans(a1, "condition"))
-(lsm02 <- update(pairs(ls02, reverse = TRUE), by=NULL, adjust = "holm"))
-
-```
-
-```{r}
-# Learning transfer using first half scores: Pairwise comparison of first halves by game ( first half RPS vs first half WFG scores....)
-(ls1 <- lsmeans(a1, "game.f", by="block"))
-(lsm1 <- update(pairs(ls1, reverse = TRUE), by=NULL, adjust = "holm"))
-lsmip(a1, game.f ~ block)
-```
-
-```{r}
-(means.int <- lsmeans(a1, specs = c("game.f","block","condition")))
-
-# Transfer level1: compare H1FWG with H1RPS 
-con1  <- contrast(means.int, list(H1_G2vsH1_G1forlvl1 = c(-1,1,0,0,0,0,0,0,0,0,0,0), H1_G3vsH1_G1forlvl1=c(-1,0,1,0,0,0,0,0,0,0,0,0)))
-summary(con1, adjust = "holm")
-
-# Transfer level2: compare H1FWG with H1RPS 
-con2  <- contrast(means.int, list(H1_G2vsH1_G1forlvl2 = c(0,0,0,0,0,0,-1,1,0,0,0,0), H1_G3vsH1_G1forlvl2=c(0,0,0,0,0,0,-1,0,1,0,0,0)))
-summary(con2, adjust = "holm")
-```
-
-```{r}
-
-#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########
-
-dat_26 <- subset(dat,round >1 & round <7, drop =TRUE)
-dat2_6 <- dat_26 %>% 
-  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
-      summarise(early_score = mean(score))
-
-# Check group means and SDs
-group_by(dat2_6, game.f) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-group_by(dat2_6, game.f,condition) %>%
-  summarise(
-    count = n(),
-    mean = mean(early_score, na.rm = TRUE),
-    sd = sd(early_score, na.rm = TRUE)
-    )
-# plot scores per game 
-ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
 ```
@@
 In order to explore learning transfer in strategic settings, it is generally useful to study simple games as a model of more complex interactions.
-More specifically, when studying learning, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
+More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
 Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to modelling learning about the opponent.
@@
 For instance, Ho et al.
-(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after traingn on similar games.
+(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
 They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-Camerer & Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to conordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+Camerer & Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
 They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
@@
 
-One of the major limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
+Still, one of the limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
 They either used deterministic strategies that did not consider the human participant's play, as in the case of pre-determined mixed strategy algorithms, or strategies that only depended on the player's patterns of past plays.
@@
 We also use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
-We measure transfer of learning about the opponent strategy between games that are similar and dissimilar.
+We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
 The first two games we use are identical except for action labels.
@@
 In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-The overall score of the players was translated into the bonus by making each point worth $£$0.02.
+The overall score of the players was translated into the bonus by making each point worth £0.02.
 This bonus is significant as players could increase the total payoff from the experiment by up to 60% assuming they'd won all rounds against the computer opponent.
@@
 The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-An example of the interface for the rock-paper-scissors game is provided in Figure XX.
+An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps).
 
-<!-- Figure\ \@ref(fig:feedback_rps) -->
+```{r feedback-rps, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align='center'}
+
+knitr::include_graphics("../Report/images/feedback_rps.png", dpi = 108)
+
+```
 
@@
 Any significantly positive group average scores would therefore reflect prior learning from past experiences.
-In figure XXX, the average score across participants by game for rounds 2-6 are plotted.
+In Figure\ \@ref(fig: exp1-early-score), the average score across participants by game for rounds 2-6 are plotted.
 Scores are also averaged across levels of condition.
+
+```{r exp1-early-score, fig.cap = "Average scores for rounds 2-6 by game in first experiment", fig.align='center'}
+
+knitr::include_graphics("../Report/images/exp1_early_scor_game.png", dpi = 108)
+
+```
+
 We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
-As expected for the initial RPS game, the average score is not significantly different from 0 ( t(148.85) = 1.04 , p = 0.89).
+As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
 In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
-Unexpectedly, this is also the case for NUMBERS ( t(148.85) = 3.00, p = 0.0092).
+This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
 
-### Moderation of learning transfer by type of opponent and game similarity
-
-Figure XXXXX shows the marginal mean scores for each game for both level-1 and level-2 facing players.
+Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
+Figure\ \@ref(fig: exp1-score-by-opp) shows the marginal mean scores for each game for both level-1 and level-2 facing players.
 Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
 To test these hypotheses, we run statistical tests on scores by game and opponent against the null hypothesis of 0 (no transfer).
-Table XXXXXXX shows the scores on rounds 2-6 for both type of opponents in each game.
+
+```{r exp1-score-by-opp, fig.cap = "Marginal means of players scores by game and type of opponents", fig.align='center'}
+
+knitr::include_graphics("../Report/images/exp1_earlyScore_by_opp.png", dpi = 108)
+
+```
+
+Table\ \@ref(tab:table-early-scores) shows the scores on rounds 2-6 for both type of opponents in each game.
 We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
 Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
-For level-1 facing players, there is evidence of learning transfer to both FWG and NUMBERS.
-For level-2 facing players, there is evidence for transfer to the similar game FWG (albeit scores are lower than for level-1 player) but not to the dissimilar game of NUMBERS.
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG and NUMBERS.
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG (albeit scores are lower than for level-1 player) but not to the dissimilar game of NUMBERS.
 
-TABLE OF SCORES BY OPPONENT AND GAME (PG 40)
+```{r ANOVA early exp1, include = FALSE, warning=FALSE}
+dat2_6 <- read.csv(file = "../exp1_early_rounds.csv")
+
+exp1_early_anova <- afex :: aov_car(
+  early_score ~ game.f*condition + Error(human_id/(game.f))
+  , data=dat2_6
+  , type = 3)
+
+apa_lm1 <- apa_print(exp1_early_anova)
+
+means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
+trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","NUM"))
+
+```
+```{r table-early-scores, results = "asis"}
+apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
+```
 
 Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from TABLE XXXXX that this transfer is exclusively driven by level-1 facing players, as scores of level-2 facing players are close to nil.
+We can see from TABLE\ \@ref(tab:table-early-scores) that this transfer is exclusively driven by level-1 facing players, as scores of level-2 facing players are close to nil.
 Therefore, both groups of condition can generalise to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
@@
 ## Second Experiment
+
+```{r load_exp2_data , include=FALSE}
+dat_int <- read.csv(file = "../Experiment_2/dat_int_exp2.csv")
+```
 
@@
 We therefore used the “afex” (Singmann & al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
-The full results of this analysis are provided in Table XXXXXXXXX.
+The full results of this analysis are provided in Table\ \@ref(tab:exp2-anova).
+
+```{r Anova exp 2, echo = FALSE}
+exp2_anova <- afex::aov_car(
+  int_score ~ (game.f*interaction_lvl*condition.f*opp_type) + Error(human_id/(game.f*interaction_lvl*opp_type))
+  , data = dat_int
+  , type = 3
+)
+
+apa_lm <- apa_print(exp2_anova)
+
+```
+
+```{r exp2-anova, results = "asis", echo=FALSE}
+apa_table( apa_lm$table, caption = "ANOVA results for experiment 2", escape = FALSE)
+```
 
@@
 There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
-This means that if we ignore potential secondary effects from interactions, neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
+This means that neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
 
@@
 
+```{r , include=FALSE}
+dat <- read.csv(file = "../Experiment_2/dat_exp2.csv")
+```
+
 As a measure for learning transfer we will compare scores only on the first 5 rounds (rounds 2-6 of each game, excluding the very first round where play is necessarily random).
 Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
-In the figure below, we show the average score across participants in rounds 2-6.
+
+```{r, include = FALSE}
+
+#looking at TRIALS 2 to 6 to test robustness of evidence for transfer of learning of opponent strategy #########
+
+dat_26 <- subset(dat,(round >1 & round < 7) & (interaction_lvl == "first interaction" ), drop =TRUE)
+
+dat2_6 <- dat_26 %>% 
+  group_by(human_id,condition.f,game.f,opp_type,confidence,difficulty) %>% 
+      summarise(early_score = mean(adj_score))
+
+# Check group means and SDs
+group_by(dat2_6, game.f) %>%
+  summarise(
+    count = n(),
+    mean = mean(early_score, na.rm = TRUE),
+    sd = sd(early_score, na.rm = TRUE)
+    )
+group_by(dat2_6, game.f,opp_type) %>%
+  summarise(
+    count = n(),
+    mean = mean(early_score, na.rm = TRUE),
+    sd = sd(early_score, na.rm = TRUE)
+    )
+```
+
+```{r exp2-early-scores, fig.cap="Average early round scores by game for experiment 2", fig.align="center"}
+# plot scores per game 
+ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Score", xlab = "Games")
+```
+
+In Figure\ \@ref(fig:exp2-early-scores), we show the average score across participants in rounds 2-6 of the first interaction with the opponent for each game.
 These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
-For both the FWG and SHOOT games, score in the early rounds of the first stage are significantly higher than 0 for both opponent types.
+For both the FWG and SHOOT games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
 (Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; SHOOT:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; SHOOT:  t(270) = 3.21, p =0.004 ).
@@
 Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was explained by each model.
-Table XXX  shows the results for experiment 1, while Table XXXX shows those for experiment 2.
-we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
-In experiment 2 hwever, that model wasn't as successful as the bayesian approached in fitting player's action choices.
+Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
+
+```{r exp1-comp-models, fig.cap = "Histogram of best fitting computational models for experiment 1", fig.align='center'}
+
+knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
+
+```
+
+In experiment 2 however, we can see from Figure\ \@ref(fig:exp2-comp-models) that Q-learning with the aforementioned state-space wasn't as successful as the bayesian approached in fitting player's action choices.
 In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) were by far the most successful.
 
+```{r exp2-comp-models, fig.cap = "Histogram of best fitting computational models for experiment 2", fig.align='center'}
+
+knitr::include_graphics("../Report/images/exp2_comp_models.png", dpi = 108)
+
+```
+
 Next we compared the performance of players whose actions are consistent with each of our hypothesized models.
-Figure XXXX shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior.
-participants whose actions are most consistent with learning an opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play.
+Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
+We can see that participants whose actions are most consistent with learning an opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play.
 EWA, QL and random players had, understandably the lowest performance.
+
+```{r exp1-cumScores, fig.cap = "Average cumulative scores of participants in experiment 1 by best fitting model", fig.align='center'}
+
+knitr::include_graphics("../Report/images/exp1_cumScores.png", dpi = 108)
+
+```
+
+Doing the same exercise for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a bayesian model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expectedm random play as well as EWA were at the bottom of cumulative performance.
+
+```{r exp2-cumScores, fig.cap = "Average cumulative scores of participants in experiment 2 by best fitting model", fig.align='center'}
+
+knitr::include_graphics("../Report/images/exp2_cumScores.png", dpi = 108)
+
+```
 
@@
 
-Coming back to evidence for learning transfer, it is undeniable that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
+Coming back to evidence for learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
 The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and SHOOT?
@@
 
-We will proceed by eliminating multiple hypotheses.
+We will proceed by considering multiple potential answers to this question.
 First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
 An example is a spatial heuristic that consists of choosing "weapons" in a particular order (for instance left to right).
-Thsi was one of the weaknesses in the design of experiment one, and we took this into accounr in experiment two by randomly shuffling the spatial order of action choices in each round.
+This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
+We took this into account in designing experiment two by randomly shuffling the spatial order of action choices in each round.
 Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.
 
-A second possible hypothesis for learning the opponent’s strategy is the use of simple heuristis based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
-Our Q-learning with states as prior round play model is a good proxy for this type of strategies.
-While this approach certainly seemed to be the best fit for player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
-Indeed, learning the best action in a particular state cannot easily transer to a new game since the state space is different and there is no simgle mapping between the state spaces of the initial and latter games.
+A second possible hypothesis for learning the opponent’s strategy is the use of simple rules based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc...).
+Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
+While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
+Indeed, learning the best action in a particular state cannot easily transfer to a new game since the state space is different and there is no simgle mapping between the state spaces of the initial and latter games.
 These rules would thereofre need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
 
-Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, require a long time to learn.
+Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, would require many rounds of practice.
 Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
@@
 
-The more likely explanation of the learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
+We are left with two possible explanations: First, it is possible that the players have uncovered a heuristic that allows them to beat the opponent without explicitly modelling their strategy, and is robust to transfer.
+Indeed, because of the cyclicality in action choices (e.g : Rock beats Scissors beats Paper beats Rock), it is possible to beat level-2 opponents most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
+This is a rule that wins and is also robust to transfer as it does not depend on action labels and even works in the dissimilar game.
+
+The second explanation of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
 A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
 For instance, the player may think “My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be”.
-
 This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
@@
 It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
-Since it is less context dependent, this type of learning is generalizable to new situations.
+Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
 
-"""
+Our second experimental design allows us to test whether the first explanation holds.
+Since there is a simple transferable heuristic that works agaisnt level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
+Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.
 
-To explain the presence of learning transfer, we believe that the most probable account is that some participants are learning a “strategic rule” by which they can anticipate the opponent’s next action and best respond to it.
-Certainly, given the heterogeneity in game scores, not all participants were able to do that.
-As we can see from figure 13, some players are able to score consistently high in early stages and keep a good performance throughout the game while other never quite manage to consistently beat the opponent.
+Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first intractions across games and using early rounds analysis.
+Based on our assumptions, we conclude that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the ourse of learning.
 
-Given the evidence for transfer in early rounds, we believe a significant number of participants did indeed uncover patterns in the opponent’s play that they could leverage to anticipate future actions.
-In fact, the correlation coefficient between scores against level-1 and level-2 opponents is 57%, significantly higher than 0.
+# Conclusion
 
-"""
+Our online experiments confirm behavioural game theory results, stating that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
+Moreover, we showed that participants do transfer their learning to new games with varying degrees of similarity.
+The most likely explanation as we saw is that players build a mental representation of their opponent strategy, rather than rely on associative learning or action-based heuristics.
+The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.
+
+Having said that, there remains a high degree of heterogeneity between players.
+There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
+Moreover, the computational modelling shows that a significant number of players are still using random strategies in the games.
+Whether this ability depends on engagement with the experiment or on other characteristics of the learner is an open question that more research in the area would hope to answer.

### 2020-01-15 Report/draft_report_v1.tex
finalise v1 of report

@@
 %
-\documentclass[,man,floatsintext]{apa6}
+\documentclass[man,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 
-\shorttitle{draft}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Department of Experimental Psychology, University College London}
-\keywords{keywords\newline\indent Word count: X}
-\usepackage{csquotes}
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
-
-\usepackage{longtable}
-\usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
-
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
-
+\usepackage{etoolbox}
 \makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-\usepackage{lineno}
-
-\linenumbers
-\usepackage[document]{ragged2e}
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
 
@@
 
-\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+\authornote{
 
@@
 For instance, Ho et al.
-(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after traingn on similar games.
+(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
 They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-Camerer \& Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to conordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+Camerer \& Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
 They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
@@
 
-One of the major limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
+Still, one of the limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
 They either used deterministic strategies that did not consider the human participant's play, as in the case of pre-determined mixed strategy algorithms, or strategies that only depended on the player's patterns of past plays.
 These strategies did not necessarily take into account the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
-Their play was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that \enquote{play like humans}, and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
+Their play was not ``human-like'' in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+It is therefore important to have agents that ``play like humans'', and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
 Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
-Instead, they will try to \enquote{satisfice} by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in \enquote{level-k} theory, first adopted by Stahl \& Wilson (1995).
+Instead, they will try to `satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
+This concept finds its natural application in `level-k' theory, first adopted by Stahl \& Wilson (1995).
 It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
@@
 In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-The overall score of the players was translated into the bonus by making each point worth \$£\$0.02.
+The overall score of the players was translated into the bonus by making each point worth £0.02.
 This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they'd won all rounds against the computer opponent.
@@
 Figure XXXXXXXXX shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose \enquote{'right}' in the next round, we can win by both choosing \enquote{'left}' and \enquote{'center}'.
+What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose `'right'' in the next round, we can win by both choosing `'left'' and `'center''.
 A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
@@
 The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-An example of the interface for the rock-paper-scissors game is provided in Figure XX.
+An example of the interface for the rock-paper-scissors game is provided in Figure~\ref{fig:feedback-rps}.
+
+\begin{figure}
+
+{\centering \includegraphics{../Report/images/feedback_rps}
+
+}
+
+\caption{Screenshot of the feedback at the end of a round of Rock-Paper-Scissors}\label{fig:feedback-rps}
+\end{figure}
 
@@
 As the number of participants facing level-2 agents was slightly higher than those facing level-1 agents (28 vs 24), the ANOVA is unbalanced.
-We therefore used the \enquote{afex} (Singmann \& al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
+We therefore used the ``afex'' (Singmann \& al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
 
@@
 
-As a measure for learning transfer, we focus on participants' scores in the earliest rounds, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
+As a measure for learning transfer, we focus on participants' scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
 A group of players with no experience of the game are expected to have scores not significantly different from 0.
 Any significantly positive group average scores would therefore reflect prior learning from past experiences.
-In figure XXX, the average score across participants by game for rounds 2-6 are plotted.
+In Figure~@ref(fig: exp1-early-score), the average score across participants by game for rounds 2-6 are plotted.
 Scores are also averaged across levels of condition.
+
+\begin{figure}
+
+{\centering \includegraphics{../Report/images/exp1_early_scor_game}
+
+}
+
+\caption{Average scores for rounds 2-6 by game in first experiment}\label{fig:exp1-early-score}
+\end{figure}
+
 We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
-As expected for the initial RPS game, the average score is not significantly different from 0 ( t(148.85) = 1.04 , p = 0.89).
+As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
 In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p \textless{} 0.0001).
-Unexpectedly, this is also the case for NUMBERS ( t(148.85) = 3.00, p = 0.0092).
+This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
 
-\hypertarget{moderation-of-learning-transfer-by-type-of-opponent-and-game-similarity}{%
-\subsubsection{Moderation of learning transfer by type of opponent and game similarity}\label{moderation-of-learning-transfer-by-type-of-opponent-and-game-similarity}}
-
-Figure 10 shows the marginal mean scores for each game for both level-1 and level-2 facing players.
+Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
+Figure~@ref(fig: exp1-score-by-opp) shows the marginal mean scores for each game for both level-1 and level-2 facing players.
 Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
 To test these hypotheses, we run statistical tests on scores by game and opponent against the null hypothesis of 0 (no transfer).
-Table XXXXXXX shows the scores on rounds 2-6 for both type of opponents in each game.
+
+\begin{figure}
+
+{\centering \includegraphics{../Report/images/exp1_earlyScore_by_opp}
+
+}
+
+\caption{Marginal means of players scores by game and type of opponents}\label{fig:exp1-score-by-opp}
+\end{figure}
+
+Table~\ref{tab:table-early-scores} shows the scores on rounds 2-6 for both type of opponents in each game.
 We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
 Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
-For level-1 facing players, there is evidence of learning transfer to both FWG and NUMBERS.
-For level-2 facing players, there is evidence for transfer to the similar game FWG (albeit scores are lower than for level-1 player) but not to the dissimilar game of NUMBERS.
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG and NUMBERS.
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG (albeit scores are lower than for level-1 player) but not to the dissimilar game of NUMBERS.
 
-TABLE OF SCORES BY OPPONENT AND GAME (PG 40)
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:table-early-scores}Average early round scores by game and condition in first experiment}
+\begin{tabular}{lllllllll}
+\toprule
+game.f & \multicolumn{1}{c}{condition} & \multicolumn{1}{c}{lsmean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{lower.CL} & \multicolumn{1}{c}{upper.CL} & \multicolumn{1}{c}{t.ratio} & \multicolumn{1}{c}{p.value}\\
+\midrule
+FWG & Level1 & 0.30 & 0.08 & 149.58 & 0.10 & 0.51 & 3.96 & 0.00\\
+NUM & Level1 & 0.29 & 0.08 & 149.58 & 0.08 & 0.49 & 3.74 & 0.00\\
+RPS & Level1 & 0.03 & 0.08 & 149.58 & -0.18 & 0.23 & 0.38 & 1.00\\
+FWG & Level2 & 0.18 & 0.07 & 147.52 & -0.01 & 0.38 & 2.48 & 0.06\\
+NUM & Level2 & 0.03 & 0.07 & 147.52 & -0.16 & 0.23 & 0.43 & 1.00\\
+RPS & Level2 & 0.08 & 0.07 & 147.52 & -0.11 & 0.28 & 1.11 & 0.80\\
+\bottomrule
+\end{tabular}
+\end{threeparttable}
+\end{center}
+\end{table}
 
 Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from TABLE XXXXX that this transfer is exclusively driven by level-1 facing players, as scores of level-2 facing players are close to nil.
+We can see from TABLE~\ref{tab:table-early-scores} that this transfer is exclusively driven by level-1 facing players, as scores of level-2 facing players are close to nil.
 Therefore, both groups of condition can generalise to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
@@
 As the number of participants facing level-1 agents was slightly higher than those facing level-2 agents (27 vs 23), the ANOVA will not be balanced between the two levels of condition.
-We therefore used the \enquote{afex} (Singmann \& al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
-The full results of this analysis are provided in Table XXXXXXXXX.
+We therefore used the ``afex'' (Singmann \& al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
+The full results of this analysis are provided in Table~\ref{tab:exp2-anova}.
+
+\begin{verbatim}
+## Warning in summary.Anova.mlm(x$Anova): HF eps > 1 treated as 1
+\end{verbatim}
+
+\begin{table}[tbp]
+\begin{center}
+\begin{threeparttable}
+\caption{\label{tab:exp2-anova}ANOVA results for experiment 2}
+\begin{tabular}{lllllll}
+\toprule
+Effect & \multicolumn{1}{c}{$F$} & \multicolumn{1}{c}{$\mathit{df}_1^{GG}$} & \multicolumn{1}{c}{$\mathit{df}_2^{GG}$} & \multicolumn{1}{c}{$\mathit{MSE}$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\hat{\eta}^2_G$}\\
+\midrule
+Condition f & 0.45 & 1 & 48 & 0.43 & .505 & .003\\
+Game f & 11.81 & 1.85 & 88.71 & 0.12 & < .001 & .039\\
+Interaction lvl & 1.34 & 1 & 48 & 0.06 & .253 & .001\\
+Opp type & 0.00 & 1 & 48 & 0.12 & .973 & .000\\
+Condition f $\times$ Game f & 1.34 & 1.85 & 88.71 & 0.12 & .266 & .005\\
+Condition f $\times$ Interaction lvl & 0.03 & 1 & 48 & 0.06 & .864 & .000\\
+Condition f $\times$ Opp type & 0.13 & 1 & 48 & 0.12 & .717 & .000\\
+Game f $\times$ Interaction lvl & 0.46 & 1.99 & 95.72 & 0.08 & .635 & .001\\
+Game f $\times$ Opp type & 5.31 & 1.7 & 81.82 & 0.11 & .010 & .015\\
+Interaction lvl $\times$ Opp type & 2.16 & 1 & 48 & 0.04 & .148 & .001\\
+Condition f $\times$ Game f $\times$ Interaction lvl & 2.43 & 1.99 & 95.72 & 0.08 & .094 & .006\\
+Condition f $\times$ Game f $\times$ Opp type & 1.23 & 1.7 & 81.82 & 0.11 & .294 & .003\\
+Condition f $\times$ Interaction lvl $\times$ Opp type & 0.02 & 1 & 48 & 0.04 & .883 & .000\\
+Game f $\times$ Interaction lvl $\times$ Opp type & 0.96 & 1.89 & 90.83 & 0.09 & .383 & .002\\
+Condition f $\times$ Game f $\times$ Interaction lvl $\times$ Opp type & 0.94 & 1.89 & 90.83 & 0.09 & .390 & .002\\
+\bottomrule
+\end{tabular}
+\end{threeparttable}
+\end{center}
+\end{table}
 
@@
 
-As a measure for learning transfer we will compare scores only on rounds 2-6 of each game (excluding the very first round where play is necessarily random).
+As a measure for learning transfer we will compare scores only on the first 5 rounds (rounds 2-6 of each game, excluding the very first round where play is necessarily random).
 Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
-In the figure below, we show the average score across participants in rounds 2-6.
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-early-scores-1}
+
+}
+
+\caption{Average early round scores by game for experiment 2}\label{fig:exp2-early-scores}
+\end{figure}
+
+In Figure~\ref{fig:exp2-early-scores}, we show the average score across participants in rounds 2-6 of the first interaction with the opponent for each game.
 These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
-For both the FWG and SHOOT games, score in the early rounds of the first stage are significantly higher than 0 for both opponent types.
+For both the FWG and SHOOT games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
 (Level-1 opponent: FWG: t(270) = 4.99, p \textless{} 0.0001; SHOOT: t(270) = 6.66, p \textless{} 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p \textless{} 0.0001; SHOOT: t(270) = 3.21, p =0.004 ).
@@
 
+\hypertarget{computational-modelling}{%
+\section{Computational modelling}\label{computational-modelling}}
+
+To gain more insight into how participants played the games against the computer opponents, we compared multiple models of strategies the players may have been using to learn how to beat the opponent.
+As a base model, we assume play is random, and each potential action is chosen with equal probability.
+Note that this corresponds to the Nash equilibrium strategy.
+Next, we include for comparison purposes a few other basic models of behavior, such as Q-learning on action choices, as well as a more sophisticatd Q-learning model incorporating a state space consisting of last round play.
+The Bayesian approach is represented by models whereby agents would update an initial belief over the opponent's strategy consisting of various level-k strategies (resp.
+0,1 and 2).
+We fitted two models in which agents best respond to the opponent model.
+In the first, the beliefs about the opponent's adopted strategy are transfered across games, and another in which no transfer of opponent models is allowed.
+
+Next, we fitted a self-tuning EWA model (Ho et al., 2004) both on action choices without states and with states consisting of lat round play.
+The self-tuning EWA model generalizes both reinforcement learning as well as fictitious play models and has been proven to do well than equilibrium models in various game situations.
+Finally, we also included a model-based reinforcement learning approach.
+whereby the agent learns the transition probabilities between states ans uses that to choose the best action, given the current state and it's belief about what the new state will be.
+
+All models were fit to each participant in both experiments, with optimal parameters being estimated using maximum likelihood.
+Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was explained by each model.
+Figure~\ref{fig:exp1-comp-models} shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
+
+\begin{figure}
+
+{\centering \includegraphics{../Report/images/exp1_comp_models}
+
+}
+
+\caption{Histogram of best fitting computational models for experiment 1}\label{fig:exp1-comp-models}
+\end{figure}
+
+In experiment 2 however, we can see from Figure~\ref{fig:exp2-comp-models} that Q-learning with the aforementioned state-space wasn't as successful as the bayesian approached in fitting player's action choices.
+In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) were by far the most successful.
+
+\begin{figure}
+
+{\centering \includegraphics{../Report/images/exp2_comp_models}
+
+}
+
+\caption{Histogram of best fitting computational models for experiment 2}\label{fig:exp2-comp-models}
+\end{figure}
+
+Next we compared the performance of players whose actions are consistent with each of our hypothesized models.
+Figure~\ref{fig:exp1-cumScores} shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
+We can see that participants whose actions are most consistent with learning an opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play.
+EWA, QL and random players had, understandably the lowest performance.
+
+\begin{figure}
+
+{\centering \includegraphics{../Report/images/exp1_cumScores}
+
+}
+
+\caption{Average cumulative scores of participants in experiment 1 by best fitting model}\label{fig:exp1-cumScores}
+\end{figure}
+
+Doing the same exercise for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a bayesian model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expectedm random play as well as EWA were at the bottom of cumulative performance.
+
+\begin{figure}
+
+{\centering \includegraphics{../Report/images/exp2_cumScores}
+
+}
+
+\caption{Average cumulative scores of participants in experiment 2 by best fitting model}\label{fig:exp2-cumScores}
+\end{figure}
+
 \hypertarget{discussion}{%
@@
 
+In this study, we investigated human learning transfer across games by making human participants play against computer agents with rule-based level-k strategies.
+We were interested in uncovering evidence for transfer and exploring whether it is modulated by the degree of similarity between games and the sophistication of the agent.
+
+The results of our first online experiment show that the majority of participants learn to adapt to the opponent strategy over multiple interactions and generalise this learning to the similar game.
+We found that using results on very early rounds is a better proxy for measuring transfer as it is not tainted by any within game learning.
+Using this approach, we showed that transfer to the more dissimilar game was modulated by the degree of sophistication of the agent, with evidence for transfer when players face the less sophisticated agent but not the more sophisticated one.
+
+In the second online experiment, the paradigm was better suited to explore our main research question, related to learning transfer rather than within-game learning.
+Indeed, when facing two opponents sequentially, there are many more opportunities to test transfer than before.
+Indeed, there are 2 opportunities to transfer knowledge within each game, and a total of three games, which means 6 opportunities to test transfer.
+When we made players face only one type of opponent each, we only had two possible learning transfers to test.
+In that regard, the results on learning transfer confirmed prior findings from the first experiment.
+While there was no evidence of learning transfer across interactions within the same game (likely due to the lower number of rounds per interaction and the higher cognitive load of facing two opponents rather than one), we found evidence for learning transfer across games as early round scores analysis confirmed.
+We also found that learning transfer is modulated by the type of opponent faced.
+When the players faced the level-1 opponent, they were able to transfer learning.
+However, when they faced the level-2 opponent, there was weaker evidence for transfer.
+The lack of transfer when facing the more sophisticated opponent might be due to the difficulty of learning that opponent strategy to start with.
+A player cannot transfer what they have not learnt and as such, since it might be harder to learn the strategy of the level-2 opponent, this in turn might translate into weaker evidence for transfer.
+
+Coming back to evidence for learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
+The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and SHOOT?
+what did the players learn exactly about the opponent strategy and what form did this learning take?
+
+We will proceed by considering multiple potential answers to this question.
+First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
+An example is a spatial heuristic that consists of choosing ``weapons'' in a particular order (for instance left to right).
+This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
+We took this into account in designing experiment two by randomly shuffling the spatial order of action choices in each round.
+Still, the learning and conclusions were similar, so this could not explain both learning and transfer in experiments one and two.
+
+A second possible hypothesis for learning the opponent's strategy is the use of simple rules based on last round play (for instance, I play scissors whenver opponent played rock in last round, or whenever the last round play was rock/scissors, I should play paper in this round, etc\ldots{}).
+Our Q-learning with states as prior-round play model is a good proxy for this type of strategies.
+While this approach certainly seemed to be the best fit for some player's behavior, it is unsatisfactory in explaining some of the learning transfer evidence we showed.
+Indeed, learning the best action in a particular state cannot easily transfer to a new game since the state space is different and there is no simgle mapping between the state spaces of the initial and latter games.
+These rules would thereofre need to be learned anew in the latter game which is inconsistent with above chance performance in very early rounds.
+
+Likewise, assuming that players learn a complete model of the environment (for instance the transition probabilities from last round play to new play) might explain learning within games but is equally unable to account for early games transfer of learning as such models, besides being cognitively very expensive to learn, would require many rounds of practice.
+Another issue with these hypotheses is that they are not consistent with significant score differences between those facing level-2 and level-1 opponents.
+After all, if players were using some type of associative learning or spatial heuristics, then their scores should not depend on the degree of strategic sophistication of the opponent since their approaches would render this variable irrelevant.
+The fact that the degree of sophisitication of the opponent matters points to the importance of opponent modelling to successful transfer of learning.
+
+We are left with two possible explanations: First, it is possible that the players have uncovered a heuristic that allows them to beat the opponent without explicitly modelling their strategy, and is robust to transfer.
+Indeed, because of the cyclicality in action choices (e.g : Rock beats Scissors beats Paper beats Rock), it is possible to beat level-2 opponents most of the time by following a simple rule: Play in the next round whatever the opponent played in the last round.
+This is a rule that wins and is also robust to transfer as it does not depend on action labels and even works in the dissimilar game.
+
+The second explanation of learning transfer is that it is driven by a group of participants that are able to build a mental representation of what the strategy of the opponent is.
+A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
+For instance, the player may think ``My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be''.
+This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
+This type of learning would be deemed ``explicit'' in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
+It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
+Since it is less context dependent, this type of learning is generalizable to new situations, akin to the more general framework of rule-based learning explored by Stahl (2000, 2003).
+
+Our second experimental design allows us to test whether the first explanation holds.
+Since there is a simple transferable heuristic that works agaisnt level-2 players, and since as far as we know, there are no similar ones against level-1 players, if indeed participants were using this, they would perform better and transfer learning more easily when facing level-2 opponents.
+Because level-2 opponents use a higher level of strategic reasoning, they should in fact be harder to play against and in the absence of such a heuristic, performance and learning transfer should be worse.
+
+Our results show that in fact, it was harder to transfer learning when facing level-2 opponents, both comparing first intractions across games and using early rounds analysis.
+Based on our assumptions, we conclude that the most likely explanation is that participants who are able to beat the opponent and transfer learning are likely to be explicitly modelling the opponent strategy using level-k reasoning, compared to using simple learning rules they uncovered during the ourse of learning.
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+Our online experiments confirm behavioural game theory results, stating that human players can deviate from Nash equilibrium play and learn to adapt to the opponent strategy and exploit it when the opponent itself is deviating from Nash equilibrium.
+Moreover, we showed that participants do transfer their learning to new games with varying degrees of similarity.
+The most likely explanation as we saw is that players build a mental representation of their opponent strategy, rather than rely on associative learning or action-based heuristics.
+The transfer is also moderated by the level of sophistication of the opponent, with participants showing more success in learning and transferring against opponents adopting a less sophisticated strategy.
+
+Having said that, there remains a high degree of heterogeneity between players.
+There is a high positive association between players who learn to beat the sophisticated and less sophisticated opponents, indicating that some players are more able to detect the patterns in opponent play and learn how to exploit them.
+Moreover, the computational modelling shows that a significant number of players are still using random strategies in the games.
+Whether this ability depends on engagement with the experiment or on other characteristics of the learner is an open question that more research in the area would hope to answer.
+
 \end{document}

### 2020-01-15 exp1_clean_analysis.Rmd
finalise v1 of report

--- 2019-10-29 clean_analysis.Rmd
@@
 ```{r}
-dat <- read.csv("data20180719.csv")
+dat1 <- read.csv("data20180719.csv")
 ```
@@
 library(multcompView)
+library(lsmeans)
 
 # transform 'winner' variable in numeric score
-dat$score <- recode(dat$winner, human = 1, tie = 0, ai = -1)
+dat1$score <- recode(dat1$winner, human = 1, tie = 0, ai = -1)
 # create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
-dat$block <- factor(as.numeric(cut(dat$round,2)),labels =c("first half", "second half"))
+dat1$block <- factor(as.numeric(cut(dat1$round,2)),labels =c("first half", "second half"))
 
 # create a new variable "game.f" as a factor variable of games
-dat$game.f <- factor(dat$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))
+dat1$game.f <- factor(dat1$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))
 
 # overall score to pay bonuses 
-dat_score <- dat %>% 
+dat_score <- dat1 %>% 
   group_by(human_id) %>% 
@@
 #Group data by human_id and calculate mean score per block of each game.
-dat2 <- dat %>% 
+dat2 <- dat1 %>% 
   group_by(human_id,condition,game,block,game.f) %>% 
@@
 
-dat_26 <- subset(dat,round >1 & round <7, drop =TRUE)
+dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
 dat2_6 <- dat_26 %>% 
@@
       summarise(early_score = mean(score))
+
+write.csv(dat2_6,"exp1_early_rounds.csv")
 
@@
     )
-# plot scores per game 
+# plot early scores per game 
 ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
@@
 # including confidence 
+#aov_conf_26 <- aov_car(early_score ~ game.f*condition*difficulty + Error(human_id/(game.f)),data=dat2_6)
+#summary(aov_conf_26)
 
-aov_conf_26 <- aov_car(early_score ~ game.f*condition*difficulty + Error(human_id/(game.f)),data=dat2_6)
-summary(aov_conf_26)
+```
 
-(ls4 <- lsmeans(aov_early, "game.f"))
-(summary(ls4, infer = c(TRUE,TRUE), null = 0,level = 0.95, adjust = "bon"))
+```{r}
+
+# (ls4 <- lsmeans(aov_early, "game.f"))
+# (summary(ls4, infer = c(TRUE,TRUE), null = 0,level = 0.95, adjust = "bon"))
 
@@
 (trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "none",ref=c("FWG","NUM")))
-(contr26 <- contrast(means.int2, list(G2L1vsG2L2 = c(0,1,0,0,-1,0))))
+#(contr26 <- contrast(means.int2, list(G2L1vsG2L2 = c(0,1,0,0,-1,0))))
 
@@
 # plots overall effect by game :
-ggboxplot(dat2_6,"game.f", "early_score", fill = "game.f",palette = c("#00AFBB", "#E7B800", "#FC4E07"),order = c("RPS","FWG","NUM"))
+ggboxplot(dat2_6,"game.f", "early_score", fill = "game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"),order = c("RPS","FWG","NUM"))
 
@@
 # adding confidence and difficulty feedback 
-datcd <- dat %>% 
+datcd <- dat1 %>% 
   group_by(human_id,condition,confidence,difficulty) %>% 
@@
 # ANCOVA with confidence as covariate 
-dat_ancova <- dat %>% 
+dat_ancova <- dat1 %>% 
   group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 
@@
 library(dplyr)
-dat_test1 <- dat %>% 
+dat_test1 <- dat1 %>% 
   group_by(human_id,game.f,condition,block,confidence,difficulty) %>% 

### 2020-01-16 Report/draft_report_v1.Rmd
citation added

@@
 title             : "Transfer of Learned Opponent Models in Zero Sum Games"
-
 shorttitle        : "Draft-1"
@@
 
-# bibliography      : ["r-references.bib"]
+bibliography      : ["Mendeley.bib"]
+csl               : "apa-6th-edition.csl"
 
@@
 
-documentclass     : "apa6"
-classoption       : "man"
+# documentclass     : "apa6"
+# classoption       : "man"
 output            : papaja::apa6_pdf
 header-includes   :
-  - \usepackage[document]{ragged2e}
+  - \shorttitle{}
 ---
@@
 
-```{r texreport}
-# texreport <- function(object,effect.name,...) UseMethod("texreport")
-# texreport.default <- function(object,effect.name,...) return(NULL)
-# 
-# texreport.summary.merMod <- function(object,effect.name,print.estimate=TRUE) {
-#   if(effect.name %in% rownames(object$coefficients)) {
-#     tab <- object$coefficients
-#     estimate <- tab[effect.name,"Estimate"]
-#     se <- tab[effect.name,"Std. Error"]
-#     Tval <- tab[effect.name,"t value"]
-#     df <- tab[effect.name,"df"]
-#     pval <- tab[effect.name,"Pr(>|t|)"]
-#     if(pval < .001) ptext <- "$p < .001$" else {
-#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-#       }
-#     }
-#     txt <- paste("$b = ",round(estimate,2),"$, $SE = ",round(se,2),"$, $t(",round(df,2),") = ",round(Tval,2),"$, ",sep="")
-#     txt <- paste(txt,ptext,sep="")
-#   } else {
-#     txt <- "error"
-#   }
-#   txt
-# }
-
-# texreport.summary.Anova.mlm <- function(object,effect.name,effect.size=TRUE,sphericity.correction=TRUE) {
-#   if(effect.name %in% rownames(object$sphericity.tests) && sphericity.correction && object$sphericity.test[effect.name,"p-value"] < .05) {
-#     epsilon <- object$pval.adjustments[effect.name,"HF eps"]
-#     pval <- object$pval.adjustments[effect.name,"Pr(>F[HF])"]
-#   } else {
-#     epsilon <- 1
-#     pval <- object$univariate.tests[effect.name,"Pr(>F)"]
-#   }
-#   df1 <- object$univariate.tests[effect.name,"num Df"]*epsilon
-#   df2 <- object$univariate.tests[effect.name,"den Df"]*epsilon
-#   Fval <- object$univariate.tests[effect.name,"F"]
-#   etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-#   # generate latex output
-#   if(pval < .001) ptext <- "$p < .001$" else {
-#     if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-#       ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-#     }
-#   }
-#   txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-#   if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-#   txt <- paste(txt,ptext,sep="")
-#   txt
-# }
-# 
-# texreport.linearHypothesis.mlm <- function(object,effect.size=TRUE) {
-#   if(ncol(object$SSPH) == 1 & nrow(object$SSPH) == 1 & ncol(object$SSPE) == 1 & nrow(object$SSPE) == 1) {
-#     df1 <- object$df
-#     df2 <- object$df.residual
-#     Fval <- (object$SSPH/df1)/(object$SSPE/df2)
-#     pval <- 1-pf(Fval,object$df,object$df.residual)
-#     etasq <- object$SSPH/(object$SSPH + object$SSPE)
-#     # generate latex output
-#     if(pval < .001) ptext <- "$p < .001$" else {
-#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-#       }
-#     }
-#     txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-#     if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-#     txt <- paste(txt,ptext,sep="")
-#   } else {
-#     txt <- "error"
-#   }
-#   txt
-# }
-# 
-# texreport.anova.lme <- function(object,effect.name,effect.size=FALSE) {
-#   if(effect.name %in% rownames(object)) {
-#     pval <- object[effect.name,"p-value"]
-#     if(is.null(pval)) pval <- object[effect.name,"Pr(>F)"]
-#     df1 <- object[effect.name,"numDF"]
-#     df2 <- object[effect.name,"denDF"]
-#     Fval <- object[effect.name,"F-value"]
-#     #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-#     # generate latex output
-#     if(pval < .001) ptext <- "$p < .001$" else {
-#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-#       }
-#     }
-#     txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-#     #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-#     txt <- paste(txt,ptext,sep="")
-#     txt
-#   }
-# }
-# 
-# texreport.anova <- function(object,effect.name,effect.size=FALSE) {
-#   if(effect.name %in% rownames(object)) {
-#     pval <- object[effect.name,"Pr(>F)"]
-#     df1 <- object[effect.name,"NumDF"]
-#     df2 <- object[effect.name,"DenDF"]
-#     Fval <- object[effect.name,"F.value"]
-#     #etasq <- object$univariate.tests[effect.name,"SS"]/(object$univariate.tests[effect.name,"SS"] + object$univariate.tests[effect.name,"Error SS"])
-#     # generate latex output
-#     if(pval < .001) ptext <- "$p < .001$" else {
-#       if(pval < .05) ptext <- paste("$p = .",strsplit(as.character(round(pval,3)),".",fixed=TRUE)[[1]][2],"$",sep="") else {
-#         ptext <- paste("$p = .",strsplit(as.character(round(pval,2)),".",fixed=TRUE)[[1]][2],"$",sep="")
-#       }
-#     }
-#     txt <- paste("$F(",round(df1,2),",",round(df2,2),") = ",round(Fval,2),"$, ",sep="")
-#     #if(effect.size) txt <- paste(txt,"$\\eta^2_\\text{p} = ",round(etasq,2),"$, ",sep="")
-#     txt <- paste(txt,ptext,sep="")
-#     txt
-#   }
-# }
-
-```
-
-```{r read-data,warning=FALSE}
-# source("R/readData.R")
-# demo_exit <-  read.csv("data/demographics_and_exit_clean.csv")
-# trial_data <- read.csv("data/trial_data_clean.csv")
-# trial_data$trial <- 1:100
-```
-
 ```{r, include=FALSE} 
@@
 # Introduction
-Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008).
+Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence [@taylor2008transfer].
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
@@
 Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-Lake et al.(2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.
+[@lakeBuildingMachinesThat2017] @lake2017building argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 We use visual aids representing the player and their computer opponent as well as the various actions that people can select built on a highly interactive interface providing image, audio and sometimes video feedback at each step, from choosing actions, to presenting outcomes of the rounds and players scores.
+
+\newpage
 
@@
 Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
+
+\newpage
 
@@
 
+\newpage
+
 # Computational modelling
@@
 ```
+
+\newpage
 
@@
 
+\newpage
+
 # Conclusion
@@
 Whether this ability depends on engagement with the experiment or on other characteristics of the learner is an open question that more research in the area would hope to answer.
+
+\newpage
+
+# References
+
+```{r create_r-references}
+# r_refs(file = "OM_transfer.bib")
+
+```
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+<div id = "refs"></div>
+\endgroup

### 2020-01-16 Report/draft_report_v1.tex
citation added

@@
 
-Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008).
+Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence ({\textbf{???}}).
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
@@
 Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-Lake et al.(2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.
+(Lake, Ullman, Tenenbaum, \& Gershman, n.d.) ({\textbf{???}}) argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 
+\newpage
+
 \hypertarget{computational-modelling}{%
@@
 
+\newpage
+
 \hypertarget{discussion}{%
@@
 
+\newpage
+
 \hypertarget{conclusion}{%
@@
 
+\newpage
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-lakeBuildingMachinesThat2017}{}%
+Lake, B.
+M., Ullman, T.
+D., Tenenbaum, J.
+B., \& Gershman, S.
+J.
+(n.d.).
+Building machines that learn and think like people.
+\emph{Behavioral and Brain Sciences}, \emph{40}.
+\url{https://doi.org/10.1017/S0140525X16001837}
+
+\endgroup
+
 \end{document}

### 2020-01-16 test.tex
citation added

--- 2019-12-17 Report/draft_report_v1.tex
@@
 \PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
 %
-\documentclass[,man,floatsintext]{apa6}
+\documentclass[man]{apa6}
 \usepackage{lmodern}
@@
 }
-\usepackage{xcolor}
 \usepackage{hyperref}
 \hypersetup{
-            pdftitle={Transfer of Learned Opponent Models in Zero Sum Games},
-            pdfauthor={Ismail Guennouni~\& Maarten Speekenbrink},
+            pdftitle={The title},
+            pdfauthor={First Author~\& Ernst-August Doelle},
             pdfkeywords={keywords},
-            colorlinks=true,
-            linkcolor=blue,
-            filecolor=Maroon,
-            citecolor=Blue,
-            urlcolor=Blue,
+            pdfborder={0 0 0},
             breaklinks=true}
@@
 
-\shorttitle{draft}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Department of Experimental Psychology, University College London}
-\keywords{keywords\newline\indent Word count: X}
-\usepackage{csquotes}
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
+\usepackage{etoolbox}
+\makeatletter
+\providecommand{\subtitle}[1]{% add subtitle to \maketitle
+  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
+}
+\makeatother
 
-\usepackage{longtable}
-\usepackage{lscape}
-\usepackage{multirow}
-\usepackage{tabularx}
-\usepackage[flushleft]{threeparttable}
-\usepackage{threeparttablex}
-
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
-
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-\usepackage{lineno}
-
-\linenumbers
-\usepackage[document]{ragged2e}
-
-\title{Transfer of Learned Opponent Models in Zero Sum Games}
-\author{Ismail Guennouni\textsuperscript{1}~\& Maarten Speekenbrink\textsuperscript{1}}
+\title{The title}
+\author{First Author\textsuperscript{1}~\& Ernst-August Doelle\textsuperscript{1,2}}
 \date{}
@@
 
-Correspondence concerning this article should be addressed to Ismail Guennouni, Department of Experimental Psychology, University College London, 26 Bedford Way, London WC1H 0AP, United Kingdom.
-E-mail: \href{mailto:i.guennouni.17@ucl.ac.uk}{\nolinkurl{i.guennouni.17@ucl.ac.uk}}}
+Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}}
 
 \abstract{
-Enter abstract here. Each new line herein must be indented, like this line.
+One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
+
+Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
+
+One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
+
+One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
+
+Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
+
+One or two sentences to put the results into a more \textbf{general context}.
+
+Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
 
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor et al., 2008).
-Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
-More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
-This typically human skill has so far eluded modern ai agents.
-Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
-Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-Lake et al.(2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.
-
-In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Premack \& Woodruff, 1978) play a role in determining human behaviour.
-
-In order to explore learning transfer in strategic settings, it is generally useful to study simple games as a model of more complex interactions.
-More specifically, when studying learning, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to modelling learning about the opponent.
-
-Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
-For instance, Ho et al.
-(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after traingn on similar games.
-They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-Camerer \& Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to conordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
-They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
-They find that transfer of learning (successful coordination) occurs more readily in the presence of both descriptive and strategic similarity.
-If the games were only strategically similar, then the transfer was much weaker.
-
-Juvina et al.(2014) made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
-However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games, Cooper \& Kagel (2003, 2004, 2008) find that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
-They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
-
-Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
-A notable exception is the effort by Haruvy and Stahl (2012) to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
-Participants played ten games, presented as 4x4 normal form (matrix payoffs).
-Their results suggest that subjects do transfer learning over descriptively similar but strategically dissimilar games and that this learning transfer is significant.
-They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on Stahl (1996), was able to capture participants dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
-
-In most of the experimental paradigms we saw, participants were playing other human players either one on one or as a group.
-In this case, players are learning about the game but so are their opponents.
-While the approach of matching groups of human players repeatedly to play economic games has ecological validity in recreating environments where social decision making can be studied, it complicates the detection and modelling of strategies used by participants.
-It is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
-It is also difficult to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-One potential solution is to replace the human opponent with a computerised agent, allowing researchers to manipulate the opponent's behaviour and observe how the human participants adapt their behaviour.
-For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
-Shachat \& Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations from the MSNE, and that this exploitation was very likely if the deviation from the MSNE play was high.
-
-One of the major limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-They either used deterministic strategies that did not consider the human participant's play, as in the case of pre-determined mixed strategy algorithms, or strategies that only depended on the player's patterns of past plays.
-These strategies did not necessarily take into account the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
-Their play was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that \enquote{play like humans}, and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
-Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
-Instead, they will try to \enquote{satisfice} by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in \enquote{level-k} theory, first adopted by Stahl \& Wilson (1995).
-It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment (Arad \& Rubinstein, 2012).
-Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
-Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below and so on.
-
-Another potential issue in the experimental paradigms used in the learning transfer literature is the use of social dilemmas and cooperative/competitive settings that may invoke confounding factors in learning and transfer.
-Social dilemma and coordination games crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
-Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
-Coordination games also test the ability of choosing the safe self-interested choice compared to the risky cooperative choice and may depend on similar latent factors.
-As such, these confounding factors may impede teasing out the process of learning an opponent model and that of whether/how these models are transferred.
-By contrast, purely competitive settings and zero sum games in particular would be more appropriate.
-They do not incentivize any cooperation, since one player's gain is necessarily the opponent's loss, and are agnostic to trust mechanisms or reputation building.
-Also choosing games with no pure strategy Nash Equilibrium shift the focus away from learning a normatively optimal action to that of reasoning dynamically about the opponent which is more amenable to modelling learning.
-Games with unique mixed strategy Nash equilibrium leading to nil average rewards facilitate inferring whether participants have learned to exploit the non-random play of the opponent.
-
-To address some of these limitations in the existing literature on learning transfer outlined above, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
-We also use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
-We measure transfer of learning about the opponent strategy between games that are similar and dissimilar.
-The first two games we use are identical except for action labels.
-In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with 0 expected reward against a Nash player.
-
-Finally, unlike the vast majority of experimental paradigms, we make participants play the games in an engaging, interactive and ultimately more ecological way rather than simply provide the matrix form of the game.
-We use visual aids representing the player and their computer opponent as well as the various actions that people can select built on a highly interactive interface providing image, audio and sometimes video feedback at each step, from choosing actions, to presenting outcomes of the rounds and players scores.
-
 \hypertarget{methods}{%
@@
 
-We ran two experiments where human participants played against computer opponents a total of 3 different games.
+We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
 
-\hypertarget{first-experiment}{%
-\subsection{first experiment:}\label{first-experiment}}
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
-In the first experiment, participants played 3 games sequentially against the same computer opponent.
-The computer opponent either used a level-1 or level-2 strategy.
-The three games were rock-paper-scissors, fire-water-grass and the numbers game.
-A typical rock-paper-scissors game (hereafter RPS) is a 3x3 zero sum game, with a cyclical hierarchy between possible actions: rock blunts scissors, paper wraps rock, and scissors cut paper.
-If one player choses an action which dominates their opponent's action, the player wins (receives a reward of 1) and the other player loses (receives a reward of -1).
-Otherwise it is a draw and both players receive a reward of 0.
-It has a unique MSNE consisting of randomly playing one of the three options each time.
+\hypertarget{material}{%
+\subsection{Material}\label{material}}
 
-The second game is identical to Rock-Paper-Scissors in all but action labels.
-We call it Fire-Water-Grass (FWG): Fire burns grass, water extinguishes fire, and grass absorbs water.
-We are interested in exploring whether learning is transferred in a fundamentally similar game where the only difference is in the description of the choice actions.
-Finally, the numbers game is a generalization of rock-paper-scissors.
-In the variant we use, 2 participants concurrently pick a number between 1 and 5.
-To win in this game, a participant needs to pick a number exactly 1 higher than the number chosen by the opponent.
-For example, if a participant thinks their opponent will pick 3, they ought to choose 4 to win the round.
-To make the strategies cyclical as in RPS, the game stipulates that the lowest number (1) beats the highest number (5), so if the participant thinks the opponent will play 5, then the winning choice is to pick 1.
-This game has a structure similar to RPS in which every action is dominated by exactly one choice.
-All other possible combination of choices that are not consecutive are considered ties.
-A win would add 1 point to the score of the player, while a loss deduces one point and a tie does not affect the score.
-Similar to RPS, the MSNE is to play each action with equal probability in a random way.
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
-Participants were informed they would play three different games against the same computer opponent.
-Each participant plays all three games consecutively and in the same order described above.
-Participants were told that the opponent cannot cheat and will choose its actions simultaneously without knowledge of the participant's choice.
-A total of 50 rounds of each game was played with the player's score displayed at the end of each game.
-The score was calculated as the number of wins minus the number of losses.
-Ties did not affect the score.
-In order to incentivise the participants to maximise the number of wins against the opponents, players were paid a bonus at the end of the experiment that was proportional to their final score.
-The overall score of the players was translated into the bonus by making each point worth \$£\$0.02.
-This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they'd won all rounds against the computer opponent.
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
 
-\hypertarget{second-experiment}{%
-\subsection{Second Experiment}\label{second-experiment}}
-
-In the second experiment, participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
-The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
-The first two games were identical to the ones used in the first experiment.
-In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper.
-Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
-If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
-Otherwise, the goalkeeper catches the ball and the player loses the round.
-There is no possibility of ties in this game.
-Figure XXXXXXXXX shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose \enquote{'right}' in the next round, we can win by both choosing \enquote{'left}' and \enquote{'center}'.
-A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
-As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
-
-Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
-Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
-Participants start by facing one of the opponents in stage one, then face the other in stage two.
-This is repeated in the same order in stages 3 and 4.
-Which opponent they faced first was counterbalanced.
-All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
-
-In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
-During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
-A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent.
-After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
-Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction.
-The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-An example of the interface for the rock-paper-scissors game is provided in Figure XX.
-
-To summarise, all the games used in both experiments have a unique MSNE consisting of randomising across actions.
-If participants follow this strategy, or simply dont engage in learning how the opponent plays, they woud score 0 on average against both level-1 and level-2 players.
-Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
+We used R (Version 3.6.1; R Core Team, 2019) for all our analyses.
 
@@
 
-\hypertarget{first-experiment-1}{%
-\subsection{First Experiment}\label{first-experiment-1}}
-
-In the first experiment, a total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
-The mean age of participants was 31.2 years.
-Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
-
-Looking at the aggregate scores, the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
-Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value = 2.1e-08 ; FWG: t(51) = 10.04 , p-value = 1.10e-13 ; NUMBERS: t(51) = 7.17, p-value = 2.87e-09).
-
-To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-As the number of participants facing level-2 agents was slightly higher than those facing level-1 agents (28 vs 24), the ANOVA is unbalanced.
-We therefore used the \enquote{afex} (Singmann \& al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
-
-There was a main effect of Game ( F(2,100) = 8.54, ges = 0.05, p = .0005), showing that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
-The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
-The main effect of Block ( F(1,50) = 22.51 , p \textless{} .001, ges = 0.03) shows that the average score in the first half of games (M = 0.29) was significantly lower than in the second half of the games played (M = 0.40), which translates to within-game learning : as players get more interaction with the agent, they learn how to win more often.
-The main effect of Condition (F(1,50) = 5.44, p = .024, ges = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
-This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
-Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, ges = 0.02), indicating that within-game learning differed between the games, as well as a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, ges = 0.01).
-
-\hypertarget{learning-transfer}{%
-\subsubsection{Learning transfer}\label{learning-transfer}}
-
-As a measure for learning transfer, we focus on participants' scores in the earliest rounds, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
-A group of players with no experience of the game are expected to have scores not significantly different from 0.
-Any significantly positive group average scores would therefore reflect prior learning from past experiences.
-In figure XXX, the average score across participants by game for rounds 2-6 are plotted.
-Scores are also averaged across levels of condition.
-We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
-As expected for the initial RPS game, the average score is not significantly different from 0 ( t(148.85) = 1.04 , p = 0.89).
-In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p \textless{} 0.0001).
-Unexpectedly, this is also the case for NUMBERS ( t(148.85) = 3.00, p = 0.0092).
-
-\hypertarget{moderation-of-learning-transfer-by-type-of-opponent-and-game-similarity}{%
-\subsubsection{Moderation of learning transfer by type of opponent and game similarity}\label{moderation-of-learning-transfer-by-type-of-opponent-and-game-similarity}}
-
-Figure 10 shows the marginal mean scores for each game for both level-1 and level-2 facing players.
-Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
-To test these hypotheses, we run statistical tests on scores by game and opponent against the null hypothesis of 0 (no transfer).
-Table XXXXXXX shows the scores on rounds 2-6 for both type of opponents in each game.
-We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
-Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
-For level-1 facing players, there is evidence of learning transfer to both FWG and NUMBERS.
-For level-2 facing players, there is evidence for transfer to the similar game FWG (albeit scores are lower than for level-1 player) but not to the dissimilar game of NUMBERS.
-
-TABLE OF SCORES BY OPPONENT AND GAME (PG 40)
-
-Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from TABLE XXXXX that this transfer is exclusively driven by level-1 facing players, as scores of level-2 facing players are close to nil.
-Therefore, both groups of condition can generalise to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
-
-\hypertarget{second-experiment-1}{%
-\subsection{Second Experiment}\label{second-experiment-1}}
-
-A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
-The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
-Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
-The participants faced two types of opponents, a level-1 and level-2 players, and played a total of 3 games (Rock-Paper-Scissors, Fire-Water-Grass, and the Penalty Shootout game), with repeated measures on the latter factor.
-Each game was split into 4 stages.
-The players faced either the level-1 or level-2 player on the first stage, and the other opponent in stage 2, for 20 rounds in each stage.
-Stages 3 and 4 were repetitions of the first two stages but with only 10 rounds in each stage.
-
-The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had the highest average score (M = 0.622, SD = 0.326).
-The higher score in shootout is expected as there are 2 out of three possible winning actions, compared to one out of three in RPS and FWG.
-Indeed, a player not aiming to uncover the opponent's strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will correct all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value \textless{} 0.0001 ; FWG: t(49) = 7.25 , p-value \textless{} 0.0001 ; SHOOT: t(49) = 13.61, p-value \textless{} 0.0001 ).
-
-Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
-We perform a two (condition: level-1 first, level-2 first) by two ( opp\_type: level\_1 or level\_2) by three (game: RPS, FWG, SHOOT) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
-As the number of participants facing level-1 agents was slightly higher than those facing level-2 agents (27 vs 23), the ANOVA will not be balanced between the two levels of condition.
-We therefore used the \enquote{afex} (Singmann \& al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
-The full results of this analysis are provided in Table XXXXXXXXX.
-
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, ges = 0.04, p \textless{} .0001), meaning that we reject the null hypothesis of scores in games being equal.
-To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
-We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the SHOOT game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
-There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
-This means that if we ignore potential secondary effects from interactions, neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
-
-\hypertarget{learning-transfer-1}{%
-\subsubsection{Learning transfer}\label{learning-transfer-1}}
-
-As a measure for learning transfer we will compare scores only on rounds 2-6 of each game (excluding the very first round where play is necessarily random).
-Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
-In the figure below, we show the average score across participants in rounds 2-6.
-These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
-For both the FWG and SHOOT games, score in the early rounds of the first stage are significantly higher than 0 for both opponent types.
-(Level-1 opponent: FWG: t(270) = 4.99, p \textless{} 0.0001; SHOOT: t(270) = 6.66, p \textless{} 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p \textless{} 0.0001; SHOOT: t(270) = 3.21, p =0.004 ).
-Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shoot) when facing a level 1 opponent.
-Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
-These early scores have also been adjusted to account for the fact that the shootout game has higher average scores when playing randomly, and therefore this difference is really due to better learning transfer and not due to chance.
-
 \hypertarget{discussion}{%
@@
 
+\newpage
+
+\hypertarget{references}{%
+\section{References}\label{references}}
+
+\begingroup
+\setlength{\parindent}{-0.5in}
+\setlength{\leftskip}{0.5in}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\endgroup
+
 \end{document}

### 2020-01-16 test2.tex
citation added

--- 2020-01-16 test.tex
@@
 
+\texttt{\{r\ setup,\ include\ =\ FALSE\}\ library("papaja")}
+
+\texttt{\{r\ analysis-preferences\}\ \#\ Seed\ for\ random\ number\ generation\ set.seed(42)\ knitr::opts\_chunk\$set(cache.extra\ =\ knitr::rand\_seed)}
+
 \hypertarget{methods}{%
@@
 
-We used R (Version 3.6.1; R Core Team, 2019) for all our analyses.
+We used \texttt{r\ cite\_r("r-references.bib")} for all our analyses.
 
@@
 
+\texttt{\{r\ create\_r-references\}\ r\_refs(file\ =\ "r-references.bib")}
+
 \begingroup
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 

### 2020-01-17 Report/draft_report_v1.Rmd
changes to draft 1 of report

@@
 # Introduction
-Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence [@taylor2008transfer].
+Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor, 2008) .
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
 More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
-This typically human skill has so far eluded modern ai agents.
+This typically human skill has so far eluded modern AI agents.
 Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
 Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-[@lakeBuildingMachinesThat2017] @lake2017building argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.
+@lake2017building argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on Stahl (1996), was able to capture participants dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
+Their rule-learning model, based on Stahl (1996), was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
 
@@
 Shachat & Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations from the MSNE, and that this exploitation was very likely if the deviation from the MSNE play was high.
+They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
 
 Still, one of the limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-They either used deterministic strategies that did not consider the human participant's play, as in the case of pre-determined mixed strategy algorithms, or strategies that only depended on the player's patterns of past plays.
-These strategies did not necessarily take into account the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
+They either used strategies that did not take into account the human participant's histpry of play (as in the case of pre-determined distribution on actions), or strategies that only depended on the player's patterns of past plays, irrespective of the computer play.
+In other words These strategies did not necessarily take into account the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
 Their play was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
@@
 Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
-Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below and so on.
+Likewise, a level-2 player will choose actions that are the best response given the belief that all opponents are exactly one level below, and so on.
 
@@
 
-Finally, unlike the vast majority of experimental paradigms, we make participants play the games in an engaging, interactive and ultimately more ecological way rather than simply provide the matrix form of the game.
-We use visual aids representing the player and their computer opponent as well as the various actions that people can select built on a highly interactive interface providing image, audio and sometimes video feedback at each step, from choosing actions, to presenting outcomes of the rounds and players scores.
+Hence, we ran a total of two experiments where human participants played against computer opponents a total of 3 different games.
+In the following sections, we wwill describe first the methods used in the first experiments and look at the results, then we will do the same for the second experiment.
 
@@
 
-# Methods
+# Experiment 1
 
-We ran two experiments where human participants played against computer opponents a total of 3 different games.
+## Methods
 
-## first experiment:
+## Participants
+
+A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
+The mean age of participants was 31.2 years.
+Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
+The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
+
+## Procedure
 
@@
 This bonus is significant as players could increase the total payoff from the experiment by up to 60% assuming they'd won all rounds against the computer opponent.
+An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps).
 
-## Second Experiment
+```{r feedback-rps, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align='center'}
+
+knitr::include_graphics("../Report/images/feedback_rps.png", dpi = 108)
+
+```
+
+## Results
+
+```{r load-exp1-data, include=FALSE}
+
+dat1 <- read.csv("../data20180719.csv")
+
+# transform 'winner' variable in numeric score
+dat1$score <- recode(dat1$winner, human = 1, tie = 0, ai = -1)
+# create a new variable 'block' with round 1...25 = block 1 and round 26...50 as block 2
+dat1$block <- factor(as.numeric(cut(dat1$round,2)),labels =c("first half", "second half"))
+
+# create a new variable "game.f" as a factor variable of games
+dat1$game.f <- factor(dat1$game, labels = c("RPS","FWG","NUM"),levels=c("rps","fwg","numbers"))
+
+#Group data by human_id and calculate mean score per block of each game.
+dat2 <- dat1 %>% 
+  group_by(human_id,condition,game,block,game.f) %>% 
+      summarize(block_score = mean(score))
+
+# Group data by game and ID
+dat3 <- group_by(dat2, human_id,game.f,game) %>% summarise(game_score = mean(block_score))
+# head(dat3,6)
+
+# Subsetting scores data by game
+rps <- subset(dat3,  game.f == "RPS",game_score)
+fwg <- subset(dat3,  game.f == "FWG",game_score)
+num <- subset(dat3,  game.f == "NUM",game_score)
+# head(rps,6)
+```
+
+```{r exp1-avg-scores-game, fig.cap = "Average scores per game across conditions", fig.align="center"}
+# Plot average  scores per game 
+ggboxplot(dat3, x = "game.f", y = "game_score", group = 1, add =c("mean_ci","jitter"), color="game.f", palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
+```
+
+Looking at the aggregate scores (See Figure\ \@ref(fig:exp1-avg-scores-game) ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
+Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value < 0.001 ;  FWG:  t(51) = 10.04 , p-value < 0.001 ; NUMBERS: t(51) = 7.17, p-value < 0.001).
+
+To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
+There was a main effect of Game ( F(2,100) = 8.54, $\eta^{2}$  = 0.05,  p < 0.001), showing that average scores varied significantly over the games.
+Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
+The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
+The main effect of Block ( F(1,50) = 22.51 , p < .001, $\eta^{2}$ = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning.
+As players interact more with the agent, they learn how to win more often.
+The main effect of Condition (F(1,50) = 5.44, p = .024, $\eta^{2}$ = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
+This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
+
+```{r exp1-3factor-plot, fig.cap = "Avergae scores by game, block and condition", fig.align = "center"}
+
+# Plot results by game and block (for all 3 games, learning is happening) 
+p <- ggboxplot(dat2, x = "game", y = "block_score", palette = c("#00AFBB", "#E7B800"),order = c("rps", "fwg","numbers"), fill="block",ylab = "Percentage score", xlab = "Games")
+
+p + facet_grid(. ~ condition)
+
+```
+
+Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, $\eta^{2}$ = 0.02), indicating that within-game learning differed between the games.
+Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p <.0001), while there was no significant difference between block scores for the other two games.
+This is indicative of the significant within game transfer within the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
+There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, $\eta^{2}$ = 0.01), which indicates, as seen in Figure\ \@ref(fig:exp1-3factor-plot) that within-game learning changes across games also depend on the sophistication of the opponent.
+For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than agaisnt level-1 opponent.
+The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
+
+### Learning transfer
+
+As a measure for learning transfer, we focus on participants’ scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
+A group of players with no experience of the game are expected to have scores not significantly different from 0.
+Any significantly positive group average scores would therefore reflect prior learning from past experiences.
+
+```{r exp1-early-score, fig.cap = "Average scores for rounds 2-6 by game in first experiment", fig.align ='center'}
+
+knitr::include_graphics("../Report/images/exp1_early_scor_game.png", dpi = 108)
+
+```
+
+In Figure\ \@ref(fig:exp1-early-score), the average score across participants by game for rounds 2-6 are plotted.
+Scores are also averaged across levels of condition.
+We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
+As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
+In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
+This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
+
+Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
+Figure\ \@ref(fig: exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players.
+Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
+To test these hypotheses, we run statistical tests on scores by game and opponent against the null hypothesis of 0 (no transfer).
+
+```{r exp1-early-rounds, include=FALSE}
+dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
+dat2_6 <- dat_26 %>% 
+  group_by(human_id,condition,game.f,confidence,difficulty) %>% 
+      summarise(early_score = mean(score))
+
+# Check group means and SDs by game and condition
+group_by(dat2_6, game.f,condition) %>%
+  summarise(
+    count = n(),
+    mean = mean(early_score, na.rm = TRUE),
+    sd = sd(early_score, na.rm = TRUE)
+    )
+
+```
+
+```{r exp1-score-by-opp, fig.cap = "Average early scores by game and type of opponent faced", fig.align='center'}
+
+p2 <- ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
+
+p2 + facet_grid(. ~ condition)
+
+```
+
+Table\ \@ref(tab:table-early-scores) shows the scores on rounds 2-6 for both type of opponents in each game.
+We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
+Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG and NUMBERS.
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG (albeit scores are lower than for level-1 player) but not to the dissimilar game of NUMBERS.
+
+```{r ANOVA early exp1, include = FALSE, warning=FALSE}
+
+exp1_early_anova <- afex :: aov_car(
+  early_score ~ game.f*condition + Error(human_id/(game.f))
+  , data=dat2_6
+  , type = 3)
+
+apa_lm1 <- apa_print(exp1_early_anova)
+
+means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
+trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","NUM"))
+
+```
+
+```{r table-early-scores, results = "asis"}
+apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
+```
+
+Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
+We can see from TABLE\ \@ref(tab:table-early-scores) that this transfer is exclusively driven by level-1 facing players, as scores of level-2 facing players are close to nil.
+Therefore, both groups of condition can generalise to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
+
+\newpage
+
+# Second Experiment
+
+## Methods
 
@@
 The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
-An example of the interface for the rock-paper-scissors game is provided in Figure\ \@ref(fig:feedback-rps).
 
-```{r feedback-rps, fig.cap = "Screenshot of the feedback at the end of a round of Rock-Paper-Scissors", fig.align='center'}
-
-knitr::include_graphics("../Report/images/feedback_rps.png", dpi = 108)
-
-```
-
-To summarise, all the games used in both experiments have a unique MSNE consisting of randomising across actions.
-If participants follow this strategy, or simply dont engage in learning how the opponent plays, they woud score 0 on average against both level-1 and level-2 players.
+Like games used in the first experiment, all the games used in this seeting have a unique MSNE consisting of randomising across actions.
+If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
 Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
 
-\newpage
-
-# Results
-
-## First Experiment
-
-In the first experiment, a total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
-The mean age of participants was 31.2 years.
-Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
-
-Looking at the aggregate scores, the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
-Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value = 2.1e-08 ;  FWG:  t(51) = 10.04 , p-value = 1.10e-13 ; NUMBERS: t(51) = 7.17, p-value = 2.87e-09).
-
-To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-As the number of participants facing level-2 agents was slightly higher than those facing level-1 agents (28 vs 24), the ANOVA is unbalanced.
-We therefore used the “afex” (Singmann & al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
-
-There was a main effect of Game ( F(2,100) = 8.54, ges  = 0.05,  p = .0005), showing that average scores varied significantly over the games.
-Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
-The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
-The main effect of Block ( F(1,50) = 22.51 , p < .001, ges = 0.03) shows that the average score in the first half of games (M = 0.29)  was significantly lower than in the second half  of the games played (M = 0.40), which translates to within-game learning : as players get more interaction with the agent, they learn how to win more often.
-The main effect of Condition (F(1,50) = 5.44, p = .024, ges = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
-This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
-Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, ges = 0.02), indicating that within-game learning differed between the games, as well as a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, ges = 0.01).
-
-### Learning transfer
-
-As a measure for learning transfer, we focus on participants’ scores in rounds 2-6, excluding the very first round for which the agent is programmed to play randomly as it has no data on prior rounds on which to build its response.
-A group of players with no experience of the game are expected to have scores not significantly different from 0.
-Any significantly positive group average scores would therefore reflect prior learning from past experiences.
-In Figure\ \@ref(fig: exp1-early-score), the average score across participants by game for rounds 2-6 are plotted.
-Scores are also averaged across levels of condition.
-
-```{r exp1-early-score, fig.cap = "Average scores for rounds 2-6 by game in first experiment", fig.align='center'}
-
-knitr::include_graphics("../Report/images/exp1_early_scor_game.png", dpi = 108)
-
-```
-
-We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
-As expected for the initial RPS game, the average score is not significantly different from 0 as this is the first game and no learning is possible (t(148.85) = 1.04 , p = 0.89).
-In FWG, the score is significantly higher than 0 ( t(148.85) = 4.58 , p < 0.0001).
-This is also the case for the more dissimilar game : NUMBERS ( t(148.85) = 3.00, p = 0.0092).
-
-Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-Figure\ \@ref(fig: exp1-score-by-opp) shows the marginal mean scores for each game for both level-1 and level-2 facing players.
-Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
-To test these hypotheses, we run statistical tests on scores by game and opponent against the null hypothesis of 0 (no transfer).
-
-```{r exp1-score-by-opp, fig.cap = "Marginal means of players scores by game and type of opponents", fig.align='center'}
-
-knitr::include_graphics("../Report/images/exp1_earlyScore_by_opp.png", dpi = 108)
-
-```
-
-Table\ \@ref(tab:table-early-scores) shows the scores on rounds 2-6 for both type of opponents in each game.
-We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
-Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG and NUMBERS.
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG (albeit scores are lower than for level-1 player) but not to the dissimilar game of NUMBERS.
-
-```{r ANOVA early exp1, include = FALSE, warning=FALSE}
-dat2_6 <- read.csv(file = "../exp1_early_rounds.csv")
-
-exp1_early_anova <- afex :: aov_car(
-  early_score ~ game.f*condition + Error(human_id/(game.f))
-  , data=dat2_6
-  , type = 3)
-
-apa_lm1 <- apa_print(exp1_early_anova)
-
-means.int2 <- lsmeans(exp1_early_anova, specs = c("game.f","condition"))
-trans26 <- summary(means.int2, infer = c(TRUE,TRUE),level = .95, adjust = "holm",ref=c("FWG","NUM"))
-
-```
-```{r table-early-scores, results = "asis"}
-apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
-```
-
-Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from TABLE\ \@ref(tab:table-early-scores) that this transfer is exclusively driven by level-1 facing players, as scores of level-2 facing players are close to nil.
-Therefore, both groups of condition can generalise to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
-
-## Second Experiment
+## Results
 
@@
 
-```{r Anova exp 2, echo = FALSE}
+```{r Anova exp 2, echo = FALSE, warning=FALSE}
 exp2_anova <- afex::aov_car(
@@
 
-```{r exp2-anova, results = "asis", echo=FALSE}
+```{r exp2-anova, results = "asis", echo=FALSE, warning=FALSE}
 apa_table( apa_lm$table, caption = "ANOVA results for experiment 2", escape = FALSE)
@@
 
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, ges = 0.04,  p < .0001), meaning that we reject the null hypothesis of scores in games being equal.
+There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, $\eta^{2}$ = 0.04,  p < .0001), meaning that we reject the null hypothesis of scores in games being equal.
 To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).

### 2020-01-17 Report/draft_report_v1.tex
changes to draft 1 of report

@@
 
-Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence ({\textbf{???}}).
+Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor, 2008) .
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
 More formally, Perkins (1992) defines transfer of learning as the application of skills, knowledge, and/or attitudes that were learned in one situation to another learning situation.
-This typically human skill has so far eluded modern ai agents.
+This typically human skill has so far eluded modern AI agents.
 Deep neural networks for instance can do very well on image recognition tasks and can even reach super-human performance levels on video and strategic board games.
 Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-(Lake, Ullman, Tenenbaum, \& Gershman, n.d.) ({\textbf{???}}) argue that human learning transfer abilities take advantage of important cognitive building blocks such as a deeper representation of concepts underlying tasks and compositionally structured causal models of the environment.
+Lake, Ullman, Tenenbaum, and Gershman (2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 Shachat \& Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations from the MSNE, and that this exploitation was very likely if the deviation from the MSNE play was high.
+They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
 
 Still, one of the limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-They either used deterministic strategies that did not consider the human participant's play, as in the case of pre-determined mixed strategy algorithms, or strategies that only depended on the player's patterns of past plays.
-These strategies did not necessarily take into account the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
+They either used strategies that did not take into account the human participant's histpry of play (as in the case of pre-determined distribution on actions), or strategies that only depended on the player's patterns of past plays, irrespective of the computer play.
+In other words These strategies did not necessarily take into account the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
 Their play was not ``human-like'' in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
@@
 
+\hypertarget{experiment-1}{%
+\section{Experiment 1}\label{experiment-1}}
+
 \hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\subsection{Methods}\label{methods}}
 
-We ran two experiments where human participants played against computer opponents a total of 3 different games.
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
-\hypertarget{first-experiment}{%
-\subsection{first experiment:}\label{first-experiment}}
+A total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
+The mean age of participants was 31.2 years.
+Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
+The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
+
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
 
@@
 This bonus is significant as players could increase the total payoff from the experiment by up to 60\% assuming they'd won all rounds against the computer opponent.
-
-\hypertarget{second-experiment}{%
-\subsection{Second Experiment}\label{second-experiment}}
-
-In the second experiment, participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
-The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
-The first two games were identical to the ones used in the first experiment.
-In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper.
-Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
-If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
-Otherwise, the goalkeeper catches the ball and the player loses the round.
-There is no possibility of ties in this game.
-Figure XXXXXXXXX shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose `'right'' in the next round, we can win by both choosing `'left'' and `'center''.
-A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
-As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
-
-Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
-Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
-Participants start by facing one of the opponents in stage one, then face the other in stage two.
-This is repeated in the same order in stages 3 and 4.
-Which opponent they faced first was counterbalanced.
-All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
-
-In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
-During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
-A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent.
-After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
-Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction.
-The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
 An example of the interface for the rock-paper-scissors game is provided in Figure~\ref{fig:feedback-rps}.
@@
 
-To summarise, all the games used in both experiments have a unique MSNE consisting of randomising across actions.
-If participants follow this strategy, or simply dont engage in learning how the opponent plays, they woud score 0 on average against both level-1 and level-2 players.
-Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
 
-\newpage
+\begin{figure}
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-avg-scores-game-1}
 
-\hypertarget{first-experiment-1}{%
-\subsection{First Experiment}\label{first-experiment-1}}
+}
 
-In the first experiment, a total of 52 (28 female, 24 male) participants were recruited on the Prolific Academic platform.
-The mean age of participants was 31.2 years.
-Participants were paid a fixed fee of £2.5 plus a bonus dependent on their performance which averaged £1.06.
-The study used a 2 (computer opponent levels 1 and 2) by 3 (games of rock-paper-scissors, fire-water-grass and numbers) design, with repeated measures on the second factor.
+\caption{Average scores per game across conditions}\label{fig:exp1-avg-scores-game}
+\end{figure}
 
-Looking at the aggregate scores, the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
-Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value = 2.1e-08 ; FWG: t(51) = 10.04 , p-value = 1.10e-13 ; NUMBERS: t(51) = 7.17, p-value = 2.87e-09).
+Looking at the aggregate scores (See Figure~\ref{fig:exp1-avg-scores-game} ), the RPS game had the lowest average score across participants (M = 0.289, SD = 0.348) followed by NUMBERS (M = 0.31, SD = 0.347) and finally the FWG game had the highest average score (M = 0.454, SD = 0.354).
+Aggregate average scores for each game were significantly different from 0 (hypothesised value of random play) using parametric one sample t-tests (RPS: t(51) = 7.26, p-value \textless{} 0.001 ; FWG: t(51) = 10.04 , p-value \textless{} 0.001 ; NUMBERS: t(51) = 7.17, p-value \textless{} 0.001).
 
 To analyse within and between game learning, we used a 2 (condition: level-1, level-2) by 3 (game: RPS, FWG, NUMBERS) by 2 (block: first half, second half) repeated measures ANOVA with the first factor varying between participants.
-As the number of participants facing level-2 agents was slightly higher than those facing level-1 agents (28 vs 24), the ANOVA is unbalanced.
-We therefore used the ``afex'' (Singmann \& al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
-
-There was a main effect of Game ( F(2,100) = 8.54, ges = 0.05, p = .0005), showing that average scores varied significantly over the games.
+There was a main effect of Game ( F(2,100) = 8.54, \(\eta^{2}\) = 0.05, p \textless{} 0.001), showing that average scores varied significantly over the games.
 Post-hoc pairwise comparisons showed that performance in the FWG game was significantly higher than in the RPS game ( t(100) =3.78, p = 0.0008 ), and the performance in NUMBERS was significantly lower than FWG game ( t(100) = -3.32 , p = 0.0024).
 The score in RPS was not significantly different from the score in NUMBERS however ( t(100) = 0.45 , p = 0.65).
-The main effect of Block ( F(1,50) = 22.51 , p \textless{} .001, ges = 0.03) shows that the average score in the first half of games (M = 0.29) was significantly lower than in the second half of the games played (M = 0.40), which translates to within-game learning : as players get more interaction with the agent, they learn how to win more often.
-The main effect of Condition (F(1,50) = 5.44, p = .024, ges = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
+The main effect of Block ( F(1,50) = 22.51 , p \textless{} .001, \(\eta^{2}\) = 0.03) shows that the average score in the first half of games (M = 0.29) was significantly lower than in the second half of the games played (M = 0.40), which translates to within-game learning.
+As players interact more with the agent, they learn how to win more often.
+The main effect of Condition (F(1,50) = 5.44, p = .024, \(\eta^{2}\) = 0.05) indicates that scores were higher against the level-1 player (M = 0.43) than against the level-2 player (M = 0.27).
 This means that it was harder for participants, on average, to learn the strategy of the more sophisticated opponent (level-2) compared to that of the comparatively less sophisticated agent (level-1).
-Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, ges = 0.02), indicating that within-game learning differed between the games, as well as a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, ges = 0.01).
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-3factor-plot-1}
+
+}
+
+\caption{Avergae scores by game, block and condition}\label{fig:exp1-3factor-plot}
+\end{figure}
+
+Finally, the analysis showed a significant interaction effects of block by game ( F(2,100) = 6.92 , p = .002, \(\eta^{2}\) = 0.02), indicating that within-game learning differed between the games.
+Indeed, second half scores in RPS are significantly higher than first-half scores (t(150) = 5.59, p \textless{}.0001), while there was no significant difference between block scores for the other two games.
+This is indicative of the significant within game transfer within the first game when players have no epxerience against the opponent, as opposed to much lower within game performance improvement in the latter games when participants have had some exprience playing against the opponenet and start with higher scores indicative of transfer.
+There was also a three-way interaction between condition, game, and block ( F(2,100) = 3.88 , p = .023, \(\eta^{2}\) = 0.01), which indicates, as seen in Figure~\ref{fig:exp1-3factor-plot} that within-game learning changes across games also depend on the sophistication of the opponent.
+For instance, there is more within game learning in the third game against level-2 opponents, since the initial scores are lower than agaisnt level-1 opponent.
+The explanation for this will become clearer when we discuss the factors moderating learning transfer in the next section.
 
@@
 Any significantly positive group average scores would therefore reflect prior learning from past experiences.
-In Figure~@ref(fig: exp1-early-score), the average score across participants by game for rounds 2-6 are plotted.
-Scores are also averaged across levels of condition.
 
@@
 
+In Figure~\ref{fig:exp1-early-score}, the average score across participants by game for rounds 2-6 are plotted.
+Scores are also averaged across levels of condition.
 We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
@@
 
-\hypertarget{second-experiment-1}{%
-\subsection{Second Experiment}\label{second-experiment-1}}
+\newpage
+
+\hypertarget{second-experiment}{%
+\section{Second Experiment}\label{second-experiment}}
+
+\hypertarget{methods-1}{%
+\subsection{Methods}\label{methods-1}}
+
+In the second experiment, participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
+The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
+The first two games were identical to the ones used in the first experiment.
+In the final game (shootout) the participants played the role of the player shooting a football (soccer) penalty, and the AI opponent was the goalkeeper.
+Players had the choice between three actions, like in the first two games: Shooting the football to the left, right or centre of the goal.
+If the player shoots in a direction different from that of where the goalkeeper dives, they win the round and the goalkeeper loses.
+Otherwise, the goalkeeper catches the ball and the player loses the round.
+There is no possibility of ties in this game.
+Figure XXXXXXXXX shows a snapshot of play in the shootout game.
+What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose `'right'' in the next round, we can win by both choosing `'left'' and `'center''.
+A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
+As such, we have programmed the level-2 computer program to choose randomly between the two possibilities that a level-1 player may choose.
+
+Like in the first experiment, the computer opponents retained the same strategy throughout the 3 games, however the participants faced each opponent twice in each game.
+Specifically, each game was divided into 4 stages numbered 1 to 4, consisting of 20, 20, 10, and 10 rounds respectively for a total of 60 rounds per game.
+Participants start by facing one of the opponents in stage one, then face the other in stage two.
+This is repeated in the same order in stages 3 and 4.
+Which opponent they faced first was counterbalanced.
+All participants engage in the same three games (namely RPS, FWG and Shootout) in this exact order, and were aware that the opponent was not able to know their choices beforehand but was choosing simultaneously with the player.
+
+In order to encourage participants to think about their next choice, a countdown timer of 3 seconds was introduced at the beginning of each round.
+During those 3 seconds, participants could not choose an option and had to wait for the timer to run out.
+A small delay that changed randomly (between 0.5 and 3 seconds) was also introduced in the time it took the AI agent to give back their response to make it seem like it is also thinking about its last actions, as a way of simulating a real human opponent.
+After each round, the participants were given detailed feedback about their opponent actions as well as whether they won or lost the last round.
+Further information about the outcome of previous rounds was also visible on the game screen below the feedback area, throughout each stage game and opponent could go back many rounds to study the history of interaction.
+The number of wins, losses and ties were clearly shown at the top of the screen for each game, and this scoreboard was reinitialised to zero at the onset of a new stage game.
+
+Like games used in the first experiment, all the games used in this seeting have a unique MSNE consisting of randomising across actions.
+If participants follow this strategy, or simply don't engage in learning how the opponent plays, they would score 0 on average against both level-1 and level-2 players.
+Evidence of sustained wins would indicate that participants have learned to exploit patterns in the opponent play.
+
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
 
@@
 The full results of this analysis are provided in Table~\ref{tab:exp2-anova}.
-
-\begin{verbatim}
-## Warning in summary.Anova.mlm(x$Anova): HF eps > 1 treated as 1
-\end{verbatim}
 
@@
 
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, ges = 0.04, p \textless{} .0001), meaning that we reject the null hypothesis of scores in games being equal.
+There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, \(\eta^{2}\) = 0.04, p \textless{} .0001), meaning that we reject the null hypothesis of scores in games being equal.
 To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-lakeBuildingMachinesThat2017}{}%
-Lake, B.
-M., Ullman, T.
-D., Tenenbaum, J.
-B., \& Gershman, S.
-J.
-(n.d.).
-Building machines that learn and think like people.
-\emph{Behavioral and Brain Sciences}, \emph{40}.
-\url{https://doi.org/10.1017/S0140525X16001837}
+\leavevmode\hypertarget{ref-lake2017building}{}%
+Lake, B. M., Ullman, T. D., Tenenbaum, J. B., \& Gershman, S. J. (2017). Building machines that learn and think like people. \emph{Behavioral and Brain Sciences}, \emph{40}.
 

### 2020-01-17 comp_model_1019.Rmd
changes to draft 1 of report

@@
   # Transition Matrices 
-  Transit_RPS = matrix(0,9,9)
+  Transit_RPS = matrix(1/9,9,9)
   dimnames(Transit_RPS) = list(states_RPS, states_RPS)
-  Transit_FWG = matrix(0,9,9)
+  Transit_FWG = matrix(1/9,9,9)
   dimnames(Transit_FWG) = list(states_FWG, states_FWG)
-  Transit_NUM = matrix(0,25,25)
+  Transit_NUM = matrix(1/25,25,25)
   dimnames(Transit_NUM) = list(states_NUM, states_NUM)
@@
  kable(Table_results)
+ barplot(Table_results)
 

### 2020-01-17 exp1_clean_analysis.Rmd
changes to draft 1 of report

@@
 
+```
+
+```{r}
 # Pairwise comparison of first halves by game ( first half RPS vs first half WFG scores....)
-(ls1 <- lsmeans(a1, "game.f", by="block"))
+(ls1 <- lsmeans(a1, "block" , by="game.f"))
 (lsm1 <- update(pairs(ls1, reverse = TRUE), by=NULL, adjust = "holm"))
-plot(lsm1,by="block")
 lsmip(a1, game.f ~ block)
+```
 
+```{r}
 # Pairwise comparison of each game score by block (first half RPS vs second half RPS....) + Control for family wise error:
@@
 lsmip(a1, ~ block * game.f)
+```
 
+```{r}
 # Pairwise comparison of scores facing the two types of players by game: 

### 2020-01-17 test.Rmd
changes to draft 1 of report

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup

### 2020-01-20 Experiment_2/Experiment_2_modelling.Rmd
draft improv and corrected faulty bayesian in exp2

@@
 ```{r}
-
-exp2_naive_bayes <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {
+# Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
+exp2_naive_bayes <- function(par,data,opp_strategy_vec,return_value,btwn_transfer) {
 
@@
   # or "likelihood_by_trial" vector  (for later plotting, etc)
-  # opp_mod_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise.
+  # btwn_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise.
 
@@
 
-  #lik_opp is a vector that holds and update probability distribution of opp strategy given actions.
+  #lik_opp is a vector that holds and updates probability distribution of opp strategy given actions.
   lik_opp <- matrix(0.0,num_strat, nrow(data))
-  # Initiate prior vector as uniform
-  opp_prior_vec <-rep(1/num_strat, num_strat)
+
+  # Initiate prior vectors for each opponent as uniform
+  opp_prior_vec <- rep(1/num_strat, num_strat)
+  opp1_prior_vec <-rep(1/num_strat, num_strat)
+  opp2_prior_vec <-rep(1/num_strat, num_strat)
 
@@
       ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer reset prior to uniform)#####
-      if (!(opp_mod_transfer) || data[t,"stage"] == 1) {
+      # Round 1 of stage 1 
+      if (data[t,"stage"] == 1) {
+        if (!(btwn_transfer)){
           opp_prior_vec <- rep(1/num_strat, num_strat)
+        } else { # <- TRANFER 
+          # if there is between game transfer, then the opp_prior_vec should store what was learned about the SECOND opponent 
+          # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
+          opp2_prior_vec <- opp_prior_vec
+          # if between game transfer use stored opp1 prior vector from previous game (or uniform if first game  RPS) 
+          opp_prior_vec <- opp1_prior_vec
+        }
 
@@
       } else if (data[t,"stage"] == 2) {
-        opp1_prior <- opp_prior_vec
+          # hold the probs vector of Opp type learned in stage 1 in memory and save to temp.
+          opp1_prior_temp <- opp_prior_vec
+          # If no between games transfer reset prior to uniform 
+          if (!(btwn_transfer)){
             opp_prior_vec <- rep(1/num_strat, num_strat)
+            } else {
+              opp_prior_vec <- opp2_prior_vec
+            }
 
-      # we are round 1 of stage 3, keep opp vector from round 20 of stage 2  for stage 4
+      # we are round 1 of stage 3, use vector learned from stage 1, keep opp vector from round 20 of stage 2 for stage 4
       } else if (data[t,"stage"] == 3) { 
-        opp2_prior <- opp_prior_vec
-        opp_prior_vec <- opp1_prior
+        opp2_prior_temp <- opp_prior_vec
+        opp_prior_vec <- opp1_prior_temp
 
-      # We are in round 1 of stage 4, use vector of priors from stage 2
-      }  else if (data[t,"stage"] == 4){ 
-        opp_prior_vec <- opp2_prior
+      # We are in round 1 of stage 4,
+      }  else if (data[t,"stage"] == 4) {
+        # Store what was learned about opponent 1 for nxt game...
+        opp1_prior_vec <- opp_prior_vec
+        # Use what was learned about opponent 2 from stage 2.
+        opp_prior_vec <- opp2_prior_temp
       }
@@
 
-  # TR_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))
+  # TR_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", btwn_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))
 
-  exp2_TR_bayes[[id]] <- optim(c(0.1,0.1),fn=exp2_naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+  exp2_TR_bayes[[id]] <- optim(c(0.1,0.1),fn=exp2_naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", btwn_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
 }

### 2020-01-20 Report/draft_report_v1.Rmd
draft improv and corrected faulty bayesian in exp2

@@
 Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
-To test these hypotheses, we run statistical tests on scores by game and opponent against the null hypothesis of 0 (no transfer).
+To test these hypotheses, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
 
@@
 dat_26 <- subset(dat1,round >1 & round <7, drop =TRUE)
-dat2_6 <- dat_26 %>% 
+exp1_dat2_6 <- dat_26 %>% 
   group_by(human_id,condition,game.f,confidence,difficulty) %>% 
@@
 # Check group means and SDs by game and condition
-group_by(dat2_6, game.f,condition) %>%
+group_by(exp1_dat2_6, game.f,condition) %>%
   summarise(
@@
 
-p2 <- ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Score", xlab = "Games")
+p2 <- ggerrorplot(exp1_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","NUM"), ylab = "Average Score rounds 2-6", xlab = "Games")
 
@@
 
-Table\ \@ref(tab:table-early-scores) shows the scores on rounds 2-6 for both type of opponents in each game.
+<!-- Table\ \@ref(tab:table-early-scores) shows the scores on rounds 2-6 for both type of opponents in each game.
 We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
 Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG and NUMBERS.
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG (albeit scores are lower than for level-1 player) but not to the dissimilar game of NUMBERS.
+-->
+
+game.f condition lsmean     SE  df lower.CL upper.CL t.ratio p.value
+ RPS    Level1    0.0292 0.0768 150  -0.1226    0.181 0.380   0.7048 
+ FWG    Level1    0.3042 0.0768 150   0.1524    0.456 3.960   0.0001 
+ NUM    Level1    0.2875 0.0768 150   0.1357    0.439 3.743   0.0003 
+ RPS    Level2    0.0815 0.0732 148  -0.0631    0.226 1.114   0.2671 
+ FWG    Level2    0.1815 0.0732 148   0.0369    0.326 2.480   0.0143 
+ NUM    Level2    0.0315 0.0732 148  -0.1131    0.176 0.431   0.6672
+
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p < 0.001) and NUMBERS (t(150) = 3.74, p < 0.001) .
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
 
@@
   early_score ~ game.f*condition + Error(human_id/(game.f))
-  , data=dat2_6
+  , data=exp1_dat2_6
   , type = 3)
@@
 ```{r table-early-scores, results = "asis"}
-apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
+# apa_table(trans26, caption = "Average early round scores by game and condition in first experiment")
 ```
@@
 Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from TABLE\ \@ref(tab:table-early-scores) that this transfer is exclusively driven by level-1 facing players, as scores of level-2 facing players are close to nil.
-Therefore, both groups of condition can generalise to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
+We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game.
+Therefore, both partiicpants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
 
@@
 
-In the second experiment, participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
+### Participants 
+A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
+This was a new set of participants unrelated to those taking part in Experiment 1.
+The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
+Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
+
+### Procedure
+
+The participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
 The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
@@
 
-A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
-The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
-Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
-The participants faced two types of opponents, a level-1 and level-2 players, and played a total of 3 games (Rock-Paper-Scissors, Fire-Water-Grass, and the Penalty Shootout game), with repeated measures on the latter factor.
-Each game was split into 4 stages.
-The players faced either the level-1 or level-2 player on the first stage, and the other opponent in stage 2, for 20 rounds in each stage.
-Stages 3 and 4 were repetitions of the first two stages but with only 10 rounds in each stage.
-
 The RPS game had the lowest average score per round (M = 0.194, SD = 0.345) followed by FWG (M = 0.27, SD = 0.394) and finally the Shootout game had the highest average score (M = 0.622, SD = 0.326).
@@
 Indeed, a player not aiming to uncover the opponent’s strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will correct all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value < 0.0001 ;  FWG:  t(49) = 7.25 , p-value < 0.0001 ; SHOOT: t(49) = 13.61, p-value < 0.0001 ).
+To make the scores more comparable, and because we are interested in player’s performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
+Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value < 0.0001 ;  FWG:  t(49) = 7.25 , p-value < 0.0001 ; Shootout: t(49) = 13.61, p-value < 0.0001 ).
 
 Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
-We perform a two (condition: level-1 first, level-2 first) by two ( opp_type: level_1 or level_2) by three (game: RPS, FWG, SHOOT) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
-As the number of participants facing level-1 agents was slightly higher than those facing level-2 agents (27 vs 23), the ANOVA will not be balanced between the two levels of condition.
-We therefore used the “afex” (Singmann & al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
-The full results of this analysis are provided in Table\ \@ref(tab:exp2-anova).
+We perform a two (condition: level-1 first, level-2 first) by two ( opponne type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
 
-```{r Anova exp 2, echo = FALSE, warning=FALSE}
+```{r Anova exp 2, include= FALSE}
 exp2_anova <- afex::aov_car(
@@
 
+(ls0 <- lsmeans(exp2_anova, "game.f", by = "opp_type"))
+(ls0 <- update(pairs(ls0, reverse = TRUE), by=NULL, adjust = "holm"))
 apa_lm <- apa_print(exp2_anova)
@@
 
-```{r exp2-anova, results = "asis", echo=FALSE, warning=FALSE}
-apa_table( apa_lm$table, caption = "ANOVA results for experiment 2", escape = FALSE)
+```{r exp2-score-by-opp, fig.cap="Avergae scores per game by opponcne type", fig.align="center"}
+p3 <- ggerrorplot(dat_int, x = "game.f", y = "int_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Scores per game", xlab = "Games")
+
+p3 + facet_grid(. ~ opp_type)
 ```
 
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, $\eta^{2}$ = 0.04,  p < .0001), meaning that we reject the null hypothesis of scores in games being equal.
+```{r exp2-anova, results = "asis", echo=FALSE, warning=FALSE}
+# apa_table( apa_lm$table, caption = "ANOVA results for experiment 2", escape = FALSE)
+```
+
+There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, $\eta^{2}$ = 0.04,  p < .0001).
 To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
-We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the SHOOT game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
+We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the Shootout game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
 There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
 This means that neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
+There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,$\eta^{2}$ = 0.02,  p = .01).
+As can be seen in Figure\ \@ref(fig:exp2-score-by-opp), when facing level-1 agents, scores increase steadily after each game, with FWG score sgnificantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG  ( t(191) = 3.05, p = 0.01).
+There was no significant difference between average scores on any two games when facing level-2 agents however.
 
@@
 
-As a measure for learning transfer we will compare scores only on the first 5 rounds (rounds 2-6 of each game, excluding the very first round where play is necessarily random).
+As a measure for learning transfer we will again compare scores only on rounds 2-6 of each game, excluding the very first round where play is necessarily random.
 Because the number of rounds here is very limited, there should be very little learning within games, and we should be better measure learning transfer if it exits.
@@
 
-dat2_6 <- dat_26 %>% 
+exp2_dat2_6 <- dat_26 %>% 
   group_by(human_id,condition.f,game.f,opp_type,confidence,difficulty) %>% 
@@
 # Check group means and SDs
-group_by(dat2_6, game.f) %>%
+group_by(exp2_dat2_6, game.f) %>%
   summarise(
@@
     )
-group_by(dat2_6, game.f,opp_type) %>%
+group_by(exp2_dat2_6, game.f,opp_type) %>%
   summarise(
@@
 # plot scores per game 
-ggerrorplot(dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Score", xlab = "Games")
+ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Score", xlab = "Games")
 ```
@@
 These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
-For both the FWG and SHOOT games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
-(Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; SHOOT:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; SHOOT:  t(270) = 3.21, p =0.004 ).
-Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shoot) when facing a level 1 opponent.
+For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
+(Level-1 opponent: FWG: t(270) = 4.99, p < 0.0001; Shootout:  t(270) = 6.66, p < 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p < 0.0001; Shootout:  t(270) = 3.21, p =0.004 ).
+Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
 Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).
@@
 
-All models were fit to each participant in both experiments, with optimal parameters being estimated using maximum likelihood.
+In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
 Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was explained by each model.
@@
 Coming back to evidence for learning transfer, we observed evidence that participants start off new games with prior knowledge as their scores are much higher than chance, confirmed both by early stage analysis as well as rounds 2-6 scores analysis.
-The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and SHOOT?
+The question we ask ourselves therefore is: What exactly did the players learn in RPS that allowed them to beat the opponent in FWG and Shootout?
 what did the players learn exactly about the opponent strategy and what form did this learning take?

### 2020-01-20 Report/draft_report_v1.tex
draft improv and corrected faulty bayesian in exp2

@@
 Next, we explore whether learning transfer is moderated by the type of opponent and game similarity.
-Figure~@ref(fig: exp1-score-by-opp) shows the marginal mean scores for each game for both level-1 and level-2 facing players.
+Figure~@ref(fig: exp1-score-by-opp) shows the mean scores for rounds 2-6 by game for both level-1 and level-2 facing players.
 Graphically we can see that the pattern is dissimilar between level-1 and level-2 players, and we suspect transfer to be positively associated with similarity and negatively with degree of sophistication of the agent.
-To test these hypotheses, we run statistical tests on scores by game and opponent against the null hypothesis of 0 (no transfer).
+To test these hypotheses, we run statistical tests on early round scores by game and opponent against the null hypothesis of 0 (no transfer).
 
@@
 
-{\centering \includegraphics{../Report/images/exp1_earlyScore_by_opp}
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-score-by-opp-1}
 
@@
 
-\caption{Marginal means of players scores by game and type of opponents}\label{fig:exp1-score-by-opp}
+\caption{Average early scores by game and type of opponent faced}\label{fig:exp1-score-by-opp}
 \end{figure}
 
-Table~\ref{tab:table-early-scores} shows the scores on rounds 2-6 for both type of opponents in each game.
-We also report the t-stats and p-values to test the null hypothesis that scores on these early rounds are equal to 0.
-Rejecting the null hypothesis means that prior learning has been used to beat the opponent in these early rounds.
-For level-1 facing players, there is evidence of learning transfer from RPS to both FWG and NUMBERS.
-For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG (albeit scores are lower than for level-1 player) but not to the dissimilar game of NUMBERS.
+game.f condition lsmean SE df lower.CL upper.CL t.ratio p.value
+RPS Level1 0.0292 0.0768 150 -0.1226 0.181 0.380 0.7048
+FWG Level1 0.3042 0.0768 150 0.1524 0.456 3.960 0.0001
+NUM Level1 0.2875 0.0768 150 0.1357 0.439 3.743 0.0003
+RPS Level2 0.0815 0.0732 148 -0.0631 0.226 1.114 0.2671
+FWG Level2 0.1815 0.0732 148 0.0369 0.326 2.480 0.0143
+NUM Level2 0.0315 0.0732 148 -0.1131 0.176 0.431 0.6672
 
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:table-early-scores}Average early round scores by game and condition in first experiment}
-\begin{tabular}{lllllllll}
-\toprule
-game.f & \multicolumn{1}{c}{condition} & \multicolumn{1}{c}{lsmean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{lower.CL} & \multicolumn{1}{c}{upper.CL} & \multicolumn{1}{c}{t.ratio} & \multicolumn{1}{c}{p.value}\\
-\midrule
-FWG & Level1 & 0.30 & 0.08 & 149.58 & 0.10 & 0.51 & 3.96 & 0.00\\
-NUM & Level1 & 0.29 & 0.08 & 149.58 & 0.08 & 0.49 & 3.74 & 0.00\\
-RPS & Level1 & 0.03 & 0.08 & 149.58 & -0.18 & 0.23 & 0.38 & 1.00\\
-FWG & Level2 & 0.18 & 0.07 & 147.52 & -0.01 & 0.38 & 2.48 & 0.06\\
-NUM & Level2 & 0.03 & 0.07 & 147.52 & -0.16 & 0.23 & 0.43 & 1.00\\
-RPS & Level2 & 0.08 & 0.07 & 147.52 & -0.11 & 0.28 & 1.11 & 0.80\\
-\bottomrule
-\end{tabular}
-\end{threeparttable}
-\end{center}
-\end{table}
+For level-1 facing players, there is evidence of learning transfer from RPS to both FWG ( t(150) = 3.96, p \textless{} 0.001) and NUMBERS (t(150) = 3.74, p \textless{} 0.001) .
+For level-2 facing players, there is evidence for transfer from RPS to the similar game FWG, albeit scores are lower than for level-1 player ( t(150) = 2.48, p = 0.01) but not to the dissimilar game of NUMBERS.
 
 Our results when averaging across conditions (previous section) showed that there was indeed evidence for transfer to the more dissimilar game (NUMBERS).
-We can see from TABLE~\ref{tab:table-early-scores} that this transfer is exclusively driven by level-1 facing players, as scores of level-2 facing players are close to nil.
-Therefore, both groups of condition can generalise to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
+We can see from splitting the participants by opponent faced that this transfer is exclusively driven by level-1 facing players, as average early round scores of level-2 facing players are close to nil in the NUMBERS game.
+Therefore, both partiicpants facing level-1 and level-2 agents can transfer learning to the similar game, but only those facing the less sophisticated opponent are able to generalise to the less similar game.
 
@@
 
-In the second experiment, participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
+\hypertarget{participants-1}{%
+\subsubsection{Participants}\label{participants-1}}
+
+A total of 48 participants (21 females, 28 males, 1 unknown) used the Prolific Academic platform to participate in the experiment.
+This was a new set of participants unrelated to those taking part in Experiment 1.
+The average age of players was 30.2 years, and the mean duration to complete the task was 39 minutes.
+Participants were incentivised using a two-tier payment mechanism: a fixed fee of £2.5 for completing the experiment plus a performance linked bonus that averaged £1.32.
+
+\hypertarget{procedure-1}{%
+\subsubsection{Procedure}\label{procedure-1}}
+
+The participants each played 3 games sequentially against both level-1 and level-2 computer opponents, rather than just one like in the first experiment.
 The three games were Rock-Paper-Scissors, Fire-Water-Grass, and the penalty shootout game.
@@
 Indeed, a player not aiming to uncover the opponent's strategy and thus choosing to play randomly should be expected to have on average score per round of 0 in both RPS and FWG, and 0.33 in the Shootout game.
-To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will correct all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
-Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value \textless{} 0.0001 ; FWG: t(49) = 7.25 , p-value \textless{} 0.0001 ; SHOOT: t(49) = 13.61, p-value \textless{} 0.0001 ).
+To make the scores more comparable, and because we are interested in player's performance that is not due to chance, we will adjust all scores in the shootout game by subtracting the average score per round of a random strategy (0.33).
+Using parametric t-tests on adjusted scores, we reject the null hypothesis of random play in all three games (RPS: t(49) = 6.26, p-value \textless{} 0.0001 ; FWG: t(49) = 7.25 , p-value \textless{} 0.0001 ; Shootout: t(49) = 13.61, p-value \textless{} 0.0001 ).
 
 Using the average scores obtained by participants in each game and interaction, we explore whether learning has occurred within and between games.
-We perform a two (condition: level-1 first, level-2 first) by two ( opp\_type: level\_1 or level\_2) by three (game: RPS, FWG, SHOOT) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
-As the number of participants facing level-1 agents was slightly higher than those facing level-2 agents (27 vs 23), the ANOVA will not be balanced between the two levels of condition.
-We therefore used the ``afex'' (Singmann \& al., 2016) package in R, as it allows us to handle unbalanced designs and produces type III sum of squares by default.
-The full results of this analysis are provided in Table~\ref{tab:exp2-anova}.
+We perform a two (condition: level-1 first, level-2 first) by two ( opponne type: level-1 or level-2) by three (game: RPS, FWG, Shootout) by two (interaction: first or second) repeated measures ANOVA with the first factor varying between participants.
 
-\begin{table}[tbp]
-\begin{center}
-\begin{threeparttable}
-\caption{\label{tab:exp2-anova}ANOVA results for experiment 2}
-\begin{tabular}{lllllll}
-\toprule
-Effect & \multicolumn{1}{c}{$F$} & \multicolumn{1}{c}{$\mathit{df}_1^{GG}$} & \multicolumn{1}{c}{$\mathit{df}_2^{GG}$} & \multicolumn{1}{c}{$\mathit{MSE}$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$\hat{\eta}^2_G$}\\
-\midrule
-Condition f & 0.45 & 1 & 48 & 0.43 & .505 & .003\\
-Game f & 11.81 & 1.85 & 88.71 & 0.12 & < .001 & .039\\
-Interaction lvl & 1.34 & 1 & 48 & 0.06 & .253 & .001\\
-Opp type & 0.00 & 1 & 48 & 0.12 & .973 & .000\\
-Condition f $\times$ Game f & 1.34 & 1.85 & 88.71 & 0.12 & .266 & .005\\
-Condition f $\times$ Interaction lvl & 0.03 & 1 & 48 & 0.06 & .864 & .000\\
-Condition f $\times$ Opp type & 0.13 & 1 & 48 & 0.12 & .717 & .000\\
-Game f $\times$ Interaction lvl & 0.46 & 1.99 & 95.72 & 0.08 & .635 & .001\\
-Game f $\times$ Opp type & 5.31 & 1.7 & 81.82 & 0.11 & .010 & .015\\
-Interaction lvl $\times$ Opp type & 2.16 & 1 & 48 & 0.04 & .148 & .001\\
-Condition f $\times$ Game f $\times$ Interaction lvl & 2.43 & 1.99 & 95.72 & 0.08 & .094 & .006\\
-Condition f $\times$ Game f $\times$ Opp type & 1.23 & 1.7 & 81.82 & 0.11 & .294 & .003\\
-Condition f $\times$ Interaction lvl $\times$ Opp type & 0.02 & 1 & 48 & 0.04 & .883 & .000\\
-Game f $\times$ Interaction lvl $\times$ Opp type & 0.96 & 1.89 & 90.83 & 0.09 & .383 & .002\\
-Condition f $\times$ Game f $\times$ Interaction lvl $\times$ Opp type & 0.94 & 1.89 & 90.83 & 0.09 & .390 & .002\\
-\bottomrule
-\end{tabular}
-\end{threeparttable}
-\end{center}
-\end{table}
+\begin{figure}
 
-There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, \(\eta^{2}\) = 0.04, p \textless{} .0001), meaning that we reject the null hypothesis of scores in games being equal.
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-score-by-opp-1}
+
+}
+
+\caption{Avergae scores per game by opponcne type}\label{fig:exp2-score-by-opp}
+\end{figure}
+
+There is evidence for a main effect of Game on scores (F(1.85,88.7) = 11.81, \(\eta^{2}\) = 0.04, p \textless{} .0001).
 To explore these differences further, we look at post-hoc analyses for pairwise comparisons between game scores (p-values adjusted using Holm method for multiple comparisons).
-We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the SHOOT game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
+We find the performance in the games increases steadily throughout the experiment, with FWG performance significantly higher than RPS (t(96) =2.53, p = 0.025), and performance in the Shootout game also significantly higher than in FWG ( t(96) = 2.32, p = 0.025 ).
 There was no main effect of either opponent type, the interaction factor( first or second time opponent was faced) , or the condition factor (whether level-1 or level-2 opponent was faced first).
 This means that neither the type of opponent faced, nor whether it was the first or second interaction with the opponent nor which opponent was faced first did have a main effect on performance.
+There was however a significant interaction effect between Game and opponent type ( F(1.7, 81.82) = 5.31,\(\eta^{2}\) = 0.02, p = .01).
+As can be seen in Figure~\ref{fig:exp2-score-by-opp}, when facing level-1 agents, scores increase steadily after each game, with FWG score sgnificantly higher than RPS ( t(191) = 2.70, p = 0.03) and Shootout scores in turn significantly higher than FWG ( t(191) = 3.05, p = 0.01).
+There was no significant difference between average scores on any two games when facing level-2 agents however.
 
@@
 These scores are also averaged across the levels of condition (meaning they are irrespective of which opponent players faced first).
-For both the FWG and SHOOT games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
-(Level-1 opponent: FWG: t(270) = 4.99, p \textless{} 0.0001; SHOOT: t(270) = 6.66, p \textless{} 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p \textless{} 0.0001; SHOOT: t(270) = 3.21, p =0.004 ).
-Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shoot) when facing a level 1 opponent.
+For both the FWG and Shootout games, score in the early rounds of the first interaction are significantly higher than 0 for both opponent types.
+(Level-1 opponent: FWG: t(270) = 4.99, p \textless{} 0.0001; Shootout: t(270) = 6.66, p \textless{} 0.0001; Level-2 opponent: FWG: t(270) = 4.40, p \textless{} 0.0001; Shootout: t(270) = 3.21, p =0.004 ).
+Looking more specifically at early scores by type of opponent faced, we confirm the result from the first experiment that it is easier to transfer learning to the more dissimilar game (Shootout) when facing a level 1 opponent.
 Indeed, while the early scores of FWG for level-1 and level-2 facing players are not significantly different from each other, the score of the players facing the level-1 opponent is indeed almost 0.2 point per round higher than that of players facing level-2 opponents, and the difference is statistically significant ( t(144) = 2.45 , p = 0.01).

### 2020-01-21 Experiment_2/Experiment_2_modelling.Rmd
changes ToM comp model

@@
 # Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
-exp2_naive_bayes <- function(par,data,opp_strategy_vec,return_value,btwn_transfer) {
+TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer) {
 
@@
       if (data[t,"stage"] == 1) {
-        if (!(btwn_transfer)){
-          opp_prior_vec <- rep(1/num_strat, num_strat)
-        } else { # <- TRANFER 
-          # if there is between game transfer, then the opp_prior_vec should store what was learned about the SECOND opponent 
+        if (btwn_transfer){
+          # if there is between game transfer, then the opp_prior_vec should have stored what was learned about the SECOND opponent 
           # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
@@
           opp_prior_vec <- opp1_prior_vec
+
+        } else { # <- No between game TRANSFER 
+          opp_prior_vec <- rep(1/num_strat, num_strat)
         }
@@
       } else if (data[t,"stage"] == 2) {
+        if (within_transfer){
           # hold the probs vector of Opp type learned in stage 1 in memory and save to temp.
           opp1_prior_temp <- opp_prior_vec
-          # If no between games transfer reset prior to uniform 
-          if (!(btwn_transfer)){
+          if (btwn_transfer){
+            # If  between games transfer get prior from opp2 prior saved from last stage of last game 
+            opp_prior_vec <- opp2_prior_vec
+          } else { # if no between transfer start of first interaction with secnd opp should be reset
             opp_prior_vec <- rep(1/num_strat, num_strat)
-            } else {
-              opp_prior_vec <- opp2_prior_vec
           }
 
-      # we are round 1 of stage 3, use vector learned from stage 1, keep opp vector from round 20 of stage 2 for stage 4
+        } else { # Assume no between game transfer if no within. reasonable. 
+          opp_prior_vec <- rep(1/num_strat, num_strat)    
+        }
+
+      # we are round 1 of stage 3
       } else if (data[t,"stage"] == 3) {
+        if (within_transfer) {
+          # if within_transfer keep opp vector from round 20 of stage 2 for stage 4
           opp2_prior_temp <- opp_prior_vec
+          # if within_transfer, use what we learned about opp1 in stage 1 as new prior.  
           opp_prior_vec <- opp1_prior_temp
+
+        } else { # No within transfer, dont store anything and reset priors
+          opp_prior_vec <- rep(1/num_strat, num_strat)    
+        }
 
@@
       }  else if (data[t,"stage"] == 4) {
+        if (within_transfer) {
+          # Use what was learned about opponent 2 from stage 2.
+          opp_prior_vec <- opp2_prior_temp
+          if (btwn_transfer) {
             # Store what was learned about opponent 1 for nxt game...
            opp1_prior_vec <- opp_prior_vec
-        # Use what was learned about opponent 2 from stage 2.
-        opp_prior_vec <- opp2_prior_temp
+          }
+
+        } else {
+          opp_prior_vec <- rep(1/num_strat, num_strat)
+        }
+
       }
@@
 
-      # Get which opponent strategy human current actn maps to (if index = 0 then human current action is br to level-0 comp_strat...)
+      # Get which opponent strategy human current actn maps to (i.e, if index = 0 then human current action is best response to level-0 comp_strat...)
       indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))
@@
 
-exp2_naive_bayes(c(0.5,0.1),test_data,c("level0","level1","level2"),"-2loglik",TRUE)
+TOM_model(c(0.5,0.1),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = TRUE, btwn_transfer = TRUE)
 ```
-## Fitting Bayesian model with transfer  
+## Fitting Bayesian model with between game transfer (as well as within)  
 ```{r}
-exp2_TR_bayes <- list()
+exp2_BT <- list()
 for(id in unique(dat_exp2$human_id)) {
-  exp2_TR_bayes[[id]] <- list()
+  exp2_BT[[id]] <- list()
   tdat <- subset(dat_exp2,human_id == id)
@@
 
-  exp2_TR_bayes[[id]] <- optim(c(0.1,0.1),fn=exp2_naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", btwn_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+  exp2_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
 }
-save(exp2_TR_bayes, file="exp2_TR_bayes.RData")
+save(exp2_BT, file="exp2_BT.RData")
 
@@
 
-## Fitting Bayesian model with NO trnsfer 
+## Fitting ToM model with NO Between transfer (but with transfer within games)
 ```{r}
 
-exp2_NT_bayes <- list()
+exp2_NO_BT <- list()
 for(id in unique(dat_exp2$human_id)) {
-  exp2_NT_bayes[[id]] <- list()
+  exp2_NO_BT[[id]] <- list()
   tdat <- subset(dat_exp2,human_id == id)
 
-  # exp2_NT_bayes[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
+  # exp2_NO_BT[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
 
-  exp2_NT_bayes[[id]] <- optim(c(0.1,0.1),fn=exp2_naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+  exp2_NO_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
 }
 
-save(exp2_NT_bayes,file="exp2_NT_bayes.RData")
+save(exp2_NO_BT,file="exp2_NO_BT.RData")
+```
+
+## Fitting Bayesian model with NO Between or within transfer
+```{r}
+
+exp2_NO_Tr <- list()
+for(id in unique(dat_exp2$human_id)) {
+  exp2_NO_Tr[[id]] <- list()
+  tdat <- subset(dat_exp2,human_id == id)
+
+  # exp2_NO_Tr[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
+
+  exp2_NO_Tr[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+}
+
+save(exp2_NO_Tr,file="exp2_NO_Tr.RData")
 ```
@@
 
-load("exp2_TR_bayes.RData")
-load("exp2_NT_bayes.RData")
+load("exp2_BT.RData")
+load("exp2_NO_BT.RData")
 load("exp2_QLS_modelling.RData")
@@
                          # Bayesian updating with/without transfer
-                         "Bayes_Tr_BIC" = exp2_TR_bayes[[id]]$value + 2*log(180),
-                         "Bayes_No_Tr_BIC" = exp2_NT_bayes[[id]]$value+ 2*log(180),
+                         "Btwn_TR_BIC" = exp2_BT[[id]]$value + 2*log(180),
+                         "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
                          # Theta is the parameter governing AI stochasticity. Truth is 0.9
-                         "theta_transfer" = exp2_TR_bayes[[id]]$par[1],
-                         "theta_no_transfer" = exp2_NT_bayes[[id]]$par[1],
+                         "theta_transfer" = exp2_BT[[id]]$par[1],
+                         "theta_no_btw_tr" = exp2_NO_BT[[id]]$par[1],
                          # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
-                         "eps_transfer" = exp2_TR_bayes[[id]]$par[2],
-                         "eps_no_transfer" = exp2_NT_bayes[[id]]$par[2],
+                         "eps_transfer" = exp2_BT[[id]]$par[2],
+                         "eps_no_btwn_tr" = exp2_NO_BT[[id]]$par[2],
 
@@
 ```{r}
-exp2_table_results <- table(exp2_results[, "condition"],c("random","Bayes Tr","Bayes No Tr", "QL_states","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+exp2_table_results <- table(exp2_results[, "condition"],c("random","Bayes Tr","Bayes No Tr", "QL_states","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
 
@@
   id_results <- subset(exp2_results, ID == id)
-  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
+  min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
 
-  best_model <- c("random","Bayes Tr","Bayes NT", "QL_states","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
+  best_model <- c("random","ToM_BT","ToM_NBT", "QL_states","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
   # 
@@
                          "Total_time" = sum(tdat$human_rt),
-                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
+                         "TR_minus_NT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
                          "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC

### 2020-01-21 Report/draft_report_v1.Rmd
changes ToM comp model

@@
 # Introduction
-Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor, 2008) .
+Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
@@
 More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to modelling learning about the opponent.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to the task of opponent modelling.
 
@@
 Note that this corresponds to the Nash equilibrium strategy.
-Next, we include for comparison purposes a few other basic models of behavior, such as Q-learning on action choices, as well as a more sophisticatd Q-learning model incorporating a state space consisting of last round play.
+
+Next, we include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
+We will use a simple temporal difference learning update rule:
+
+$$ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) $$
+
+Where $ V_{t}(a) $ is the vlue associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
+Actions are chosen based on action values using a softmax choice rule.
+
+We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm [@watkins1992q]. The update rule becomes:
+
+$$ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) $$
+
+Where $Q(s_{t},a_{t})$ is the value of taking action $a$ when in state $s$ at time $t$,  $\gamma$ is the discount rate applied to future rewards.
+For instance, $Q(RS,P)$ denotes the value of taking action "Paper" this round if the player's last action was "Rock" and the opponent played "Scissors".
+This is a much richer model allowing the players to compute the values of actions conditional on past play.
+
+### EWA Models 
+Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics].
+EWA models are  model of behavior in repeated games, that nest two seemingly different approaches, namely reinforcement learning and belief learning.
+Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
+In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
+The self-tunign EWA model has been shown to perform better than both these nested models in multiple repeated gmes and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
+
+Lt's define some notation in order to write the pdate rule of the self-tuning EWA model.
+For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j).
+Strategies actually played by i in period t, are denoted $s_{i}(t)$, while the opponent's strategy at time t is denoted $s_{-i}(t)$.
+After playing  $s_{i}^{j}$ at time $t$, player i payoff is denoted $\pi_{i}(s_{i}^{j},s_{-i}(t))$, and the actual payoff the player received is $\pi_{i}(t)$.
+
+The EWA model is based on updating "Attractions" for each action over time.
+For instance, the attraction of strategy $j$ to player $i$ at time $t$ is written $A_{i}^{j}(t)$.
+Future action choice probabilities are based on these attractions using the softmax playing rule:
+
+$$P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} $$
+
+The attractions are updated over every time step $t$ using the followng update rule :
+
+$$ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} $$
+
+Here, I(x,y) is the indicator function equla to 1 if $ x = y$ and 0 otherwise.
+A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince ($N(t-1)$) which is itself decaying by a wight $\phi$.
+The result is added to either the payoff received (when the indicator function is 0), or to $\delta$ times the foregone payoff (when indicator function is 1).
+We can see that setting $\delta = 0$ leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play [@cheung1994learning].
+While the assumption in expanding the update rule above is that $\phi$ and $\delta$ are free parameters [@camerer1997experience], the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in [@ho2004economics].
+
+### ToM models
+
+In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
+We use values of k  in ${0,1,2}$.
+We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
+In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
+In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second intraction with the opponent, but are not able to transfer that learning to new games.
+
+Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
+In the context of experiment 2, we still assume that within game transfer is still present (from first to second interaction).
+
+In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive).
+And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniforme probability of level-k opponent (NT), so no within or between opponent model learning transfer.
+
+In summary, we fit two ToM models for experiment 1-play ( NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive)
+
+#############################################################
 The Bayesian approach is represented by models whereby agents would update an initial belief over the opponent's strategy consisting of various level-k strategies (resp.
@@
 
-Next, we fitted a self-tuning EWA model (Ho et al., 2004) both on action choices without states and with states consisting of lat round play.
+Next, we fitted a self-tuning EWA model [@ho2004economics] both on action choices without states and with states consisting of lat round play.
 The self-tuning EWA model generalizes both reinforcement learning as well as fictitious play models and has been proven to do well than equilibrium models in various game situations.
@@
 whereby the agent learns the transition probabilities between states ans uses that to choose the best action, given the current state and it's belief about what the new state will be.
+#############################################################
 

### 2020-01-22 Experiment_2/Experiment_2_modelling.Rmd
report changes to comp modelling section

@@
 load("exp2_NO_BT.RData")
+load("exp2_NO_Tr.RData")
 load("exp2_QLS_modelling.RData")
@@
                          "No_Btwn_Tr_BIC" = exp2_NO_BT[[id]]$value+ 2*log(180),
+                         "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
+
                          # Theta is the parameter governing AI stochasticity. Truth is 0.9
@@
                          "theta_no_btw_tr" = exp2_NO_BT[[id]]$par[1],
+                         "theta_no_tr" =  exp2_NO_Tr[[id]]$par[1],
                          # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
@@
                          "eps_no_btwn_tr" = exp2_NO_BT[[id]]$par[2],
+                         "eps_no_tr" = exp2_NO_Tr[[id]]$par[2],
 
@@
 ```{r}
-exp2_table_results <- table(exp2_results[, "condition"],c("random","Bayes Tr","Bayes No Tr", "QL_states","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT", "QL_states","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
 
@@
   id_results <- subset(exp2_results, ID == id)
-  min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
+  min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC", "QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
 
-  best_model <- c("random","ToM_BT","ToM_NBT", "QL_states","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
+  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","QL_states","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
   # 

### 2020-01-22 Report/draft_report_v1.Rmd
report changes to comp modelling section

@@
 
-In most of the experimental paradigms we saw, participants were playing other human players either one on one or as a group.
-In this case, players are learning about the game but so are their opponents.
-While the approach of matching groups of human players repeatedly to play economic games has ecological validity in recreating environments where social decision making can be studied, it complicates the detection and modelling of strategies used by participants.
-It is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
-It is also difficult to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-One potential solution is to replace the human opponent with a computerised agent, allowing researchers to manipulate the opponent's behaviour and observe how the human participants adapt their behaviour.
-For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
-Shachat & Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
-
-Still, one of the limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-They either used strategies that did not take into account the human participant's histpry of play (as in the case of pre-determined distribution on actions), or strategies that only depended on the player's patterns of past plays, irrespective of the computer play.
-In other words These strategies did not necessarily take into account the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
-Their play was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+Still, one of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
+The strategies implemented by the computer opponents had a style of play that was not "human-like" in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
 It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
@@
 
-Another potential issue in the experimental paradigms used in the learning transfer literature is the use of social dilemmas and cooperative/competitive settings that may invoke confounding factors in learning and transfer.
-Social dilemma and coordination games crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
+In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
+The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
+
+Our choice of using computer oponents sinstead of matching groups of participants makes it easier  to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
+When playing against other human opponents,players are learning about the game and the strategy of the opponent simultaneously.
+Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
+The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
+For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
+Shachat & Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
+They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
+
+We chose to use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
+We avoid social dilemma and coordination games that crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
 Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
@@
 
-To address some of these limitations in the existing literature on learning transfer outlined above, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
-We also use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
 We measure transfer of learning about the opponent strategy between games with varying degrees of similarity.
 The first two games we use are identical except for action labels.
-In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with 0 expected reward against a Nash player.
+In one experiment, the third game is strategically similar to the first two but descriptively different, while in a second experiment, we introduce a third game that is dissimilar to the first two in terms of payoff matrix and strategic structure while retaining, like all other games, a unique mixed strategy Nash equilibrium of random action with a fixed expected reward against a Nash player.
 
-Hence, we ran a total of two experiments where human participants played against computer opponents a total of 3 different games.
-In the following sections, we wwill describe first the methods used in the first experiments and look at the results, then we will do the same for the second experiment.
+Hence, we ran a total of two experiments where human participants played 3 different games against either 1 (first experiment ) or 2 (second experiment) computer opponents.
+In the following sections, we will describe each experiment's methodology and results separately, then discuss the findings before using computational modelling to shed light on some of the results.
 
@@
 
-Where $ V_{t}(a) $ is the vlue associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
+Where $V_{t}(a)$ is the vlue associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
 Actions are chosen based on action values using a softmax choice rule.
@@
 Next, we use a self-tuning Experience Weighted attraction model [@ho2004economics].
-EWA models are  model of behavior in repeated games, that nest two seemingly different approaches, namely reinforcement learning and belief learning.
+EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning.
 Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
 In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
-The self-tunign EWA model has been shown to perform better than both these nested models in multiple repeated gmes and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
+The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated gmes and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
 
-Lt's define some notation in order to write the pdate rule of the self-tuning EWA model.
+Let's define some notation in order to write the pdate rule of the self-tuning EWA model.
 For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j).
@@
 
-In summary, we fit two ToM models for experiment 1-play ( NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive)
+In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
+Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
 
-#############################################################
-The Bayesian approach is represented by models whereby agents would update an initial belief over the opponent's strategy consisting of various level-k strategies (resp.
-0,1 and 2).
-We fitted two models in which agents best respond to the opponent model.
-In the first, the beliefs about the opponent's adopted strategy are transfered across games, and another in which no transfer of opponent models is allowed.
+## Experiment 1 modelling :
 
-Next, we fitted a self-tuning EWA model [@ho2004economics] both on action choices without states and with states consisting of lat round play.
-The self-tuning EWA model generalizes both reinforcement learning as well as fictitious play models and has been proven to do well than equilibrium models in various game situations.
-Finally, we also included a model-based reinforcement learning approach.
-whereby the agent learns the transition probabilities between states ans uses that to choose the best action, given the current state and it's belief about what the new state will be.
-#############################################################
+```{r load-comp-mod-distrib, include=FALSE}
 
-In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
-Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was explained by each model.
-Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
+All_comp_results <- read.csv(file="../All_results.csv")
+exp1_comp_table <- table(All_comp_results[, "condition"],c("random","Bayes Tr","Bayes No Tr","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(All_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC","MBM_BIC")],1,which.min)])
 
-```{r exp1-comp-models, fig.cap = "Histogram of best fitting computational models for experiment 1", fig.align='center'}
+ #write.csv(exp1_comp_table ,file="exp1_comp_table ",row.names = TRUE)
+ kable(exp1_comp_table)
+```
 
-knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
+```{r exp1-cum-score-plots, include=FALSE}
+
+exp1_dat = read.csv("../exp1_data.csv")
+exp1_model_comp = read.csv("../exp1_model_comp.csv")
+
+datalist = list()
+i = 0
+new_dat <- setNames(data.frame(matrix(ncol = ncol(exp1_dat), nrow = 0)), colnames(exp1_dat))
+for(id in unique(exp1_dat$human_id)) {
+  i <- i+1
+  tdat <- subset(exp1_dat,human_id == id)
+  tdat$part_num <- i
+  tdat <- within(tdat, acc_sum <- cumsum(tdat$score))
+  datalist[[i]] <- tdat
+}
+
+# Merge all datasets into one 
+new_dat <- dplyr::bind_rows(datalist)
+# or new_dat <- data.table::rbindlist(datalist)
+
+# Add column for time t
+new_dat <- new_dat %>% group_by(exp1_dat$human_id) %>% mutate(t = row_number())
+
+# Add best fitting model per participant
+new_dat <- merge(new_dat, exp1_model_comp[, c("human_id", "Best_model")], by="human_id")
+
+temp <- new_dat[,c("t","acc_sum","Best_model","condition","part_num")]
+dat_by_model <- temp %>% group_by(Best_model,t) %>% 
+  summarize(model_acc_sum = mean(acc_sum))
 
@@
 
-In experiment 2 however, we can see from Figure\ \@ref(fig:exp2-comp-models) that Q-learning with the aforementioned state-space wasn't as successful as the bayesian approached in fitting player's action choices.
-In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) were by far the most successful.
+Figure\ \@ref(fig:exp1-comp-models)  shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
 
-```{r exp2-comp-models, fig.cap = "Histogram of best fitting computational models for experiment 2", fig.align='center'}
+```{r exp1-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 1", fig.align='center'}
 
-knitr::include_graphics("../Report/images/exp2_comp_models.png", dpi = 108)
+#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
+par(las=2) # make label text perpendicular to axis
+par(mar=c(5,8,4,2)) # increase y-axis margin.
+barplot(exp1_comp_table,
+        horiz =TRUE, # rotate barplot for better visibility 
+        las=1, # change orientation x axis labels 
+        cex.names=0.8, # text label size
+        legend = rownames(exp1_comp_table),
+        beside =TRUE,
+        xlab="Number of participants",
+        args.legend=list( # positioning of legend box 
+        x=ncol(exp1_comp_table) + 4,
+        y=max(colSums(exp1_comp_table)) + 4,
+        bty = "n")
+ )
 
@@
 
-```{r exp1-cumScores, fig.cap = "Average cumulative scores of participants in experiment 1 by best fitting model", fig.align='center'}
+```{r exp1-comp-model, fig.cap = "Histogram of best fitting computational models for experiment 1", fig.align='center'}
+ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
+   geom_line(aes(color= Best_model))
+```
 
-knitr::include_graphics("../Report/images/exp1_cumScores.png", dpi = 108)
+## Experiment 2
+
+```{r, include = FALSE}
+
+exp2_comp_results <- read.csv(file="../Experiment_2/exp2_results.csv")
+exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "QL_states","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+
+ # write.csv(exp2_table_results,file="exp2_table_results.csv",row.names = TRUE)
+ kable(exp2_comp_table)
+```
+
+```{r exp2-comp-models, fig.cap = "Histogram of best fitting computational models by condition for experiment 2", fig.align='center'}
+
+#knitr::include_graphics("../Report/images/exp1_comp_models.png", dpi = 108)
+par(las=2) # make label text perpendicular to axis
+par(mar=c(5,8,4,2)) # increase y-axis margin.
+barplot(exp2_comp_table,
+        horiz =TRUE, # rotate barplot for better visibility 
+        las=1, # change orientation x axis labels 
+        cex.names=0.8, # text label size
+        beside =TRUE,
+        xlab="Number of participants",
+        # legend = c("level-1 opp first","level-2 opp first"),
+        legend = paste0(rownames(exp2_comp_table) , " faced first"),
+        args.legend=list( # positioning of legend box 
+        x=ncol(exp1_comp_table) + 3,
+        y=max(colSums(exp1_comp_table)) -1,
+        bty = "n")
+ )
 
@@
 
-Doing the same exercise for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a bayesian model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expectedm random play as well as EWA were at the bottom of cumulative performance.
+In experiment 2, we can see from Figure\ \@ref(fig:exp2-comp-models) that Q-learning with the aforementioned state-space wasn't as successful as the bayesian approached in fitting player's action choices.
+In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) were by far the most successful.
+
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a bayesian model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expectedm random play as well as EWA were at the bottom of cumulative performance.
 

### 2020-01-22 Report/draft_report_v1.tex
report changes to comp modelling section

@@
 
-Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence (Taylor, 2008) .
+Being able to transfer previously acquired knowledge to a new domain is one of the hallmarks of human intelligence.
 Humans are naturally endowed with the ability to extract relevant features from a situation, identify the presence of these features in a novel setting and use previously acquired knowledge to adapt to previously unseen challenges using acquired knowledge.
@@
 
-In most of the experimental paradigms we saw, participants were playing other human players either one on one or as a group.
-In this case, players are learning about the game but so are their opponents.
-While the approach of matching groups of human players repeatedly to play economic games has ecological validity in recreating environments where social decision making can be studied, it complicates the detection and modelling of strategies used by participants.
-It is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
-It is also difficult to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-One potential solution is to replace the human opponent with a computerised agent, allowing researchers to manipulate the opponent's behaviour and observe how the human participants adapt their behaviour.
-For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
-Shachat \& Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
-They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
-
-Still, one of the limitations in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-They either used strategies that did not take into account the human participant's histpry of play (as in the case of pre-determined distribution on actions), or strategies that only depended on the player's patterns of past plays, irrespective of the computer play.
-In other words These strategies did not necessarily take into account the computer's own past plays, or the degree of strategic reasoning of the human player about the computer.
-Their play was not ``human-like'' in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+Still, one of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
+The strategies implemented by the computer opponents had a style of play that was not ``human-like'' in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
 It is therefore important to have agents that ``play like humans'', and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
@@
 
-Another potential issue in the experimental paradigms used in the learning transfer literature is the use of social dilemmas and cooperative/competitive settings that may invoke confounding factors in learning and transfer.
-Social dilemma and coordination games crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
+In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
+The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
+
+Our choice of using computer oponents sinstead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
+When playing against other human opponents,players are learning about the game and the strategy of the opponent simultaneously.
+Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
+The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
+For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
+Shachat \& Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
+They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
+
+We chose to use a set of purely competitive zero-sum games that incentivise reasoning about the opponent without introducing social confounding factors.
+We avoid social dilemma and coordination games that crystallise the conflict between competing with others out of self-interest or cooperating to reach a socially optimal outcome.
 Playing these games repeatedly implicates important social constructs such as reputation building, trust and other individual psychological attributes such as cooperativeness and inequity aversion.
@@
 Note that this corresponds to the Nash equilibrium strategy.
-Next, we include for comparison purposes a few other basic models of behavior, such as Q-learning on action choices, as well as a more sophisticatd Q-learning model incorporating a state space consisting of last round play.
-The Bayesian approach is represented by models whereby agents would update an initial belief over the opponent's strategy consisting of various level-k strategies (resp.
-0,1 and 2).
-We fitted two models in which agents best respond to the opponent model.
-In the first, the beliefs about the opponent's adopted strategy are transfered across games, and another in which no transfer of opponent models is allowed.
 
-Next, we fitted a self-tuning EWA model (Ho et al., 2004) both on action choices without states and with states consisting of lat round play.
-The self-tuning EWA model generalizes both reinforcement learning as well as fictitious play models and has been proven to do well than equilibrium models in various game situations.
-Finally, we also included a model-based reinforcement learning approach.
-whereby the agent learns the transition probabilities between states ans uses that to choose the best action, given the current state and it's belief about what the new state will be.
+Next, we include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
+We will use a simple temporal difference learning update rule:
+
+\[ V_{t+1}(a) = V_{t}(a) + \alpha*( R_{t}  - V_{t}(a)) \]
+
+Where \$ V\_\{t\}(a) \$ is the vlue associated with action \(a\) at time \(t\), \(\alpha\) is the learning rate and \(R_{t}\) the reward at time t.
+Actions are chosen based on action values using a softmax choice rule.
+
+We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm ({\textbf{???}}). The update rule becomes:
+
+\[ Q^{new}(s_{t},a_{t}) = Q(s_{t},a_{t}) + \alpha*( R_{t}  + \gamma*\underset{a}{\max}Q(s_{t+1},a) - Q(s_{t},a_{t}) ) \]
+
+Where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), \(\gamma\) is the discount rate applied to future rewards.
+For instance, \(Q(RS,P)\) denotes the value of taking action ``Paper'' this round if the player's last action was ``Rock'' and the opponent played ``Scissors''.
+This is a much richer model allowing the players to compute the values of actions conditional on past play.
+
+\hypertarget{ewa-models}{%
+\subsubsection{EWA Models}\label{ewa-models}}
+
+Next, we use a self-tuning Experience Weighted attraction model ({\textbf{???}}).
+EWA models are model of behavior in repeated games, that nest two seemingly different approaches, namely reinforcement learning and belief learning.
+Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
+In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
+The self-tunign EWA model has been shown to perform better than both these nested models in multiple repeated gmes and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
+
+Lt's define some notation in order to write the pdate rule of the self-tuning EWA model.
+For player i, there are \(m_{i}\) strategies, denoted \(s_{i}^{j}\) (i.e player i's strategy number j).
+Strategies actually played by i in period t, are denoted \(s_{i}(t)\), while the opponent's strategy at time t is denoted \(s_{-i}(t)\).
+After playing \(s_{i}^{j}\) at time \(t\), player i payoff is denoted \(\pi_{i}(s_{i}^{j},s_{-i}(t))\), and the actual payoff the player received is \(\pi_{i}(t)\).
+
+The EWA model is based on updating ``Attractions'' for each action over time.
+For instance, the attraction of strategy \(j\) to player \(i\) at time \(t\) is written \(A_{i}^{j}(t)\).
+Future action choice probabilities are based on these attractions using the softmax playing rule:
+
+\[P_{i}^{j}(t+1) = \frac{e^{\lambda . A_{i}^{j}(t)}}{\sum_{k=1}^{m_{i}}e^{\lambda . A_{i}^{k}(t)}} \]
+
+The attractions are updated over every time step \(t\) using the followng update rule :
+
+\[ A_{i}^{j}(t) =  \frac{\phi . N(t-1) . A_{i}^{j}(t-1) + [ \delta + (1-\delta) . I(s_{i}^{j},s_{i}(t))] . \pi_{i}(s_{i}^{j},s_{-i}(t)) } {\phi . N(t-1) + 1} \]
+
+Here, I(x,y) is the indicator function equla to 1 if \$ x = y\$ and 0 otherwise.
+A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince (\(N(t-1)\)) which is itself decaying by a wight \(\phi\).
+The result is added to either the payoff received (when the indicator function is 0), or to \(\delta\) times the foregone payoff (when indicator function is 1).
+We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play ({\textbf{???}}).
+While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters ({\textbf{???}}), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in ({\textbf{???}}).
+
+\hypertarget{tom-models}{%
+\subsubsection{ToM models}\label{tom-models}}
+
+In this set of models, we assume that participants have a belief that the opponent is a level-k agent, with uniform probability of the level k, and use evidence of past play to update their beliefs in a Bayesian way about the true value of k.
+We use values of k in \({0,1,2}\).
+We distinguish between multiple ToM models based on their ability to keep what was learned about the opponent in memory and hence facilitate transfer.
+In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
+In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second intraction with the opponent, but are not able to transfer that learning to new games.
+
+Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
+In the context of experiment 2, we still assume that within game transfer is still present (from first to second interaction).
+
+In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive).
+And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniforme probability of level-k opponent (NT), so no within or between opponent model learning transfer.
+
+In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive)
 

### 2020-01-22 comp_model_1019.Rmd
report changes to comp modelling section

@@
 
-```
-
-## Modelling fixed level-k type participant
-```{r}
-# FIXED STRATEGIES (level-k) 
-# create a function which computes the -2 log Likelihood over the three games for a particular strategy
-# modelLL <- function(par,data,strategy, return_value=c("-2logLik","likelihood_by_trial")) {
-#   # par = parameter vector (just has one element here) 
-#   # dat = data subset for one participant
-#   # strategy = c("level1","level2","level3","WSLS")
-#   # return = -2logLik (default, for use in optimization) or "likelihood_by_trial" (for later plotting, etc)
-#   return_value <- match.arg(return_value)
-#   
-#   # count the number of supplied parameters. If 1, it is a _1 model, 
-#   # if 3, it is a _3 model. For the _3 model we will use unbounded
-#   # optimization (transforming parameters from a logit scale back to 0 to 1)
-#   n_theta <- length(par)
-#   if(n_theta == 3) par <-my_logistic(par)
-#   theta <- par[1]
-#   # set up a vector to store the likelihood
-#   lik <- rep(0.0,nrow(data))
-#   for(t in 1:nrow(data)) {
-#     t_game <- data[t,"game"]
-#     pred_file <- switch(as.character(t_game),rps=rps_predict,fwg = fwg_predict, numbers = numbers_predict)
-#     if(n_theta == 3) {
-#       theta <- switch(as.character(t_game),rps=par[1],fwg = par[2], numbers = par[3])
-#     }
-#     if(t_game == "numbers") nopts <- 5 else nopts <- 3
-#     if(data[t,"round"] == 1) {
-#       # first round is uniform prediction
-#       pred <- NA
-#       lik[t] <- 1/nopts
-#     } else {
-#       # get prediction from file
-#       pred <- as.character(filter(pred_file,human_previous == as.character(data[t-1,"h_action"]) & computer_previous == as.character(data[t-1,"a_action"]))[strategy][1,])
-#       if(as.character(data[t,"h_action"]) == pred) {
-#         lik[t] <- theta + (1-theta)/nopts
-#       } else {
-#         lik[t] <- (1-theta)/nopts
-#       }
-#     }
-#     # for debugging uncomment the line below
-#     # cat(as.character(pred),as.character(data[t,"h_action"]),lik[t],"\n")
-#   }
-#   if(return_value == "-2logLik") {
-#     ret <- -2*sum(log(lik))
-#     if(ret == Inf) {
-#       return(1e+300)
-#     } else {
-#       return(ret)
-#     }
-#   }
-#   if(return_value == "likelihood_by_trial") return(lik)
-# }
-# 
-# all_modelling <- list()
-# for(id in unique(dat$human_id)) {
-#   all_modelling[[id]] <- list()
-#   tdat <- subset(dat,human_id == id)
-#   # level 1
-#   all_modelling[[id]]$level1_1 <- optimize(modelLL,interval=c(0,1),data=tdat,strategy="level1")
-#   all_modelling[[id]]$level1_3 <- optim(my_logit(rep(all_modelling[[id]]$level1_1$minimum,3)),fn=modelLL,data=tdat,strategy="level1")
-#   # level 2
-#   all_modelling[[id]]$level2_1 <- optimize(modelLL,interval=c(0,1),data=tdat,strategy="level2")
-#   all_modelling[[id]]$level2_3 <- optim(my_logit(rep(all_modelling[[id]]$level2_1$minimum,3)),fn=modelLL,data=tdat,strategy="level2")
-#   # level 3
-#   all_modelling[[id]]$level3_1 <- optimize(modelLL,interval=c(0,1),data=tdat,strategy="level3")
-#   all_modelling[[id]]$level3_3 <- optim(my_logit(rep(all_modelling[[id]]$level3_1$minimum,3)),fn=modelLL,data=tdat,strategy="level3")
-#   # WSLS
-#   all_modelling[[id]]$WSLS_1 <- optimize(modelLL,interval=c(0,1),data=tdat,strategy="WSLS")
-#   all_modelling[[id]]$WSLS_3 <- optim(my_logit(rep(all_modelling[[id]]$WSLS_1$minimum,3)),fn=modelLL,data=tdat,strategy="WSLS")
-# }
-# 
-# save(all_modelling,file="all_modelling.RData")
-
-```
-
-```{r}
-# create a table with BIC
-# BIC_results <- data.frame()
-# for(id in unique(dat$human_id)) {
-#     BIC_results <- rbind(BIC_results,
-#                          data.frame(
-#                            "id" = id,
-#                            "condition" = dat[dat$human_id==id,"condition"][1],
-#                            "random_BIC" = -2*(100*log(1/3) + 50*log(1/5)), 
-#                            "level1_1_theta" = all_modelling[[id]]$level1_1$minimum,
-#                            "level1_1_BIC" = all_modelling[[id]]$level1_1$objective + 1*log(150),
-#                            "level1_3_theta1" = my_logistic(all_modelling[[id]]$level1_3$par[1]),
-#                            "level1_3_theta2" = my_logistic(all_modelling[[id]]$level1_3$par[2]),
-#                            "level1_3_theta3" = my_logistic(all_modelling[[id]]$level1_3$par[3]),
-#                            "level1_3_BIC" = all_modelling[[id]]$level1_3$value + 3*log(150),
-#                            "level2_1_theta" = all_modelling[[id]]$level2_1$minimum,
-#                            "level2_1_BIC" = all_modelling[[id]]$level2_1$objective + 1*log(150),
-#                            "level2_3_theta1" = my_logistic(all_modelling[[id]]$level2_3$par[1]),
-#                            "level2_3_theta2" = my_logistic(all_modelling[[id]]$level2_3$par[2]),
-#                            "level2_3_theta3" = my_logistic(all_modelling[[id]]$level2_3$par[3]),
-#                            "level2_3_BIC" = all_modelling[[id]]$level2_3$value + 3*log(150),
-#                            "level3_1_theta" = all_modelling[[id]]$level3_1$minimum,
-#                            "level3_1_BIC" = all_modelling[[id]]$level3_1$objective + 1*log(150),
-#                            "level3_3_theta1" = my_logistic(all_modelling[[id]]$level3_3$par[1]),
-#                            "level3_3_theta2" = my_logistic(all_modelling[[id]]$level3_3$par[2]),
-#                            "level3_3_theta3" = my_logistic(all_modelling[[id]]$level3_3$par[3]),
-#                            "level3_3_BIC" = all_modelling[[id]]$level3_3$value + 3*log(150),
-#                            "WSLS_1_theta" = all_modelling[[id]]$WSLS_1$minimum,
-#                            "WSLS_1_BIC" = all_modelling[[id]]$WSLS_1$objective + 1*log(150),
-#                            "WSLS_3_theta1" = my_logistic(all_modelling[[id]]$WSLS_3$par[1]),
-#                            "WSLS_3_theta2" = my_logistic(all_modelling[[id]]$WSLS_3$par[2]),
-#                            "WSLS_3_theta3" = my_logistic(all_modelling[[id]]$WSLS_3$par[3]),
-#                            "WSLS_3_BIC" = all_modelling[[id]]$WSLS_3$value + 3*log(150)
-#                          ))
-# }
-# write.csv(BIC_results,file="BIC_result.csv",row.names = FALSE)
-# kable(BIC_results)
-```
-
-```{r}
-
-# create a table with best fitting models by condition
-# table(dat$condition[dat$round==1 & dat$game == "rps"],c("random","level1_1","level2_1","level3_1","WSLS_1","level1_3","level2_3","level3_3","WSLS_3")[apply(BIC_results[,c("random_BIC","level1_1_BIC","level2_1_BIC","level3_1_BIC","WSLS_1_BIC","level1_3_BIC","level2_3_BIC","level3_3_BIC","WSLS_3_BIC")],1,which.min)])
-# 
-# ## treat 1 theta and 3 theta versions the same
-# # create a table with best fitting models by condition
-# table(dat$condition[dat$round==1 & dat$game == "rps"],c("random","level1","level2","level3","WSLS","level1","level2","level3","WSLS")[apply(BIC_results[,c("random_BIC","level1_1_BIC","level2_1_BIC","level3_1_BIC","WSLS_1_BIC","level1_3_BIC","level2_3_BIC","level3_3_BIC","WSLS_3_BIC")],1,which.min)])
-#
-
-```
-
-## Fixed level-k type: Likelihood of the different models by trial
-This plot ks based on the three parameter versions of each strategy, and shows the average probability according to each model of participants' choices.
-It can be seen that, compared to the RPS game, where the fit grows slowly over trials, the fit in the later games increases much more rapidly.
-
-```{r}
-# long_likelihood_by_trial <- data.frame()
-# for(id in unique(dat$human_id)) {
-#   tdat <- subset(dat,human_id == id)
-#   for(strategy in c("level1","level2","level3","WSLS")) {
-#     long_likelihood_by_trial <- rbind(long_likelihood_by_trial,
-#                                       data.frame(id = id,
-#                                                  condition = dat[dat$human_id==id,"condition"][1],
-#                                                  strategy = strategy,
-#                                                  round = 1:50,
-#                                                  game = rep(c("rps","fwg","numbers"),each=50),
-#                                                  likelihood = modelLL(all_modelling[[id]][[paste(strategy,"_3",sep="")]]$par,
-#                                                                       data=tdat,
-#                                                                       strategy = strategy,
-#                                                                       return_value = "likelihood_by_trial")
-#                                       )
-#                                 )
-#   }
-# }
-# library(ggplot2)
-# plot_dat <- long_likelihood_by_trial %>% group_by(condition,game,round,strategy) %>%
-#       summarize(probability = mean(likelihood))
-# # make sure the different games are ordered in the way they were played
-# plot_dat$game <- factor(plot_dat$game,levels=c("rps","fwg","numbers"))
-# ggplot(plot_dat,aes(x=round,y=probability,colour=strategy)) + geom_line() + facet_grid(game~condition)
 ```
@@
 
-naive_bayes <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {
+exp1_ToM <- function(par,data,opp_strategy_vec,return_value,opp_mod_transfer) {
 
@@
       lik_hum[t] <- 1/nopts
-      ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transferreset prior to uniform)
+      ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer, reset prior to uniform)
       if (!(opp_mod_transfer)) {
@@
 # data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
-# naive_bayes(c(0.9,0.99),data,c("level0","level1","level2"),"-2loglik",FALSE)
-```
-
-```{r}
-rps_predict_opp <- read.csv("rps_predict_opp.csv")
-red_opp <- filter(rps_predict_opp, rps_predict_opp$human_previous == "R" & rps_predict_opp$computer_previous == "S")
-
-as.character(red_opp[["level0"]])
-```
-
-# Fitting a bayesian model WITH TRANSFER of opp strat distribution between games 
-```{r}
-
-TR_bayes_modelling <- list()
+# exp1_ToM(c(0.9,0.99),data,c("level0","level1","level2"),"-2loglik",FALSE)
+```
+
+```{r}
+# rps_predict_opp <- read.csv("rps_predict_opp.csv")
+# red_opp <- filter(rps_predict_opp, rps_predict_opp$human_previous == "R" & rps_predict_opp$computer_previous == "S")
+# 
+# as.character(red_opp[["level0"]])
+```
+
+# Fitting a bayesian model WITH BETWEEN GAME TRANSFER of opp strat distribution between games 
+```{r, cache=TRUE}
+exp1_ToM_TR <- list()
 for(id in unique(dat$human_id)) {
-  TR_bayes_modelling[[id]] <- list()
+  exp1_ToM_TR[[id]] <- list()
   tdat <- subset(dat,human_id == id)
 
-  # TR_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))
-
-  TR_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-}
-save(TR_bayes_modelling,file="TR_bayes_modelling.RData")
-
-```
-
-# Fitting a bayesian model with NO TRANSFER of opp strat distribution between games 
-```{r}
-NT_bayes_modelling <- list()
+  # exp1_ToM_TR[[id]] <- DEoptim(fn=exp1_ToM, lower = c(0,0), upper = c(1,1), data=tdat, opp_strategy_vec = c("level0","level1","level2") ,return_value = "-2loglik", opp_mod_transfer = TRUE, control=list(trace = FALSE, parallelType=1,parVar = c("best_response")))
+
+  exp1_ToM_TR[[id]] <- optim(c(0.1,0.1),fn=exp1_ToM,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+}
+save(exp1_ToM_TR,file="exp1_ToM_TR.RData")
+
+```
+
+# Fitting a bayesian model with NO BETWEEN GAME TRANSFER of opp strat distribution between games 
+```{r, cache =TRUE}
+exp1_ToM_NT <- list()
 for(id in unique(dat$human_id)) {
-  NT_bayes_modelling[[id]] <- list()
+  exp1_ToM_NT[[id]] <- list()
   tdat <- subset(dat,human_id == id)
 
-  # NT_bayes_modelling[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
-
-  NT_bayes_modelling[[id]] <- optim(c(0.1,0.1),fn=naive_bayes,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE ,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
-}
-
-save(NT_bayes_modelling,file="NT_bayes_modelling.RData")
+  # exp1_ToM_NT[[id]] <- DEoptim(fn=exp1_ToM, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
+
+  exp1_ToM_NT[[id]] <- optim(c(0.1,0.1),fn=exp1_ToM,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE ,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+}
+
+save(exp1_ToM_NT,file="exp1_ToM_NT.RData")
 
@@
                          # BICs 
-                         "BIC_transfer" = TR_bayes_modelling[[id]]$value + 2*log(150),
-                         "BIC_no_transfer" = NT_bayes_modelling[[id]]$value+ 2*log(150),
+                         "BIC_transfer" = exp1_ToM_TR[[id]]$value + 2*log(150),
+                         "BIC_no_transfer" = exp1_ToM_NT[[id]]$value+ 2*log(150),
                          # Theta is the parameter governing AI stochasticity. Truth is 0.9
-                         "theta_transfer" = TR_bayes_modelling[[id]]$par[1],
-                         "theta_no_transfer" = NT_bayes_modelling[[id]]$par[1],
+                         "theta_transfer" = exp1_ToM_TR[[id]]$par[1],
+                         "theta_no_transfer" = exp1_ToM_NT[[id]]$par[1],
                          # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
-                         "eps_transfer" = TR_bayes_modelling[[id]]$par[2],
-                         "eps_no_transfer" = NT_bayes_modelling[[id]]$par[2]))
+                         "eps_transfer" = exp1_ToM_TR[[id]]$par[2],
+                         "eps_no_transfer" = exp1_ToM_NT[[id]]$par[2]))
 }
@@
 ## Q-learning fit
-```{r}
+```{r, cache=TRUE}
 QL_modelling <- list()
@@
 ## Fitting Q_learning with states
-```{r}
+```{r , cache =TRUE}
 # data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
@@
 ## Fitting Self-Tuning EWA to data 
-```{r}
+```{r, cache=TRUE}
 
@@
 
-```{r}
+```{r, cache=TRUE}
 # data = subset(dat,human_id == "38VxtUSv_h6RR5-tAAA2")
@@
 
-```{r}
+```{r, cache=TRUE}
 MBM_modelling <- list()
@@
 ```{r}
-load("TR_bayes_modelling.RData")
-load("NT_bayes_modelling.RData")
-load("QL_modelling.RData")
-load("QL_states_modelling.RData")
-load("EWA_modelling.RData")
-load("EWA_self_modelling.RData")
-load("MBM_modelling.RData")
-load("EWA_states_modelling.RData")
+# load("exp1_ToM_TR.RData")
+# load("exp1_ToM_NT.RData")
+# load("QL_modelling.RData")
+# load("QL_states_modelling.RData")
+# load("EWA_modelling.RData")
+# load("EWA_self_modelling.RData")
+# load("MBM_modelling.RData")
+# load("EWA_states_modelling.RData")
 
@@
                          # Bayesian updating with/without transfer
-                         "Bayes_Tr_BIC" = TR_bayes_modelling[[id]]$value + 2*log(150),
-                         "Bayes_No_Tr_BIC" = NT_bayes_modelling[[id]]$value+ 2*log(150),
+                         "Bayes_Tr_BIC" = exp1_ToM_TR[[id]]$value + 2*log(150),
+                         "Bayes_No_Tr_BIC" = exp1_ToM_NT[[id]]$value+ 2*log(150),
                          # Theta is the parameter governing AI stochasticity. Truth is 0.9
-                         "theta_transfer" = TR_bayes_modelling[[id]]$par[1],
-                         "theta_no_transfer" = NT_bayes_modelling[[id]]$par[1],
+                         "theta_transfer" = exp1_ToM_TR[[id]]$par[1],
+                         "theta_no_transfer" = exp1_ToM_NT[[id]]$par[1],
                          # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
-                         "eps_transfer" = TR_bayes_modelling[[id]]$par[2],
-                         "eps_no_transfer" = NT_bayes_modelling[[id]]$par[2],
+                         "eps_transfer" = exp1_ToM_TR[[id]]$par[2],
+                         "eps_no_transfer" = exp1_ToM_NT[[id]]$par[2],
 
@@
  write.csv(Table_results,file="Table_results.csv",row.names = TRUE)
- kable(Table_results)
+ #kable(Table_results)
  barplot(Table_results)

### 2020-01-23 Experiment_2/Experiment_2_modelling.Rmd
corrected bug in ToM model

@@
         if (within_transfer) {
-          # Use what was learned about opponent 2 from stage 2.
-          opp_prior_vec <- opp2_prior_temp
           if (btwn_transfer) {
@@
           } 
+          # Use what was learned about opponent 2 from stage 2.
+          opp_prior_vec <- opp2_prior_temp
 
@@
     } else {
+      #cat("stage", data[t,"stage"], " opps ",  opp_prior_vec, "\n")
       # get prediction of opponent action from CSV files
@@
   # for debugging uncomment the line below
-  #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"\n")
+  #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"/n")
   }
@@
 ## Fitting Bayesian model with between game transfer (as well as within)  
-```{r}
+```{r, cache=TRUE}
 exp2_BT <- list()
@@
 ## Fitting ToM model with NO Between transfer (but with transfer within games)
-```{r}
+```{r, cache=TRUE}
 
@@
 ## Fitting Bayesian model with NO Between or within transfer
-```{r}
+```{r, cache=TRUE}
 
@@
 ## Fitting Q_learning with state space of possible last round plays 
-```{r}
+```{r, cache=TRUE}
 exp2_QL_states <- function(par,data,return_value,gamma){
@@
 
-```{r}
+```{r, cache=TRUE}
 exp2_QLS_modelling <- list()
@@
 ## Fitting SEWA 
-```{r}
+```{r, cache=TRUE}
 
@@
 
-```{r}
+```{r, cache=TRUE}
 
@@
 # Load various modelling tables 
-
-load("exp2_BT.RData")
-load("exp2_NO_BT.RData")
-load("exp2_NO_Tr.RData")
-load("exp2_QLS_modelling.RData")
-load("exp2_SEWA_modelling.RData")
-load("MBM2_modelling.RData")
+# 
+# load("exp2_BT.RData")
+# load("exp2_NO_BT.RData")
+# load("exp2_NO_Tr.RData")
+# load("exp2_QLS_modelling.RData")
+# load("exp2_SEWA_modelling.RData")
+# load("MBM2_modelling.RData")
 

### 2020-01-23 Experiment_2/exp2_score_plots.Rmd
corrected bug in ToM model

@@
 
-#Build empty datafrsme with same names as original data
+#Build empty dataframe with same names as original data
 exp2_cum_score <- setNames(data.frame(matrix(ncol = ncol(dat_exp2), nrow = 0)), colnames(dat_exp2))

### 2020-01-23 Report/draft_report_v1.Rmd
corrected bug in ToM model

@@
 
+One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the opponent strategy that may inform what actions they are likely to take next.
+Once we learn about the opponent's strategy, we can use this knowledge to inform how to best act in novel situations involving a previously encountered opponent.
+This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about the opponent is an abstract representation that is not too dependent on the environment of the initial interaction.
+
+There is evidence that people learn models of the opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
@@
 
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a bayesian model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expectedm random play as well as EWA were at the bottom of cumulative performance.
+```{r, include=FALSE}
+
+dat_exp2 = read.csv("../Experiment_2/data_exp2.csv")
+
+#Adjust shootout score tor eflect easier game
+dat_exp2$adj_score <- ifelse(as.character(dat_exp2$game) == "shootout", dat_exp2$score - 0.333, dat_exp2$score)
+
+# Load data comparing models BIC for each participant 
+model_comp_2 = read.csv("../Experiment_2/exp2_model_comp.csv")
+
+datalist2 = list()
+i = 0
+
+#Build empty dataframe with same names as original data
+exp2_cum_score <- setNames(data.frame(matrix(ncol = ncol(dat_exp2), nrow = 0)), colnames(dat_exp2))
+for(id in unique(dat_exp2$human_id)) {
+  i <- i+1
+  tdat <- subset(dat_exp2,human_id == id)
+  tdat$part_num <- i
+  # NB : USE ADJUSTED SCORE IN SHOOTOUT
+  tdat <- within(tdat, acc_sum <- cumsum(tdat$adj_score))
+  datalist2[[i]] <- tdat
+}
+
+# Merge all datasets into one 
+exp2_cum_score <- dplyr::bind_rows(datalist2)
+# or exp2_cum_score <- data.table::rbindlist(datalist)
+
+# Add column for time t
+exp2_cum_score <- exp2_cum_score %>% group_by(human_id) %>% mutate(t = row_number())
+
+# Participant number as a factor 
+# tdat$part_num <- as.factor(tdat$part_num)
+
+# Add best fitting model per participant
+exp2_cum_score <- merge(exp2_cum_score, model_comp_2[, c("human_id", "Best_model")], by="human_id")
+
+temp2 <- exp2_cum_score[,c("t","acc_sum","Best_model","condition","part_num")]
+dat_by_model_2 <- temp2 %>% group_by(Best_model,t) %>% 
+  summarize(model_acc_sum = mean(acc_sum))
+
+```
 
@@
 
-knitr::include_graphics("../Report/images/exp2_cumScores.png", dpi = 108)
+ggplot(data = dat_by_model_2, aes(x = t, y=model_acc_sum, group = Best_model)) + 
+   geom_line(aes(color= Best_model)) +
+  scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))
+
+```
+
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a bayesian model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expectedm random play as well as EWA were at the bottom of cumulative performance.
+
+```{r exp2-cumScores-bis, fig.cap = "Average cumulative scores of participants in experiment 2 by best fitting model", fig.align='center'}
+# 
+# knitr::include_graphics("../Report/images/exp2_cumScores.png", dpi = 108)
 

### 2020-01-23 Report/draft_report_v1.tex
corrected bug in ToM model

@@
 
-Where \$ V\_\{t\}(a) \$ is the vlue associated with action \(a\) at time \(t\), \(\alpha\) is the learning rate and \(R_{t}\) the reward at time t.
+Where \(V_{t}(a)\) is the vlue associated with action \(a\) at time \(t\), \(\alpha\) is the learning rate and \(R_{t}\) the reward at time t.
 Actions are chosen based on action values using a softmax choice rule.
@@
 Next, we use a self-tuning Experience Weighted attraction model ({\textbf{???}}).
-EWA models are model of behavior in repeated games, that nest two seemingly different approaches, namely reinforcement learning and belief learning.
+EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning.
 Belief based models are based on the assumption that players keep track of the frequency of past plays and best respond to that.
 In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
-The self-tunign EWA model has been shown to perform better than both these nested models in multiple repeated gmes and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
+The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated gmes and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
 
-Lt's define some notation in order to write the pdate rule of the self-tuning EWA model.
+Let's define some notation in order to write the pdate rule of the self-tuning EWA model.
 For player i, there are \(m_{i}\) strategies, denoted \(s_{i}^{j}\) (i.e player i's strategy number j).
@@
 
-In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive)
+In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
+Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
 
-In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
-Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was explained by each model.
+\hypertarget{experiment-1-modelling}{%
+\subsection{Experiment 1 modelling :}\label{experiment-1-modelling}}
+
 Figure~\ref{fig:exp1-comp-models} shows the results for experiment 1: we can see that while some participant's learning behavior was either random or explained by some of the base models, a significant number of participants in experiment one had learning most consistent with Q-learning conditional on last round play.
@@
 
-{\centering \includegraphics{../Report/images/exp1_comp_models}
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-comp-models-1}
 
@@
 
-\caption{Histogram of best fitting computational models for experiment 1}\label{fig:exp1-comp-models}
-\end{figure}
-
-In experiment 2 however, we can see from Figure~\ref{fig:exp2-comp-models} that Q-learning with the aforementioned state-space wasn't as successful as the bayesian approached in fitting player's action choices.
-In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) were by far the most successful.
-
-\begin{figure}
-
-{\centering \includegraphics{../Report/images/exp2_comp_models}
-
-}
-
-\caption{Histogram of best fitting computational models for experiment 2}\label{fig:exp2-comp-models}
+\caption{Histogram of best fitting computational models by condition for experiment 1}\label{fig:exp1-comp-models}
 \end{figure}
@@
 
-{\centering \includegraphics{../Report/images/exp1_cumScores}
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-comp-model-1}
 
@@
 
-\caption{Average cumulative scores of participants in experiment 1 by best fitting model}\label{fig:exp1-cumScores}
+\caption{Histogram of best fitting computational models for experiment 1}\label{fig:exp1-comp-model}
 \end{figure}
 
-Doing the same exercise for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a bayesian model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expectedm random play as well as EWA were at the bottom of cumulative performance.
+\hypertarget{experiment-2}{%
+\subsection{Experiment 2}\label{experiment-2}}
 
@@
 
-{\centering \includegraphics{../Report/images/exp2_cumScores}
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-comp-models-1}
+
+}
+
+\caption{Histogram of best fitting computational models by condition for experiment 2}\label{fig:exp2-comp-models}
+\end{figure}
+
+In experiment 2, we can see from Figure~\ref{fig:exp2-comp-models} that Q-learning with the aforementioned state-space wasn't as successful as the bayesian approached in fitting player's action choices.
+In experiment 2 when participants faced both level-1 and level-2 agents sequentially, the bayesian models (with or without transfer) were by far the most successful.
+
+\begin{figure}
+
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp2-cumScores-1}
 
@@
 \end{figure}
+
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a bayesian model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expectedm random play as well as EWA were at the bottom of cumulative performance.
 

### 2020-01-27 Report/draft_report_v1.tex
modify plots in exp2

@@
 
-\usepackage{etoolbox}
+\shorttitle{Draft-1}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Department of Experimental Psychology, University College London}
+\keywords{keywords\newline\indent Word count: X}
+\usepackage{csquotes}
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
+
+\usepackage{longtable}
+\usepackage{lscape}
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
+
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+
 \makeatletter
-\providecommand{\subtitle}[1]{% add subtitle to \maketitle
-  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
-}
-\makeatother
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+\usepackage{lineno}
+
+\linenumbers
+\shorttitle{}
 
@@
 Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-Lake, Ullman, Tenenbaum, and Gershman (2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
+Lake, Ullman, Tenenbaum, \& Gershman (2017) argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
+One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the opponent strategy that may inform what actions they are likely to take next.
+Once we learn about the opponent's strategy, we can use this knowledge to inform how to best act in novel situations involving a previously encountered opponent.
+This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about the opponent is an abstract representation that is not too dependent on the environment of the initial interaction.
+There is evidence that people learn models of the opponents when they play repeated economic games ({\textbf{???}}), engage in bilateral negotiations ({\textbf{???}}), or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors ({\textbf{???}}).
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
@@
 Still, one of the commonalities in studies of how humans adapt to computerised opponents is that they have mostly looked at the ability of players to detect and exploit action-based learning rules.
-The strategies implemented by the computer opponents had a style of play that was not ``human-like'' in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
-It is therefore important to have agents that ``play like humans'', and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
+The strategies implemented by the computer opponents had a style of play that was not \enquote{human-like} in the sense that humans are not very good at playing specific mixed strategies with any precision of at detecting patterns from long sequences of past play due to cognitive constraints.
+It is therefore important to have agents that \enquote{play like humans}, and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
 Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
-Instead, they will try to `satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in `level-k' theory, first adopted by Stahl \& Wilson (1995).
+Instead, they will try to \enquote{satisfice} by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
+This concept finds its natural application in \enquote{level-k} theory, first adopted by Stahl \& Wilson (1995).
 It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
@@
 Figure XXXXXXXXX shows a snapshot of play in the shootout game.
-What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose `'right'' in the next round, we can win by both choosing `'left'' and `'center''.
+What makes this game different however is that there are two ways to beat the opponent in each round: if we think the opponent is going to choose \enquote{'right}' in the next round, we can win by both choosing \enquote{'left}' and \enquote{'center}'.
 A level-1 player (thinks that his opponent will repeat his last action) has two ways to win the next round.
@@
 Where \(Q(s_{t},a_{t})\) is the value of taking action \(a\) when in state \(s\) at time \(t\), \(\gamma\) is the discount rate applied to future rewards.
-For instance, \(Q(RS,P)\) denotes the value of taking action ``Paper'' this round if the player's last action was ``Rock'' and the opponent played ``Scissors''.
+For instance, \(Q(RS,P)\) denotes the value of taking action \enquote{Paper} this round if the player's last action was \enquote{Rock} and the opponent played \enquote{Scissors}.
 This is a much richer model allowing the players to compute the values of actions conditional on past play.
@@
 
-The EWA model is based on updating ``Attractions'' for each action over time.
+The EWA model is based on updating \enquote{Attractions} for each action over time.
 For instance, the attraction of strategy \(j\) to player \(i\) at time \(t\) is written \(A_{i}^{j}(t)\).
@@
 First, maybe players simply learn spatial heuristics that allow them to perform better than chance.
-An example is a spatial heuristic that consists of choosing ``weapons'' in a particular order (for instance left to right).
+An example is a spatial heuristic that consists of choosing \enquote{weapons} in a particular order (for instance left to right).
 This was one of the weaknesses in the design of experiment one, as it was indeed possible using very simple spatial sequences to beat the opponent on most rounds.
@@
 A successful mental representation would take the perspective of the opponent or endow it with intentionality in order to detect its strategy when the opponent is playing based on a level-k reasoning model.
-For instance, the player may think ``My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be''.
+For instance, the player may think \enquote{My opponent is always trying to be one step ahead of me, therefore, I will be one step ahead of where it thinks I will be}.
 This mental representation would facilitate the use of theory of mind abilities and thus enable the players to learn opponent strategies when they are based on human-like reasoning models such as level-k or cognitive hierarchy.
-This type of learning would be deemed ``explicit'' in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
+This type of learning would be deemed \enquote{explicit} in the psychology literature as a process through which knowledge consists of cognitive representations of concepts and rules, as well as the relationship between them.
 It involves the evaluation of explicit hypotheses and results in better problem-solving skills (Mandler, 2004).
@@
 
+\leavevmode\hypertarget{ref-lake2017building}{}%
+Lake, B. M., Ullman, T. D., Tenenbaum, J. B., \& Gershman, S. J. (2017). Building machines that learn and think like people. \emph{Behavioral and Brain Sciences}, \emph{40}.
+
 \endgroup

### 2020-01-27 Experiment_2/Experiment_2_modelling.Rmd
added naive tom and qls with transfer

@@
 # Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
-TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer) {
+# TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer) {
+#   
+#   # dat = data subset for one participant
+#   # opp_strategy_vec = vector of possible opponent strtegies, model assumes humans restrict opp strategy space to vector   c("level0","level1","level2")
+#   # return = -2logLik 
+#   # or "likelihood_by_trial" vector  (for later plotting, etc)
+#   # btwn_transfer is a boolean. True if distribution of opponent strategies is kept across games. False otherwise. 
+#   
+#   # theta = parameter, probability computer will play its best response to what it thinks human is. Truth = 90%. in [0,1].
+#   # eps: parameter controlling noise in human choice. Probability human will DEVIATE from its best response. In [0,1].
+#   theta <- par[1]
+#   eps <- par[2]
+#   
+#   num_strat = length(opp_strategy_vec) 
+#   
+#   # Load tables predicting oppponent movel
+#   
+#   rps_predict_opp <- read.csv("rps_predict_opp.csv")
+#   fwg_predict_opp <- read.csv("fwg_predict_opp.csv")
+#   shootout_predict_opp <- read.csv("shootout_predict_opp.csv")
+#   
+# 
+#   #lik_opp is a vector that holds and updates probability distribution of opp strategy given actions.
+#   lik_opp <- matrix(0.0,num_strat, nrow(data))
+#   
+#   # Initiate prior vectors for each opponent as uniform
+#   opp_prior_vec <- rep(1/num_strat, num_strat)
+#   opp1_prior_vec <-rep(1/num_strat, num_strat)
+#   opp2_prior_vec <-rep(1/num_strat, num_strat)
+#   
+#   lik_hum <- matrix(0.0,nrow(data))
+#   # br_hum is vector that stores best responses of human to actions taken by each level-k ai opponent at the round.
+#   br_hum <- rep(NA,num_strat)
+# 
+#   
+#   for(t in 1:nrow(data)) {
+#     t_game <- data[t,"game"]
+#     pred_file_opp <- switch(as.character(t_game),rps = rps_predict_opp,fwg = fwg_predict_opp, shootout = shootout_predict_opp)
+#     nopts <- 3
+#     if(data[t,"round"] == 1) {
+#       # first round is uniform prediction
+#       pred_opp <- NA
+#       lik_hum[t] <- 1/nopts
+#       
+#       ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer reset prior to uniform)#####
+#       # Round 1 of stage 1 
+#       if (data[t,"stage"] == 1) {
+#         if (btwn_transfer){
+#           # if there is between game transfer, then the opp_prior_vec should have stored what was learned about the SECOND opponent 
+#           # ...from stage 4 of previous game (or uniform if it is first game of RPS). store that before proceeding
+#           opp2_prior_vec <- opp_prior_vec
+#           # if between game transfer use stored opp1 prior vector from previous game (or uniform if first game  RPS) 
+#           opp_prior_vec <- opp1_prior_vec
+# 
+#         } else { # <- No between game TRANSFER 
+#           opp_prior_vec <- rep(1/num_strat, num_strat)
+#         }
+#         
+#       # we are round 1 of stage 2, keep opp vector from round 20 of stage 1  for stage 3
+#         } else if (data[t,"stage"] == 2) {
+#           if (within_transfer){
+#             # hold the probs vector of Opp type learned in stage 1 in memory and save to temp.
+#             opp1_prior_temp <- opp_prior_vec
+#           if (btwn_transfer){
+#             # If  between games transfer get prior from opp2 prior saved from last stage of last game 
+#             opp_prior_vec <- opp2_prior_vec
+#           } else { # if no between transfer start of first interaction with secnd opp should be reset
+#             opp_prior_vec <- rep(1/num_strat, num_strat)
+#           }
+#           
+#         } else { # Assume no between game transfer if no within. reasonable. 
+#           opp_prior_vec <- rep(1/num_strat, num_strat)    
+#         }
+#         
+#       # we are round 1 of stage 3
+#       } else if (data[t,"stage"] == 3) {
+#         if (within_transfer) {
+#           # if within_transfer keep opp vector from round 20 of stage 2 for stage 4
+#           opp2_prior_temp <- opp_prior_vec
+#           # if within_transfer, use what we learned about opp1 in stage 1 as new prior.  
+#           opp_prior_vec <- opp1_prior_temp
+#           
+#         } else { # No within transfer, dont store anything and reset priors
+#           opp_prior_vec <- rep(1/num_strat, num_strat)    
+#         }
+# 
+#       
+#       # We are in round 1 of stage 4,
+#       }  else if (data[t,"stage"] == 4) {
+#         if (within_transfer) {
+#           if (btwn_transfer) {
+#             # Store what was learned about opponent 1 for nxt game...
+#            opp1_prior_vec <- opp_prior_vec
+#           } 
+#           # Use what was learned about opponent 2 from stage 2.
+#           opp_prior_vec <- opp2_prior_temp
+#           
+#         } else {
+#           opp_prior_vec <- rep(1/num_strat, num_strat)
+#         }
+#         
+#       }
+#       
+#     # Rounds 2 to End of stage
+#     } else {
+#       cat("stage", data[t,"stage"], " opps ",  opp_prior_vec, "\n")
+#       # get prediction of opponent action from CSV files
+#       for (strategy in opp_strategy_vec) {
+#         k = match(strategy,opp_strategy_vec)
+#         pred_opp <- as.character(filter(pred_file_opp, pred_file_opp$human_previous == as.character(data[t-1,"h_action"]) & pred_file_opp$computer_previous == as.character(data[t-1,"a_action"]))[[strategy]])
+#         
+#         # Given opponent action predicted, what would be human action best response for each opp strat
+#         br_hum[[k]] <- exp2_best_response(t_game,as.character(pred_opp))
+#         
+#         # First we deal with easy case of unique predicted action ( multiple possible preds in shoot are separated by "/" sign)
+#         if (!grepl("/",pred_opp,fixed = TRUE)) {
+#            # Multiply prior by likelihood of observation to get posterior. Done here ot take advantage of For loop. 
+#           if(as.character(data[t,"a_action"]) == pred_opp) {
+#             lik_opp[k,t] <- (theta + (1-theta)/nopts)*opp_prior_vec[k]
+#           } else {
+#             lik_opp[k,t] <- ((1-theta)/nopts)*opp_prior_vec[k]
+#           }
+#         # Here we are in shootout and opponent predicted action is a vector of two possible moves (e.g "left/center")  
+#         } else {
+#           if(grepl(as.character(data[t,"a_action"]), pred_opp,fixed = TRUE)) {
+#             # Assume each action has likelihood of 50%
+#              lik_opp[k,t] <- 0.5*(theta + (1-theta)/nopts)*opp_prior_vec[k]
+#           } else {
+#             #the 2 is to standardise the theta dependent probs: P(ai plays pred | opp is level k)
+#             lik_opp[k,t] <- 2*((1-theta)/nopts)*opp_prior_vec[k]
+#           }
+#         }
+#         
+#       # Get which opponent strategy human current actn maps to (i.e, if index = 0 then human current action is best response to level-0 comp_strat...)
+#       indices <- which(grepl(as.character(data[t,"h_action"]),br_hum,fixed = TRUE))
+# 
+#       # THEN likelihood of current human action is just prior on opponent vec (haven't updated priors with curr opp act yet)
+#       # if action is not predicted by any level-k OM, assume human chooses randomly with prob eps
+#       if(length(indices) == 0){
+#         lik_hum[t] <- eps/nopts
+#       # if same br action for multiple possible ai opponents, add probabilities 
+#       } else {
+#         lik_hum[t] <- sum(opp_prior_vec[indices])*(1-eps) + eps/nopts
+#       }
+#     }  
+#       # Standardising the probabilities and updating prior
+#       lik_opp[,t] <- lik_opp[,t]/sum(lik_opp[,t])
+#       opp_prior_vec <- lik_opp[,t]
+#     }
+#   # for debugging uncomment the line below
+#   #cat(as.character(pred_opp),as.character(data[t,"a_action"]),lik_opp[,t],"/n")
+#   }
+#   
+#   if(return_value == "-2loglik") {
+#     ret <- -2*sum(log(lik_hum))
+#     if(is.infinite(ret) || is.nan(ret)) {
+#       return(1e+300)
+#     } else {
+#       return(ret)
+#     }
+#   }
+#   if(return_value == "likelihood_by_trial") return(lik_hum)
+#   
+# }
+
+```
+
+```{r}
+# Assumes within game transfer of opponent model between stages, but boolena for between game transfer. 
+TOM_model <- function(par, data, opp_strategy_vec, return_value, within_transfer, btwn_transfer, Naive = FALSE) {
 
@@
 
-      ## KEY CODE FOR LEARNING TRANSFER !! (if no OM transfer reset prior to uniform)#####
+      ## KEY CODE FOR LEARNING TRANSFER !! #####
+      #Naive 
+      if (Naive) {
+        # pass. no update to prior vector throughout all rounds and games
+      } else {
+        #abc
+        #def
         # Round 1 of stage 1 
@@
             opp_prior_vec <- opp1_prior_vec
-
           } else { # <- No between game TRANSFER 
@@
         }
+
+      } #End of no naive condition
 
@@
 
-TOM_model(c(0.5,0.1),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = TRUE, btwn_transfer = TRUE)
+TOM_model(c(0.8,0.1),test_data,c("level0","level1","level2"),"-2loglik", within_transfer = FALSE, btwn_transfer = FALSE, Naive = TRUE)
 ```
@@
 
-  exp2_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = TRUE,lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+  exp2_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = TRUE, Naive = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
 }
@@
 
-  exp2_NO_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+  exp2_NO_BT[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = TRUE, btwn_transfer = FALSE, Naive = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
 }
@@
 
-  exp2_NO_Tr[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+  exp2_NO_Tr[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, Naive =FALSE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
 }
@@
 
+#Fitting model where player does not distinguish between opponents 
+```{r, cache=TRUE}
+
+exp2_Naive <- list()
+for(id in unique(dat_exp2$human_id)) {
+  exp2_Naive[[id]] <- list()
+  tdat <- subset(dat_exp2,human_id == id)
+
+  # exp2_Naive[[id]] <- DEoptim(fn=naive_bayes, lower = c(0.0,0.0), upper = c(1.0,1.0), data=tdat, opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", opp_mod_transfer = FALSE, control=list(trace = FALSE, parallelType=0,parVar = c("best_response")))
+
+  exp2_Naive[[id]] <- optim(c(0.1,0.1),fn=TOM_model,gr = NULL, data=tdat,opp_strategy_vec = c("level0","level1","level2"),return_value = "-2loglik", within_transfer = FALSE , btwn_transfer = FALSE, Naive = TRUE, lower = c(0.01,0.01), upper = c(0.99,0.99), method="L-BFGS-B")
+}
+
+save(exp2_Naive,file="exp2_Naive.RData")
+```
+
 ## Fitting Q_learning with state space of possible last round plays 
 ```{r, cache=TRUE}
-exp2_QL_states <- function(par,data,return_value,gamma){
+exp2_QL_states <- function(par,data,return_value,gamma, within_transfer = FALSE){
   # Par[1] -> beta= inverse temperature parameter in softmax choice function
@@
     if(data[t,"round"] == 1) {
+
+      # Within game transfer Code 
+      if (!within_transfer){
+              Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
+      } else {
+        if (data[t,"stage"] == 1){
+          Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
+        } else if (data[t,"stage"] == 2) {
+          Q_vals_opp1 <- Q_vals
+          Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
+        } else if (data[t,"stage"] == 3) {
+          Q_vals_opp2 <- Q_vals 
+          Q_vals <- Q_vals_opp1
+        } else if (data[t,"stage"] == 4) {
+          Q_vals <- Q_vals_opp2
+        }
+      }
+
+      #cat(Q_vals,"\n") 
+      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, shootout = states_SHOOT)
       # first round is uniform prediction
-      Q_vals <- switch(as.character(t_game),rps=Q_vals_RPS,fwg = Q_vals_FWG, shootout = Q_vals_SHOOT)
-      state_vec <- switch(as.character(t_game),rps=states_RPS,fwg = states_FWG, shootout = states_SHOOT)
       lik_hum[t] <- 1/nopts
@@
     probs <- exp(Q_vals[new_state,]/beta)/sum(exp(Q_vals[new_state,]/beta))
-    #if (data[t,"round"] == 20) { cat(probs,"\n") }
+    #if (data[t,"round"] == 1) { cat(probs,"\n") }
 
@@
 ```{r}
-exp2_QL_states(c(5,0.4),test_data, "-2loglik", 0.0)
+exp2_QL_states(c(5,0.4),test_data, "-2loglik", 0.0, TRUE)
 ```
@@
 ```
+
+```{r, cache=TRUE}
+exp2_QLS_within_Tr <- list()
+for(id in unique(dat_exp2$human_id)) {
+  exp2_QLS_within_Tr[[id]] <- list()
+  tdat <- subset(dat_exp2,human_id == id)
+  # QL_states_modelling[[id]] <- optim(c(1,0.1),fn=Q_learn_states,gr = NULL, data=tdat,"-2loglik", gamma =0 , lower = c(0,0), upper = c(10,0.99), method="L-BFGS-B")
+
+   exp2_QLS_within_Tr[[id]] <- DEoptim(fn=exp2_QL_states,lower = c(0,0), upper = c(20,1), data=tdat,"-2loglik", gamma = 0, within_transfer =TRUE, control=list(trace = FALSE, parallelType=1))
+}
+
+save(exp2_QLS_within_Tr , file="exp2_QLS_within_Tr.RData")
+```
+
+##Self tuning EWA model
 
@@
 
-# Load various modelling tables 
-# 
-# load("exp2_BT.RData")
-# load("exp2_NO_BT.RData")
-# load("exp2_NO_Tr.RData")
-# load("exp2_QLS_modelling.RData")
-# load("exp2_SEWA_modelling.RData")
-# load("MBM2_modelling.RData")
-
 exp2_results <- data.frame()
@@
                          "No_Tr_BIC" = exp2_NO_Tr[[id]]$value+ 2*log(180),
+                         "Naive_BIC" = exp2_Naive[[id]]$value+ 2*log(180),
 
@@
                          "theta_no_tr" =  exp2_NO_Tr[[id]]$par[1],
+                         "theta_naive" = exp2_Naive[[id]]$par[1],
                          # Epsilone is parameter showing cases where human deviates from predictions about opponent (lower better)
@@
                          "eps_no_tr" = exp2_NO_Tr[[id]]$par[2],
+                         "eps_naive" = exp2_Naive[[id]]$par[2],
 
-                         # Q-learning with last round states
+                         # Q-learning with last round states (No within transfer)
                          "QL_states_BIC" = exp2_QLS_modelling[[id]]$optim$bestval + 2*log(180),
@@
                          "QL_states_alpha" = exp2_QLS_modelling[[id]]$optim$bestmem[2],
+
+                         # QLS assuming within game transfer
+                         "QLS_within_Tr_BIC" = exp2_QLS_within_Tr[[id]]$optim$bestval + 2*log(180),
+                         # beta ->  inverse temperature parameter in softmax choice function
+                         "QLS_within_Tr_Beta" = exp2_QLS_within_Tr[[id]]$optim$bestmem[1],
+                         # alpha -> learning rate in QL update
+                         "QLS_within_Tr_alpha" = exp2_QLS_within_Tr[[id]]$optim$bestmem[2],
 
@@
 ```{r}
-exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT", "QL_states","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+exp2_table_results <- table(exp2_results[, "condition"],c("random","TOM_BT","TOM_NBT", "TOM_NT","ToM_Naive", "QL_states","QLS_within","S_EWA","MBM")[apply(exp2_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
 
@@
   id_results <- subset(exp2_results, ID == id)
-  min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC", "QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
+  min_BIC <- apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC", "QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,min)
 
-  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","QL_states","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
+  best_model <- c("random","ToM_BT","ToM_NBT", "ToM_NT","ToM_Naive","QL_states","QLS_within","S_EWA", "MBM")[apply(id_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)]
   # 
@@
                          "Total_score" = tot_score,
-                         "Best_model" = best_model,
+                         "Best_model_2" = best_model,
                          "Total_time" = sum(tdat$human_rt),
-                         "TR_minus_NT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
+                         "BT_minus_NBT_BIC" = id_results[,"Btwn_TR_BIC"] - id_results[,"No_Btwn_Tr_BIC"],
                          "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
@@
 
-cor.test(exp2_model_comp$TR_minus_NT_BIC, exp2_model_comp$Early_game_score, method="spearman")
+cor.test(exp2_model_comp$BT_minus_NBT_BIC, exp2_model_comp$Early_game_score, method="spearman")
 
@@
 
-exp2_model_comp$model <- recode(exp2_model_comp$Best_model,"Bayes Tr" = "Tranfer","Bayes NT" = "No Transfer", "QL_states" = "Q_Learning",  .default = "Random")
+exp2_model_comp$model <- recode(exp2_model_comp$Best_model,"ToM_BT" = "btwn Tranfer","ToM_NBT" = "No btwn Transfer", "ToM_NT" = "No within or btwn Tr","QL_states" = "Q_Learning",  .default = "Random")
 model <- factor(exp2_model_comp$model)

### 2020-01-27 Report/draft_report_v1.Rmd
modify plots in exp2
added naive tom and qls with transfer

@@
 Yet they struggle to learn as fast or as efficiently as humans do, and more importantly they have a very limited ability to generalize and transfer knowledge to new domains.
-@lake2017building argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
+@Lake2017 argue that human learning transfer abilities take advantage of important cognitive building blocks such as an abstract representation of concepts underlying tasks and compositionally structured causal models of the environment.
 
@@
 This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about the opponent is an abstract representation that is not too dependent on the environment of the initial interaction.
-
 There is evidence that people learn models of the opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Premack & Woodruff, 1978) play a role in determining human behaviour.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities [@Woodruff] play a role in determining human behaviour.
 
@@
 More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
-Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences (Mertens, 1990) are particularly adapted to the task of opponent modelling.
+Repeated games, in which players interact repeatedly with the same opponent and have the ability to learn about the opponent's strategies and preferences [@mertens1990repeated] are particularly adapted to the task of opponent modelling.
 
 Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
-For instance, Ho et al.
-(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
+For instance, @ho1998iterated measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
 They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-Camerer & Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+@knez2000increasing test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
 They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
@@
 
-Juvina et al.(2014)  made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
+@Juvina2013 made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
 However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games, Cooper & Kagel (2003, 2004, 2008) find that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+In a series of experiments using economic signalling games [@cooper2003lessons; @Cooper2008] the researchers found that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
 They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
@@
 Most of these studies fail to offer a formal explanation of this transfer or a modelling framework that can explain the experimental observation of transfer between games and generalise it to extensive classes of games.
-A notable exception is the effort by Haruvy and Stahl (2012) to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
+A notable exception is the effort by @Haruvy2012 to specify a model of learning where players learn abstract rules that they can generalise and transfer across dissimilar games, rather than action choices that can only be used within the same game.
 Participants played ten games, presented as 4x4 normal form (matrix payoffs).
@@
 They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on Stahl (1996), was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
+Their rule-learning model, based on @stahl1995players, was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
 
@@
 It is therefore important to have agents that "play like humans", and one way of achieving that is to embed theses agents with human-like theory of mind abilities based on limited steps of recursive reasoning.
-Simon (1972) explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
+@simon1972theories explains that humans have limited cognitive capacities and as such cannot be expected to solve computationally intractable problems such as finding Nash equilibria.
 Instead, they will try to 'satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in 'level-k' theory, first adopted by Stahl & Wilson (1995).
+This concept finds its natural application in 'level-k' theory, first adopted by @stahl1995players.
 It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment (Arad & Rubinstein, 2012).
+At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment @arad201211.
 Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
@@
 In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
+The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit @goodie2012levels.
 
 Our choice of using computer oponents sinstead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-When playing against other human opponents,players are learning about the game and the strategy of the opponent simultaneously.
+When playing against other human opponents, players are learning about the game and the strategy of the opponent simultaneously.
 Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
 The use of computer opponents to elicit learning behavior has been explored in the literature with encouraging results.
-For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
-Shachat & Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
+For instance, @spiliopoulos2013strategic made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
+@shachat2004we made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
 They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
@@
 Figure\ \@ref(fig:exp1-cumScores) shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning an opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play.
+We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play.
 EWA, QL and random players had, understandably the lowest performance.
 
-```{r exp1-comp-model, fig.cap = "Histogram of best fitting computational models for experiment 1", fig.align='center'}
+```{r exp1-cumScores, fig.cap = "Average cumulative scores of participants in experiment 1 by best fitting model", fig.align='center'}
 ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
@@
 exp2_comp_results <- read.csv(file="../Experiment_2/exp2_results.csv")
-exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "QL_states","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","QL_states_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
+exp2_comp_table <- table(exp2_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT", "ToM_NT", "ToM_Naive","QL_states", "QLS_within","S_EWA","MBM")[apply(exp2_comp_results[,c("Random_BIC","Btwn_TR_BIC","No_Btwn_Tr_BIC","No_Tr_BIC","Naive_BIC","QL_states_BIC","QLS_within_Tr_BIC","EWA_self_BIC","MBM2_BIC")],1,which.min)])
 
@@
         args.legend=list( # positioning of legend box 
-        x=ncol(exp1_comp_table) + 3,
-        y=max(colSums(exp1_comp_table)) -1,
+        x=ncol(exp2_comp_table) + 6,
+        y=max(colSums(exp2_comp_table)) +1,
         bty = "n")
@@
 # Add best fitting model per participant
-exp2_cum_score <- merge(exp2_cum_score, model_comp_2[, c("human_id", "Best_model")], by="human_id")
+exp2_cum_score <- merge(exp2_cum_score, model_comp_2[, c("human_id", "Best_model_2")], by="human_id")
 
-temp2 <- exp2_cum_score[,c("t","acc_sum","Best_model","condition","part_num")]
-dat_by_model_2 <- temp2 %>% group_by(Best_model,t) %>% 
-  summarize(model_acc_sum = mean(acc_sum))
+temp2 <- exp2_cum_score[,c("t","acc_sum","Best_model_2","condition","part_num")]
+dat_by_model_2 <- temp2 %>% group_by(Best_model_2,t) %>% 
+  summarize(avg_acc_sum = mean(acc_sum))
 
@@
 
-ggplot(data = dat_by_model_2, aes(x = t, y=model_acc_sum, group = Best_model)) + 
-   geom_line(aes(color= Best_model)) +
+ggplot(data = dat_by_model_2, aes(x = t, y=avg_acc_sum, group = Best_model_2)) + 
+   geom_line(aes(color= Best_model_2)) +
   scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))
@@
 
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a bayesian model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expectedm random play as well as EWA were at the bottom of cumulative performance.
-
-```{r exp2-cumScores-bis, fig.cap = "Average cumulative scores of participants in experiment 2 by best fitting model", fig.align='center'}
-# 
-# knitr::include_graphics("../Report/images/exp2_cumScores.png", dpi = 108)
-
-```
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expected random play as well as EWA were at the bottom of cumulative performance.
 
@@
 ```{r create_r-references}
-# r_refs(file = "OM_transfer.bib")
+r_refs(file = "Mendeley.bib")
 

### 2020-01-27 Report/draft_report_v1.tex
added naive tom and qls with transfer

--- 2020-01-23 Report/draft_report_v1.tex
@@
 
+One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the opponent strategy that may inform what actions they are likely to take next.
+Once we learn about the opponent's strategy, we can use this knowledge to inform how to best act in novel situations involving a previously encountered opponent.
+This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about the opponent is an abstract representation that is not too dependent on the environment of the initial interaction.
+There is evidence that people learn models of the opponents when they play repeated economic games (Stahl \& Wilson, 1995), engage in bilateral negotiations (Baarslag, Hendrikx, Hindriks, \& Jonker, 2016), or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors (Weerd, Verbrugge, \& Verheij, 2012).
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
-These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Premack \& Woodruff, 1978) play a role in determining human behaviour.
+These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Woodruff, Sciences, Brain, \& 1978, n.d.) play a role in determining human behaviour.
 
@@
 Early literature on learning transfer in games has mostly focused on measuring the proportion of people who play normatively optimal (Nash Equilibria) or salient actions (e.g Risk Dominance) in later games, having had experience with a similar game environment previously.
-For instance, Ho et al.
-(1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
+For instance, Ho, Camerer, and Weigelt (1998) measure transfer as the proportion of players who choose the Nash Equilibrium in later p-beauty contest games, after training on similar games.
 They find there is no evidence of immediate transfer (Nash equilibrium play in the first round of the new game) but positive structural learning transfer as shown by the faster convergence to equilibrium play by experienced vs non experienced players.
-Camerer \& Knez (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
+Knez and Camerer (2000) test learning transfer in players exposed to two games with multiple equilibria sequentially and explore the ability of players to coordinate their actions to choose a particular equilibrium in subsequent games having reached it in prior ones.
 They distinguish between games that are similar in a purely descriptive way, meaning similar choice labels, identity of players, format and number of action choices; and games that are similar in a strategic sense, meaning similar payoffs from combination of actions, identical equilibrium properties or significant social characteristics of payoffs such as possibility of punishment, need for fairness and cooperative vs competitive settings.
@@
 
-Juvina et al.(2014) made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
+Juvina, Saleem, Martin, Gonzalez, and Lebiere (2013) made a similar distinction between what they deemed surface and deep similarities and find that both contribute to positive learning transfer.
 However, they show that surface similarity is not necessary for deep transfer and can either aid or block this type of transfer depending on whether it leads to congruent or incongruent actions in later games.
-In a series of experiments using economic signalling games, Cooper \& Kagel (2003, 2004, 2008) find that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
+In a series of experiments using economic signalling games (Cooper \& Kagel, 2003, 2008) the researchers found that participants who have learned to play according to Nash Equilibrium in one game can transfer this to subsequent games, even though the actions consistent with Nash Equilibrium in later games are different.
 They show that this transfer is driven by the emergence of sophisticated players who are able to represent the strategic implications of their actions and reason about the consequences of changed opponent payoffs.
@@
 They also showed that players learn abstract aspects of the game that are then transferred to new settings.
-Their rule-learning model, based on Stahl (1996), was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
+Their rule-learning model, based on Stahl and Wilson (1995), was able to capture participants' dynamic behavior and show that the propensity to select particular rules is perfectly transferred across games.
 
@@
 Instead, they will try to `satisfice' by choosing a strategy that is adequate in a simplified model of the environment, rather than an optimal one.
-This concept finds its natural application in `level-k' theory, first adopted by Stahl \& Wilson (1995).
+This concept finds its natural application in `level-k' theory, first adopted by Stahl and Wilson (1995).
 It posits that deviations from Nash equilibrium solutions in simple games are explained by the fact that humans have a heterogenous degree of strategic sophistication.
-At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment (Arad \& Rubinstein, 2012).
+At the bottom of the ladder, level-0 players are non-strategic and play either randomly or use a salient strategy in the game environment Arad and Rubinstein (2012).
 Level-1 players are next up the ladder of strategic sophistication and will assume all their opponents belong to the level-0 category and as such will best respond to them given this assumption.
@@
 In this study, we propose to explore opponent modelling and its transfer with the use of computer agents possessing human-like theory of mind abilities with limited degrees of iterated reasoning.
-The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit (Goodie et al., 2012).
+The agents will have a fixed strategy played stochastically and will either be level-1 or level-2 behavioral rule, mimicking human theory of mind abilities and the limited recursion depth they exhibit Goodie, Doshi, and Young (2012).
 
 Our choice of using computer oponents sinstead of matching groups of participants makes it easier to disentangle the process of learning about the opponent from that of learning about the game structure and payoffs.
-When playing against other human opponents,players are learning about the game and the strategy of the opponent simultaneously.
+When playing against other human opponents, players are learning about the game and the strategy of the opponent simultaneously.
 Thus, it is harder to focus on an individual and how her strategies are changing and adapting to the opponent's play if we cannot experimentally control the behaviour of the opponent.
@@
 For instance, Spiliopoulos (2013) made humans play constant sum games against 3 computer opponents programmed to take advantage of known patterns in human play such as imperfect randomization and heuristics use and found that human participants do adapt to the opponent they are facing.
-Shachat \& Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
+Shachat and Swarthout (2004) made human participants face computer opponents playing various mixed strategies in a zero-sum asymmetric matching pennies game.
 They found that the players changed their strategies towards exploiting the deviations from the Mixed Strategy Nash Equilibrium (MSNE), and that this exploitation was very likely if the deviation from the MSNE play was high.
@@
 
-We extend this very simple model by adding a state space that consists of last round human and agent play. This is akin to using a Q-learning algorithm ({\textbf{???}}). The update rule becomes:
+We extend this very simple model by adding a state space that consists of last round human and agent play.
+This is akin to using a Q-learning algorithm (Watkins \& Dayan, 1992).
+The update rule becomes:
 
@@
 
-Next, we use a self-tuning Experience Weighted attraction model ({\textbf{???}}).
+Next, we use a self-tuning Experience Weighted attraction model (Ho, Camerer, \& Chong, 2004).
 EWA models particularity is that thet nest two seemingly different approaches, namely reinforcement learning and belief learning.
@@
 The result is added to either the payoff received (when the indicator function is 0), or to \(\delta\) times the foregone payoff (when indicator function is 1).
-We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play ({\textbf{???}}).
-While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters ({\textbf{???}}), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in ({\textbf{???}}).
+We can see that setting \(\delta = 0\) leads to reinforcement of past actions, while positive and high delta parameters make the update rule take into account foregone payoffs, which is similar to weighted fictitous play (Cheung \& Friedman, 1994).
+While the assumption in expanding the update rule above is that \(\phi\) and \(\delta\) are free parameters (Camerer, Ho, \& Others, 1997), the self-tuning aspect of the model comes from the fact that these are now self-tuned using the formulas expanded in (Ho et al., 2004).
 
@@
 Figure~\ref{fig:exp1-cumScores} shows the average cumulative performance of players across games, for participants grouped by which model best fits their behavior in experiment 1.
-We can see that participants whose actions are most consistent with learning an opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play.
+We can see that participants whose actions are most consistent with learning a ToM opponent model in a Bayesian way had the best overall performance (both with and witout transfer), followed by Q-learning conditional on last round play.
 EWA, QL and random players had, understandably the lowest performance.
@@
 
-{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-comp-model-1}
+{\centering \includegraphics{draft_report_v1_files/figure-latex/exp1-cumScores-1}
 
@@
 
-\caption{Histogram of best fitting computational models for experiment 1}\label{fig:exp1-comp-model}
+\caption{Average cumulative scores of participants in experiment 1 by best fitting model}\label{fig:exp1-cumScores}
 \end{figure}
@@
 
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a bayesian model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expectedm random play as well as EWA were at the bottom of cumulative performance.
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expected random play as well as EWA were at the bottom of cumulative performance.
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-lake2017building}{}%
-Lake, B. M., Ullman, T. D., Tenenbaum, J. B., \& Gershman, S. J. (2017). Building machines that learn and think like people. \emph{Behavioral and Brain Sciences}, \emph{40}.
+\leavevmode\hypertarget{ref-arad201211}{}%
+Arad, A., \& Rubinstein, A. (2012). The 11-20 money request game: A level-k reasoning study. \emph{American Economic Review}, \emph{102}(7), 3561--3573.
+
+\leavevmode\hypertarget{ref-baarslag2016learning}{}%
+Baarslag, T., Hendrikx, M.
+J.
+C., Hindriks, K.
+V., \& Jonker, C.
+M.
+(2016).
+Learning about the opponent in automated bilateral negotiation: a comprehensive survey of opponent modeling techniques.
+\emph{Autonomous Agents and Multi-Agent Systems}, \emph{30}(5), 849--898.
+
+\leavevmode\hypertarget{ref-camerer1997experience}{}%
+Camerer, C., Ho, T.-H., \& Others. (1997). \emph{Experience-weighted attraction learning in games: A unifying approach}.
+
+\leavevmode\hypertarget{ref-cheung1994learning}{}%
+Cheung, Y.-W., \& Friedman, D. (1994). \emph{Learning in evolutionary games: some laboratory results}. University of California, Santa Cruz.
+
+\leavevmode\hypertarget{ref-cooper2003lessons}{}%
+Cooper, D. J., \& Kagel, J. H. (2003). Lessons learned: generalizing learning across games. \emph{American Economic Review}, \emph{93}(2), 202--207.
+
+\leavevmode\hypertarget{ref-Cooper2008}{}%
+Cooper, D. J., \& Kagel, J. H. (2008). Learning and transfer in signaling games. \emph{Economic Theory}, \emph{34}(3), 415--439. \url{https://doi.org/10.1007/s00199-006-0192-5}
+
+\leavevmode\hypertarget{ref-goodie2012levels}{}%
+Goodie, A. S., Doshi, P., \& Young, D. L. (2012). Levels of theory-of-mind reasoning in competitive games. \emph{Journal of Behavioral Decision Making}, \emph{25}(1), 95--108.
+
+\leavevmode\hypertarget{ref-Haruvy2012}{}%
+Haruvy, E., \& Stahl, D.
+O.
+(2012).
+Between-game rule learning in dissimilar symmetric normal-form games.
+\emph{Games and Economic Behavior}, \emph{74}(1), 208--221.
+\url{https://doi.org/10.1016/j.geb.2011.06.001}
+
+\leavevmode\hypertarget{ref-ho2004economics}{}%
+Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
+
+\leavevmode\hypertarget{ref-ho1998iterated}{}%
+Ho, T.-H., Camerer, C., \& Weigelt, K. (1998). Iterated dominance and iterated best response in experimental" p-beauty contests". \emph{The American Economic Review}, \emph{88}(4), 947--969.
+
+\leavevmode\hypertarget{ref-Juvina2013}{}%
+Juvina, I., Saleem, M., Martin, J.
+M., Gonzalez, C., \& Lebiere, C.
+(2013).
+Reciprocal trust mediates deep transfer of learning between games of strategic interaction.
+\emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215.
+\url{https://doi.org/10.1016/j.obhdp.2012.09.004}
+
+\leavevmode\hypertarget{ref-knez2000increasing}{}%
+Knez, M., \& Camerer, C.
+(2000).
+Increasing cooperation in prisoner's dilemmas by establishing a precedent of efficiency in coordination games.
+\emph{Organizational Behavior and Human Decision Processes}, \emph{82}(2), 194--216.
+
+\leavevmode\hypertarget{ref-Lake2017}{}%
+Lake, B.
+M., Ullman, T.
+D., Tenenbaum, J.
+B., \& Gershman, S.
+J.
+(2017).
+Building machines that learn and think like people.
+\emph{Behavioral and Brain Sciences}, \emph{40}.
+\url{https://doi.org/10.1017/S0140525X16001837}
+
+\leavevmode\hypertarget{ref-mertens1990repeated}{}%
+Mertens, J.-F. (1990). Repeated games. In \emph{Game theory and applications} (pp. 77--130). Elsevier.
+
+\leavevmode\hypertarget{ref-shachat2004we}{}%
+Shachat, J., \& Swarthout, J. T. (2004). Do we detect and exploit mixed strategy play by opponents? \emph{Mathematical Methods of Operations Research}, \emph{59}(3), 359--373.
+
+\leavevmode\hypertarget{ref-simon1972theories}{}%
+Simon, H. A. (1972). Theories of bounded rationality. \emph{Decision and Organization}, \emph{1}(1), 161--176.
+
+\leavevmode\hypertarget{ref-spiliopoulos2013strategic}{}%
+Spiliopoulos, L. (2013). Strategic adaptation of humans playing computer algorithms in a repeated constant-sum game. \emph{Autonomous Agents and Multi-Agent Systems}, \emph{27}(1), 131--160.
+
+\leavevmode\hypertarget{ref-stahl1995players}{}%
+Stahl, D. O., \& Wilson, P. W. (1995). On players models of other players: Theory and experimental evidence. \emph{Games and Economic Behavior}, \emph{10}(1), 218--254.
+
+\leavevmode\hypertarget{ref-watkins1992q}{}%
+Watkins, C. J. C. H., \& Dayan, P. (1992). Q-learning. \emph{Machine Learning}, \emph{8}(3-4), 279--292.
+
+\leavevmode\hypertarget{ref-de2012higher}{}%
+Weerd, H.
+de, Verbrugge, R., \& Verheij, B.
+(2012).
+Higher-order social cognition in rock-paper-scissors: A simulation study.
+\emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3}, 1195--1196.
+
+\leavevmode\hypertarget{ref-Woodruff}{}%
+Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). \emph{Does the chimpanzee have a theory of mind}.
 

### 2020-01-28 Report/draft_report_v1.Rmd
updated report" git status "

@@
 bibliography      : ["Mendeley.bib"]
-csl               : "apa-6th-edition.csl"
+# csl               : "apa-6th-edition.csl"
 
@@
 
-# documentclass     : "apa6"
-# classoption       : "man"
+documentclass     : "apa6"
+classoption       : "man"
 output            : papaja::apa6_pdf
-header-includes   :
-  - \shorttitle{}
 ---
@@
 
-One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the opponent strategy that may inform what actions they are likely to take next.
-Once we learn about the opponent's strategy, we can use this knowledge to inform how to best act in novel situations involving a previously encountered opponent.
-This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about the opponent is an abstract representation that is not too dependent on the environment of the initial interaction.
-There is evidence that people learn models of the opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
+One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
+Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations.
+This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
+There is evidence that people learn models of their opponents when they play repeated economic games [@stahl1995players], engage in bilateral negotiations [@baarslag2016learning], or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors [@de2012higher].
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
 These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities [@Woodruff] play a role in determining human behaviour.
-
-In order to explore learning transfer in strategic settings, it is generally useful to study simple games as a model of more complex interactions.
+In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
 More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
@@
 
-```{r exp1-early-score, fig.cap = "Average scores for rounds 2-6 by game in first experiment", fig.align ='center'}
-
-knitr::include_graphics("../Report/images/exp1_early_scor_game.png", dpi = 108)
-
-```
-
-In Figure\ \@ref(fig:exp1-early-score), the average score across participants by game for rounds 2-6 are plotted.
-Scores are also averaged across levels of condition.
 We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
@@
 
-```{r exp2-score-by-opp, fig.cap="Avergae scores per game by opponcne type", fig.align="center"}
-p3 <- ggerrorplot(dat_int, x = "game.f", y = "int_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Scores per game", xlab = "Games")
+```{r exp2-score-by-opp, fig.cap="Average scores per game by opponent type", fig.align="center"}
+# p3 <- ggerrorplot(dat_int, x = "game.f", y = "int_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Scores per game", xlab = "Games")
+# 
+# p3 + facet_grid(. ~ opp_type)
 
-p3 + facet_grid(. ~ opp_type)
+p4 <- ggboxplot(dat_int, x = "game.f", y = "int_score", palette = c("#00AFBB", "#E7B800"),order = c("RPS", "FWG","SHOOT"), fill="interaction_lvl",ylab = "Percentage score", xlab = "Games")
+
+p4 + facet_grid(. ~ opp_type)
+
 ```
@@
 # plot scores per game 
-ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Score", xlab = "Games")
+p2 <- ggerrorplot(exp2_dat2_6, x = "game.f", y = "early_score", group = 1, color="game.f", desc_stat = "mean_ci",palette = c("#00AFBB", "#E7B800", "#FC4E07"), order = c("RPS", "FWG","SHOOT"), ylab = "Average Score rounds 2-6", xlab = "Games")
+
+p2 + facet_grid(. ~ opp_type)
 ```
@@
 Note that this corresponds to the Nash equilibrium strategy.
+In this sectionn, we will go through the various models we have used and explain how they update what they learn about the game or the opponent
 
-Next, we include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
+## Reinforcement Learning
+
+We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
 We will use a simple temporal difference learning update rule:
@@
 
-Where $V_{t}(a)$ is the vlue associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
+Where $V_{t}(a)$ is the value associated with action $a$ at time $t$, $\alpha$ is the learning rate and $R_{t}$ the reward at time t.
 Actions are chosen based on action values using a softmax choice rule.
@@
 
+In experiment 2, we allow this richer model to have a memory of the interaction.
+In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used.
+In another instance, we fit a model in which what was learned about an opponent in the first interaction is transfered to the first round of the second interaction, so there is a within-game trasnfer of Q-values allowed (QLS-within).
+We fit both models to all participant's data in the second experiment where both opponents are faced.
+
 ### EWA Models 
@@
 In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
-The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated gmes and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
+The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
 
-Let's define some notation in order to write the pdate rule of the self-tuning EWA model.
+Let's define some notation in order to write the update rule of the self-tuning EWA model.
 For player i, there are $m_{i}$ strategies, denoted $s_{i}^{j}$ (i.e player i's strategy number j).
@@
 
-Here, I(x,y) is the indicator function equla to 1 if $ x = y$ and 0 otherwise.
+Here, I(x,y) is the indicator function equal to 1 if $ x = y$ and 0 otherwise.
 A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince ($N(t-1)$) which is itself decaying by a wight $\phi$.
@@
 In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second intraction with the opponent, but are not able to transfer that learning to new games.
+In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between trasnfer)
 
 Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
-In the context of experiment 2, we still assume that within game transfer is still present (from first to second interaction).
+In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
 
+We fit the above two models to experiment 1 data.
 In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive).
-And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniforme probability of level-k opponent (NT), so no within or between opponent model learning transfer.
+And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
 
-In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
+In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).
+In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
 Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
@@
 All_comp_results <- read.csv(file="../All_results.csv")
-exp1_comp_table <- table(All_comp_results[, "condition"],c("random","Bayes Tr","Bayes No Tr","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(All_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC","MBM_BIC")],1,which.min)])
+exp1_comp_table <- table(All_comp_results[, "condition"],c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(All_comp_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])
 
@@
 exp1_dat = read.csv("../exp1_data.csv")
-exp1_model_comp = read.csv("../exp1_model_comp.csv")
+# exp1_model_comp = read.csv("../exp1_model_comp.csv")
+
+exp1_model_comp <- data.frame()
+for(id in unique(exp1_dat$human_id)) {
+  tdat <- subset(exp1_dat,human_id == id)
+  tot_score <- sum(tdat$score)
+  tot_time <- sum(tdat$human_rt)
+  early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg"))
+  #early_dat <- subset(tdat,between(tdat$round,2,6) & (game =="fwg" | game =="numbers") )
+  tr_score <- sum(early_dat$score)
+  id_results <- subset(All_comp_results, ID == id)
+  min_BIC <- apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,min)
+
+  best_model <- c("Random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
+  # 
+  exp1_model_comp <- rbind(exp1_model_comp,
+                       data.frame(
+                         "human_id" = id,
+                         "condition" = exp1_dat[exp1_dat$human_id==id,"condition"][1],
+                         "Early_game_score" = tr_score,
+                         "Total_score" = tot_score,
+                         "Best_model" = best_model,
+                         "Total_time" = sum(tdat$human_rt),
+                         "TR_minus_NT_BIC" = id_results[,"Bayes_Tr_BIC"] - id_results[,"Bayes_No_Tr_BIC"],
+                         "Rand_minus_best_BIC" =  id_results[,"Random_BIC"] - min_BIC
+
+                       ))
+}
 
@@
 ```{r exp1-cumScores, fig.cap = "Average cumulative scores of participants in experiment 1 by best fitting model", fig.align='center'}
-ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
+p5 <- ggplot(data = dat_by_model, aes(x = t, y=model_acc_sum, group = Best_model)) + 
    geom_line(aes(color= Best_model))
+
+p5+ labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
 ```
@@
 
-ggplot(data = dat_by_model_2, aes(x = t, y=avg_acc_sum, group = Best_model_2)) + 
+ p8 <- ggplot(data = dat_by_model_2, aes(x = t, y=avg_acc_sum, group = Best_model_2)) + 
    geom_line(aes(color= Best_model_2)) +
@@
 
+p8 + labs(color = "Best fitting model", x = "Round Number", y="Accumulated score")
+
 ```
 
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expected random play as well as EWA were at the bottom of cumulative performance.
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure\ \@ref(fig:exp2-cumScores), in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
+Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance, folowed by a model in which both within and between trasnfer of opponent models is allowed (BT).
+The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive).
+As expected, random play as well as self-tuning EWA were at the bottom of cumulative performance.
 

### 2020-01-28 Report/draft_report_v1.tex
updated report" git status "

@@
 
+In experiment 2, we allow this richer model to vary.
+In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used.
+In another instance, we fit a model in which what was learned about an opponent in the first interaction is transfered to the first round of the second interaction, so there is a within-game trasnfer of Q-values allowed (QLS-within).
+We fit both models to all participant's data in the second experiment where both opponents are faced.
+
 \hypertarget{ewa-models}{%
@@
 In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive).
-And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniforme probability of level-k opponent (NT), so no within or between opponent model learning transfer.
+And finally, we also fit a model in which all stages of the game and all new games start with a fresh uniform probability of level-k opponent (NT), so no within or between opponent model learning transfer.
 

### 2020-01-28 comp_model_1019.Rmd
updated report" git status "

@@
 ## Fitting Parametric EWA to data 
-```{r}
+```{r, cache =TRUE}
 
@@
 ```{r}
-# load("exp1_ToM_TR.RData")
-# load("exp1_ToM_NT.RData")
-# load("QL_modelling.RData")
-# load("QL_states_modelling.RData")
-# load("EWA_modelling.RData")
-# load("EWA_self_modelling.RData")
-# load("MBM_modelling.RData")
-# load("EWA_states_modelling.RData")
+load("exp1_ToM_TR.RData")
+load("exp1_ToM_NT.RData")
+load("QL_modelling.RData")
+load("QL_states_modelling.RData")
+load("EWA_modelling.RData")
+load("EWA_self_modelling.RData")
+load("MBM_modelling.RData")
+load("EWA_states_modelling.RData")
 
@@
                          "Bayes_Tr_BIC" = exp1_ToM_TR[[id]]$value + 2*log(150),
-                         "Bayes_No_Tr_BIC" = exp1_ToM_NT[[id]]$value+ 2*log(150),
+                         "Bayes_No_Tr_BIC" = exp1_ToM_NT[[id]]$value + 2*log(150),
                          # Theta is the parameter governing AI stochasticity. Truth is 0.9
@@
                          "EWA_states_BIC" = EWA_states_modelling[[id]]$optim$bestval + 1*log(150),
-                         "EWA_states_Lambda" = EWA_states_modelling[[id]]$optim$bestmem[1],
-
-                         # MBM 
-                          # MBM BIC
-                         "MBM_BIC" = MBM_modelling[[id]]$optim$bestval + 2*log(150),
-                          # BEta parameter inverse temp in softmax 
-                         "MBM_beta" = MBM_modelling[[id]]$optim$bestmem[1],
-                         "MBM_alpha" = MBM_modelling[[id]]$optim$bestmem[2]
+                         "EWA_states_Lambda" = EWA_states_modelling[[id]]$optim$bestmem[1]
+
+                         # 
+                         # # MBM 
+                         #  # MBM BIC
+                         # "MBM_BIC" = MBM_modelling[[id]]$optim$bestval + 2*log(150),
+                         #  # BEta parameter inverse temp in softmax 
+                         # "MBM_beta" = MBM_modelling[[id]]$optim$bestmem[1],
+                         # "MBM_alpha" = MBM_modelling[[id]]$optim$bestmem[2]
 
@@
 ```{r}
-Table_results <- table(All_results[, "condition"],c("random","Bayes Tr","Bayes No Tr","QL", "QL_states","EWA","S_EWA","EWA_states", "MBM")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC","MBM_BIC")],1,which.min)])
+Table_results <- table(All_results[, "condition"],c("random","ToM_BT","ToM_NBT","QL", "QL_states","EWA","S_EWA","EWA_states")[apply(All_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC","EWA_states_BIC")],1,which.min)])
 
@@
 
-  best_model <- c("random","Bayes Tr","Bayes NT","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
+  best_model <- c("random","ToM_BT","Bayes NT","QL", "QL_states","EWA","S_EWA")[apply(id_results[,c("Random_BIC","Bayes_Tr_BIC","Bayes_No_Tr_BIC","QL_BIC","QL_states_BIC","EWA_BIC","EWA_self_BIC")],1,which.min)]
   # 

### 2020-01-29 Report/draft_report_v1.Rmd
report bug fixes

@@
 
-keywords          : "keywords"
-wordcount         : "X"
+# keywords          : "keywords"
+# wordcount         : "X"
 
@@
 documentclass     : "apa6"
-classoption       : "man"
+# classoption       : a4paper
+classoption       : man
 output            : papaja::apa6_pdf
@@
 library(lsmeans)
+library(magick)
 ```
@@
 
-knitr::include_graphics("../Report/images/feedback_rps.png", dpi = 108)
+knitr::include_graphics("images/feedback_rps.png")
 

### 2020-01-29 Report/draft_report_v1.tex
report bug fixes

@@
             pdfauthor={Ismail Guennouni~\& Maarten Speekenbrink},
-            pdfkeywords={keywords},
             colorlinks=true,
@@
 
-One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the opponent strategy that may inform what actions they are likely to take next.
-Once we learn about the opponent's strategy, we can use this knowledge to inform how to best act in novel situations involving a previously encountered opponent.
-This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about the opponent is an abstract representation that is not too dependent on the environment of the initial interaction.
-There is evidence that people learn models of the opponents when they play repeated economic games (Stahl \& Wilson, 1995), engage in bilateral negotiations (Baarslag, Hendrikx, Hindriks, \& Jonker, 2016), or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors (Weerd, Verbrugge, \& Verheij, 2012).
+One way to build abstract representations of the environment when the task involves interactions with others is to build a model of the person we are interacting with that may inform what actions they are likely to take next.
+Once we learn something about them, we can use this knowledge to inform how to best behave in novel situations.
+This may lead to very efficient generalization of knowledge, even to situations that are dissimilar to the history of interaction, assuming what we have learned about others is an abstract representation that is not too dependent on the environment of the initial interaction.
+There is evidence that people learn models of their opponents when they play repeated economic games (Stahl \& Wilson, 1995), engage in bilateral negotiations (Baarslag, Hendrikx, Hindriks, \& Jonker, 2016), or simply try to exploit a non random player in chance games such as Rock-Paper-Scissors (Weerd, Verbrugge, \& Verheij, 2012).
 In this paper, we are specifically interested in the way in which people build and use models of their opponent to facilitate learning transfer, when engaged in situations involving an interaction with strategic considerations.
 These situations arise frequently such as in negotiations, auctions, strategic planning and all other domains in which theory of mind abilities (Woodruff, Sciences, Brain, \& 1978, n.d.) play a role in determining human behaviour.
-
-In order to explore learning transfer in strategic settings, it is generally useful to study simple games as a model of more complex interactions.
+In order to explore learning transfer in these strategic settings, it is generally useful to study simple games as a model of more complex interactions.
 More specifically, we need a framework that allows the study of whether and how a player takes into consideration, over time, the impact of its current and future actions on the future actions of the opponent and the future cumulative rewards.
@@
 
-{\centering \includegraphics{../Report/images/feedback_rps}
+{\centering \includegraphics{images/feedback_rps}
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics{../Report/images/exp1_early_scor_game}
-
-}
-
-\caption{Average scores for rounds 2-6 by game in first experiment}\label{fig:exp1-early-score}
-\end{figure}
-
-In Figure~\ref{fig:exp1-early-score}, the average score across participants by game for rounds 2-6 are plotted.
-Scores are also averaged across levels of condition.
 We test the average scores for each game against a hypothesised value of 0 for a non-experienced player using parametric one sample t-tests.
@@
 
-\caption{Avergae scores per game by opponcne type}\label{fig:exp2-score-by-opp}
+\caption{Average scores per game by opponent type}\label{fig:exp2-score-by-opp}
 \end{figure}
@@
 Note that this corresponds to the Nash equilibrium strategy.
+In this sectionn, we will go through the various models we have used and explain how they update what they learn about the game or the opponent
 
-Next, we include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
+\hypertarget{reinforcement-learning}{%
+\subsection{Reinforcement Learning}\label{reinforcement-learning}}
+
+We include for comparison purposes a simple model-free reinforcement learning algorithm, that reinforces actions that have led to positive rewards, and conversely lowers the likelihood of choosing actions that led to a negative reward, irrespective of any state.
 We will use a simple temporal difference learning update rule:
@@
 
-Where \(V_{t}(a)\) is the vlue associated with action \(a\) at time \(t\), \(\alpha\) is the learning rate and \(R_{t}\) the reward at time t.
+Where \(V_{t}(a)\) is the value associated with action \(a\) at time \(t\), \(\alpha\) is the learning rate and \(R_{t}\) the reward at time t.
 Actions are chosen based on action values using a softmax choice rule.
@@
 
-In experiment 2, we allow this richer model to vary.
+In experiment 2, we allow this richer model to have a memory of the interaction.
 In effect, we have a Q-learning model with a state space consisting of last round play, but in one instance, we fit a model (QLS) in which, when encountering an opponent, learning starts anew with no prior knowledge from previous encounters with the opponent used.
@@
 In contrast, reinforcement learning does not take into account beliefs about other players, but is such that an action followed by a positive reward is more likely to be repeated than an action followed by a negative reward.
-The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated gmes and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
+The self-tuning EWA model has been shown to perform better than both these nested models in multiple repeated games and has the advantage of having only one free parameter, the inverse temperature in the softmax choice function.
 
-Let's define some notation in order to write the pdate rule of the self-tuning EWA model.
+Let's define some notation in order to write the update rule of the self-tuning EWA model.
 For player i, there are \(m_{i}\) strategies, denoted \(s_{i}^{j}\) (i.e player i's strategy number j).
@@
 
-Here, I(x,y) is the indicator function equla to 1 if \$ x = y\$ and 0 otherwise.
+Here, I(x,y) is the indicator function equal to 1 if \$ x = y\$ and 0 otherwise.
 A simple way to think about this update rule is that attractions are multipled by a parameter that represents experince (\(N(t-1)\)) which is itself decaying by a wight \(\phi\).
@@
 In a No-Between-Transfer (NBT) model, players have no memory of what was learned about the opponent and start every new game assuming each level-k has equal probability.
-In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second intraction with the opponent, but are not able to transfer that learning to new games.
+In the context of Experiment 2 where players face both opponents, this model assumes that participants transfer learning within the same game, from the first to the second interaction with the opponent, but are not able to transfer that learning to new games (So within but no between trasnfer)
 
 Conversely, In a Between-Transfer model (BT), players are assumed to keep in memory what was learned about the type of opponent faced (vector of probabilities of level-k) and use that at the beginning of each new game.
-In the context of experiment 2, we still assume that within game transfer is still present (from first to second interaction).
+In the context of experiment 2, we still assume that if between transfer is present, then within game transfer is also present (from first to second interaction).
 
+We fit the above two models to experiment 1 data.
 In experiment two, on top of these two models, we fit two other models: One in which we assume that players don't distinguish between the two opponents faced, so the opponent model vector is never updated (Naive).
@@
 
-In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
+In summary, we fit two ToM models for experiment 1-play (NBT and BT), and 4 ToM models for experiment 2 ( NBT, BT, NT and Naive).
+In both experiments, all models were fit to each participant data, with optimal parameters being estimated using maximum likelihood.
 Using information criteria based Bayesian model comparison (BIC), the best fitting model for each participant was chosen and we compared the number of participants whose behavior was best explained by each model.
@@
 
-Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance, followed by theose relying on reinforcement learning with a state space of last round play, and as expected random play as well as EWA were at the bottom of cumulative performance.
+Plotting cumulative scores by best model for experiment 2, we see very similar results looking at Figure~\ref{fig:exp2-cumScores}, in that participants whose behavior was best fit by a ToM model of learning the oppponent strategy had the highest cumulative performance.
+Out of these ToM models, the one in which there is within-game but no between-game transfer (NBT) had the best cumulative performance, folowed by a model in which both within and between trasnfer of opponent models is allowed (BT).
+The next best model from a performance perspective was a Q-learning model with states and within game transfer, followed by ToM models where either players started learning from scratch at each stage of each game (NT) and the model in which they didn't distinguish between opponenets (Naive).
+As expected, random play as well as self-tuning EWA were at the bottom of cumulative performance.
 
@@
 \leavevmode\hypertarget{ref-Cooper2008}{}%
-Cooper, D. J., \& Kagel, J. H. (2008). Learning and transfer in signaling games. \emph{Economic Theory}, \emph{34}(3), 415--439. \url{https://doi.org/10.1007/s00199-006-0192-5}
+Cooper, D.
+J., \& Kagel, J.
+H.
+(2008).
+Learning and transfer in signaling games.
+\emph{Economic Theory}, \emph{34}(3), 415--439.
+doi:\href{https://doi.org/10.1007/s00199-006-0192-5}{10.1007/s00199-006-0192-5}
 
@@
 \emph{Games and Economic Behavior}, \emph{74}(1), 208--221.
-\url{https://doi.org/10.1016/j.geb.2011.06.001}
+doi:\href{https://doi.org/10.1016/j.geb.2011.06.001}{10.1016/j.geb.2011.06.001}
 
 \leavevmode\hypertarget{ref-ho2004economics}{}%
-Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). \emph{The economics of learning models: A self-tuning theory of learning in games}.
+Ho, T. H., Camerer, C. F., \& Chong, J.-K. (2004). The economics of learning models: A self-tuning theory of learning in games.
 
@@
 \emph{Organizational Behavior and Human Decision Processes}, \emph{120}(2), 206--215.
-\url{https://doi.org/10.1016/j.obhdp.2012.09.004}
+doi:\href{https://doi.org/10.1016/j.obhdp.2012.09.004}{10.1016/j.obhdp.2012.09.004}
 
@@
 \emph{Behavioral and Brain Sciences}, \emph{40}.
-\url{https://doi.org/10.1017/S0140525X16001837}
+doi:\href{https://doi.org/10.1017/S0140525X16001837}{10.1017/S0140525X16001837}
 
@@
 Higher-order social cognition in rock-paper-scissors: A simulation study.
-\emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3}, 1195--1196.
+In \emph{Proceedings of the 11th international conference on autonomous agents and multiagent systems-volume 3} (pp.
+1195--1196).
 
 \leavevmode\hypertarget{ref-Woodruff}{}%
-Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). \emph{Does the chimpanzee have a theory of mind}.
+Woodruff, G., Sciences, D. P. B., Brain, \& 1978. (n.d.). Does the chimpanzee have a theory of mind.
 
